### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/doc/IS_2014_package/IS2014_AuthorsKit/IS14full_paper.tex
Uploads INTERSPEECH 2018 paper

\documentclass[a4paper]{article}
\usepackage{INTERSPEECH2014,amssymb,amsmath,epsfig}
\setcounter{page}{1}
\sloppy     % better line breaks
\ninept
%SM below a registered trademark definition
\def\reg{{\rm\ooalign{\hfil
     \raise.07ex\hbox{\scriptsize R}\hfil\crcr\mathhexbox20D}}}

%% \newcommand{\reg}{\textsuperscript{\textcircled{\textsc r}}}
\title{Paper Template for INTERSPEECH 2014}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If multiple authors, uncomment and edit the lines shown below.       %%
%% Note that each line must be emphasized {\em } by itself.             %%
%% (by Stephen Martucci, author of spconf.sty).                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\makeatletter
%\def\name#1{\gdef\@name{#1\\}}
%\makeatother
%\name{{\em Firstname1 Lastname1, Firstname2 Lastname2, Firstname3 Lastname3,}\\
%      {\em Firstname4 Lastname4, Firstname5 Lastname5, Firstname6 Lastname6,
%      Firstname7 Lastname7}}
%%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother \name{{\em Author Name$^1$, Co-author Name$^2$}}

\address{$^1$Author Affiliation \\
  $^2$Co-author Affiliation \\
{\small \tt author@university.edu, coauthor@company.com}}

%\twoauthors{Karen Sp\"{a}rck Jones.}{Department of Speech and Hearing \\
%  Brittania University, Ambridge, Voiceland \\
%  {\small \tt Karen@sh.brittania.edu} }
%  {Rose Tyler}{Department of Linguistics \\
%  University of Speechcity, Speechland \\
%  {\small \tt RTyler@ling.speech.edu} }

%
\begin{document}
\maketitle
%
\begin{abstract}
This is the layout specification and template definition for the
INTERSPEECH 2014 Conference, which will be held in Singapore, 14-18
September 2014. This template has been generated from previous
INTERSPEECH templates. The format is essentially the one used for
IEEE ICASSP conferences. The maximum number of pages is 5. The
$5^{th}$ page may be used exclusively for references. Index terms
should be included as shown below.
\end{abstract}
\noindent{\bf Index Terms}: speech synthesis, unit selection, join costs

%
\section{Introduction}

This template can be found on the conference website. Please use
either a LibreOffice, MS-Word\reg\ or a \LaTeX\ format file when preparing your
submission. Information for full paper submission is available on the
conference web site.

\section{Page layout and style}

Authors should observe the following rules for page layout. A
highly recommended way to meet these requirements is to use a given
template (LibreOffice, Word\reg\ or \LaTeX) and check details against the
corresponding example file.

\subsection{Basic layout features}

\begin{itemize}
%\itemsep -1.3mm
\item Proceedings will be printed in A4 format. Authors must submit their papers
in A4 format.
\item Two columns are used except for the title part and possibly for large
figures that need a full page width.
\item Left margin is 20 mm.
\item Column width is 80 mm.
\item Spacing between columns is 10 mm.
\item Top margin 25 mm (except for the first page which is 30 mm to the title top).
\item Text height (without headers and footers) is maximum 235 mm.
\item Headers and footers must be left empty (they will be added for
printing and the INTERSPEECH 2014 media).
\item Check indentations and spacings by comparing to this
example file (in pdf).
\end{itemize}

\subsubsection{Headings}

Section headings are centered in boldface
with the first word capitalized and the rest of the heading in
lower case. Sub-headings appear like major headings, except they
start at the left margin in the column.
Sub-sub-headings appear like sub-headings, except they are in italics
and not boldface. See the examples given in this
file. No more than 3 levels of headings should be used.

\subsection{Text font}

Times or Times Roman font is used for the main text. Font size in the main text
must be 9 points, and in the References section 8 points. Other font
types may be used if needed for special purposes. It is VERY IMPORTANT
that while making the final PDF file, you embed all used fonts!

\LaTeX\ users: users should use Adobe Type 1 fonts such as Times or
Times Roman. These are used automatically by the INTERSPEECH2014.sty
style file. Authors must not use Type 3 (bitmap) fonts.

\subsection{Figures}

All figures must be centered on the column (or page, if the figure spans
both columns).
Figure captions should follow each figure and have the format given in
Figure~\ref{spprod}.

Figures should preferably be line drawings. If they contain gray
levels or colors, they should be checked to print well on a
high-quality non-color laser printer.

Graphics (i.e. illustrations, figures) must not use stipple fill
patterns because they will not reproduce properly in Acrobat PDF.
Please use only SOLID FILL COLORS.

Figures which span 2 columns (i.e. occupy full page width) should be
placed at the top or bottom of the page.

\subsection{Tables}

An example of a table is shown as Table \ref{table1}. The caption
text may be above or below the table.

\begin{table} [t,h]
\caption{\label{table1} {\it This is an example of a table.}}
\vspace{2mm}
\centerline{
\begin{tabular}{|c|c|}
\hline
ratio & decibels \\
\hline  \hline
1/1 & 0 \\
2/1 & $\approx 6$ \\
3.16 & 10 \\
10/1 & 20 \\
1/10 & -20 \\
100/1 & 40 \\
1000/1 & 60 \\
\hline
\end{tabular}}
\end{table}

\subsection{Equations}

Equations should be placed on separate lines and numbered. Examples
of equations are given below.
Particularly,
%
%\vspace{-3mm}
\begin{equation}
x(t) = s(f_\omega(t))
\label{eq1}
\end{equation}
where \(f_\omega(t)\) is a special warping function
\begin{equation}
f_\omega(t)=\frac{1}{2\pi j}\oint_C \frac{\nu^{-1k}d\nu}
{(1-\beta\nu^{-1})(\nu^{-1}-\beta)}
\label{eq2}
\end{equation}
A residue theorem states that
\begin{equation}
\oint_C F(z)dz=2 \pi j \sum_k Res[F(z),p_k]
\label{eq3}
\end{equation}
Applying (\ref{eq3}) to (\ref{eq1}),
it is straightforward to see that
\begin{equation}
1 + 1 = \pi
\label{eq4}
\end{equation}

Finally we have proven the secret theorem of all speech sciences.
No more math is needed to show how useful the result is!

\begin{figure}[t]
\centerline{\epsfig{figure=figure,width=80mm}}
\caption{{\it Schematic diagram of speech production.}}
\label{spprod}
\end{figure}

\subsection{Hyperlinks}

For technical reasons, the proceedings editor will strip all active
links from the papers during processing. Hyperlinks can be included in
your paper, if written in full, eg. ``http://www.foo.com/index.html''.
The link text must be all black. Please make sure that they present no
problems in printing to paper.

\subsection{Multimedia files}

The INTERSPEECH 2014 organizing committee offers the possibility to
submit multimedia files. These files are meant for audio-visual
illustrations that cannot be conveyed in text, tables and graphs.
Just like you would when including graphics, make sure that you have
sufficient author rights to the multimedia materials that you submit
for publication. The proceeding media will NOT contain readers or
players, so be sure to use widely accepted file formats, such as
MPEG, Windows WAVE PCM (.wav) or Windows Media Video (.wmv) using
standard codecs. The files you submit will be accessible from the
abstract cards on the media and via a bookmark in the manuscript.
From within the manuscript, refer to a multimedia illustration by
its filename. Use short file names without blanks.

\subsection{Page numbering}

Final page numbers will be added later to the document
electronically.
{\em Don't make any footers or headers!}

\subsection{References}

The reference format is the standard IEEE one.
References should be numbered in order of appearance,
for example \cite{ES1}, \cite{ES2}, and \cite{ES3}.

\subsection{Abstract}

The total length of the abstract is limited to 200 words. The
abstract included in your paper and the one you enter during web-based
submission must be identical. Avoid non-ASCII characters or symbols as they
may not display correctly in the abstract book.

\subsection{Author affiliation}
Please list country names as part of the affiliation for each country.

\subsection{Submitted files}
Authors are requested to submit PDF files of their manuscripts. You
can use commercially available tools or for instance
http://www.pdfforge.org/products/pdfcreator.  The PDF file should
comply with the following requirements: (a) there must be no PASSWORD
protection on the PDF file at all; (b) all fonts must be embedded; and
(c) the file must be text searchable (do CTRL-F and try to find a
common word such as 'the'). The proceedings editors (Causal
Productions) will contact authors of non-complying files to obtain a
replacement. In order not to endanger the preparation of the
proceedings, papers for which a replacement is not provided timely
will be withdrawn.

\section{Discussion}
This is the discussion. This is the discussion. This is the discussion.
Is there any discussion.

This is the next paragraph of the discussion. And the last sentence of it.

\section{Conclusions}

Authors must proof read their PDF file prior to submission to ensure it is
correct. Authors should not rely on proofreading the Word file. Please
proofread the PDF file before it is submitted.

\section{Acknowledgements}
The ISCA Board would like to thank the organizing committees of past
INTERSPEECH conferences for their help and for kindly providing the template
files.

\newpage
%
\eightpt
\bibliographystyle{IEEEtran}
\begin{thebibliography}{10}
\bibitem[1]{ES1} Smith, J. O. and Abel, J. S.,
``Bark and {ERB} Bilinear Transforms'',
IEEE Trans. Speech and Audio Proc., 7(6):697--708, 1999.
\bibitem[2]{ES2} Soquet, A., Saerens, M. and Jospa, P.,``Acoustic-articulatory
inversion'', in T. Kohonen [Ed], Artificial Neural Networks, 371-376,
Elsevier, 1991.
\bibitem[3]{ES3} Stone, H.S., ``On the uniqueness of the convolution theorem
for the Fourier transform'', NEC Labs. Amer. Princeton, NJ.
Online: http://citeseer.ist.psu.edu/176038.html, accessed on 19 Mar 2008.
\end{thebibliography}
\end{document}

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/doc/main.icassp.arun.tex
Uploads INTERSPEECH 2018 paper

% Template for ASRU-2017 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage{amssymb,amsmath,bm}
\usepackage{textcomp}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{multirow}
\usepackage[justification=centering]{caption}
\usepackage[caption = false]{subfig}

% Custom settings

\usepackage{tikz,placeins}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]
\usetikzlibrary{positioning, shapes}
%\usepackage{xcolor} %already loaded by tikz
%
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

\graphicspath{{../figures/}}

\newcommand{\specialcell}[2][c]{%
     \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcommand{\chanwcom}{{C. Kim}}
\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}
\renewcommand{\textfraction}{0.01}
\renewcommand{\floatpagefraction}{1.0}
\renewcommand{\dbltopfraction}{1.0}
\renewcommand{\floatpagefraction}{1.0}  % require fuller float pages
\renewcommand{\dblfloatpagefraction}{1.0} % require fuller float pages
\newcommand{\AR}[1]{{\color{red} arunnt@ COMMENT: #1}}

\ninept

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{Efficient Implementation of the Room Simulator \\ for Training Deep Neural Network Acoustic Models}
%
% Single address.
% ---------------
\name{{Chanwoo Kim, Ehsan Variani, Arun Narayanan, and Michiel Bacchiani}}

\address{Google Speech \\
%  {\small \tt \{chanwcom, tsainath, arunnt, misra, rnongpiur, michiel\}@google.com }}
  {\small \tt \{chanwcom, variani, arunnt, michiel\}@google.com }}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%
\maketitle
%
\begin{abstract}
In this paper, we describe how to efficiently implement
an acoustic room simulator to generate large-scale
simulated data for training deep neural networks.
Even though the \textit{Room Simulator} in \cite{C_Kim_INTERSPEECH_2017_1} was shown
 to be quite effective in reducing the Word
Error Rates (WERs) for far-field applications by generating
simulated far-field training sets, it requires
high dimensional Fast Fourier Transforms (FFTs).
\textit{Room Simulator} in \cite{C_Kim_INTERSPEECH_2017_1} used 
  approximately 80 percent of CPU usage in our CPU/GPU
training architecture. In this work, we implement an efficient OverLap
  Addition (OLA) based filtering using the open-source \texttt{FFTW3}
library. Further, we investigate the effects of the Room
Impulse Response (RIR) lengths. Experimentally, we conclude that we can cut
the tail portions of RIRs whose power is less than 20 \textit{dB}
below the maximum power without sacrificing the speech recognition accuracy.
Using these approaches, we were able to reduce CPU usage for the
room simulator portion down to 9.69 \%
in CPU/GPU training architecture. Profiling result shows that
we obtain 22.4 times speed-up on a single machine and 37.3 times
  speed up on Google's distributed training infrastructure.
\AR{I don't think we should use borg to describe clusters since it's not something known externally.}
 \end{abstract}
%
\begin{keywords}
Simulated data, room acoustics, robust speech recognition, deep learning
\end{keywords}
%
%
\section{Introduction}
With advancements in deep learning,
\cite{Seltzer2013DNNAurora4, Yu2013FeatureLearningDNN, V_Vanhoucke_Deep_Learning_NIPS_Workshop_2011,
G_Hinton_IEEE_Signal_Process_Mag_2012,
T_Sainath_IEEETran_2017_1, T_Sainath_Book_Chapter_2017_1},
speech recognition accuracy has improved dramatically.
Now, speech recognition systems
are used not only on portable devices
but also on standalone devices for far-field speech recognition.
Examples include voice assistant systems such as Amazon Alexa
and Google Home \cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}.
In far-field speech recognition, the impact of noise and reverberation
is much larger than near-field cases. Traditional approaches to far-field
speech recognition include noise robust feature extraction algorithms
\cite{C_Kim_IEEETran_2016_1, U_H_Yapanel_SpeechComm_2008},
on-set enhancement algorithms
\cite{C_Kim_INTERSPEECH_2010_2, C_Kim_INTERSPEECH_2014_2} \AR{Classification seems too narrow!}.
\AR{Maybe change: Recently, we observed that -> Several studies have now shown that} Recently, we observed that training with noisy data generated
by a \textit{Room Simulator} \cite{C_Kim_INTERSPEECH_2017_1}
improves speech recognition accuracy dramatically.
This system has been successfully employed
for training acoustic models for Google Home or Google voice
search \cite{C_Kim_INTERSPEECH_2017_1}.

\textit{Room Simulator} creates millions of virtual rooms
with different dimensions and different number of sound sources
at different locations and Signal-to-Noise Ratios (SNRs).
For every new utterance in the training set, we use a randomly
sampled room configuration, so that the same utterance
is simulated under different acoustic environments in every epoch during training.
As will be seen in Sec. \ref{sec:experimental_results}, if
we generate the simulated utterance only once for each
input example, the performance is worse.
Since different RIRs are applied for the same
utterance at every epoch, the intermediate results cannot be cached.
Therefore, the noisification process requires several large convolution operations. As will be seen
in Sec. \ref{sec:experimental_results}, during training, it uses up to 80 \%
of the whole CPU usage if we use the CPU/GPU architecture
shown in Fig. \ref{fig:gpu_cpu_structure}.

In this paper, we describe our approach to reduce the
computational cost of the \textit{Room Simulator}. We
first switch from \texttt{Kiss FFT} in
\texttt{Eigen3} to Real FFT in \texttt{FFTW3}. Then we
investigate the required length of RIRs for robust
speech recognition.
%As will be seen in Sec.
%\ref{sec:experimental_results}, we observe that we can remove
%the tail portion or an RIR whose power is 20-dB below
%the maximum power of the original RIR.
%This approach reduced the RIR length to 47 \% compared to the
%original RIR length.
%Combined with OLA filtering, on a local machine, the speed-up
%was 25.2 times. On Google Borg, the speed up was 37.3 times.
%
%
%
%
%
\begin{figure}%[!tbp]
  \begin{center}
    \resizebox{85mm}{!}{\input{../figures/gpu_cpu_structure.tex}}
      \caption {
        \label{fig:gpu_cpu_structure}
        Training architecture using cluster of CPUs and GPUs.
        \cite{E_Variani_INTERSPEECH_2017_01}.
        The ``Room Simulator" is on the CPU side to generate
        simulated utterances using room configurations.
        \cite{C_Kim_INTERSPEECH_2017_1}.}
  \end{center}
\vspace{-10mm}
\end{figure}
%
%
%
%
\section{Efficient Implementation of the Room Simulation System}
  \label{sec:implementation}
%
Fig. \ref{fig:gpu_cpu_structure} shows a high level block diagram of
the acoustic model training infrastructure
\cite{E_Variani_INTERSPEECH_2017_01}. Since it is not easy to
run all the front-end processing blocks, such as feature
extraction and Voice Activity Detection (VAD) on Graphics
Processing Units (GPUs), during training, they run on Central Processing
Units (CPUs). Even though Fast Fourier Transform (FFT) of the
\textit{Room Simulator} may be efficiently implemented on GPUs,
since
\textit{Room Simulator} must feed the simulated utterances
to the rest of CPU optimized front-end components, the Room Simulator
is also running on CPUs.
%
%As will be seen in Table \ref{tbl:cpu_percentage}, the ``\texttt{Room Simulator}"
%system described in \cite{C_Kim_INTERSPEECH_2017_1} consumes 80 percent of the
%CPU cycles in the architecture shown in Fig. \ref{fig:gpu_cpu_structure}.
%
%
%
\subsection{Review of the Room Simulator for Data Augmentation}
%
%
\begin{figure}
  \begin{center}
  \subfloat[\label{fig:room_diagram}] {
    \includegraphics[width=70mm]{room_diagram.eps}} \\
  \subfloat[\label{fig:image_method}] {
    \includegraphics[width=70mm]{image_method.eps}}
   \caption{
    (a) A simulated room: There may be multiple microphones, a single target
    sound source, multiple noise sources in a cuboid-shape room with
    acoustically reflective walls. (b) A diagram showing the location
    of the real and the virtual sound sources assuming that the walls
    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
  \end{center}
  \vspace{-10mm}
\end{figure}
%
%
In this section, we briefly review the structure of the Google
Room Simulator for generating simulated utterances
to train acoustic models for speech recognition systems
\cite{C_Kim_INTERSPEECH_2017_1}. We assume a room of a
rectangular cuboid-shape as shown in Fig. \ref{fig:room_diagram}.
Assuming that all the walls of a room reflect acoustically uniformly,
we use the image method to model the Room Impulse Responses (RIRs)
\cite{J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007, S_G_McGovern_RIR}.

Fig. \ref{fig:image_method} shows how virtual sources
appearing as empty circles are constructed in the image method.
Even though the virtual rooms appear to be created in two-dimensions
in Fig. \ref{fig:image_method}, in the ``\emph{Room Simulator}",
they are constructed in three-dimensions. For example, in our
work for training the acoustic model for Google Home, we consider
$17 \times 17 \times 17 = 4913$ virtual rooms for RIR calculation
\cite{C_Kim_INTERSPEECH_2017_1}.
Following the image method, the impulse response is calculated
using the following equation
\cite{ J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007}:
\begin{align}
    h[n] = \sum_{i = 0}^{I-1} \frac{r^{g_i}}{d_i}
    \delta \left[n -\left \lceil{\frac{d_i f_s}{c_0}}\right \rceil \right],
      \label{eq:h_n_calculation}
\end{align}
where $i$ is the index of each virtual sound source, and $d_i$ is the distance
from that sound source to the microphone, $r$ is
the reflection coefficient of the wall, $g_i$ is
the number of the reflections
to that sound source, $f_s$ is the sampling rate of the RIR, and $c_0$ is the
speed of sound in the air. We use the value of $f_s = 16,000$ \textit{Hz} and
$c_0 = 343$ \textit{m/s} for the room simulator \cite{B_Li_INTERSPEECH_2017_1}.
For $d_i$, $r$, we use numbers created by a random number generator
following specified distributions for each impulse response \cite{C_Kim_INTERSPEECH_2017_1}.

Assuming that there are $I$ sound sources including one target
source and $J$ microphones, the received signal at microphone
$j$ is given by:
\begin{align}
  y_j[n] =  \sum_{i=0}^{I-1} \alpha_{ij} \left(h_{ij}[n] * x_i[n]\right).
  \label{eq:y_j_def}
\end{align}
Since we used a two-microphones system in
\cite{B_Li_INTERSPEECH_2017_1, C_Kim_INTERSPEECH_2017_1},
$J$ is two, and for the number noise sources, we used a value from zero
up to three \cite{C_Kim_INTERSPEECH_2017_1}.
%
%
%
%
%
%
%\begin{figure}[!tbp]
%  \begin{center}
%    \resizebox{75mm}{!}{\input{../figures/entire_diagram.tex}}
%      \caption {
%        The architecture for acoustic model training using
%        the room simulator and LSTMs and a DNN (LDNN)
%     \cite{T_Sainath_ICASSP_2016_1, C_Kim_INTERSPEECH_2017_1}. }
%          \label{fig:entire_diagram}
%  \end{center}
%\vspace{-7mm}
%\end{figure}
%
%
%
%%
%\begin{figure}%[tbp]
%  \begin{center}
%    \includegraphics[width=70mm]{reverb_time_distribution}
%    \label{fig:target_length}
%    \caption {
%      Reverberation time ($T_{60}$) distribution in our
%      configuration for training the acoustic model for Google Home
%      and the real Google Home user usage.
%    }
%   \vspace{-7mm}
%  \end{center}
%\end{figure}
%

%
%
%
\subsection{Efficient Room Impulse Response filtering}
%
%
%
When the signal and the room impulse response length are $N_x$ and
$M$, respectively, to calculate \eqref{eq:y_j_def} using the time-domain
convolution, the number of multiplications $C_{td}$ is given by:
\begin{align}
  C_{td} = I \times J \times  M  \times N_x.
  \label{eq:num_mults_linear_convolution}
\end{align}
In our training set used in Sec. \ref{sec:experimental_results},
the average utterance length including \emph{non-speech} portions
marked by the Voice Activity Detector (VAD) is 6.35 \textit{s}.
This corresponds to $N_x$ of 101,523 at 16 \textit{kHz}. The average
length of the RIR in the room simulator used in
\cite{C_Kim_INTERSPEECH_2017_1} is 0.243 \textit{s} \AR{Sounds a bit too smalle?}, corresponding
to the $M$ value of 3893.
For Google Home the number of noise sources in our training
set is 1.55 on average.
Thus $I$ is 1.55 including one target source, and $J$ is two, since
we use a two-microphones system in
\cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}.
Thus, if we directly use the linear convolution, it requires
two billion multiplications per utterance from
\eqref{eq:num_mults_linear_convolution}, which is prohibitively large.
Thus, in the ``\textit{Room Simulator}" in
\cite{C_Kim_INTERSPEECH_2017_1},
we used the frequency domain multiplication using \texttt{Kiss FFT}
\cite{M_Borgerding_kiss_fft_2010}. To avoid time aliasing,
the FFT size $N$ must satisfy $N \ge N_x + M - 1$.
The $j$-th microphone channel
of the simulated signal $y_j[n]$ in \eqref{eq:y_j_def}
\begin{align}
  y_{j} [n] = \sum_{i=0}^{I-1}FFT^{-1} \left \{
      FFT \left \{ h_{ij}[n] \right \} \times
      FFT \left \{ x_i[n] \right \}
      \right \}  %* FFT\{X_i[omega_k}\}\}
\end{align}
Considering we perform two FFTs \AR{Why 2? You should consider speech and 1.55 noises right?}, one IFFT, and one complex spectrum
element-wise multiplications, the number of real multiplications
$C_{\textit{FFT}}$ is given by:
\begin{align}
  C_{\textit{FFT}} = 6 N \log_2(N) + 4 N.
  \label{eq:c_fft}
\end{align}
where $N$ is the FFT size. \AR{Shouldn't all this be in big-O notation? So not exactly NlogN but O(NlogN)?} The number of real multiplications
in \eqref{eq:c_fft} is based on the assumption that a single FFT 
requires $\frac{N}{2} \log_2(N)$ multiplications \AR{This is confusing, I think it makes sense to just use NlogN given you are already ignoring other constants that are not O(NlogN).}, and a single
complex multiplication requires four real multiplications. The $4N$
term in \eqref{eq:c_fft} appears since there is one frequency domain
element-wise multiplications.
If we use $N = 2 ^ {17}$, it requires 70.9 million multiplications
per utterance. The room simulator was implemented in C++ using
the \texttt{Eigen3} linear algebra library \cite{eigenweb}.
In \texttt{Eigen3}, \texttt{Kiss FFT} \cite{M_Borgerding_kiss_fft_2010} and \texttt{FFTW3}
\cite{M_Frigo_proceedings_of_the_ieee_20015} are unofficially supported.
We used the \texttt{Kiss FFT} version of FFT in \texttt{Eigen3} since
there were some technical issues in using \texttt{FFTW3} in \texttt{Eigen3}
to run on \texttt{Google Borg} cluster \cite{A_Verma_eurosys_2015_1}.
But, to fruther speed up frontend computation, we switched from
\texttt{Kiss FFT} in \texttt{Eigen3} to a custom  C++ class
implementation which internally using real FFT in \texttt{FFTW3}.
\AR{The argument seems weak. Consider rephrasing? Maybe say, our initial implementation was based on KissFFT. But, to further speed up computation, we switched ... i.e., don't mention about technical issues on borg cluster -- that seems something very specific and scientifically uninteresting.}

A more efficient approach is using the OverLap Add (OLA)
FFT filtering \AR{cite?}. With the OLA FFT filtering,
the approximate number of real multiplications is given by:
\begin{align}
  C_{\textit{OLA}} =  \left \lfloor{\frac{N_x}{N - M + 1}}\right \rfloor
  \left[4 N \log_2(N) + 4 N  \right] + 2 N \log_2(N)
  \label{eq:c_ola}
\end{align}
where $N$ is the FFT size, $N_x$ is the length of the entire
signal, and $M$ is the length of the impulse response. The term
$4 N \log_2(N) + 4 N $ appears in \eqref{eq:c_ola}, since there is
one FFT and one IFFT for each block. 
$\left \lfloor{\frac{N_x}{N - M + 1}}\right \rfloor$
is the number of blocks to process an utterance of length $N_x$.
The $2 N \log_2(N)$ term in \eqref{eq:c_ola} is the required multiplications
for the impulse response. For the impulse response $h_{ij}[n]$, we do not
need to repeat it for every block.
In our training set consisting of 22 million utterances, the
average utterance length is 7.31 \textit{s} \AR{Earlier you said it is 6.55s, Fix?}.
Then we can find we find the optimal value of $M = 11300$, and the
number of approximate number of real multiplication is 39.2 millions.
%
%
%
%
\subsection{Room Impulse Response Length Selection}
%
%In our original implementation of the room simulator, we covered up to
%17 reflections. The RIR length depends on the room size we used in the
%simulator. Since we used a distribution of room size, the RIR length is
%not fixed.
%Even though the reverberation time is usually given in terms of
%$T_{60}$, which is defined to be the time for XXX.
%
The average length of the Room Impulse Response in the original room
simulator is estimated to be 3893 samples, which corresponds to 0.243
\textit{s}.
%
We perform a simple RIR tail-cutoff by finding the RIR power threshold
which is $\eta$ \textit{dB} below the maximum power of the RIR
$h_{ij}[n]$:
\begin{align}
  p_{th} = \max \left \{h_{ij}^2[n] \right \} \times 10^{-\frac{\eta}{10}}.
\end{align}
Using $p_{th}$, we find the cut-off index $n_c$ which is the smallest
sample index beyond which all the trailing $h_{ij}[n]$ has power
below the threshold $p_{th}$:
\begin{align}
  n_c = \min_{m} \left\{
  m \middle| \max_{n > m} \left\{  h^2[n] \right \} <  p_{th}  \right \}.
\end{align}
Then the final RIR cut-off $\widehat{h}_{ij}[n]$ is given
by the following equation:
\begin{align}
  \widehat{h}_{ij}[n] = h_{ij}[n], \qquad 0 \le n \le n_c + 1.
\end{align}
Fig. \ref{fig:rir_cutoff} shows impulse responses when different RIR
cutoff threshold $\eta$ is used. To reflect the typical case in
our training set, we used the average room dimension, average
microphone-to-target distance, and average $T_{60}$ value among
3 million room configurations described in \cite{C_Kim_INTERSPEECH_2017_1}.

As shown in Table \ref{tbl:local_machine_prof} and \ref{tbl:cpu_percentage},
the RIR tail cut-off at 20 \textit{dB} shows relatively 35.6 \% to 69.4 \%
speed improvement on a local desktop machine and on \texttt{Google Borg}
cluster \cite{A_Verma_eurosys_2015_1}.
Fig. \ref{fig:rir_cutoff_local_profiling} shows the profiling results
on a local machine with different RIR cutoff thresholds $\eta$.
The local machine we used has a single \texttt{Intel(R) Xeon(R) CPU E5-1650 @ 3.20GHz}
CPU with 6 cores and 32 GB of memory. In Fig. \ref{fig:rir_cutoff_local_profiling},
we observe that the computational cost becomes less for the OLA filtering
case as we cut the tail portion of the RIR more. For the full FFT case,
theoretically, it should remain almost constant regardless of the
impulse response length, but due to variation
in profiling measurement, there is some small variation.
%
%\begin{figure}%[tbp]
%  \begin{center}
%    \includegraphics[width=70mm]{plot_mic_source_target_2d_asymmetric}
%      \caption { Room configuration used for generating Room Impulse Responses (RIRs)
%         in Fig. \ref{fig:rir_cutoff}
%      \ref{sec:experimental_results}}
%          \label{fig:room_configuration}
%    \includegraphics[width=50mm]{plot_mic_source_target_2d_symmetric}
%      \caption { A microphone array with two microphones in an anechoic chamber.
%      The azimuth angle with respect to the $x$-axis is $\theta$. }
%          \label{fig:recording_room_final}
%  \vspace{-7mm}
%  \end{center}
%\end{figure}
%
%\begin{figure}[tbp]
%  \begin{center}
%    \includegraphics[width=70mm]{target_length}
%    \label{fig:target_length}
%    \caption {
%      Word Error Rates (WERs) for the voice search test set 
%      at different reverberation time corrupted by (a) an
%      interfering speaker and (b) various noise in the 
%      DEMAND noise database.
%    }   
%   \vspace{-7mm}
%  \end{center}
%\end{figure}
%
\begin{figure}%[tbp]
  \begin{center}
    \subfloat[] {
      \includegraphics[width=70mm]{rir_no_cutoff}
      \label{fig:rir_cutoff_simulated_sets}
    }
    \vspace{-5mm}
    \\
    \subfloat[] {
      \includegraphics[width=70mm]{rir_20db_cutoff}
      \label{fig:rir_cutoff_rerecorded_sets}
    }
    \vspace{-5mm}
    \\
%    \subfloat[] {
%      \includegraphics[width=70mm]{rir_10db_cutoff}
%      \label{fig:rir_cutoff_rerecorded_sets}
%    }
%    \\
    \subfloat[] {
      \includegraphics[width=70mm]{rir_5db_cutoff}
      \label{fig:rir_cutoff_rerecorded_sets}
    }
    \caption {
      The simulated room impulse responses generated in the
      ``Room Simulator" described in Sec. \ref{sec:implementation}:
      (a) The impulse response without the RIR tail cut-off,
      (b) with the RIR tail cut-off at 20 \textit{dB},
      and (c) with the RIR tail cut-off at 5 \textit{dB}.
    }
   \vspace{-7mm}
  \label{fig:rir_cutoff}
  \end{center}
\end{figure}
%
%
%\begin{figure}%[tbp]
%  \begin{center}
%    \subfloat[] {
%      \includegraphics[width=70mm]{rir_cutoff_simulated_sets}
%      \label{fig:rir_cutoff_simulated_sets}
%    }
%    \vspace{-4mm}
%    \\
%    \subfloat[] {
%      \includegraphics[width=70mm]{rir_cutoff_rerecorded_sets}
%      \label{fig:rir_cutoff_rerecorded_sets}
%    }
%    \vspace{-4mm}
%    \caption {
%      Word Error Rates (WERs) for the voice search test set 
%      at different reverberation time corrupted by (a) an
%      interfering speaker and (b) various noise in the 
%      DEMAND noise database.
%    }   
%   \vspace{-7mm}
%  \end{center}
%\end{figure}
%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=70mm]{rir_cutoff_time}
    \caption {
      \label{fig:rir_cutoff_local_profiling}
      Profiling result on local desktop machine with
      different RIR cut-off threshold with and without
      OverLap Addition FIR filtering.
    }
  \end{center}
  \vspace{-7mm}
\end{figure}
%%   \vspace{-7mm}
%  \end{center}
%\end{figure}
\begin{table}%[!htbp]
  \renewcommand{\arraystretch}{1.3}
  \centering
  \caption{\label{tbl:local_machine_prof}The profiling result for processing a single utterance using
           the ``Room Simulator" on a local desktop machine}
\begin{tabular}{| c | c |}
  \hline
                         & \specialcell{Avg. Time per \\ Utterance (\textit{ms})} \\
   \hline
   \hline
  \specialcell{Original System \\
               \textit{Room Simulator} in \cite{C_Kim_INTERSPEECH_2017_1}}                            &  320.8 \textit{ms} \\
   \hline
  \specialcell{\texttt{FFTW3} Real FFT Filtering }                  &  44.2  \textit{ms} \\
   \hline
  \specialcell{OLA filtering }                             &  19.4  \textit{ms} \\
   \hline
  \specialcell{OLA filtering and 20 dB RIR cut-off}        &  14.3  \textit{ms} \\
  \hline  
\end{tabular}
\end{table}
%
%
%%
%
%
%
\begin{table*}%[th]
  \caption{\label{tbl:cpu_percentage} {The CPU usage portion of the FFT
          and \textit{Room Simulator} with the respect to the entire
          CPU pipeline in Fig. \ref{fig:gpu_cpu_structure}  and \\ relative
          speed up on \texttt{Google Borg} cluster \cite{A_Verma_eurosys_2015_1}.}}
  \vspace{2mm}
  \centerline{
    \begin{tabular}{| c | c | c | c | c | c | c |}
      \hline
            &  \specialcell{Original system}
            &  \specialcell{\texttt{FFTW3} OLA Filter   }
            &  \specialcell{\texttt{FFTW3} OLA Filter \\ with 20 dB RIR  Cut-off}
            &  \specialcell{\texttt{FFTW3} OLA Filter \\ with 10 dB RIR  Cut-off}  \\
      \hline \hline
      FFT portion (\%)       & 79.27 \%  &  10.11 \% &  \textbf{6.23} \% & 5.08 \% \\
      \hline
      \specialcell{Relative Speed Up \\ in FFT Portion (\%) }
                             &  -    & 34.0 times    &  \textbf{57.6 times} & 59.6 times       \\
      \hline \hline
      \specialcell{Entire Acoustic \\ Simulation (\%) }
                             & 80.01 \%  &  13.30 \% &  \textbf{9.69} \% & 8.05 \%  \\
      \hline
      \specialcell{Relative Speed Up \\ in Acoustic Simulation Portion (\%) }
                             &  -    &  26.1 times    &  \textbf{37.3 times}  & 45.7 times       \\
      \hline
    \end{tabular}
  }
\end{table*}
%
%
\begin{table*}%[th]
  \caption{\label{tbl:results} {Speech recognition experimental result in terms of Word Error Rates (WERs) \\
          with and without MTR using the room simulation system in \cite{C_Kim_INTERSPEECH_2017_1}  \\
          and different RIR cutoff thresholds.}}
  \vspace{2mm}
  \centerline{
    \begin{tabular}{| c | c | c | c | c | c | c |}
      \hline
            &  \specialcell{Baseline \\ without  MTR}
            &  \specialcell{MTR using  \\ One-time Batch \\ Room Simulation}
            &  \specialcell{Baseline   \\ (On-the-fly    \\ Room Simulation)}
            &  \specialcell{20 dB RIR  \\ Cut-off}
            &  \specialcell{10 dB RIR  \\ Cut-off}
            &  \specialcell{5 dB RIR   \\ Cut-off}  \\
      \hline \hline
      Original Test Set        & 11.70 \%   &  12.07 \% & 11.95 \%  & \textbf{11.43} \%  & 10.75 \% &  11.20  \%  \\
      \hline
      Simulated Noisy Set A    & 20.75 \%  &  15.58 \% & 14.88 \%  & \textbf{13.96} \% & 13.59 \%  &  14.99 \%  \\
      \hline
      Simulated Noisy Set B    & 50.78 \%  &  22.47 \% & 20.64 \%  & \textbf{19.58} \% & 21.37 \%  &   28.27 \%  \\
      \hline
      \specialcell{Device 1  } & 52.56 \%  &  22.39 \% & 21.69 \%  & \textbf{21.35} \% & 23.20 \%   &  29.53 \%  \\
      \hline
      \specialcell{Device 2  } & 51.59 \%  &  22.12 \% & 21.62 \%  &  \textbf{21.26} \% & 22.90 \%   & 29.39 \%  \\
      \hline
      \specialcell{Device 3  } & 54.89 \%  &  23.42 \% & 22.29 \%  &  \textbf{22.86} \%  & 26.47 \%  &  36.71 \%  \\
      \hline
      \specialcell{Device 3 \\ (Noisy Condition)  }
                              &  72.09 \%  &  36.21 \% & 35.88 \%  &  \textbf{35.83} \%  & 39.99 \%  &  51.11 \%  \\
      \hline
      \specialcell{Device 3 \\ (Multi-Talker Condition)  }
                             &  74.60 \%   &  47.63 \% & 46.03 \%  &  \textbf{46.21} \%  & 48.36 \%  & 58.31 \%   \\
      \hline
    \end{tabular}
  }
\end{table*}
%
%
%
%
%  fig.set_size_inches(10.0, 3.0)
%   bbox_inches='tight'

%
%
%\begin{subequations}
%  \begin{align}
%    \begin{split}
%      \mu_{\theta}^{o}[m] = \frac{\sum_{k \in \mathcal{K}^{o}}{p[m, k]\theta[m, \omega_k]}}
%          {\sum_{k \in \mathcal{K}^{+}}{p[m, k]}},
%    \end{split}
%    \\
%    \begin{split}
%      \sigma_{\theta}^{o}[m] = \frac{\sum_{k \in \mathcal{K}^{o}}{\theta[m, \omega_k]^2 p[m, k]}}
%          {\sum_{k \in \mathcal{K}^{o}}{p[m, k]}}
%          - \left( \mu_{\theta}^{o}[m] \right)^2,
%    \end{split}
%  \end{align}
%\end{subequations}
%$\mu_{\theta}^{-}[m]$ and $\sigma_{\theta}^{-}[m]$ are obtained in the same way:
%\begin{subequations}
%  \begin{align}
%    \begin{split}
%      \mu_{\theta}^{-}[m] = \frac{\sum_{k \in \mathcal{K}^{+}}{p[m, k]\theta[m, \omega_k]}}
%          {\sum_{k \in \mathcal{K}^{-}}{p[m, k]}},
%    \end{split}
%    \\
%    \begin{split}
%      \sigma_{\theta}^{-}[m] = \frac{\sum_{k \in \mathcal{K}^{-}}{\theta[m, \omega_k]^2 p[m, k]}}
%          {\sum_{k \in \mathcal{K}^{-}}{p[m, k]}}
%          - \left( \mu_{\theta}^{-}[m] \right)^2.
%    \end{split}
%  \end{align}
%\end{subequations}
%\subsection{Reliable Channel Mask Selection (RCMS)}
%\label{sec:RCMS}
%
%
\section{Experimental results}
\label{sec:experimental_results}
%
%
%
\begin{table}%[!htbp]
  \renewcommand{\arraystretch}{1.3}
  \centering
  \caption{Average $T_{60}$ Time of the Simulated Traing Set and
           Simulated Test Sets A and B.}
\begin{tabular}{| c | c | c | c |}
  \hline
                         & \specialcell{Simulated \\ Training Set}
                         & \specialcell{Simulated \\ Noisy Set A}
                         & \specialcell{Simulated \\ Noisy Set B}  \\
   \hline
  \specialcell{Average $T_{60}$ Time}
      & 0.482 \textit{s}
      & 0.167 \textit{s}
      & 0.479 \textit{s}\\
  \hline
\end{tabular}
\vspace{-7mm}
\end{table}
%
%
%\begin{figure}[tbp]
%  \begin{center}
%    \subfloat[] {
%      \includegraphics[width=70mm]{interfering_speaker_0db}
%      \label{fig:interfering_speaker_0db}
%    }
%    \\
%    \subfloat[] {
%      \label{fig:demand_noise_0db}
%      \includegraphics[width=70mm]{demand_0db}
%    }
%    \caption {
%      Word Error Rates (WERs) for the voice search test set
%      at different reverberation time corrupted by (a) an
%      interfering speaker and (b) various noise in the
%      DEMAND noise database.
%    }

%%
In this section, we present speech recognition results and CPU profiling
results obtained using \textit{Room Simulator} with different RIR cut-off
thresholds. For acoustic modeling, we use the structure shown in
% Is this the structure you used? I thought the model is plain lstm?
\AR{+1. I think these numbers are using logmel LSTMs? Clarify.}
\cite{B_Li_INTERSPEECH_2017_1}
%
with some modification.
One major difference is instead of generating two-channel simulated
waveform, we generate one-channel waveform \AR{Why? Maybe say for quicker turn around time?}.
We use the 128 dimension log-Mel feature whose window
size is 32 \textit{ms}. The interval between successive frame is 10
\textit{ms}. The low and upper cutoff frequencies of the Mel filterbank
are 125 \textit{Hz} and 7500 \textit{Hz} respectively.
Since it has been shown that long-duration features represented by overlapping
features are helpful \cite{H_Sak_INTERSPEECH_2015_1}, four frames
are stacked together and the input is downsampled by a factor of 3.
Thus we use a context dependent feature consisting of 512 elements
given by 128 (the size of the log-mel feature) x 4 (number of stacked frames).
The feature is processed by a typical multi-layer LSTM acoustic model.
We use 5-layer LSTMs with 768 units in each layer.
The output of the final LSTM layer is passed to a 768
unit DNN \AR{I don't think the model has DNNs. It's just a 5layer LSTM.}, followed by a softmax layer.
The softmax layer has 8192 nodes corresponding to the number of tied
context-dependent phones in our ASR system. The output state label is delayed
by five frames, since it was observed that
the information about future frames improves the prediction of the current frame
% This is not right reference for output delay, this is the one we used in speech team:
%\bibitem{sak2014long}
%H.~Sak, A.~W. Senior, and F.~Beaufays, ``Long short-term memory recurrent
%  neural network architectures for large scale acoustic modeling.'' in
%  \emph{Interspeech}, 2014, pp. 338--342.
%And if you want the main reference for delay in RNNs is Mike Schuster's paper:
%@article{schuster1997bidirectional,
%  title={Bidirectional recurrent neural networks},
%  author={Schuster, Mike and Paliwal, Kuldip K},
%  journal={IEEE Transactions on Signal Processing},
%  volume={45},
%  number={11},
%  pages={2673--2681},
%  year={1997},
%  publisher={IEEE}
%}
  \cite{H_Sak_INTERSPEECH_2014_1, M_Schuster_ieee_trans_signal_processing_1997}.
%
The acoustic model was trained using the Cross-Entropy (CE) loss
as the objective function, using precomputed alignments for utterance as targets.
To obtain results in Table \ref{tbl:results}, we trained for about 45 epochs.

For training, we used an anonymized and hand-transcribed
22-million English utterances (18,000-hr) set. The training set is the same as what we
used in \cite{B_Li_INTERSPEECH_2017_1, C_Kim_INTERSPEECH_2017_1}.
For evaluation, we used around 15-hour of utterances (13,795 utterances)
obtained from anonymized mobile voice search data. 
  We also generate noisy evaluation
sets from this relatively clean voice search data.
We use both simulated and rerecorded noisy sets.
Since our objective is deploying our speech recognition
systems on far-field standalone devices such as Google Home,
we rerecorded these evaluation sets using the actual hardware
in far-field environment.
Note that the actual Google Home hardware has two microphones
with microphone spacing of 7.1 cm. In our experiments in this section,
we selected the first channel out of two channel data.
 Three different devices
were used in rerecording, and each device was placed in five
different locations in an actual room resembling a real living
room. These devices are listed in Table 1 as ``Device 1'', ``Device 2'',
and ``Device 3''. As shown in Table \ref{tbl:results},
we observe that the RIR cut-off up to 20 \textit{dB} threshold does not
adversely affect the performance. However, if we cut the
RIR to 5 \textit{dB} threshold, then the performance under far-field
environment becomes significantly worse. This observation also confirms
that far-field speech recognition benefits from
RIRs with sufficiently long tails in the training set.
%
%
Table \ref{tbl:cpu_percentage} shows how much CPU resource was used
when training is done on \texttt{Google Borg} cluster
\cite{A_Verma_eurosys_2015_1} using the CPU/GPU
training architecture in Fig. \ref{fig:gpu_cpu_structure}. We observe that
if we use the \texttt{FFTW3}-based OLA filter using 20 \textit{dB} rir cutoff, we
may obtain 57.6 times speed-up in the FFT portion. The entire speed-up
of \textit{Room Simulator} portion is 37.3 times.
% 
\section{Conclusions}
In this paper, we describe how to efficiently implement
an acoustic room simulator to generate large-scale
simulated data for training deep neural networks.
We implement an efficient OverLap
Addition (OLA) based filtering using the open-source \texttt{FFTW3}
library. We investigate into the effects of the Room
Impulse Response (RIR) lengths. We conclude that we can cut
the tail portions of RIRs whose power is less than 20 \textit{dB}
below the maximum power without sacrificing speech recognition accuracy.
However, if we cut off RIR more than that, we observe it adversely
affects the performance for reverberant cases.
Using the approaches mentioned here, we could reduce the
room simulator portion in the CPU usage down to 9.69 \%
in CPU/GPU training architecture. Profiling result shows that
we obtain 22.4 times speed-up on a local desktop machine and 37.3 times
speed up on \texttt{Google Borg} cluster.
%
%\clearpage
%\newpage
%
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}
%
%
\end{document}

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/doc/main.tex
Uploads INTERSPEECH 2018 paper

--- 2018-06-17 room_simulator_comp_reduction_interspeech_2018/doc/main.icassp.arun.tex
@@
 % --------------------------------------------------------------------------
-\documentclass{article}
-\usepackage{spconf,amsmath,graphicx}
+\documentclass[a4paper]{article}
+
+\usepackage{INTERSPEECH2016}
+
+\usepackage{amsmath,graphicx}
 \usepackage{amssymb,amsmath,bm}
@@
 
-\graphicspath{{../figures/}}
+\graphicspath{{.}{../figures/}}
+\makeatletter
+  \def\input@path{{.}{../figures/}}
+\makeatother
 
@@
 % ---------------
-\name{{Chanwoo Kim, Ehsan Variani, Arun Narayanan, and Michiel Bacchiani}}
+\name{{Chanwoo Kim$^{1\dagger}$\thanks{$^\dagger$Work performed while at Google.}, Ehsan Variani$^2$, Arun Narayanan$^2$, and Michiel Bacchiani$^2$}}
 
-\address{Google Speech \\
+\address{$^1$Samsung Research, $^2$Google Speech \\
 %  {\small \tt \{chanwcom, tsainath, arunnt, misra, rnongpiur, michiel\}@google.com }}
-  {\small \tt \{chanwcom, variani, arunnt, michiel\}@google.com }}
+  {\small \tt $^1$chanw.com@samsung.com $^2$\{variani, arunnt, michiel\}@google.com }}
 %
@@
 \begin{abstract}
+
 In this paper, we describe how to efficiently implement
@@
 simulated data for training deep neural networks.
-Even though the \textit{Room Simulator} in \cite{C_Kim_INTERSPEECH_2017_1} was shown
+Even though \textit{Google Room Simulator} in \cite{C_Kim_INTERSPEECH_2017_1} was shown
  to be quite effective in reducing the Word
 Error Rates (WERs) for far-field applications by generating
-simulated far-field training sets, it requires
-high dimensional Fast Fourier Transforms (FFTs).
-\textit{Room Simulator} in \cite{C_Kim_INTERSPEECH_2017_1} used 
-  approximately 80 percent of CPU usage in our CPU/GPU
-training architecture. In this work, we implement an efficient OverLap
+simulated far-field training sets, it requires a very large 
+number of FFTs.
+\textit{Room Simulator} used approximately 80 \% of CPU usage
+  in our \textit{CPU/GPU} training architecture
+  \cite{E_Variani_INTERSPEECH_2017_01}.
+  In this work, we implement an efficient OverLap
   Addition (OLA) based filtering using the open-source \texttt{FFTW3}
@@
 below the maximum power without sacrificing the speech recognition accuracy.
+However, we observe that cutting  RIR tail more than this threshold
+harms the speech recognition accuracy for rerecorded test sets.
 Using these approaches, we were able to reduce CPU usage for the
@@
   speed up on Google's distributed training infrastructure.
-\AR{I don't think we should use borg to describe clusters since it's not something known externally.}
  \end{abstract}
 %
-\begin{keywords}
-Simulated data, room acoustics, robust speech recognition, deep learning
-\end{keywords}
+%\begin{keywords}
+  \noindent{\bf Index Terms}: Simulated data, room acoustics, robust speech recognition, deep learning
+%\end{keywords}
 %
@@
 \section{Introduction}
-With advancements in deep learning,
+With advancements in deep learning
 \cite{Seltzer2013DNNAurora4, Yu2013FeatureLearningDNN, V_Vanhoucke_Deep_Learning_NIPS_Workshop_2011,
@@
 speech recognition include noise robust feature extraction algorithms
-\cite{C_Kim_IEEETran_2016_1, U_H_Yapanel_SpeechComm_2008},
+\cite{C_Kim_IEEETran_2016_1, U_H_Yapanel_SpeechComm_2008, C_Kim_ICASSP_2010_1},
 on-set enhancement algorithms
-\cite{C_Kim_INTERSPEECH_2010_2, C_Kim_INTERSPEECH_2014_2} \AR{Classification seems too narrow!}.
-\AR{Maybe change: Recently, we observed that -> Several studies have now shown that} Recently, we observed that training with noisy data generated
+\cite{C_Kim_INTERSPEECH_2010_2, C_Kim_INTERSPEECH_2014_2}, and multi-microphone
+approaches \cite{T_Nekatani_ICASSP_2017_1, T_Higuchi_ICASSP_2016_1,
+H_Erdogan_INTERSPEECH_2016_1, C_Kim_INTERSPEECH_2015_1, C_Kim_INTERSPEECH_2009_1, C_Kim_ICASSP_2012_2, C_Kim_ICASSP_2011_2}.
+Recently, we observed that training with large-scale noisy data generated
 by a \textit{Room Simulator} \cite{C_Kim_INTERSPEECH_2017_1}
@@
 utterance at every epoch, the intermediate results cannot be cached.
-Therefore, the noisification process requires several large convolution operations. As will be seen
-in Sec. \ref{sec:experimental_results}, during training, it uses up to 80 \%
+Therefore, the noisification process requires very large number of convolution operations. As will be seen
+in Sec. \ref{sec:experimental_results}, during training, \textit{Room Simulator} used up to 80 \%
 of the whole CPU usage if we use the CPU/GPU architecture
 shown in Fig. \ref{fig:gpu_cpu_structure}.
-
 In this paper, we describe our approach to reduce the
-computational cost of the \textit{Room Simulator}. We
-first switch from \texttt{Kiss FFT} in
-\texttt{Eigen3} to Real FFT in \texttt{FFTW3}. Then we
-investigate the required length of RIRs for robust
-speech recognition.
+computational portion of the \textit{Room Simulator} below 10 \% of the CPU usage
+in our CPU/GPU training scheme.
+%We
+%first switch from \texttt{Kiss FFT} in
+%\texttt{Eigen3} to Real FFT in \texttt{FFTW3}. Then we
+%investigate the required length of RIRs for robust
+%speech recognition.
 %As will be seen in Sec.
@@
   \begin{center}
-    \resizebox{85mm}{!}{\input{../figures/gpu_cpu_structure.tex}}
+    \resizebox{75mm}{!}{\input{gpu_cpu_structure.tex}}
       \caption {
@@
         \cite{E_Variani_INTERSPEECH_2017_01}.
-        The ``Room Simulator" is on the CPU side to generate
+        \textit{Room Simulator} is on the CPU side to generate
         simulated utterances using room configurations.
@@
 \cite{E_Variani_INTERSPEECH_2017_01}. Since it is not easy to
-run all the front-end processing blocks, such as feature
-extraction and Voice Activity Detection (VAD) on Graphics
-Processing Units (GPUs), during training, they run on Central Processing
-Units (CPUs). Even though Fast Fourier Transform (FFT) of the
+run all the front-end processing blocks such as feature
+extraction and Voice Activity Detection (VAD) on GPUs,
+ they run on CPUs during training.
+Even though Fast Fourier Transform (FFT) of the
 \textit{Room Simulator} may be efficiently implemented on GPUs,
@@
   \begin{center}
-  \subfloat[\label{fig:room_diagram}] {
-    \includegraphics[width=70mm]{room_diagram.eps}} \\
-  \subfloat[\label{fig:image_method}] {
-    \includegraphics[width=70mm]{image_method.eps}}
+%  \subfloat[\label{fig:room_diagram}] {
+    \includegraphics[width=70mm]{room_diagram.pdf}
+%  } 
+%  \\
+% \subfloat[\label{fig:image_method}] {
+%   \includegraphics[width=70mm]{image_method.eps}}
    \caption{
-    (a) A simulated room: There may be multiple microphones, a single target
+    A simulated room: There may be multiple microphones, a single target
     sound source, multiple noise sources in a cuboid-shape room with
-    acoustically reflective walls. (b) A diagram showing the location
-    of the real and the virtual sound sources assuming that the walls
-    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
+    acoustically reflective walls \cite{C_Kim_INTERSPEECH_2017_1}. 
+    \label{fig:room_diagram}
+    %(b) A diagram showing the location
+  }
+%    of the real and the virtual sound sources assuming that the walls
+%    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
   \end{center}
@@
 we use the image method to model the Room Impulse Responses (RIRs)
-\cite{J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007, S_G_McGovern_RIR}.
-
-Fig. \ref{fig:image_method} shows how virtual sources
-appearing as empty circles are constructed in the image method.
-Even though the virtual rooms appear to be created in two-dimensions
-in Fig. \ref{fig:image_method}, in the ``\emph{Room Simulator}",
-they are constructed in three-dimensions. For example, in our
-work for training the acoustic model for Google Home, we consider
-$17 \times 17 \times 17 = 4913$ virtual rooms for RIR calculation
-\cite{C_Kim_INTERSPEECH_2017_1}.
-Following the image method, the impulse response is calculated
-using the following equation
+\cite{J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007,
+s_g_mcgovern_mathworks_file_exchange_2013_00,
+s_g_mcgovern_applied_acoustics_2009_00}.
+In the image method, a real room is acoustically mirrored
+with respect to each wall, which results in grids of virtual rooms.
+%
+%Fig. \ref{fig:image_method} shows how virtual sources
+%appearing as empty circles are constructed in the image method.
+%Even though the virtual rooms appear to be created in two-dimensions
+%in Fig. \ref{fig:image_method}, in the ``\emph{Room Simulator}",
+%they are constructed in three-dimensions. 
+In our work for training the acoustic model for Google Home
+\cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}, we consider
+$17 \times 17 \times 17 = 4913$ virtual rooms for RIR calculation.
+Following the image method and assuming that there are $V$ 
+virtual sound sources including one real source, 
+the impulse response is calculated using the following equation
 \cite{ J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007}:
 \begin{align}
-    h[n] = \sum_{i = 0}^{I-1} \frac{r^{g_i}}{d_i}
-    \delta \left[n -\left \lceil{\frac{d_i f_s}{c_0}}\right \rceil \right],
+    h[n] = \sum_{v = 0}^{V-1} \frac{r^{g_v}}{d_v}
+    \delta \left[n -\left \lceil{\frac{d_v f_s}{c_0}}\right \rceil \right],
       \label{eq:h_n_calculation}
 \end{align}
-where $i$ is the index of each virtual sound source, and $d_i$ is the distance
-from that sound source to the microphone, $r$ is
-the reflection coefficient of the wall, $g_i$ is
+where $v$ is the index of each virtual sound source, and $d_v > 0$ is the distance
+from that sound source to the microphone, $0 < r < 1$ is
+the reflection coefficient of the wall, $g_v$ is
 the number of the reflections
@@
 speed of sound in the air. We use the value of $f_s = 16,000$ \textit{Hz} and
-$c_0 = 343$ \textit{m/s} for the room simulator \cite{B_Li_INTERSPEECH_2017_1}.
-For $d_i$, $r$, we use numbers created by a random number generator
+$c_0 = 343$ \textit{m/s} for \textit{Room Simulator} \cite{B_Li_INTERSPEECH_2017_1}.
+For $d_v$, $r$, we use numbers created by a random number generator
 following specified distributions for each impulse response \cite{C_Kim_INTERSPEECH_2017_1}.
@@
 Since we used a two-microphones system in
-\cite{B_Li_INTERSPEECH_2017_1, C_Kim_INTERSPEECH_2017_1},
-$J$ is two, and for the number noise sources, we used a value from zero
-up to three \cite{C_Kim_INTERSPEECH_2017_1}.
+\cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}
+$J$ is two, and for the number of noise sources, we used a value from zero
+up to three with an average of 1.55. Including the target source, the average
+number of $I$ is 2.55 \cite{C_Kim_INTERSPEECH_2017_1}.
 %
@@
 %
-When the signal and the room impulse response length are $N_x$ and
-$M$, respectively, to calculate \eqref{eq:y_j_def} using the time-domain
-convolution, the number of multiplications $C_{td}$ is given by:
+When the signal and the room impulse response lengths are $N_x$ and
+$N_h$ respectively, the number of multiplications $C_{td}$ required for
+calculating \eqref{eq:y_j_def} using the time-domain convolution is given by:
 \begin{align}
-  C_{td} = I \times J \times  M  \times N_x.
+  C_{td} = I \times J \times N_x \times N_h.
   \label{eq:num_mults_linear_convolution}
 \end{align}
-In our training set used in Sec. \ref{sec:experimental_results},
+In our training set used in \cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1},
 the average utterance length including \emph{non-speech} portions
-marked by the Voice Activity Detector (VAD) is 6.35 \textit{s}.
-This corresponds to $N_x$ of 101,523 at 16 \textit{kHz}. The average
+marked by the Voice Activity Detector (VAD) is 7.31 \textit{s}.
+This corresponds to $N_x$ of 116,991 at 16 \textit{kHz}. The average
 length of the RIR in the room simulator used in
-\cite{C_Kim_INTERSPEECH_2017_1} is 0.243 \textit{s} \AR{Sounds a bit too smalle?}, corresponding
-to the $M$ value of 3893.
+\cite{C_Kim_INTERSPEECH_2017_1} is 0.243 \textit{s}, corresponding
+to the $N_h$ value of 3893.
 For Google Home the number of noise sources in our training
 set is 1.55 on average.
-Thus $I$ is 1.55 including one target source, and $J$ is two, since
+Thus $I$ is 2.55 including one target source, and $J$ is two, since
 we use a two-microphones system in
@@
 Thus, if we directly use the linear convolution, it requires
-two billion multiplications per utterance from
+2.32 billion multiplications per utterance from
 \eqref{eq:num_mults_linear_convolution}, which is prohibitively large.
@@
 \cite{M_Borgerding_kiss_fft_2010}. To avoid time aliasing,
-the FFT size $N$ must satisfy $N \ge N_x + M - 1$.
+the FFT size $N$ must satisfy $N \ge N_x + M - 1$, where
+$M$ is the length of the impulse response.
 The $j$-th microphone channel
 of the simulated signal $y_j[n]$ in \eqref{eq:y_j_def}
+is given by:
 \begin{align}
@@
       FFT \left \{ x_i[n] \right \}
-      \right \}  %* FFT\{X_i[omega_k}\}\}
+      \right \}.  %* FFT\{X_i[omega_k}\}\}
+  \label{eq:fir_fft_convolution}
 \end{align}
-Considering we perform two FFTs \AR{Why 2? You should consider speech and 1.55 noises right?}, one IFFT, and one complex spectrum
-element-wise multiplications, the number of real multiplications
-$C_{\textit{FFT}}$ is given by:
+As shown in \eqref{eq:fir_fft_convolution}, we perform
+two FFTs, one IFFT, and one complex element-wise multiplications
+between two complex spectra for each convolution term in \eqref{eq:y_j_def}.
+Assuming that radix-2 FFTs are employed, each FFT or IFFT requires
+$\frac{N}{2} \log_2(N)$ multiplications
+\cite{A_V_Oppenheim_PrenticeHall_1999}.
+In addition, a single element-wise complex multiplication
+between two complex spectra is required for each convolution
+term in \eqref{eq:y_j_def}.
+For real time-domain signals, we need to perform element-wise
+multiplications for the lower half-spectrum for
+Discrete Fourier Transform (DFT) indices
+$0 \le k \le N / 2$ since the spectrum has the Hermitian symmetry
+property \cite{A_V_Oppenheim_PrenticeHall_1999}.
+From this discussion, we conclude that the number of real multiplications
+$C_{\textit{FFT}}$ for calculating \eqref{eq:fir_fft_convolution} is given by:
 \begin{align}
-  C_{\textit{FFT}} = 6 N \log_2(N) + 4 N.
+  C_{\textit{FFT}} = I J \left(6 N \log_2(N) + 2 N\right).
   \label{eq:c_fft}
 \end{align}
-where $N$ is the FFT size. \AR{Shouldn't all this be in big-O notation? So not exactly NlogN but O(NlogN)?} The number of real multiplications
-in \eqref{eq:c_fft} is based on the assumption that a single FFT 
-requires $\frac{N}{2} \log_2(N)$ multiplications \AR{This is confusing, I think it makes sense to just use NlogN given you are already ignoring other constants that are not O(NlogN).}, and a single
-complex multiplication requires four real multiplications. The $4N$
-term in \eqref{eq:c_fft} appears since there is one frequency domain
-element-wise multiplications.
-If we use $N = 2 ^ {17}$, it requires 70.9 million multiplications
-per utterance. The room simulator was implemented in C++ using
-the \texttt{Eigen3} linear algebra library \cite{eigenweb}.
-In \texttt{Eigen3}, \texttt{Kiss FFT} \cite{M_Borgerding_kiss_fft_2010} and \texttt{FFTW3}
-\cite{M_Frigo_proceedings_of_the_ieee_20015} are unofficially supported.
-We used the \texttt{Kiss FFT} version of FFT in \texttt{Eigen3} since
-there were some technical issues in using \texttt{FFTW3} in \texttt{Eigen3}
-to run on \texttt{Google Borg} cluster \cite{A_Verma_eurosys_2015_1}.
-But, to fruther speed up frontend computation, we switched from
+For the average $N_x$ of 116,991 mentioned above,
+if we assume that the average $N$ is $2 ^ {17}$,  \eqref{eq:c_fft} 
+requires 69.5 million multiplications per utterance on average. 
+\textit{Room Simulator} for \cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}
+was implemented in C++ using the \texttt{Eigen3} linear algebra library \cite{eigenweb}.
+%In \texttt{Eigen3}, \texttt{Kiss FFT} \cite{M_Borgerding_kiss_fft_2010} and \texttt{FFTW3}
+%\cite{M_Frigo_proceedings_of_the_ieee_20015} are unofficially supported.
+So far we have used the \texttt{Kiss FFT} version of FFT in \texttt{Eigen3}
+including acoustic model training for Google Home described in
+\cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}.
+But, to further speed up frontend computation, we switched from
 \texttt{Kiss FFT} in \texttt{Eigen3} to a custom  C++ class
-implementation which internally using real FFT in \texttt{FFTW3}.
-\AR{The argument seems weak.
-Consider rephrasing?
-Maybe say, our initial implementation was based on KissFFT.
-But, to further speed up computation, we switched ...
-i.e., don't mention about technical issues on borg cluster -- that seems something very specific and scientifically uninteresting.}
+implementation which internally uses real FFT in \texttt{FFTW3}.
 
 A more efficient approach is using the OverLap Add (OLA)
-FFT filtering \AR{cite?}. With the OLA FFT filtering,
+FFT filtering \cite{A_V_Oppenheim_PrenticeHall_1999, 
+r_crochiere_ieee_tassp_1980_00}.
+With the OLA FFT filtering,
 the approximate number of real multiplications is given by:
 \begin{align}
-  C_{\textit{OLA}} =  \left \lfloor{\frac{N_x}{N - M + 1}}\right \rfloor
-  \left[4 N \log_2(N) + 4 N  \right] + 2 N \log_2(N)
+  C_{\textit{OLA}} = I J \left( 
+          \left \lfloor{\frac{N_x}{N - N_h + 1}}\right \rfloor
+          \left(4 N \log_2(N) + 2 N  \right)   \right.  \nonumber \\
+           \left.
+                   \vphantom{\left \lfloor{\frac{N_x}{N - M + 1}}\right \rfloor}
+            + 2 N \log_2(N) \right),
   \label{eq:c_ola}
@@
 where $N$ is the FFT size, $N_x$ is the length of the entire
-signal, and $M$ is the length of the impulse response. The term
-$4 N \log_2(N) + 4 N $ appears in \eqref{eq:c_ola}, since there is
-one FFT and one IFFT for each block. 
+signal, and $N_h$ is the length of the impulse response. The term
+$4 N \log_2(N) + 2 N $ appears in \eqref{eq:c_ola}, since there is
+one FFT, one IFFT, and one element-wise complex multiplication
+for $0 \le k \le N / 2$ for each block.
+As before, we assumed that each FFT or IFFT requires
+$\frac{N}{2} \log_2(N)$ multiplications and one complex multiplication
+requires four real multiplications in \eqref{eq:c_ola}.
 $\left \lfloor{\frac{N_x}{N - M + 1}}\right \rfloor$
 is the number of blocks to process an utterance of length $N_x$.
-The $2 N \log_2(N)$ term in \eqref{eq:c_ola} is the required multiplications
-for the impulse response. For the impulse response $h_{ij}[n]$, we do not
+The $2 N \log_2(N)$ term in \eqref{eq:c_ola} is required for
+FFT of the impulse response $h_{ij}[n]$.
+For the impulse response $h_{ij}[n]$, we do not
 need to repeat it for every block.
-In our training set consisting of 22 million utterances, the
-average utterance length is 7.31 \textit{s} \AR{Earlier you said it is 6.55s, Fix?}.
-Then we can find we find the optimal value of $M = 11300$, and the
-number of approximate number of real multiplication is 39.2 millions.
+In our training set consisting of 22 million utterances mentioned above,
+the average $N$ is 116,991 and the average $N_h$ is 3,893.
+For this average $N$ and $N_h$, the minimum value of $C_{\textit{OLA}}$
+in \eqref{eq:c_ola} is 50.8 millions of real multiplications when $N = 2^{14}$.
+The optimal value of $N$ minimizing $C_{\textit{OLA}}$ is different for
+different $N_h$ and $N_x$ values. For each filtering, we minimize
+$C_{\textit{OLA}}$ by evaluating this equation with different values of
+$N = 2^{m}$ where $m$ is an integer.
 %
@@
   p_{th} = \max \left \{h_{ij}^2[n] \right \} \times 10^{-\frac{\eta}{10}}.
+  \label{eq:p_th_def}
 \end{align}
@@
 \end{align}
-Fig. \ref{fig:rir_cutoff} shows impulse responses when different RIR
-cutoff threshold $\eta$ is used. To reflect the typical case in
+Fig. \ref{fig:rir_cutoff} shows the original impulse responses and
+the corresponding RIR when the cutoff threshold of $\eta$ is used.
+To reflect the typical case in
 our training set, we used the average room dimension, average
@@
 on a local machine with different RIR cutoff thresholds $\eta$.
-The local machine we used has a single \texttt{Intel(R) Xeon(R) CPU E5-1650 @ 3.20GHz}
+The local machine we used has a single \texttt{Intel(R) Xeon(R) E5-1650 @ 3.20GHz}
 CPU with 6 cores and 32 GB of memory. In Fig. \ref{fig:rir_cutoff_local_profiling},
@@
     }
-    \vspace{-5mm}
+    \vspace{-2mm}
     \\
@@
 %    \\
-    \subfloat[] {
-      \includegraphics[width=70mm]{rir_5db_cutoff}
-      \label{fig:rir_cutoff_rerecorded_sets}
-    }
+%    \subfloat[] {
+%      \includegraphics[width=70mm]{rir_5db_cutoff}
+%      \label{fig:rir_cutoff_rerecorded_sets}
+%    }
     \caption {
@@
       (a) The impulse response without the RIR tail cut-off,
-      (b) with the RIR tail cut-off at 20 \textit{dB},
-      and (c) with the RIR tail cut-off at 5 \textit{dB}.
+      (b) with the RIR tail cut-off at 20 \textit{dB}.
+%      and (c) with the RIR tail cut-off at 5 \textit{dB}.
     }
-   \vspace{-7mm}
+   \vspace{-8mm}
   \label{fig:rir_cutoff}
@@
   \end{center}
-  \vspace{-7mm}
+  \vspace{-9mm}
 \end{figure}
@@
    \hline
-  \specialcell{Original System \\
-               \textit{Room Simulator} in \cite{C_Kim_INTERSPEECH_2017_1}}                            &  320.8 \textit{ms} \\
+  \specialcell{Original \textit{Room Simulator} in \cite{C_Kim_INTERSPEECH_2017_1}}                            &  320.8 \textit{ms} \\
    \hline
@@
    \hline
-  \specialcell{OLA filtering }                             &  19.4  \textit{ms} \\
+  \specialcell{+OLA filtering }                             &  19.4  \textit{ms} \\
    \hline
-  \specialcell{OLA filtering and 20 dB RIR cut-off}        &  14.3  \textit{ms} \\
+  \specialcell{+20 dB RIR cut-off}        &  14.3  \textit{ms} \\
   \hline  
@@
           CPU pipeline in Fig. \ref{fig:gpu_cpu_structure}  and \\ relative
-          speed up on \texttt{Google Borg} cluster \cite{A_Verma_eurosys_2015_1}.}}
+          speed up measured in terms of execution time with respect to our baseline 
+          in \cite{C_Kim_INTERSPEECH_2017_1} on \texttt{Google Borg} 
+          cluster \cite{A_Verma_eurosys_2015_1}.}}
   \vspace{2mm}
@@
       \hline
-            &  \specialcell{Original system}
+            &  \specialcell{Original system in \cite{C_Kim_INTERSPEECH_2017_1}}
             &  \specialcell{\texttt{FFTW3} OLA Filter   }
@@
   \caption{\label{tbl:results} {Speech recognition experimental result in terms of Word Error Rates (WERs) \\
-          with and without MTR using the room simulation system in \cite{C_Kim_INTERSPEECH_2017_1}  \\
-          and different RIR cutoff thresholds.}}
+          with and without MTR using the room simulation system in \cite{C_Kim_INTERSPEECH_2017_1} and different RIR cutoff thresholds.}}
   \vspace{2mm}
@@
       \hline
-      Simulated Noisy Set A    & 20.75 \%  &  15.58 \% & 14.88 \%  & \textbf{13.96} \% & 13.59 \%  &  14.99 \%  \\
+      \textit{Simulated Noisy Set A}    & 20.75 \%  &  15.58 \% & 14.88 \%  & \textbf{13.96} \% & 13.59 \%  &  14.99 \%  \\
       \hline
-      Simulated Noisy Set B    & 50.78 \%  &  22.47 \% & 20.64 \%  & \textbf{19.58} \% & 21.37 \%  &   28.27 \%  \\
+      \textit{Simulated Noisy Set B}    & 50.78 \%  &  22.47 \% & 20.64 \%  & \textbf{19.58} \% & 21.37 \%  &   28.27 \%  \\
       \hline
-      \specialcell{Device 1  } & 52.56 \%  &  22.39 \% & 21.69 \%  & \textbf{21.35} \% & 23.20 \%   &  29.53 \%  \\
+      \specialcell{\textit{Device 1}} & 52.56 \%  &  22.39 \% & 21.69 \%  & \textbf{21.35} \% & 23.20 \%   &  29.53 \%  \\
       \hline
-      \specialcell{Device 2  } & 51.59 \%  &  22.12 \% & 21.62 \%  &  \textbf{21.26} \% & 22.90 \%   & 29.39 \%  \\
+      \specialcell{\textit{Device 2}} & 51.59 \%  &  22.12 \% & 21.62 \%  &  \textbf{21.26} \% & 22.90 \%   & 29.39 \%  \\
       \hline
-      \specialcell{Device 3  } & 54.89 \%  &  23.42 \% & 22.29 \%  &  \textbf{22.86} \%  & 26.47 \%  &  36.71 \%  \\
+      \specialcell{\textit{Device 3}} & 54.89 \%  &  23.42 \% & 22.29 \%  &  \textbf{22.86} \%  & 26.47 \%  &  36.71 \%  \\
       \hline
-      \specialcell{Device 3 \\ (Noisy Condition)  }
+      \specialcell{\textit{Device 3} \\ (Noisy Condition)  }
                               &  72.09 \%  &  36.21 \% & 35.88 \%  &  \textbf{35.83} \%  & 39.99 \%  &  51.11 \%  \\
       \hline
-      \specialcell{Device 3 \\ (Multi-Talker Condition)  }
+      \specialcell{\textit{Device 3} \\ (Multi-Talker Condition)  }
                              &  74.60 \%   &  47.63 \% & 46.03 \%  &  \textbf{46.21} \%  & 48.36 \%  & 58.31 \%   \\
@@
 %
-\begin{table}%[!htbp]
-  \renewcommand{\arraystretch}{1.3}
-  \centering
-  \caption{Average $T_{60}$ Time of the Simulated Traing Set and
-           Simulated Test Sets A and B.}
-\begin{tabular}{| c | c | c | c |}
-  \hline
-                         & \specialcell{Simulated \\ Training Set}
-                         & \specialcell{Simulated \\ Noisy Set A}
-                         & \specialcell{Simulated \\ Noisy Set B}  \\
-   \hline
-  \specialcell{Average $T_{60}$ Time}
-      & 0.482 \textit{s}
-      & 0.167 \textit{s}
-      & 0.479 \textit{s}\\
-  \hline
-\end{tabular}
-\vspace{-7mm}
-\end{table}
 %
@@
 results obtained using \textit{Room Simulator} with different RIR cut-off
-thresholds. For acoustic modeling, we use the structure shown in
-% Is this the structure you used? I thought the model is plain lstm?
-\AR{+1. I think these numbers are using logmel LSTMs? Clarify.}
-\cite{B_Li_INTERSPEECH_2017_1}
-%
-with some modification.
-One major difference is instead of generating two-channel simulated
-waveform, we generate one-channel waveform \AR{Why? Maybe say for quicker turn around time?}.
-We use the 128 dimension log-Mel feature whose window
+thresholds. The acoustic modeling structure to obtain
+ experimental results in this section is somewhat different
+from those described in \cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}
+  for faster training.
+We use a single-channel 128 log-Mel feature whose window
 size is 32 \textit{ms}. The interval between successive frame is 10
@@
 features are helpful \cite{H_Sak_INTERSPEECH_2015_1}, four frames
-are stacked together and the input is downsampled by a factor of 3.
+are stacked together.
 Thus we use a context dependent feature consisting of 512 elements
 given by 128 (the size of the log-mel feature) x 4 (number of stacked frames).
-The feature is processed by a typical multi-layer LSTM acoustic model.
+  This input is down-sampled by a factor of three 
+  \cite{g_pundak_interspeech_2016_00}.
+  The feature is processed by a typical multi-layer Long Short-Term Memory 
+  (LSTM) \cite{S_Hochreiter_neural_computation_1997_00, T_Sainath_ICASSP_2015_1} acoustic model.
 We use 5-layer LSTMs with 768 units in each layer.
-The output of the final LSTM layer is passed to a 768
-unit DNN \AR{I don't think the model has DNNs. It's just a 5layer LSTM.}, followed by a softmax layer.
+The output of the final LSTM layer is passed to a softmax layer.
 The softmax layer has 8192 nodes corresponding to the number of tied
@@
 To obtain results in Table \ref{tbl:results}, we trained for about 45 epochs.
-
+%
+\begin{table}%[!htbp]
+  \renewcommand{\arraystretch}{1.3}
+  \centering
+  \caption{\label{tbl:avg_t_60}Average $T_{60}$ Time of the Simulated 
+  Training Set and Simulated Test Sets A and B.}
+\begin{tabular}{| c | c | c | c |}
+  \hline
+                         & \specialcell{Simulated \\ Training Set}
+                         & \specialcell{Simulated \\ Noisy Set A}
+                         & \specialcell{Simulated \\ Noisy Set B}  \\
+   \hline
+  \specialcell{Average $T_{60}$ \textit{(s)}}
+      & 0.482 \textit{s}
+      & 0.167 \textit{s}
+      & 0.479 \textit{s}\\
+  \hline
+\end{tabular}
+\vspace{-7mm}
+\end{table}
 For training, we used an anonymized and hand-transcribed
 22-million English utterances (18,000-hr) set. The training set is the same as what we
-used in \cite{B_Li_INTERSPEECH_2017_1, C_Kim_INTERSPEECH_2017_1}.
+used in \cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}.
 For evaluation, we used around 15-hour of utterances (13,795 utterances)
@@
 We use both simulated and rerecorded noisy sets.
+The average reverberation time in $T_{60}$ of the simulated training set
+and two simulated test sets are shown in Table \ref{tbl:avg_t_60}.
+These two simulated test sets are named \textit{Simulated Noisy Set A} and 
+\textit{Simulated Noisy Set B} respectively.
+
 Since our objective is deploying our speech recognition
@@
 different locations in an actual room resembling a real living
-room. These devices are listed in Table 1 as ``Device 1'', ``Device 2'',
+room. These devices are listed in Table \ref{tbl:results} as ``Device 1'', ``Device 2'',
 and ``Device 3''. As shown in Table \ref{tbl:results},
@@
 training architecture in Fig. \ref{fig:gpu_cpu_structure}. We observe that
-if we use the \texttt{FFTW3}-based OLA filter using 20 \textit{dB} rir cutoff, we
+if we use the \texttt{FFTW3}-based OLA filter using 20 \textit{dB} RIR cutoff, we
 may obtain 57.6 times speed-up in the FFT portion. The entire speed-up
@@
 %
+\eightpt
 \bibliographystyle{IEEEtran}
 \bibliography{../../common_bib_file/common_bib_file}
+%\bibliography{common_bib_file}
 %

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/doc/main_new.tex
Uploads INTERSPEECH 2018 paper

\documentclass[a4paper]{article}

\usepackage{INTERSPEECH2016}

\usepackage{graphicx}
\usepackage{amssymb,amsmath,bm}
\usepackage{textcomp}
\usepackage{algorithm}
\usepackage{algpseudocode}

% Custom settings
\usepackage{tikz,placeins}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

\graphicspath{{../figures/}}
% End of custom settings

\usepackage[tight,footnotesize]{subfigure}

\def\vec#1{\ensuremath{\bm{{#1}}}}
\def\mat#1{\vec{#1}}

\newcommand{\specialcell}[2][c]{%
   \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcommand{\chanwcom}{{C. Kim}}
\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}
\renewcommand{\textfraction}{0.01}
\renewcommand{\floatpagefraction}{1.0}
\renewcommand{\dbltopfraction}{1.0}
\renewcommand{\floatpagefraction}{1.0}  % require fuller float pages
\renewcommand{\dblfloatpagefraction}{1.0} % require fuller float pages

\sloppy % better line breaks
\ninept

\title{Phase distortion model for training phase-sensitive deep-neural networks for far-field speech recognition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If multiple authors, uncomment and edit the lines shown below.       %%
%% Note that each line must be emphasized {\em } by itself.             %%
%% (by Stephen Martucci, author of spconf.sty).                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\makeatletter
%\def\name#1{\gdef\@name{#1\\}}
%\makeatother
%\name{{\em Firstname1 Lastname1, Firstname2 Lastname2, Firstname3 Lastname3,}\\
%      {\em Firstname4 Lastname4, Firstname5 Lastname5, Firstname6 Lastname6,
%      Firstname7 Lastname7}}
%%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother \name{{\em Chanwoo Kim$^1$, Taran Sainath$^1$, Arun Narayana$^1$} \\ { \em Ananya Misra$^1$,
Rajeev Nongpiur$^2$, and Michiel Bacchiani$^1$}}

\address{$^1$Google Speech, $^2$Nest \\
  {\small \tt \{chanwcom, tsainath, arunnt, amisra, rnongpiur, michiel\}@google.com }
}

%\twoauthors{Karen Sp\"{a}rck Jones.}{Department of Speech and Hearing \\
%  Brittania University, Ambridge, Voiceland \\
%  {\small \tt Karen@sh.brittania.edu} }
%  {Rose Tyler}{Department of Linguistics \\
%  University of Speechcity, Speechland \\
%  {\small \tt RTyler@ling.speech.edu} }

%
\begin{document}

\maketitle
  %
\begin{abstract}
In this paper, we present an algorithm which introduces phase-perturbation
to the training database when training phase-sensitive deep neural-network
models. Traditional features such as log-mel or cepstral features do not have
have any phase-relevant information. However more recent features such as
raw-waveform or complex spectra features contain phase-relevant information.
Phase-sensitive features have the advantage of being able to detect differences
in time of arrival across different microphone channels or
frequency bands. However, compared to magnitude-based features, phase
information is more sensitive to various kinds of distortions such as
variations in microphone characteristics, reverberation, and so on.
For traditional magnitude-based features, it is widely known that
adding noise or reverberation, often called Multistyle-TRaining (MTR)
, improves robustness. In similar spirit, we propose an algorithm which introduces spectral
distortion to make the deep-learning model more robust against phase-distortion.
We call this approach Spectral-Distortion TRaining (SDTR) and Phase-Distortion TRaining (PDTR).
In our experiments using a training set consisting of 22-million utterances, this approach has
proved to be quite successful in reducing Word Error Rates in test sets
obtained with real microphones on Google Home.
\end{abstract}
\noindent{\bf Index Terms}: Phase Difference, Phase-Sensitive Model,
Far-field Speech Recognition, Deep-Neural Network Model.

\section{Introduction}
After the breakthrough of deep learning technology
\cite{V_Vanhoucke_Deep_Learning_NIPS_Workshop_2011,
G_Hinton_IEEE_Signal_Process_Mag_2012, T_Sainath_ICASSP_2015_1,
T_Sainath_IEEETran_2017_1}, speech recognition accuracy has
improved dramatically. Recently, speech recognition systems
have begun to be employed not only in smart phones and Personal Computers
(PCs) but also in standalone devices in far-field environments.
The latter examples include voice assistant systems such as Amazon Alexa
or Google Home \cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}.
In far-field speech recognition, the impact of noise and reverberation
is much larger than near-field cases. To tackle this problem, various
kinds of multi-microphone approaches
\cite{U_H_Yapanel_SpeechComm_2008, C_Kim_INTERSPEECH_2015, C_Kim_ICASSP_2012_2,
C_Kim_ICASSP_2011_2, R_M_Stern_HSCMA_2008} have been proposed. However,
traditional multi-channel beam-forming has shown limited improvements
under reverberation \cite{C_Kim_INTERSPEECH_2009_1}.

The other approach is using multi-channel features which may contain
temporal information between two microphones \cite{T_Sainath_ICASSP_2016_1}.
It has been known that the Inter-microphone Time Delay (ITD) or
Phase Difference (PD) between two microphones may be used to identify
the Angle of Arrival (AoA) \cite{C_Kim_INTERSPEECH_2009_1, C_Kim_ICASSP_2011_2}.
Even if the features do not contain the phase information, especially
at high-frequencies, the Inter-microphone Intensity Difference (IID)
may also serve as a cue for determining the AoA \cite{ColburnKulkarni05}.

Acoustic model training using multi-channel features is much more
challenges than training a single-channel model. First, it is far
more difficult to obtain a large amount of training utterances
required for training deep-neural network from a particular
multi-channel device than collecting single-channel training
utterances. This is largely because multi-channel features
have device-dependent characteristics such as the number of
microphones and the distance between microphones.

In our recently developed Google Home \cite{C_Kim_INTERSPEECH_2017_1,
B_Li_INTERSPEECH_2017_1}, we have used the Multi-style TRaining (MTR)
using the room simulator described
in \cite{C_Kim_INTERSPEECH_2017_1} to train phase-sensitive
deep-neural networks. In this room simulator, we
assumed that all the microphones are ideal, which means that they all
have zero-phase all-pass responses. Even though this assumption is very
convenient, it is not true with actual microphones. Microphone
distortion might not be the only factor which limit the ideal multi-
channel feature assumptions. There might be other factors such as
electrical noise in the circuity, acoustic auralization due to the
surface of the hardware, and various vibration etc.

In the conventional MTR, we usually add additive noise and
reverberation effects to the training set. However we do not
usually model relative phase distortion across different
frequency channels or microphone channels. In this paper, we propose
an algorithm which adds phase distortion to make phase-sensitive
deep learning model more robust.
%
%
\section{Spectral distortion in real hardware recording}
\label{sec:spectral_distortion}
%
%
%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=50mm]{recording_room_final}
      \caption { A microphone array with two microphones in an anechoic chamber.
      The polar angle with respect to the $x$-axis is $\theta$. }
          \label{fig:recording_room_final}
  \end{center}
\end{figure}
%
%
Before discussing the Phase-Distortion TRaining (PDTR)/
Spectral-Distortion TRaining (SDTR) model in detail
in the next section, we briefly examine how the magnitude-phase distortion
occurs with real recording. Let us consider
a configuration for recording in an "anechoic" chamber as shown in Fig.
\ref{fig:recording_room_final}. The target sound source is a high-quality
loud speaker in this anechoic chamber without other noisy sound sources.
In this setup, the distance between two microphones was 5.1 $cm$.
The distance from the target sound source to the microphone array is two
meters. Let us denote the polar angle by $\theta$, which is the angle
between the perpendicular bisector to the line connecting two microphones
and the line connecting the center of the array to the loud speaker.
Fig. \ref{fig:microphone_responses} show a two-channel microphone
response obtained in this configuration with $\theta=0^{o}$.
Impulse responses were obtained using the method proposed by A. Farina
\cite{A_Frina_AES_2000}.
%
%
\begin{figure}
  \begin{center}
    \subfigure[\label{fig:time_domain_response_2_91_90_rir_anechoic_16k}] {
    \includegraphics[width=70mm]{time_domain_response_2_91_90_rir_anechoic_16k}}
  \subfigure[\label{fig:magnitude_response_2_91_90_rir_anechoic_16k}] {
    \includegraphics[width=70mm]{magnitude_response_2_91_90_rir_anechoic_16k}}
  \subfigure[\label{fig:phase_response_2_91_90_rir_anechoic_16k}] {
    \includegraphics[width=70mm]{phase_response_2_91_90_rir_anechoic_16k}}
  \caption {\label{fig:microphone_responses} \emph{ 
    (a) A microphone response recorded in an anechoic chamber.
    (b) Magnitudes of two microphone transfer functions from a single microphone array,
    and (c) Phases of two microphone transfer functions from a single microphone array.}}
  \end{center}
\end{figure}
%
%
%
As shown in Fig. \ref{fig:magnitude_response_2_91_90_rir_anechoic_16k}
and Fig. \ref{fig:target_to_mic_distribution}, the magnitude and the phase
responses are different from the ideal responses, which is the all-pass
zero-phase response. Since the polar angle $\theta=0^{0}$ in this case,
the phase components from two microphones are the same in the ideal case.
However, as shown in Fig. \ref{fig:phase_response_2_91_90_rir_anechoic_16k},
the phases from two microphones are not the same.
%
The relationship between the phase difference and Angle of Arrival (AoA) $\theta$
at discrete frequency $k$ is given by the following equation
\cite{C_Kim_INTERSPEECH_2015, C_Kim_ICASSP_2012_2}:
\begin{align}
  \theta(\omega_k) = \arcsin \left( \frac{\Delta \phi (\omega_k) c_0}{\omega_k d_m f_s}  \right)
\end{align}
where $\omega_k$ is the discrete frequency, $\Delta \phi (\omega_k)$ is the
phase difference at this frequency $\omega_k$. $f_s$, $d_m$ and $c_0$ are
sampling rates in Hz, the distance between two microphones, and
the speed of sound, respectively. Using this equation, the estimated
Angle of Arrivals(AoAs) are obtained in Fig. \ref{fig:estimated_aoa}
for three different locations with
the true polar angle $\theta$ of $45^{o}$, $0^{0}$, and $-45^{o}$ respectively.
From this figure, the phase distortion of real hardware may be easily observed.

\begin{figure}
  \begin{center}
  \subfigure[\label{fig:room_snr_db_distribution}] {
    \includegraphics[width=70mm]{estimated_angle_2_45_90_rir_anechoic_16k}
  %  \caption{$\theta=45^{o}$}
  }
  \subfigure[\label{fig:estimated_angle_2_91_90_rir_anechoic_16k}] {
    \includegraphics[width=70mm]{estimated_angle_2_91_90_rir_anechoic_16k}}
  \subfigure[\label{fig:target_to_mic_distribution}] {
    \includegraphics[width=70mm]{estimated_angle_2_135_90_rir_anechoic_16k}}
  \caption {\label{fig:estimated_aoa}\emph{ The estimated Angle of Arrival when the true polar
    angle $\theta$ is (a) $45^{o}$ (b) $0^{o}$, and (c) $-45^{o}$. }}
  \end{center}
\end{figure}
%
%
%
\section{Spectral-Distortion TRaining (SDTR)/Phase-Distortion TRaining (PDTR)}

In this section, we explain the entire structure of
Spectral-Distortion TRaining (SDTR)/Phase-Distortion TRaining (PDTR).
PDTR is a subset of SDTR where distortion is only
applied to the phase component without modifying the magnitude component
of complex features.
PDTR is devised for enhancing the robustness of phase-sensitive
multi-microphone neural network models such as
\cite{ B_Li_INTERSPEECH_2017_1, T_Sainath_INTERSPEECH_2015_1}.
Fig. \ref{fig:entire_diagram} shows the structure of the acoustic model
pipeline used in the experiment in Sec. \label{sec:experimental_results}.
This pipeline is based on the architecture described in
\cite{T_Sainath_ICASSP_2016_1, B_Li_INTERSPEECH_2017_1}. To make
the phase-sensitive multi-channel feature more robust, we add
the Spectral Distortion Model (SDM) to each channel. The actual equation
we use for this SDM is described in \eqref{eq:spectrum_distortion}.
The first stage of the pipeline in Fig \ref{fig:entire_diagram} is
is the room simulator to  generate millions of different utterances
in millions different virtual rooms \cite{C_Kim_INTERSPEECH_2017_1}.
In the room simulation system, we assume that all microphones
have the same zero-phase all-pass response.
This assumption is not true for real microphone arrays as observed in Sec.
\ref{sec:spectral_distortion}
%
\begin{figure}[t]
  \begin{center}
    \resizebox{50mm}{!}{\input{../figures/entire_diagram.tex}}
      \caption { \it  A pipeline containing the Spectrum Distortion
      Model (SDM) for training deep-neural networks for acoustic modeling.
     This acoustic model pipeline is modified based on
     \cite{T_Sainath_ICASSP_2016_1}. }
          \label{fig:entire_diagram}
  \end{center}
\end{figure}
%
%
%
\begin{figure}
    \begin{center}
    \resizebox{50mm}{!}
      {\input{../figures/spectrum_distortion_block_diagram.tex}}
    \caption {
      \it A diagram showing the structure of applying magnitude-phase
      distortion to each microphone channel. Note that $i$ in this diagram denotes
      the microphone channel index.
      \label{fig:spectrum_distortion_block_diagram}
    }
    \end{center}
\end{figure}
%
%
%
The spectrum distortion procedure is summarized by the following pseudo-code:

\vspace{5mm}
\begin{algorithmic}
\For {each utterance in the training set}
  \For {each microphone channel of the utterance}
     \State Creates the random transfer function in \eqref{eq:spectrum_distortion}.
     \State Performs Short-Time Fourier Transform (STFT).
     \State Applies this transfer function to the spectrum.
     \State Re-synthesizes the output microphone-channel using OverLap Addition (OLA).
  \EndFor
\EndFor
\end{algorithmic}
\vspace{5mm}
For each microphone channel of each utterance, we create a transfer function
to distort spectrum. Unlike the case of adding random noise to speech signals,
once transfer functions are created for a specific utterance, then these
transfer functions are maintained for that utterance. We use the spectral
distortion model described by the following equation:
%
\begin{align}
  D_l(e^{j\omega_k}) = e^{a m_l(k) + jp_l(k)}, \qquad
          & 0 \le k \le \frac{K}{2}, \nonumber \\
          & 0 \le l \le L - 1.
  \label{eq:spectrum_distortion}
\end{align}
%
where $l$ is the microphone channel index and $L$ is the number of
microphone channels. In case of Google Home, since we have two microphones,
$L = 2$.
$\omega_k$ is discrete frequency index, which is defined by
$\omega_k = \frac{2 \pi k}{K}$ where $K$ is the Discrete Fourier Transform (DFT)size.
$m_l(k)$ and $p_l(k)$ are Gaussian random samples pulled from the following
Gaussian distributions  $\mathbf{m}$ and $\mathbf{p}$ respectively:
%
\begin{subequations}
  \begin{align}
    \mathbf{m} \sim  \mathcal{N}(0, \sigma_m^2)\\
    \mathbf{p} \sim  \mathcal{N}(0, \sigma_p^2)
  \end{align}
  \label{eq:random_variables}
\end{subequations}
%
The scaling coefficient $a$ in \eqref{eq:spectrum_distortion} is defined
by the following equation:
%
\begin{align}
  a = \ln(10.0) / 20.0
  \label{eq:scaling_coeff_a}
\end{align}
%
This scaling coefficient $a$ is introduced to make $\sigma_m$
the standard deviation of the magnitude dB.
From \eqref{eq:spectrum_distortion}, it is evident that $m_l(k)$ and
$p_l(k)$ are related to the magnitude and phase distortion, respectively.
The magnitude distortion is accomplished by the $e^{a_l(k)}$ term. Since
$e^{a_l(k)} = 20.0 ^ {a_l(k) \log_{20}(e)}$,
the standard deviation of magnitude in Decibel is
given by $\log_{20}(e) \sigma_n$. For the phase term, since
the complex exponential has a period of $2 \pi$, the distribution
actually becomes the wrapped Gaussian distribution which is shown
in \label{fig:wrapped_gaussian_pdf}
\cite{E_Breitenberger_Biometrika_1963}.
%
%
\begin{figure}
  \includegraphics[width=80mm]{wrapped_gaussian_pdf}
  \caption{\label{fig:wrapped_gaussian_pdf} \emph{
    The probability density functions(PDFs) of the wrapped Gaussian
    distribution with different $\sigma_p$}.}
\end{figure}
%
%
%
After creating the spectrum distortion transfer function $D_l\left(e^{j(\omega_k)}\right)$
in \eqref{eq:spectrum_distortion}, we process each channel using the
structure shown in Fig. \label{eq:spectrum_distortion_block_diagram}.
We segment each microphone channels into successive frames with the
frame length of $160 ms$. The period between successive frames is $10 ms$.
We apply the Hanning window instead of the more frequently-used Hamming window
to each frame. We use the Hanning window to better satisfy the OverLap-Add (OLA)
constraint. After multiplying the complex spectrum of each frame with the
spectrum distortion transfer function $D_l\left(e^{j(\omega_k)}\right)$
in the frequency domain, the time-domain signal is re-synthesized
using OverLap-Add(OLA) synthesis. This processing is shown in detail
in Fig. \ref{fig:spectrum_distortion_block_diagram}. The reason for
going back to the time domain is because we use Complex Fast Fourier
Transform (CFFT) as feature whose frame size is $32 ms$ in Fig.
\ref{fig:entire_diagram}.

%
%
\section{Experimental Results}
\label{sec:experimental_results}
%
\begin{table*}[th]
  \caption{\label{tab:result} {\it Speech recognition experimental result in terms of Word Error Rates (WERs).}}
  \vspace{2mm}
  \centerline{
    \begin{tabular}{| c | c | c | c | }
      \hline
                             & \specialcell{Baseline system \\ WER}  &  \specialcell{PDTR WER}  &   \specialcell{SDTR WER}  \\
      \hline \hline
      Original Test Set         &  11.87 \% & 12.07 \%  & 12.36 \%       \\
      \hline
      Simulated Noise Set       &  18.68 \% & 18.71 \%  & 19.40 \%       \\
      \hline
      \specialcell{Device 1  }  &  20.31 \% & 19.42 \%  & 19.57 \%      \\
      \hline
      \specialcell{Device 2  }  &  20.62 \% & 19.72 \%  & 19.64 \%      \\
      \hline
      \specialcell{Device 3  }  &  20.67 \% & 19.87 \%  & 20.17 \%     \\
      \hline
    \end{tabular}
  }
\end{table*}
%
In this section, we shows experimental results obtained with
the PDM and SDM. For training, we used an anonymized
22-million English utterances (15,000-hr), which are
hand-transcribed.  For training the acoustic model, instead of
directly using the these close-talking utterances, we use a
room simulator \cite{C_Kim_INTERSPEECH_2017_1} to generate
simulated utterances for our hardware.
In the simulator, we use 7.1 cm distance between two microphones.
For each utterance, one room configuration was selected out of
three million room configurations with varying room dimension, and
varying the target speaker and noise source locations. In each
room, number of noise sources may be up to three. This configuration
changes for each training utterance. Based on our experimental results,
after every epoch, we apply a different room configuration to the
utterance so that each utterance may be regenerated in somewhat
different ways.  For additive noise, we used Youtube videos,
recordings of daily activities, and recordings at various locations
inside cafes. We picked up the SNR value from a distribution
ranging from 0 dB to 30 dB, with an average of 11 dB. We used
reverberation time varying from 0 $ms$ up to 900.0 $ms$ with
an average of 500 $ms$. To model the reverberation, we employed
the image method \cite{J_Allen_JASA_1979}. We constructed
$17^3 - 1 = 4912$ virtual sources for each real sound source.
The acoustic model was trained using the Cross-Entropy (CE) minimization
as the objective function after aligning each utterance.

For evaluation, we used around 15-hour of utterances (13,795 utterances)
obtained from anonymized voice search data. Since our objective is
testing the robustness when our system is deployed in the actual hardware
we re-recorded these utterances using our actual hardware in a real room
at five different locations. We used three different devices as shown in
Table \ref{tab:result}. These three devices are prototype Google
Home devices. Each device is placed at five different positions and
orientations in a real room with mild reverberation. The entire
15-hour test utterances are rerecorded using each device.

In Table \ref{tab:result}, we compare the performance of
the baseline system, the PDTR system, and the SDTR system.
In case of the PDTR system, we use $\sigma_m = 0$ , and
 $\sigma_p = 0.1$ in \eqref{eq:random_variables}. In case of
 the SDTR system, we used $\sigma_m = 2.0$ and $\sigma_p = 0.1$
in \eqref{eq:random_variables}. These values are heuristically
selected from a few microphone transfer functions we observed.
From this table, we may observe
that PDTR and SDTR system may slightly harm the original
test set. However, we observe that they show better speech recognition
accuracy on real hardware, which is much more important.

\section{Conclusions}
In this paper, we described the PDTR algorithm to add phase distortion
to the training set to make  the trained phase-sensitive neural net
model robust against various distortion in signals. Our experimental
results show that the phase-sensitive neural-net trained with PDTR is
much more robust against real-world distortions.

\section{Acknowledgements}
The authors are thankful to Dr. Eunjoon Cho and Dr. Kean Chin for helpful
discussions. This research was supported by Google.

\newpage
%\eightpt
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}

\end{document}

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/doc/presentation_debug.tex
Uploads INTERSPEECH 2018 paper

\documentclass[a4paper]{article}
\usepackage{INTERSPEECH2014,amssymb,amsmath,epsfig,url}
\setcounter{page}{1}
\sloppy     % better line breaks
\ninept
%SM below a registered trademark definition
\def\reg{{\rm\ooalign{\hfil
     \raise.07ex\hbox{\scriptsize R}\hfil\crcr\mathhexbox20D}}}

%% \newcommand{\reg}{\textsuperscript{\textcircled{\textsc r}}}
\title{Robust speech recognition using temporal masking and thresholding algorithm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If multiple authors, uncomment and edit the lines shown below.       %%
%% Note that each line must be emphasized {\em } by itself.             %%
%% (by Stephen Martucci, author of spconf.sty).                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\makeatletter
%\def\name#1{\gdef\@name{#1\\}}
%\makeatother
%%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother \name{{\em Chanwoo~Kim$^1$, Kean~K.~Chin$^1$, Michiel~Bacchiani$^1$, Richard~M.~Stern$^2$}}

\address{Google, Mountain View CA 94043 USA $^1$\\
  Carnegie Mellon University, Pittsburgh PA 15213 USA $^2$\\
{\small \tt \{chanwcom, kkchin, michiel\}@google.com, rms@cs.cmu.edu}}

%\twoauthors{Karen Sp\"{a}rck Jones.}{Department of Speech and Hearing \\
%  Brittania University, Ambridge, Voiceland \\
%  {\small \tt Karen@sh.brittania.edu} }
%  {Rose Tyler}{Department of Linguistics \\
%  University of Speechcity, Speechland \\
%  {\small \tt RTyler@ling.speech.edu} }

%
\usepackage{tikz}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]
\usepackage[caption=false,font=footnotesize]{subfig}
\begin{document}
\maketitle
%
\begin{abstract}
In this paper, we present a new dereverberation algorithm called
 Temporal Masking and Thresholding (TMT) to enhance the temporal
 spectra of spectral features for robust speech recognition
 in reverberant environments. This algorithm is motivated
 by the precedence effect and temporal masking of human
 auditory perception. This work is an improvement
 of our previous dereverberation work called Suppression of 
 Slowly-varying components and the falling edge of the power
 envelope (SSF).  The TMT algorithm  uses a different mathematical
 model to characterize temporal masking and thresholding compared
 to the model that had been used to characterize the SSF algorithm.
 Specifically, the nonlinear highpass filtering used in the SSF
 algorithm has been replaced by a masking mechanism
 based on a combination of peak detection and dynamic thresholding.
 Speech recognition results show that the TMT algorithm provides
 superior recognition accuracy compared to other algorithms such
 as LTLSS, VTS, or SSF in reverberant environments.

\end{abstract}
\noindent{\bf Index Terms}: Robust speech recognition, speech enhancement, reverberation,
temporal masking, precedence effect

%
\section{Introduction}

\begin{eqnarray}
  y[n] & = & x[n] * h[n]  \nonumber \\
  \log (Y[m, e^{j \omega_k})) & = & \log(X[m, e^{j \omega_k}))  \nonumber \\
            && + \log(H[m, e^{j \omega_k}))  \nonumber
\end{eqnarray}

\begin{eqnarray}
 \log   \left(\Big| Z[m, e^{j \omega_k}) \Big| \right)  & = &  \log \left(\Big| Y[m, e^{j \omega_k}) \Big| \right)  
  - \frac{1}{M} \log \left( \sum_{m = 0}^{M - 1} \Big| Y[m, e^{j \omega_k}) \Big| \right) \nonumber \\
&=& \log \left(\Big| X[m, e^{j \omega_k}) \Big| \right) 
 - \frac{1}{M} \log \left( \sum_{m = 0}^{M - 1} \Big| X[m, e^{j \omega_k}) \Big| \right) \nonumber
\end{eqnarray}

\section{Conclusion}
%TODO(chanwcom)
% Revise the conclusion
In this paper, we describe a new dereverberation algorithm,
TMT, that is based on temporal enhancement by estimating the
peak sound level and applying the temporal masking. In the
experimental results, we have observed that TMT algorithm
is simple, but has shown better speech recognition accuracies
than existing algorithms like LTLSS or VTS. The matlab code
for this algorithm may be found at 
\url{http://www.cs.cmu.edu/~robust/archive/algorithms/tmt}.

% use section* for acknowledgement
\section{Acknowledgements}
This research was supported by Google.

\end{document}

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/doc/tex_to_pdf.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+pdflatex main
+bibtex main
+pdflatex main
+pdflatex main
+#dvipdf main

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/batch_eps_to_pdf.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+
+for eps_file in *.eps; do
+  pdf_file=${eps_file%.*}.pdf
+  echo $pdf_file
+  convert $eps_file $pdf_file
+done

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/batch_plot_microphone_responses.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+bin="plot_microphone_magnitude_phase_difference.py"
+python $bin "figure_data/2_0_90_rir_anechoic_16k.wav"
+python $bin "figure_data/2_45_90_rir_anechoic_16k.wav"
+python $bin "figure_data/2_91_90_rir_anechoic_16k.wav"
+python $bin "figure_data/2_135_90_rir_anechoic_16k.wav"
+python $bin "figure_data/2_180_90_rir_anechoic_16k.wav"
+python $bin "figure_data/2_270_90_rir_anechoic_16k.wav"

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/cal_num.py

@@ -1,0 +1,58 @@
+#!/usr/bin/python
+
+import numpy as np
+
+Nx = 116991.0
+Nh = 3893.0
+I = 2.55
+J = 2
+
+print ("FIR FFT filter")
+N = 2 ** 17
+c_fir_fft = I * J * (6 * N * np.log2(N) + 2 * N)
+print (c_fir_fft)
+
+
+print ("---------------12---------------")
+N = 2 ** 12
+
+c_ola = I * J * (np.ceil(Nx / (N - Nh + 1)) * (4 * N * np.log2(N) + 2 * N) + 2 * N * np.log2(N))
+print (np.ceil(Nx / (N - Nh + 1)))
+print (c_ola / 1.0e6)
+
+print ("---------------13---------------")
+N = 2 ** 13
+
+c_ola = I * J * (np.ceil(Nx / (N - Nh + 1)) * (4 * N * np.log2(N) + 2 * N) + 2 * N * np.log2(N))
+print (np.ceil(Nx / (N - Nh + 1)))
+print (c_ola / 1.0e6)
+
+print ("---------------14---------------")
+N = 2 ** 14
+
+c_ola = I * J * (np.ceil(Nx / (N - Nh + 1)) * (4 * N * np.log2(N) + 2 * N) + 2 * N * np.log2(N))
+
+print (np.ceil(Nx / (N - Nh + 1)))
+print (c_ola / 1.0e6)
+
+print ("----------------15--------------")
+
+N = 2 ** 15
+
+c_ola = I * J * (np.ceil(Nx / (N - Nh + 1)) * (4 * N * np.log2(N) + 2 * N) + 2 * N * np.log2(N))
+print (np.ceil(Nx / (N - Nh + 1)))
+print (c_ola / 1.0e6)
+
+print ("----------------16--------------")
+N = 2 ** 16
+
+c_ola = I * J * (np.ceil(Nx / (N - Nh + 1)) * (4 * N * np.log2(N) + 2 * N) + 2 * N * np.log2(N))
+print (c_ola / 1.0e6)
+
+print ("----------------17-------------")
+N = 2 ** 17
+c_ola = I * J * (np.ceil(Nx / (N - Nh + 1)) * (4 * N * np.log2(N) + 2 * N) + 2 * N * np.log2(N))
+print (Nx / (N - Nh + 1))
+print (np.ceil(Nx / (N - Nh + 1)))
+print (c_ola / 1.0e6)
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/calculate_avg_t60.py

@@ -1,0 +1,35 @@
+#!/usr/bin/python
+
+import numpy as np
+
+# the information is obtained from:
+# https://cs.corp.google.com/piper///depot/google3/speech/recipes/robustness/config/mtr3/generate_room_simulator_params.py
+
+reverb_time = np.array([0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0])
+hist_mtr3 = np.array([4.0, 6.0, 8.0, 10.0, 13.0, 17.0, 17.0, 13.0, 8.0, 4.0, 0.0])
+
+print ((np.sum(reverb_time * hist_mtr3)) / np.sum(hist_mtr3))
+
+# These values are "tweaked" ( by hand :-( ) from the above to prevent having an
+# identical room response in training and testing
+TEST_REVERB_DISTRIBUTION = np.array([
+    [0.01, 4.0], [0.12, 6.0], [0.19, 8.0], [0.31, 10.0], [0.38, 13.0],
+    [0.49, 17.0], [0.57, 17.0], [0.72, 13.0], [0.81, 8.0], [0.92, 4.0]])
+
+print ((np.sum(TEST_REVERB_DISTRIBUTION[:, 0] * TEST_REVERB_DISTRIBUTION[:, 1]))
+       / np.sum(TEST_REVERB_DISTRIBUTION[:, 1]))
+
+
+# reverb distributions are skewed to match the snr distributions
+# in the caco1 mtr set-up.
+# These values come from the table
+# speech/recipes/robustness/
+# config/room_simulation_distribution_target_reverb_snr.pb
+CACO1_TEST_REVERB_DISTRIBUTION = np.array([
+    [0.0, 27.5], [0.1, 23.2], [0.2, 19.0], [0.3, 16.0], [0.4, 14.3]])
+
+
+print ((np.sum(CACO1_TEST_REVERB_DISTRIBUTION[:, 0] * CACO1_TEST_REVERB_DISTRIBUTION[:, 1]))
+       / np.sum(CACO1_TEST_REVERB_DISTRIBUTION[:, 1]))
+
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/calculate_speed_up.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+
+import numpy as np
+
+def CalculateRelImprovement(data):
+  relative = data / (1.0 - data)
+  print (relative[0] / relative)
+
+data= np.array([79.27, 10.11, 6.23, 6.03]) / 100
+
+CalculateRelImprovement(data)
+
+data= np.array([80.01, 13.30, 9.69, 8.05]) / 100
+
+CalculateRelImprovement(data)
+
+
+#baseline = 80.01 / 100
+#data= [13.30, 9.69, 8.05] / 100

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/convert.py

@@ -1,0 +1,8 @@
+#!/usr/bin/python
+
+import numpy as np
+
+sigma = np.array([0.0, 0.4, 1.6, np.inf])
+y = 1.0 - np.exp(-sigma ** 2 / 2.0)
+print y
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/draw_rir_cutoff_profiling.py

@@ -1,0 +1,44 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+
+cutoff_db = np.array([5.0, 10.0, 15.0, 20.0, float("inf")])
+time1 = np.array([0.97, 1.16, 1.21, 1.43, 1.94]) * 10
+time2 = np.array([3.24, 3.35, 3.41, 3.28, 3.36]) * 10
+
+
+
+
+data = []
+data.append((cutoff_db,
+             time1,
+             "OLA FFT Filtering"))
+
+data.append((cutoff_db,
+             time2,
+             "Full FFT Filtering"))
+
+print (data)
+
+#plt.axis([0.0, 1.0, 0.0, 3.5])
+
+data_list_plot.PlotSnrdbAccData(data)
+fig = plt.gcf()
+
+plt.xlabel('Room Impulse Response Cutoff Threshold (dB)')
+plt.ylabel('Calculation Time (ms)')
+plt.axis([5, 25, 0, 50])
+
+
+#fig.set_size_inches(10.0, 6.0)
+fig.savefig("./rir_cutoff_time.eps",  bbox_inches='tight')
+#fig.savefig("./rir_cutoff_time.eps", dpi=100)
+
+
+
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/draw_rir_length_histogram.py

@@ -1,0 +1,60 @@
+#!/usr/bin/python
+"""TODO(chanwcom): DO NOT SUBMIT without one-line documentation for process.
+
+TODO(chanwcom): DO NOT SUBMIT without a detailed description of process.
+"""
+
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import matplotlib.pyplot as plt
+import numpy as np
+import re
+import sys
+
+from plot_util import data_list_plot
+
+def PlotRirHistogram(input_text_file, output_eps_file):
+  x = np.array([])
+  with open(input_text_file) as file:
+    for line in file:
+      match = re.search("\|\s+(\d+)\s+\|", line.rstrip())
+
+      if match:
+        data = float(match.group(1))
+        # To handle zero length rir in the noise RIRs when SNR is inf. dB.
+        if data >  0:
+          x = np.append(x, data)
+
+  # Converts samples into seconds.
+  print (np.mean(x))
+  x = x / 16000.0
+
+  bin = np.arange(0, 0.5, 0.02)
+
+  hist, bin_edges = np.histogram(x, bin)
+
+  bin_centers = np.zeros(len(bin_edges) - 1)
+  for i in range(0, len(bin_centers)):
+    bin_centers[i] = (bin_edges[i] + bin_edges[i + 1]) / 2.0
+
+  hist = np.concatenate(([0.0], hist, [0.0]))
+  bin_centers = np.concatenate(([0.0], bin_centers, [0.5]))
+
+  data = []
+  data.append((bin_centers, hist, ""))
+
+  plt.gcf().clear()
+  data_list_plot.PlotSolidContinuousData(data)
+  plt.title('The Distribution of \n Room Impulse Response (RIR) Lengths')
+  plt.xlabel(r'Length (s)')
+  plt.ylabel('Probability Density Function (PDF)')
+  #plt.show()
+
+  fig = plt.gcf()
+  fig.savefig(output_eps_file)
+
+if __name__ == "__main__":
+  PlotRirHistogram("target_length.txt", "target_length.eps")
+  PlotRirHistogram("noise_length.txt", "noise_length.eps")

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/draw_t60_distribution.py

@@ -1,0 +1,33 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+reverb_time = np.array([0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0])
+hist_mtr3 = np.array([4.0, 6.0, 8.0, 10.0, 13.0, 17.0, 17.0, 13.0, 8.0, 4.0, 0.0])
+hist_mtr3 = hist_mtr3 / np.sum(hist_mtr3) / 0.1
+
+
+hist_real = np.array([0, 0, 0, 0, 2, 10, 11, 16, 13, 17, 19, 31, 21, 23, 16, 17, 4, 4, 3, 0])
+hist_real = hist_real / float(np.sum(hist_real)) / 0.05
+reverb_real = np.linspace(0.025, 0.975, len(hist_real)) 
+
+
+data = []
+data.append((reverb_time,
+             hist_mtr3,
+             "Room Simulator"))
+data.append((reverb_real,
+             hist_real,
+             "Real Usage"))
+
+plt.axis([0.0, 1.0, 0.0, 3.5])
+
+data_list_plot.PlotDiscreteData(data)
+fig = plt.gcf()
+fig.savefig("./reverb_time_distribution.eps")
+
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/draw_von_mises_pdf.py

@@ -1,0 +1,37 @@
+#!/usr/bin/python
+# Draws the von Mises Distribution pdf.
+#
+# Refer to the von Mises distribution in
+# https://en.wikipedia.org/wiki/Von_Mises_distribution
+
+import numpy as np
+
+from plot_util import data_list_plot
+from scipy.stats import vonmises
+import matplotlib.pyplot as plt
+
+def PlotPDF():
+  mu = 0.0
+  kappa_list = [0.0, 0.5, 1.0, 2.0, 4.0, 8.0]
+
+  data = []
+  for kappa in kappa_list:
+    x = np.linspace(-np.pi, np.pi, 100)
+    if kappa == 0.0:
+      y = 1 / (2.0 * np.pi) * np.ones(len(x))
+    else:
+      y = vonmises.pdf(x, kappa)
+
+    data.append(([x, y, "$\kappa = {0}$".format(kappa)]))
+
+  data_list_plot.PlotContinuousData(data)
+  plt.axis([-np.pi, np.pi, 0.0, 1.2])
+  plt.xlabel('$x$')
+  plt.ylabel('Probability Density Function (PDF)')
+  fig = plt.gcf()
+  fig.savefig("./von_mises_pdf.eps")
+
+
+if __name__ == "__main__":
+  PlotPDF()
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/draw_wrapped_gaussian_pdf.py

@@ -1,0 +1,44 @@
+#!/usr/bin/python
+# Draws the von Mises Distribution pdf.
+#
+# Refer to the von Mises distribution in
+# https://en.wikipedia.org/wiki/Von_Mises_distribution
+
+import numpy as np
+import mpmath
+
+from plot_util import data_list_plot
+from scipy.stats import vonmises
+import matplotlib.pyplot as plt
+
+def PlotPDF():
+  mu = 0.0
+#  sigma_list = np.sqrt([1.0/8.0, 1.0/4.0, 1.0/2.0, 1.0, 2.0, 1000.0])
+  sigma_list = np.sqrt([1.0/8.0, 1.0/4.0, 1.0/2.0, 1.0, 2.0])
+
+
+  data = []
+  x = np.linspace(-np.pi, np.pi, 100)
+  for sigma in sigma_list:
+    tau = 1.0j * sigma ** 2 / (2.0 * np.pi)
+    q = np.exp(1.0j * np.pi * tau)
+
+    mapping = np.frompyfunc(lambda *a: float(mpmath.jtheta(*a)), 3, 1)
+    y = 1 / (2.0 * np.pi) * mapping(3, x / 2.0, q)
+    data.append(([x, y, "$\sigma = {0}$".format(sigma * sigma)]))
+
+  # TODO(chanwcom) Process the infinity standard deviation case.
+  y = 1 / (2.0 * np.pi) * np.ones(np.shape(x))
+  data.append(([x, y, "$\sigma = \infty$"]))
+
+  data_list_plot.PlotContinuousData(data)
+  plt.axis([-np.pi, np.pi, 0.0, 1.2])
+  plt.xlabel('$x$')
+  plt.ylabel('Probability Density Function (PDF)')
+  fig = plt.gcf()
+  fig.savefig("./wrapped_gaussian_pdf.eps")
+
+
+if __name__ == "__main__":
+  PlotPDF()
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/ex00.py

@@ -1,0 +1,10 @@
+#!/usr/bin/python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+x = np.arange(0, 1000, 10)
+y = x / 100 *  np.log2(x / 100)
+
+plt.plot(x, y)
+plt.show()

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/extract.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+dia --export=room_diagram.png --filter=png room_diagram.dia
+convert recording_room.dia -roate 90 recording_room_rotated.dia

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/fig_data.py

@@ -1,0 +1,3 @@
+#!/usr/bin/python
+
+snr_0_db = 

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/figure_data/copy_figure.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+src_dir="/google/src/cloud/chanwcom/chanwcom-speech9999/google3/experimental/users/chanwcom/work/wavs_to_room_configuration_sstable/wavefiles"
+
+cp $src_dir/2_0_90_rir_anechoic_16k.wav 2_0_90_rir_anechoic_16k.wav
+cp $src_dir/2_45_90_rir_anechoic_16k.wav 2_45_90_rir_anechoic_16k.wav
+cp $src_dir/2_91_90_rir_anechoic_16k.wav 2_91_90_rir_anechoic_16k.wav
+cp $src_dir/2_135_90_rir_anechoic_16k.wav 2_135_90_rir_anechoic_16k.wav
+cp $src_dir/2_180_90_rir_anechoic_16k.wav 2_180_90_rir_anechoic_16k.wav
+cp $src_dir/2_270_90_rir_anechoic_16k.wav 2_270_90_rir_anechoic_16k.wav

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/get_rir_length.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+
+# MTR3 room configurations
+input_sstable=/placer/prod/home/speech-placer/speech/mtr/room_configurations/mtr3/NOISY_TRAIN_3m_2mics/mtr3_3m_NOISY_TRAIN_room_config@300
+limit_size=100000
+
+gqui from $input_sstable proto speech.dsp.RoomConfiguration select target_source.impulse_response_at_microphone[0].sample.size_ limit $limit_size  --sstable_random_sampling=true  > target_length.txt
+
+gqui from $input_sstable proto speech.dsp.RoomConfiguration select noise_source[0].impulse_response_at_microphone[0].sample.size_ limit $limit_size --sstable_random_sampling=true  > noise_length.txt
+
+#gqui from $input_sstable proto speech.dsp.RoomConfiguration limit 100 --outfile=sstable:sample_room_configuration@1

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/noisy_set1_noisy_set2.py

@@ -1,0 +1,144 @@
+#!/usr/bin/python
+
+
+
+dist = 0.6
+
+
+
+TEST_DISTANCE_SNR_DISTRIBUTIONS = [
+    HistogramBin(value=DistanceSnrDistribution(
+        distance=UniformProto(0.2, 1),
+        snr=HistogramProto([(3.2, 5), (6.3, 10), (8.9, 10), (12.1, 20),
+                            (14.8, 30), (18.2, 30), (20.8, 20), (24.3, 10),
+                            (26.7, 10), (30.2, 5)])),
+                 selection_frequency=10),
+    HistogramBin(value=DistanceSnrDistribution(
+        distance=UniformProto(1, 2),
+        snr=HistogramProto([(0.3, 5), (3.2, 10), (5.8, 10), (9.2, 20),
+                            (12.1, 30), (15.3, 30), (17.7, 20), (21.4, 10),
+                            (24.1, 10)])),
+                 selection_frequency=15),
+    HistogramBin(value=DistanceSnrDistribution(
+        distance=UniformProto(2, 3),
+        snr=HistogramProto([(0.2, 10), (2.9, 10), (6.2, 20), (9.3, 30),
+                            (12.1, 30), (14.8, 20), (18.3, 10), (21.4, 10)])),
+                 selection_frequency=20),
+    HistogramBin(value=DistanceSnrDistribution(
+        distance=UniformProto(3, 4),
+        snr=HistogramProto([(0.3, 10), (3.2, 20), (6.2, 30), (8.9, 30),
+                            (11.8, 20), (15.2, 10), (17.8, 10), (21.3, 5)])),
+                 selection_frequency=15),
+    # Distance 4-6m has identical SNR distributions.
+    HistogramBin(value=DistanceSnrDistribution(
+        distance=UniformProto(4, 5),
+        snr=HistogramProto([(0.2, 20), (3.4, 30), (6.2, 30), (9.3, 20),
+                            (12.1, 10), (14.8, 10), (18.4, 5), (20.8, 5)])),
+                 selection_frequency=10),
+    HistogramBin(value=DistanceSnrDistribution(
+        distance=UniformProto(5, 6),
+        snr=HistogramProto([(0.2, 20), (3.4, 30), (6.2, 30), (9.3, 20),
+                            (12.1, 10), (14.8, 10), (18.4, 5), (20.8, 5)])),
+                 selection_frequency=10),
+    # Distance 6-10m has identical SNR distributions.
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/draw_filter_bank_responses.m

@@ -1,0 +1,38 @@
+%
+% To plot the normalized frequency responses.
+filter_bank_freq_responses ...
+    = CalculateGammatoneShapeFilterBankResponse( ...
+        40, 1024, 16000, 0, 8000, true);
+normalized_filter_bank_responses ...
+    = MakeSumOfFreqResonsesUnity(filter_bank_freq_responses);
+
+% Use the PlotData class for plotting. 
+plot_data = PlotData();
+plot_data = plot_data.set_legend(repmat('b^', 40, 1));
+plot_data.Plot(normalized_filter_bank_responses);
+xlabel('{\it Frequency (Hz)}', 'interpreter', 'latex')
+ylabel('{\it Frequency response}', 'interpreter', 'latex')
+
+grid on
+axis([0, 512, 0, 1])
+set(gca, 'XTick', linspace(0, 512, 5)); 
+set(gca, 'XTickLabel', {'0', '2000', '4000', '6000', '8000'})
+
+%
+% TODO(chanwcom) There should be some default class for 
+% containing attributes 
+if export == 1
+
+% TODO(chanwcom)
+%Separate it as a separate class. Encapsulate exportfig as a class
+  file_name = 'draw_filter_bank_responses';
+  height = 4.0;
+  width = 6.0;
+  line_width = 2.5;
+  font_size = 16.0;
+
+  export_fig(gcf, file_name, 'width', width, 'height', height, ... 
+           'fontmode', 'fixed', 'fontsize', font_size,  ... 
+           'color', 'cmyk', 'LineWidth', line_width, 'LineMode', 'fixed')
+end
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/draw_spectrograms.m

@@ -1,0 +1,86 @@
+figure;
+
+clean_speech = wavread('figure_data/sb01_Clean.in.wav');
+reverb_speech = wavread('figure_data/sb01_Reverb0P5sec.in.wav');
+tmt_speech = wavread('figure_data/sb01_Reverb0P5sec.tmt.wav');
+
+sampling_rate = 16000;
+start_index = sampling_rate * 3.0;
+end_index = sampling_rate * 5.0;
+portion = [start_index : end_index];
+
+if 0
+  subplot(4, 1, 1)
+  spectrogram(clean_speech(portion), hamming(160), 80, 1024, sampling_rate); view(90, -90);
+
+  subplot(4, 1, 2)
+  spectrogram(reverb_speech(portion), hamming(160),80, 1024, sampling_rate); view(90, -90);
+
+  subplot(4, 1, 3)
+  spectrogram(ssf_speech(portion), hamming(160), 80, 1024, sampling_rate); view(90, -90);
+
+  subplot(4, 1, 4)
+  spectrogram(tmt_speech(portion), hamming(160), 80, 1024, sampling_rate); view(90, -90);
+end 
+
+figure
+spectrogram(clean_speech(portion), hamming(160), 80, 1024, sampling_rate); view(90, -90);
+ylabel('Time (s)')
+%title('Clean speech');
+
+if export == 1
+
+% TODO(chanwcom)
+%Separate it as a separate class. Encapsulate exportfig as a class
+  file_name = 'clean_speech_spectrogram';
+  height = 2.0;
+  width = 7.0;
+  line_width = 2.5;
+  font_size = 6.0;
+
+  export_fig(gcf, file_name, 'width', width, 'height', height, ... 
+           'fontmode', 'fixed', 'fontsize', font_size,  ... 
+           'color', 'cmyk', 'LineWidth', line_width, 'LineMode', 'scaled')
+end
+
+
+figure
+spectrogram(reverb_speech(portion), hamming(160),80, 1024, sampling_rate); view(90, -90);
+%title('Reverberant speech when $T_{60}$ is 500 ms')
+
+ylabel('Time (s)')
+
+if export == 1
+
+% TODO(chanwcom)
+%Separate it as a separate class. Encapsulate exportfig as a class
+  file_name = 'reverb_speech_spectrogram';
+  height = 2.0;
+  width = 7.0;
+  line_width = 2.5;
+  font_size = 6.0;
+
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/CMCWProcess.m

@@ -1,0 +1,89 @@
+% CMCWProcess
+%
+% Continous Masking Using Channel Weighting.
+%
+% This class performs spectral smoothing using the channel weighting
+% algorithm. For more detailed information, please refer to the
+% following paper. TODO(chanwcom) mentioning the paper.
+%
+% Usage:
+%
+% CMCWProcess cmcw_prcess(filter_bank_response)
+%
+% output_spectrum = cmcw_process.Process(...
+%     input_spectrum, binary_mask);
+classdef CMCWProcess 
+  methods
+    % freq_response_set has the following indexes:
+    % freq_response_set(frequency_index, channel_index)
+    % So, l-th channel is the l-th column.
+    % Also note that the frequency response should be from 0 to
+    function [obj] = CMCWProcess(freq_response_set)
+      [~, num_channels] = size(freq_response_set)
+      obj.filter_bank_response_ = zeros(size(freq_response_set));
+
+      % Normalize the filter gain.
+      % This procedure is done to make the summation 
+      % of the frequency response the unity. After doing
+      % this process, the filter bank satisfies the following
+      % relationship:
+      %
+      % \sum_{l = 0}^{L-1} H_l(e^{j \omega_k}) = 1.
+      %
+      % where L is the number of channels.
+      sum_spectrum = sum(freq_response_set')';
+      for channel_index = 1 : num_channels,
+        obj.filter_bank_response_(:, channel_index) ...
+            = freq_response_set(:, channel_index) ... 
+                ./ sum_spectrum;
+      end
+    end
+
+    % The original_spectrum and binary_mask should be given
+    % from zero up to N / 2 - 1, where N is the FFT size.
+    % We assume that the original signal is a real signal, so
+    % we assume that the spectrum satisfies the following symmetry
+    % equation.
+    function [obj, output_spectrum] = Process(...
+        obj, original_spectrum, binary_mask)
+        [half_spectrum_length , num_channels]... 
+            = size(obj.filter_bank_response_); 
+
+        expected_size = [half_spectrum_length, 1];
+      
+        assert(all(size(binary_mask) == expected_size), ...
+            'The size of "binary mask" is incorrect.\n');
+        assert(all(size(original_spectrum) == expected_size), ...
+            'The size of "original_spectrum" is incorrect.\n');
+
+        output_spectrum = zeros(size(original_spectrum)); 
+        
+        % TODO(chanwcom)
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/CMCWProcessTest.m

@@ -1,0 +1,26 @@
+% TODO (chanwcom)
+%
+% As of now, it is not using the unit test framework defined in Matlab.
+%
+function [] = SumTest()
+
+end
+
+function [] = ProcessCMCWTest()
+
+  gammatone_response = ComputeFilterResponse(iNumFilts, 
+  
+  % TODO(chanwcom) Replace the following by a general filter bank
+  % response class. Consider the factory pattern.
+  num_channels = 40; 
+  fft_size = 512;
+  low_freq = 0;
+  high_freq = 8000;
+  sampling_rate = 16000;
+
+  freq_response_set = ComputeFilterResponse(...
+    num_channels, fft_size, low_freq, high_freq, sampling_rate);
+
+
+
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/CalculateGammatoneShapeFilterBankResponse.m

@@ -1,0 +1,213 @@
+% TODO(chanwcom)
+% This will be reimplemented as a classdef using the Factor pattern.
+%
+% This code is based on the algorithm implemented in Malcome Slaney's 
+% auditory toolbox. 
+% https://engineering.purdue.edu/~malcolm/interval/1998-010/
+%
+% If include_pi option is set false, then this function calculates
+% the frequency response from 0 to N / 2.
+%
+function [H] = ComputeFilterResponse(... 
+  num_filters, fft_size, samp_rate, low_freq, high_req, include_pi)
+  num_channels = num_filters;
+
+  filter_coeff = ComputerFilterCoeff(...
+      samp_rate,num_channels, low_freq, high_req);
+  A0  = filter_coeff(:,1);
+  A11 = filter_coeff(:,2);
+  A12 = filter_coeff(:,3);
+  A13 = filter_coeff(:,4);
+  A14 = filter_coeff(:,5);
+  A2  = filter_coeff(:,6);
+  B0  = filter_coeff(:,7);
+  B1  = filter_coeff(:,8);
+  B2  = filter_coeff(:,9);
+  gain= filter_coeff(:,10);
+  
+  if include_pi
+    H = zeros(fft_size / 2, length(gain));
+  else
+    H = zeros(fft_size / 2 + 1, length(gain));
+  end
+
+  for chan = 1 : length(gain)
+    channel_index = length(gain) + 1 - chan;
+
+    H1Num = [A0(chan)/gain(chan) A11(chan)/gain(chan) ...
+        A2(chan)/gain(chan)];
+    H1Den = [B0(chan) B1(chan) B2(chan)];
+    [H1, W] = freqz(H1Num, H1Den, fft_size / 2);
+    H1_highest = (sum(H1Num .* ([1 -1 1]))) ...
+        / (sum(H1Den .* ([1 -1 1])));
+
+    H2Num = [A0(chan) A12(chan) A2(chan)];
+    H2Den = [B0(chan) B1(chan) B2(chan)];
+    [H2, W] = freqz(H2Num, H2Den, fft_size / 2);
+    H2_highest = (sum(H2Num .* ([1 -1 1]))) ...
+        / (sum(H2Den .* ([1 -1 1])));
+
+    H3Num = [A0(chan) A13(chan) A2(chan)];
+    H3Den = [B0(chan) B1(chan) B2(chan)];
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/FilterBankResponse.m

@@ -1,0 +1,4 @@
+classdef CreateFilterBankResponse
+
+
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/FullSpectrumToHalfSpectrum.m

@@ -1,0 +1,19 @@
+% This method converts the lower half of the spectrum to the full 
+% spectrum assuming that the signal is a real signal. Note that
+% if a signal is a real signal, then the following assumption
+% holds:
+%
+% X(e ^ {j  \omega}) = X(e ^ {j (pi - \omega)}
+%
+% 0 to N / 2 where N is the number of frequency components.
+%
+% The half spectrum is given from 0 \le k \le N / 2
+%
+
+function [full_spectrum] = HalfSpectrumToFullSpectrum(half_spectrum)
+  half_spectrum = ToColumn(half_spectrum);
+
+  full_spectrum = [half_spectrum(1 : length(half_spectrum) - 1); ... 
+      half_spectrum(length(half_spectrum)); ...
+      half_spectrum(length(half_spectrum) - 1 : -1 : 1)];
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/HalfToFullSpectrum.m

@@ -1,0 +1,19 @@
+% This method converts the lower half of the spectrum to the full 
+% spectrum assuming that the signal is a real signal. Note that
+% if a signal is a real signal, then the following assumption
+% holds:
+%
+% X(e ^ {j  \omega}) = X(e ^ {j (pi - \omega)}
+%
+% 0 to N / 2 where N is the number of frequency components.
+%
+% The half spectrum is given from 0 \le k \le N / 2
+%
+
+function [full_spectrum] = HalfToFullSpectrum(half_spectrum)
+  half_spectrum = ToColumn(half_spectrum);
+
+  full_spectrum = [half_spectrum(1 : length(half_spectrum) - 1); ... 
+      half_spectrum(length(half_spectrum)); ...
+      half_spectrum(length(half_spectrum) - 1 : -1 : 1)];
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/NormalizeFilterGain.m

@@ -1,0 +1,26 @@
+%
+% Programmed by Chanwoo Kim
+%
+% Normalize the Gain of the filter
+
+function [aad_H] = NormalizeGain(aad_H)
+	[M, N] = size(aad_H);
+
+
+	adWeight = sqrt(sum(abs(aad_H .* aad_H)));
+
+	adWeight = adWeight / adWeight(1);
+
+
+	for i = 1 : N
+
+		aad_H(:, i) = aad_H(:, i) / adWeight(i); 
+
+	end
+
+%	plot(linspace(0, 8000, length(aad_H)), 20 * log10(abs(aad_H)));
+
+
+
+
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/ToColumn.m

@@ -1,0 +1,12 @@
+% This method convers a row vector to a column vector
+%
+% If the input is not a vector but a matrix, then it reports an
+% error.
+function [in_vector] = ToColumn(in_vector)
+  [rows, cols] = size(in_vector);
+  assert(rows == 1 || cols == 1);
+
+  if (cols > 1)
+    in_vector = in_vector';
+  end
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/main_process.m

@@ -1,0 +1,148 @@
+%
+% Programmed by Chanwoo Kim
+%
+% This is the Matlab code for the Temporal Masking and Thresholding 
+% (TMT) algorithm.
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+%
+% * Usage
+%     [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%         'out.wav', 0.1, 0.995, 0.01);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+% main_process(sb01_Clean.in.wav, 'sb01_Clean.out.wav', 0.1, 0.995);
+function [out_speech] = main_process(...
+    in_file_name, out_file_name, frame_length_sec, lambda_factor, floor_coeff)
+
+%  [in_speech, sampling_rate] = wavread(in_file_name);
+%  in_speech = in_speech * 32768;
+  fid = fopen(in_file_name, 'rb');
+  fseek(fid, 1024, 'bof');
+  in_speech = fread(fid, 'int16');
+  fclose(fid);
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+  sampling_rate = 16000;
+  num_channels = 40;
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
+  frame_length = floor(frame_length_sec * sampling_rate);
+  frame_period = floor(0.01 * sampling_rate);
+  fft_size = 2 ^ceil(log(frame_length) / log(2));
+  signal_length = length(in_speech);
+
+  % TODO(chanwcom) Separate as a separate class.
+  % Gammatone-shape Frequency Response
+  filter_bank_freq_responses = CalculateGammatoneShapeFilterBankResponse(...
+      num_channels, fft_size, sampling_rate, ...
+      0.0, sampling_rate / 2.0, true);
+
+  normalized_filter_bank_freq_responses = ...
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/main_process_old.m

@@ -1,0 +1,153 @@
+%
+% Programmed by Chanwoo Kim
+%
+% TODO(chanwcom)
+% Think about a good name and description.
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+
+%
+% test
+% [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%     'out.wav', 0.05);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+% main_process(sb01_Clean.in.wav, 'sb01_Clean.out.wav', 0.1, 0.99);
+
+function [out_speech] = main_process(...
+    in_file_name, out_file_name, frame_length_sec, lambda_factor)
+  [in_speech, sampling_rate] = wavread(in_file_name);
+  in_speech = in_speech * 32768;
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+  sampling_rate = 16000;
+  num_channels = 40;
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
+  frame_length = floor(frame_length_sec * sampling_rate);
+  frame_period = floor(0.01 * sampling_rate);
+  fft_size = 2 ^ceil(log(frame_length) / log(2));
+  signal_length = length(in_speech);
+
+  % TODO(chanwcom) Separate as a separate class.
+  % Gammatone-shape Frequency Response
+  filter_bank_response = CalculateGammatoneShapeFilterBankResponse(...
+      num_channels, fft_size, sampling_rate, ...
+      0.0, sampling_rate / 2.0, true);
+
+  for m = 1 : num_channels
+    aad_symH(:, m) = abs([filter_bank_response(:, m); ...
+        flipud(filter_bank_response(:, m))]);
+  end
+
+  frame_spectrum = zeros(fft_size,  1);
+  frame_half_spectrum = zeros(fft_size / 2, 1);
+
+  cmcw_process = CMCWProcess(filter_bank_response);
+
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/obtain_peak_sound_countour.m

@@ -1,0 +1,158 @@
+%
+% Programmed by Chanwoo Kim
+%
+% This is the Matlab code for the Temporal Masking and Thresholding 
+% (TMT) algorithm.
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+%
+% * Usage
+%     [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%         'out.wav', 0.1, 0.995, 0.01);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+% main_process(sb01_Clean.in.wav, 'sb01_Clean.out.wav', 0.1, 0.995);
+function [peak_sound_level_matrix, sound_level_matrix] = main_process(...
+    in_file_name, out_file_name, frame_length_sec, lambda_factor, floor_coeff)
+
+%  [in_speech, sampling_rate] = wavread(in_file_name);
+%  in_speech = in_speech * 32768;
+  fid = fopen(in_file_name, 'rb');
+  fseek(fid, 1024, 'bof');
+  in_speech = fread(fid, 'int16');
+  fclose(fid);
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+  sampling_rate = 16000;
+  num_channels = 40;
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
+  frame_length = floor(frame_length_sec * sampling_rate);
+  frame_period = floor(0.01 * sampling_rate);
+  fft_size = 2 ^ceil(log(frame_length) / log(2));
+  signal_length = length(in_speech);
+
+  % TODO(chanwcom) Separate as a separate class.
+  % Gammatone-shape Frequency Response
+  filter_bank_freq_responses = CalculateGammatoneShapeFilterBankResponse(...
+      num_channels, fft_size, sampling_rate, ...
+      0.0, sampling_rate / 2.0, true);
+
+  normalized_filter_bank_freq_responses = ...
+      MakeSumOfFreqResonsesUnity(filter_bank_freq_responses);
+
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/figure_generation_code/spectral_analysis.m

@@ -1,0 +1,96 @@
+%
+% Programmed by Chanwoo Kim
+%
+% TODO(chanwcom)
+% Think about a good name and description.
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+
+%
+% test
+% [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%     'out.wav', 0.05);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+% spectral_analysis(sb01_Clean.in.wav, 'sb01_Clean.out.wav', 0.1, 0.995);
+function [power_matrix] = spectral_analysis(...
+    in_file_name, frame_length_sec)
+  [in_speech, sampling_rate] = wavread(in_file_name);
+  in_speech = in_speech * 32768;
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+  sampling_rate = 16000;
+  num_channels = 40;
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
+  frame_length = floor(frame_length_sec * sampling_rate);
+  frame_period = floor(0.01 * sampling_rate);
+  fft_size = 2 ^ceil(log(frame_length) / log(2));
+  signal_length = length(in_speech);
+
+  % TODO(chanwcom) Separate as a separate class.
+  % Gammatone-shape Frequency Response
+  filter_bank_response = CalculateGammatoneShapeFilterBankResponse(...
+      num_channels, fft_size, sampling_rate, ...
+      0.0, sampling_rate / 2.0, true);
+
+  frame_spectrum = zeros(fft_size,  1);
+  frame_half_spectrum = zeros(fft_size / 2, 1);
+
+  cmcw_process = CMCWProcess(filter_bank_response);
+
+  % TODO TODO(chanwcom)
+  % Instead of doing this, consider the first and the last frame
+  % as the special case. And separate it as a function.
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/plot_freq_vs_erb.m

@@ -1,0 +1,38 @@
+sampling_rate = 16000;
+linear_freq = linspace(0, sampling_rate / 2, 100);
+erb_rate = frq2erb(linear_freq);
+
+linear_erb = [linear_freq; erb_rate]';
+
+% Use the PlotData class for plotting. 
+plot_data = PlotData();
+plot_data = plot_data.set_legend({'b-'});
+plot_data.PlotXY(linear_erb);
+xlabel('{\it Frequency (Hz)}', 'interpreter', 'latex')
+ylabel('{\it ERB scale}', 'interpreter', 'latex')
+
+grid on
+%axis([0, 1.2, 0, 100])
+%axis([0, 0.9, 0, 100])
+
+
+%set(gca, 'XTick', linspace(0, 512, 5)); 
+%set(gca, 'XTickLabel', {'0', '2000', '4000', '6000', '8000'})
+
+%
+% TODO(chanwcom) There should be some default class for 
+% containing attributes 
+if export == 1
+
+% TODO(chanwcom)
+%Separate it as a separate class. Encapsulate exportfig as a class
+  file_name = 'plot_freq_vs_erb';
+  height = 4.0;
+  width = 6.5;
+  line_width = 2.5;
+  font_size = 14.0;
+
+  export_fig(gcf, file_name, 'width', width, 'height', height, ... 
+           'fontmode', 'fixed', 'fontsize', font_size,  ... 
+           'color', 'cmyk', 'LineWidth', line_width, 'LineMode', 'fixed')
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/plot_peak_sound_level.m

@@ -1,0 +1,50 @@
+window_length = 0.025;
+start_frame_index = 300; 
+end_frame_index = start_frame_index + 199;
+channel_index = 20;
+
+path(path, './figure_generation_code');
+
+[peak_sound_level_matrix, sound_level_matrix] ... 
+    = obtain_peak_sound_countour(...
+        'sb01_Clean.in.wav', 'tmp.wav', ... 
+            0.5, 0.99, 0.01);
+
+
+plot_data = PlotData();
+plot_data = plot_data.set_legend(['b', 'g'])
+figure_data = zeros(end_frame_index - start_frame_index + 1, 2);
+figure_data(:,  1) = 10 * log10((sound_level_matrix(start_frame_index : end_frame_index, channel_index)) .^ 15);
+figure_data(:,  2) = 10 * log10((peak_sound_level_matrix(start_frame_index : end_frame_index, channel_index)) .^ 15);
+plot_data.Plot(figure_data);
+%axis([0 200 -20 30])
+set(gca, 'XTick', linspace(0, 200, 5)); 
+%set(gca, 'XTickLabel', {'0', '0.5', '1.0', '1.5', '2.0', '2.5', '3.0', '3.5', '4.0', '4.5', '5.0'})
+set(gca, 'XTickLabel', {'0', '0.5', '1.0', '1.5', '2.0'})%, '2.5', '3.0', '3.5', '4.0', '4.5', '5.0'})
+set(gca, 'YTick'); 
+set(gca, 'YTickLabel', {''})
+xlabel('{\it Time (sec)}', 'interpreter', 'latex')
+ylabel('{\it Power (in dB)}', 'interpreter', 'latex')
+
+ legend(...
+      'Sound level', ...
+      'Peak sound level', ...
+      'Location', 'SouthWest');
+
+if  export == 1
+
+% TODO(chanwcom)
+%Separate it as a separate class. Encapsulate exportfig as a class
+  file_name = 'sound_level_and_peak_sound_level';
+  height = 2.5
+  width = 12.0;
+  line_width = 2.5;
+  font_size = 16.0;
+
+  export_fig(gcf, file_name, 'width', width, 'height', height, ... 
+           'fontmode', 'fixed', 'fontsize', font_size,  ... 
+           'color', 'cmyk', 'LineWidth', line_width, 'LineMode', 'fixed')
+
+end
+
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/plot_power_contour.m

@@ -1,0 +1,93 @@
+window_length = 0.025;
+start_frame_index = 300;
+end_frame_index = start_frame_index + 199;
+channel_index = 14;
+
+path(path, './figure_generation_code');
+
+clean_matrix ... 
+    = spectral_analysis( ... 
+        'figure_data/sb01_Clean.in.wav', window_length);
+reverb_matrix ... 
+    = spectral_analysis( ... 
+        'figure_data/sb01_Reverb0P5sec.in.wav', window_length);
+clean_tmt_matrix ...
+    = spectral_analysis( ...
+        'figure_data/sb01_Clean.tmt.wav', window_length);
+reverb_tmt_matrix ...
+    = spectral_analysis(...
+        'figure_data/sb01_Reverb0P5sec.tmt.wav', window_length);
+
+plot_data = PlotData();
+plot_data = plot_data.set_legend(['b', 'g'])
+figure_data = zeros(end_frame_index - start_frame_index + 1, 2);
+figure_data(:,  1) = log(clean_matrix(start_frame_index : end_frame_index, channel_index));
+figure_data(:,  2) = log(reverb_matrix(start_frame_index : end_frame_index, channel_index));
+plot_data.Plot(figure_data);
+axis([0 200 -20 30])
+set(gca, 'XTick', linspace(0, 200, 5)); 
+set(gca, 'XTickLabel', {'0', '0.5', '1.0', '1.5', '2.0'})
+set(gca, 'YTick'); 
+set(gca, 'YTickLabel', {''})
+xlabel('{\it Time (sec)}', 'interpreter', 'latex')
+ylabel('{\it Power (dB)}', 'interpreter', 'latex')
+
+
+%
+% TODO(chanwcom) There should be some default class for 
+% containing attributes 
+if export == 1
+
+% TODO(chanwcom)
+%Separate it as a separate class. Encapsulate exportfig as a class
+  file_name = 'power_contour_unprocessed'
+  height = 2.0;
+  width = 12.0;
+  line_width = 2.5;
+  font_size = 16.0;
+
+  export_fig(gcf, file_name, 'width', width, 'height', height, ... 
+           'fontmode', 'fixed', 'fontsize', font_size,  ... 
+           'color', 'cmyk', 'LineWidth', line_width, 'LineMode', 'fixed')
+
+end
+
+
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/plot_wer_is_is.m

@@ -1,0 +1,151 @@
+%
+% To plot the normalized frequency responses.
+wer = [...
+  0.0,  0.1,  0.2,  0.3,  0.4,  0.5,  0.6,  0.7, 0.8;
+  16.7, 25.1, 33.4, 42.4, 52.7, 61.3, 68.2, 73.0, 76.7;
+  0.0,  0.1,  0.2,  0.3,  0.4,  0.5,  0.6,  0.7, 0.8;
+  14.3, 22.3, 37.3, 53.9, 69.6, 79.7, 86.4, 90.5, 93.4;
+];
+wer = wer';
+wer(:, 2) = 100 - wer(:, 2);
+wer(:, 4) = 100 - wer(:, 4);
+
+% Use the PlotData class for plotting. 
+plot_data = PlotData();
+plot_data.PlotXY(wer);
+xlabel('{\it Reverberation time $T_{60}$ (ms)}', 'interpreter', 'latex')
+ylabel('{\it Accuracy (100 -WER)}', 'interpreter', 'latex')
+
+grid on
+%axis([0, 1.2, 0, 100])
+axis([0, 0.8, 0, 100])
+
+legend(...
+       'SSF with power normalization', ...
+       'Baseline with power normalization', ...
+       'Location', 'NorthEast')
+
+%set(gca, 'XTick', linspace(0, 512, 5)); 
+%set(gca, 'XTickLabel', {'0', '2000', '4000', '6000', '8000'})
+
+%
+% TODO(chanwcom) There should be some default class for 
+% containing attributes 
+if export == 1
+
+% TODO(chanwcom)
+%Separate it as a separate class. Encapsulate exportfig as a class
+  file_name = 'wer_is_is_ssf_inf_db';
+  height = 4.0;
+  width = 6.5;
+  line_width = 2.5;
+  font_size = 14.0;
+
+  export_fig(gcf, file_name, 'width', width, 'height', height, ... 
+           'fontmode', 'fixed', 'fontsize', font_size,  ... 
+           'color', 'cmyk', 'LineWidth', line_width, 'LineMode', 'fixed')
+end
+
+%
+% To plot the normalized frequency responses.
+wer = [...
+  0.0,  0.1,  0.2,  0.3,  0.4,  0.5,  0.6,  0.7, 0.8;
+  16.7, 25.1, 33.4, 42.4, 52.7, 61.3, 68.2, 73.0, 76.7;
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/plot_wer_is_is_without_retraining.m

@@ -1,0 +1,99 @@
+%
+% To plot the normalized frequency responses.
+wer = [...
+   0.0,  0.1,  0.2,  0.3,  0.4,  0.5,  0.6,  0.7, 0.8;
+   22.7, 32.9, 40.4, 46.8, 56.2, 65.8, 73.3, 78.7, 82.8
+   0.0,  0.1,  0.2,  0.3,  0.4,  0.5,  0.6,  0.7, 0.8;
+   14.3, 22.3, 37.3, 53.9, 69.6, 79.7, 86.4, 90.5, 93.4;
+   0.0,  0.1,  0.2,  0.3,  0.4,  0.5,  0.6,  0.7, 0.8;
+   21.7, 36.4, 55.0, 70.5, 82.0, 89.7, 93.8, 96.6, 98.1;
+];
+wer = wer';
+wer(:, 2) = 100 - wer(:, 2);
+wer(:, 4) = 100 - wer(:, 4);
+wer(:, 6) = 100 - wer(:, 6);
+
+% Use the PlotData class for plotting. 
+plot_data = PlotData();
+plot_data.PlotXY(wer);
+xlabel('{\it Reverberation time $T_{60}$ (ms)}', 'interpreter', 'latex')
+ylabel('{\it Accuracy (100 -WER)}', 'interpreter', 'latex')
+
+grid on
+%axis([0, 1.2, 0, 100])
+axis([0, 0.8, 0, 100])
+
+legend(...
+       'TMT with power normalization', ...
+       'power normalization', ...
+       'TMT with power normalization but without retraining', ...
+       'Location', 'NorthEast')
+
+%set(gca, 'XTick', linspace(0, 512, 5)); 
+%set(gca, 'XTickLabel', {'0', '2000', '4000', '6000', '8000'})
+
+%
+% TODO(chanwcom) There should be some default class for 
+% containing attributes 
+if export == 1
+
+% TODO(chanwcom)
+%Separate it as a separate class. Encapsulate exportfig as a class
+  file_name = 'wer_is_is_inf_db_without_retraining';
+  height = 4.0;
+  width = 6.5;
+  line_width = 2.5;
+  font_size = 14.0;
+
+  export_fig(gcf, file_name, 'width', width, 'height', height, ... 
+           'fontmode', 'fixed', 'fontsize', font_size,  ... 
+           'color', 'cmyk', 'LineWidth', line_width, 'LineMode', 'fixed')
+end
+
+%
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/plot_wer_rm_wsj.m

@@ -1,0 +1,186 @@
+%
+% To plot the normalized frequency responses.
+rm_wer = [...
+  0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.9, 1.2; ... % x-axis
+  7.4 10.9 12.8 14.2 17.1 20.2 24.9 34.0 40.1; ... % TMT
+  0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.9, 1.2; ... % x-axis
+  6.7 10.8 13.9 17.6 22.5 27.1 30.7 40.0 44.0; ... % SSF
+  0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.9, 1.2; ... % x-axis
+  7.9, 9.2, 17.1, 30.5, 43.6, 52.8, 60.4, 68.9,73.3 % LTLSS (Update the result)
+  0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.9, 1.2; ... % x-axis
+  6.8 10.3 21.8 38.0 50.5 58.8 63.7 71.8 74.7; ... % VTS
+  0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.9, 1.2; ... % x-axis
+  6.8 9.7 21.6 37.9 50.5 58.9 63.6 71.8 74.7; ... % MFCC
+];
+rm_wer = rm_wer';
+rm_wer(:, 2) = 100 - rm_wer(:, 2);
+rm_wer(:, 4) = 100 - rm_wer(:, 4);
+rm_wer(:, 6) = 100 - rm_wer(:, 6);
+rm_wer(:, 8) = 100 - rm_wer(:, 8);
+rm_wer(:, 10) = 100 - rm_wer(:, 10);
+
+
+% Use the PlotData class for plotting. 
+plot_data = PlotData();
+plot_data.PlotXY(rm_wer);
+xlabel('{\it Reverberation time $T_{60}$ (ms)}', 'interpreter', 'latex')
+ylabel('{\it Accuracy (100 -WER)}', 'interpreter', 'latex')
+
+grid on
+%axis([0, 1.2, 0, 100])
+axis([0, 0.9, 0, 100])
+
+legend(...
+       'TMT', ...
+       'SSF', ...
+       'LTLSS', ...
+       'VTS', ...
+       'Baseline MFCC', ...
+       'Location', 'SouthWest');
+
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/spectral_analysis.m

@@ -1,0 +1,94 @@
+%
+% Programmed by Chanwoo Kim
+%
+% TODO(chanwcom)
+% Think about a good name and description.
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+
+%
+% test
+% [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%     'out.wav', 0.05);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+% spectral_analysis(sb01_Clean.in.wav, 'sb01_Clean.out.wav', 0.1, 0.995);
+function [power_matrix] = spectral_analysis(...
+    in_file_name, frame_length_sec)
+  [in_speech, sampling_rate] = wavread(in_file_name);
+  in_speech = in_speech * 32768;
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+  sampling_rate = 16000;
+  num_channels = 40;
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
+  frame_length = floor(frame_length_sec * sampling_rate);
+  frame_period = floor(0.01 * sampling_rate);
+  fft_size = 2 ^ceil(log(frame_length) / log(2));
+  signal_length = length(in_speech);
+
+  % TODO(chanwcom) Separate as a separate class.
+  % Gammatone-shape Frequency Response
+  filter_bank_response = CalculateGammatoneShapeFilterBankResponse(...
+      num_channels, fft_size, sampling_rate, ...
+      0.0, sampling_rate / 2.0, true);
+
+  frame_spectrum = zeros(fft_size,  1);
+  frame_half_spectrum = zeros(fft_size / 2, 1);
+
+  % TODO TODO(chanwcom)
+  % Instead of doing this, consider the first and the last frame
+  % as the special case. And separate it as a function.
+  num_frames = floor((signal_length - frame_length) / frame_period) + 1;
+  padded_in_speech ... 
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/angle_identification_rect.m

@@ -1,0 +1,152 @@
+%
+% Programmed by Chanwoo Kim
+%
+% This is the skeleton code for frame-by-frame
+% processing. Eventually, it will be replaced by
+% classdef version, but the problem is classdef is not
+% supported by octave as of now (Apr. 2014).
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+%
+% * Usage
+%     [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%         'out.wav', 0.1, 0.995, 0.01);
+%
+%  [out_speech] = main_process('sb01_Clean.in.wav', 'out.wav', 0.05, 0.99, 0.01);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+function [angle_bias, source_angle_matrix, amplitude_matrix] = angle_identification(...
+    in_speech, num_channels, sampling_rate)
+  set_path;
+  frame_length_sec = 0.075;
+
+
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+  % TODO(chanwcom)
+  % Move it to another file defining the constsnts
+  speed_of_sound_meters_per_sec = 343.0;
+  microphone_distance_meters = 0.02;
+  angle_target_threshold = inf; % 30 / 180 * pi; % 30 degrees
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+      % TODO(chanwcom)
+      % Don't know whether the following can process multiple columns.
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
+  % The problem is octave currently does not support classdef.
+  frame_length = floor(frame_length_sec * sampling_rate);
+  frame_period = floor(frame_period_sec * sampling_rate);
+  fft_size =  2 ^ceil(log(frame_length) / log(2));
+  [signal_length, num_microphones] = size(in_speech);
+
+  assert(num_microphones == 2);
+
+  frame_spectrum = zeros(fft_size,  1);
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/calculate_band_frequencies.m

@@ -1,0 +1,10 @@
+function [frequency_band_hz] = calculate_band_frequencies(...
+    frequency_hz, erb_rate_bandwidth)
+  assert(erb_rate_bandwidth >= 0);
+  assert(frequency_hz >= 0);
+  center = frq2erb(frequency_hz);
+  erb_band = [center - erb_rate_bandwidth / 2, ...
+      center + erb_rate_bandwidth / 2];
+  frequency_band_hz = erb2frq(erb_band); 
+end
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/calculate_phase_offset.m

@@ -1,0 +1,211 @@
+%
+% Programmed by Chanwoo Kim
+%
+% This is the skeleton code for frame-by-frame
+% processing. Eventually, it will be replaced by
+% classdef version, but the problem is classdef is not
+% supported by octave as of now (Apr. 2014).
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+%
+% * Usage
+%     [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%         'out.wav', 0.1, 0.995, 0.01);
+%
+%  [out_speech] = main_process('sb01_Clean.in.wav', 'out.wav', 0.05, 0.99, 0.01);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+% calculate_phase_offset(in_speech, 16000, 0.1, 0.01, 0.02, 343.0, 0.0, 20.0, 100.0); 
+function [phase_offset, phase_diff_matrix, power_matrix] = ...
+    calculate_phase_offset(...
+    in_speech, ... 
+    sampling_rate_herz, ...  
+    frame_length_sec, ...                     % frame length second : default 0.1 
+    frame_period_sec, ...                     % frame period second
+    distance_between_microphones_meters, ...  % distance between microphones
+    speed_of_sound_meters_per_sec, ...        % speed of sound
+    expected_target_angle_degrees, ...         % default zero 
+    expected_target_angle_margin_degrees, ...          % \theta_w by default it is 60 degrees.
+    num_channels)          
+  set_path;
+
+
+  % TODO(chanwcom)
+  % Move it to another file defining the constsnts
+  angle_target_threshold = inf; % 30 / 180 * pi; % 30 degrees
+
+  if sampling_rate_herz ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+      % TODO(chanwcom)
+      % Don't know whether the following can process multiple columns.
+     in_speech = resample(in_speech, 16000, sampling_rate_herz);
+  end
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/calculate_phase_offset_old.m

@@ -1,0 +1,165 @@
+%
+% Programmed by Chanwoo Kim
+%
+% This is the skeleton code for frame-by-frame
+% processing. Eventually, it will be replaced by
+% classdef version, but the problem is classdef is not
+% supported by octave as of now (Apr. 2014).
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+%
+% * Usage
+%     [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%         'out.wav', 0.1, 0.995, 0.01);
+%
+%  [out_speech] = main_process('sb01_Clean.in.wav', 'out.wav', 0.05, 0.99, 0.01);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+% TODO(chanwcom) Number of channels will be removed.
+%
+% example
+% calculate_phase_offset(in_speech, 16000, 0.1, 0.01, 0.02, 343.0, 0.0, 30.0, 5.0); 
+function [average_phase_diff, band, phase_diff_matrix, power_matrix] = ... 
+    calculate_phase_offset(...
+    in_speech, ...
+    sampling_rate, ...  
+    frame_length_sec, ...                     % frame length second : default 0.1
+    frame_period_sec, ...                     % frame period second
+    distance_between_microphones_meters, ...  % distance between microphones
+    speed_of_sound_meters_per_sec, ...        % speed of sound
+    expected_target_angle_degree, ...         % default zero 
+    expected_target_angle_width_degree, ...          % \theta_w by default it is 60 degrees.
+    width_ERB_rate)                           % no default as of now.
+  set_path;
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ... 
+          'tested other than 16 kHz sampling rate case']);
+      % TODO(chanwcom)
+      % Don't know whether the following can process multiple columns.
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end 
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/calculate_phase_threshold.m

@@ -1,0 +1,27 @@
+% example
+% calculate_phase_threshold(16000, 2048, 0.02, 343.0, 0.0, 20.0);
+function [phi_target_minus, phi_target, phi_target_plus] ...
+    = calculate_phase_threshold( ...
+    sampling_rate_herz, ...
+    fft_size, ...
+    distance_between_microphones_meters, ...
+    speed_of_sound_meters_per_sec, ...
+    expected_target_angle_degrees, ...
+    expected_target_angle_margin_degrees)
+  % Obtain the phase threshold
+  theta_target_minus = (expected_target_angle_degrees - ... 
+      expected_target_angle_margin_degrees) * pi / 180.0;
+  theta_target = expected_target_angle_degrees * pi / 180.0;
+  theta_target_plus = (expected_target_angle_degrees + ... 
+      expected_target_angle_margin_degrees) * pi / 180.0;
+
+  % omega_k sin(\theta) f_s d / c_{air}
+  omega_k = (2 * pi) * (0 : fft_size / 2)' / fft_size;
+  phi_target_minus = omega_k .* sin(theta_target_minus) * sampling_rate_herz ... 
+      * distance_between_microphones_meters / speed_of_sound_meters_per_sec;
+  phi_target = omega_k .* sin(theta_target) * sampling_rate_herz ... 
+      * distance_between_microphones_meters / speed_of_sound_meters_per_sec;
+  phi_target_plus = omega_k .* sin(theta_target_plus) * sampling_rate_herz ... 
+      * distance_between_microphones_meters / speed_of_sound_meters_per_sec;
+end
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/main_process.m

@@ -1,0 +1,278 @@
+%
+% Programmed by Chanwoo Kim
+%
+% This is the skeleton code for frame-by-frame
+% processing. Eventually, it will be replaced by
+% classdef version, but the problem is classdef is not
+% supported by octave as of now (Apr. 2014).
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+%
+% * Usage
+%     [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%         'out.wav', 0.1, 0.995, 0.01);
+%
+%  [out_speech] = main_process('sb01_Clean.in.wav', 'out.wav', 0.05, 0.99, 0.01);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+%
+% filter_bank_type is as follows
+% 
+% TODO(chanwcom) Couldn't we use either the enumeration type or
+% string instead of using the number?
+%
+% 0 the value is obtained for every frequency index.
+% 1, the value is obtained using the rectangular weighting
+% 2, the value is obtained using the gammatone weighting
+%
+% TODO(chanwcom) Implement linear
+function [out_speech] = main_process(...
+    in_file_name, out_file_name, num_channels, num_channels_offset)
+  set_path;
+  frame_length_sec = 0.1;
+
+  [in_speech, sampling_rate] = wavread(in_file_name);
+  in_speech = in_speech * 32768;
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+  % TODO(chanwcom)
+  % Move it to another file defining the constants
+  speed_of_sound_meters_per_sec = 343.0;
+  microphone_distance_meters = 0.02;
+  angle_threshold = 20 / 180 * pi; % 20 degrees
+  angle_target_threshold = 20 / 180 * pi; % 10 degrees
+  angle_near_noise_threshold = 40 / 180 * pi; % 20 degrees
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+      % TODO(chanwcom)
+      % Don't know whether the following can process multiple columns.
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/main_process_no_offset.m

@@ -1,0 +1,278 @@
+%
+% Programmed by Chanwoo Kim
+%
+% This is the skeleton code for frame-by-frame
+% processing. Eventually, it will be replaced by
+% classdef version, but the problem is classdef is not
+% supported by octave as of now (Apr. 2014).
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+%
+% * Usage
+%     [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%         'out.wav', 0.1, 0.995, 0.01);
+%
+%  [out_speech] = main_process('sb01_Clean.in.wav', 'out.wav', 0.05, 0.99, 0.01);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+%
+% filter_bank_type is as follows
+% 
+% TODO(chanwcom) Couldn't we use either the enumeration type or
+% string instead of using the number?
+%
+% 0 the value is obtained for every frequency index.
+% 1, the value is obtained using the rectangular weighting
+% 2, the value is obtained using the gammatone weighting
+%
+% TODO(chanwcom) Implement linear
+function [out_speech] = main_process(...
+    in_file_name, out_file_name, num_channels, num_channels_offset)
+  set_path;
+  frame_length_sec = 0.1;
+
+  [in_speech, sampling_rate] = wavread(in_file_name);
+  in_speech = in_speech * 32768;
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+  % TODO(chanwcom)
+  % Move it to another file defining the constsnts
+  speed_of_sound_meters_per_sec = 343.0;
+  microphone_distance_meters = 0.02;
+  angle_threshold = 20 / 180 * pi; % 20 degrees
+  angle_target_threshold = 20 / 180 * pi; % 10 degrees
+  angle_near_noise_threshold = 40 / 180 * pi; % 20 degrees
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+      % TODO(chanwcom)
+      % Don't know whether the following can process multiple columns.
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/arithmetic/weighted_median.m

@@ -1,0 +1,95 @@
+function  [wMed] = weighted_median(D,W)
+
+%Copyright (c) 2009, Sven Haase
+%All rights reserved.
+%
+%Redistribution and use in source and binary forms, with or without
+%modification, are permitted provided that the following conditions are
+%met:
+%
+%    * Redistributions of source code must retain the above copyright
+%      notice, this list of conditions and the following disclaimer.
+%    * Redistributions in binary form must reproduce the above copyright
+%      notice, this list of conditions and the following disclaimer in
+%      the documentation and/or other materials provided with the distribution
+%
+%THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
+%AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
+%IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
+%ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE
+%LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR
+%CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
+%SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+%INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+%CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE)
+%ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
+%POSSIBILITY OF SUCH DAMAGE.
+
+
+% ----------------------------------------------------------------------
+% Function for calculating the weighted median 
+% Sven Haase
+%
+% For n numbers x_1,...,x_n with positive weights w_1,...,w_n, 
+% (sum of all weights equal to one) the weighted median is defined as
+% the element x_k, such that:
+%           --                        --
+%           )   w_i  <= 1/2   and     )   w_i <= 1/2
+%           --                        --
+%        x_i < x_k                 x_i > x_k
+%
+%
+% Input:    D ... matrix of observed values
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/dsp/filter/CalculateGammatoneShapeFilterBankResponse.m

@@ -1,0 +1,214 @@
+% TODO(chanwcom)
+% This will be reimplemented as a classdef using the Factory pattern.
+%
+% This code is based on the algorithm implemented in Malcome Slaney's 
+% auditory toolbox. 
+% https://engineering.purdue.edu/~malcolm/interval/1998-010/
+%
+% If include_pi option is set false, then this function calculates
+% the frequency response from 0 to N / 2.
+%
+% TODO(chanwcom)
+% Rename filter_bank_responses to filter_bank_responses
+function [filter_bank_responses] ...
+    = CalculateGammatoneShapeFilterBankResponse( ...
+        num_filters, fft_size, samp_rate, low_freq, high_req, include_pi)
+  num_channels = num_filters;
+
+  filter_coeff = ComputerFilterCoeff(...
+      samp_rate,num_channels, low_freq, high_req);
+  A0  = filter_coeff(:,1);
+  A11 = filter_coeff(:,2);
+  A12 = filter_coeff(:,3);
+  A13 = filter_coeff(:,4);
+  A14 = filter_coeff(:,5);
+  A2  = filter_coeff(:,6);
+  B0  = filter_coeff(:,7);
+  B1  = filter_coeff(:,8);
+  B2  = filter_coeff(:,9);
+  gain= filter_coeff(:,10);
+  
+  if include_pi
+    filter_bank_responses = zeros(fft_size / 2, length(gain));
+  else
+    filter_bank_responses = zeros(fft_size / 2 + 1, length(gain));
+  end
+
+  for chan = 1 : length(gain)
+    channel_index = length(gain) + 1 - chan;
+
+    H1Num = [A0(chan)/gain(chan) A11(chan)/gain(chan) ...
+        A2(chan)/gain(chan)];
+    H1Den = [B0(chan) B1(chan) B2(chan)];
+    [H1, W] = freqz(H1Num, H1Den, fft_size / 2);
+    H1_highest = (sum(H1Num .* ([1 -1 1]))) ...
+        / (sum(H1Den .* ([1 -1 1])));
+
+    H2Num = [A0(chan) A12(chan) A2(chan)];
+    H2Den = [B0(chan) B1(chan) B2(chan)];
+    [H2, W] = freqz(H2Num, H2Den, fft_size / 2);
+    H2_highest = (sum(H2Num .* ([1 -1 1]))) ...
+        / (sum(H2Den .* ([1 -1 1])));
+
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/dsp/filter/MakeSumOfFreqResponsesUnity.m

@@ -1,0 +1,28 @@
+%
+% This procedure makes the sum of frequency responses unity.
+% This characteristic can be expressed in the following equation:
+%
+% \sum_{l = 0}^{L-1} H_l(e^{j \omega_k}) = 1.
+%
+% where L is the number of channels, and \omega_k is the discrete-
+% requency.
+%
+% The following operation is done for this purpose..
+% TODO(chanwcom) write down the equation.
+%
+% TODO(chanwcom) Make the unit test.
+%
+% in_filter_bank_responses, the frequency responses in each channel
+% should be stored in each column. 
+function [out_filter_bank_responses] = MakeSumOfFreqResponsesUnity(...
+    in_filter_bank_responses)
+  [response_size, num_channels] = size(in_filter_bank_responses); 
+     
+  out_filter_bank_responses = zeros(size(in_filter_bank_responses));
+  sum_spectrum = sum(abs(in_filter_bank_responses)')';
+  for channel_index = 1 : num_channels,
+    out_filter_bank_responses(:, channel_index) ... 
+        = abs(in_filter_bank_responses(:, channel_index)) ... 
+            ./ sum_spectrum;
+  end 
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/dsp/filter/compute_erb_space.m

@@ -1,0 +1,42 @@
+%
+% TODO(chanwcom)
+% 
+% Rename the variables to follow the coding convention.
+function center_frequency_array = compute_erb_space(low_freq, high_freq, N)
+% center_frequency_array = ComputeERBSpace(low_freq, high_freq, N)
+% function center_frequency_array = ERBSpace(low_freq, high_freq, N)
+% This function computes an array of N frequencies uniformly spaced between
+% high_freq and low_freq on an ERB scale.  N is set to 100 if not specified.
+%
+% See also linspace, logspace, MakeERBCoeffs, MakeERBFilters.
+%
+% For a definition of ERB, see Moore, B. C. J., and Glasberg, B. R. (1983).
+% "Suggested formulae for calculating auditory-filter bandwidths and 
+% excitation patterns," J. Acoust. Soc. Am. 74, 750-753.
+  if nargin < 1 
+      low_freq = 100;
+  end 
+
+  if nargin < 2 
+      high_freq = 44100/4;
+  end 
+
+  if nargin < 3 
+      N = 100;
+  end 
+
+  % Change the following three parameters if you wish to use a different
+  % ERB scale.  Must change in MakeERBCoeffs too.
+  EarQ = 9.26449;       %  Glasberg and Moore Parameters
+  minBW = 24.7;
+  order = 1;
+
+  % All of the follow_freqing expressions are derived in Apple TR #35, "An 
+  % Efficient Implementation of the Patterson-Holdsworth Cochlear
+  % Filter Bank."  See pages 33-34.
+  center_frequency_array = -(EarQ*minBW) + ... 
+      exp((1:N)'*(-log(high_freq + EarQ*minBW) + ... 
+      log(low_freq + EarQ*minBW))/N) * (high_freq + EarQ*minBW);
+
+end
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/dsp/multi_channel/cross_correlation/analyze_delay.m

@@ -1,0 +1,29 @@
+function [delay] = analyze_delay(in_data, up_sampling_factor)
+  if (nargin == 1)
+      up_sampling_factor = 1;
+      in_upsampled_data = in_data;
+  elseif (nargin == 2)
+    assert(up_sampling_factor >= 1);
+    in_upsampled_data = resample(in_data, up_sampling_factor, 1);
+  end
+
+  [signal_length, num_microphones] = size(in_upsampled_data)
+
+  assert(signal_length > num_microphones);
+
+  reference_signal = in_upsampled_data(:, 1);
+
+  delay = zeros(num_microphones, 1);
+
+  center_of_corr_index = signal_length;
+
+  for m = 2 : num_microphones
+    corr_signal = xcorr(reference_signal, in_upsampled_data(:, m));
+    [val, index] = max(corr_signal);
+
+    delay(m) = center_of_corr_index - index; 
+  end
+
+  delay = delay / up_sampling_factor;
+
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/dsp/multi_channel/phase_difference/calculate_angle_from_spectra.m

@@ -1,0 +1,47 @@
+% This method calculates the azimuth angle of the sound source
+% When we have two microphones.
+%
+% The angle is defined with respect to the perpendicular bisector
+% of the line connecting two microphones.
+%
+% TODO(chanwcom) Make the unit test.
+% spectrum_x and spectrum_y are two spectra
+function [source_angle] = calculate_angle_from_spectra(...
+    spectrum_left, spectrum_right, fft_size, ...
+    microphone_distance_meters, sampling_rate, ...
+    speed_of_sound_meters_per_sec)
+  assert(size(spectrum_left, 1) == fft_size / 2 + 1);
+  assert(size(spectrum_left, 2) == 1);
+  assert(size(spectrum_right, 1) == fft_size / 2 + 1);
+  assert(size(spectrum_right, 2) == 1);
+
+  phase_diff = angle(spectrum_left) - angle(spectrum_right);
+
+  % The phase difference angle should be between -pi and pi but
+  % the above calculation may range from -2 * pi up to 2 * pi.
+  indices1 = find(phase_diff < -pi);
+  indices2 = find(phase_diff > pi);
+  phase_diff(indices1) = phase_diff(indices1) + 2 * pi;
+  phase_diff(indices2) = phase_diff(indices2) - 2 * pi;
+
+  % Angle calculation from the phase difference.
+  % \tau = \frac{phase_difference}{\omega}
+  % where tau is the delay and \omega is the frequency.
+  % \omega = 2 \pi k / K where K is the FFT size.
+  omega = 2 * pi * (1 : fft_size / 2)' / fft_size;
+  delay = zeros(fft_size / 2 + 1, 1);
+  delay(1) = 0;
+  delay(2 : fft_size / 2 + 1) ...
+      = phase_diff(2 : fft_size / 2 + 1) ./ omega;
+
+  % The absolute value of the delay cannot be larger than the 
+  % microphone distance. This is the theoretic value, but in
+  % reality, the value can be larger than this value. This
+  % needs to be corrected.
+  delay_max = microphone_distance_meters ...
+      / speed_of_sound_meters_per_sec * sampling_rate;
+  delay = max(min(delay, delay_max), -delay_max);
+
+  source_angle = asin(delay * speed_of_sound_meters_per_sec ...
+      / microphone_distance_meters / sampling_rate);
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/dsp/multi_channel/phase_difference/calculate_phase_diff_from_spectra.m

@@ -1,0 +1,20 @@
+% This method calculates the azimuth angle of the sound source
+% When we have two microphones.
+%
+% The angle is defined with respect to the perpendicular bisector
+% of the line connecting two microphones.
+%
+% TODO(chanwcom) Make the unit test.
+% spectrum_x and spectrum_y are two spectra
+function [phase_diff] = calculate_phase_diff_from_spectra(...
+    spectrum_left, ... 
+    spectrum_right, ... 
+    fft_size)
+  assert(size(spectrum_left, 1) == fft_size / 2 + 1);
+  assert(size(spectrum_left, 2) == 1);
+  assert(size(spectrum_right, 1) == fft_size / 2 + 1);
+  assert(size(spectrum_right, 2) == 1);
+
+  phase_diff = angle(spectrum_left) - angle(spectrum_right);
+  phase_diff = mod(phase_diff + pi, 2 * pi) - pi;
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/dsp/multi_channel/phase_difference/test_calculate_angle_from_spectra.m

@@ -1,0 +1,94 @@
+% This method calculates the azimuth angle of the sound source
+% When we have two microphones.
+%
+% The angle is defined with respect to the perpendicular bisector
+% of the line connecting two microphones.
+%
+% TODO(chanwcom) Make the unit test.
+% spectrum_x and spectrum_yh are two spectra
+
+
+% [spectrum_mat, angle] = test_calculate_angle_from_spectra('testdata/angle_30.wav');
+%sum((abs(spectrum_mat(:)) .* angle(:))) / sum((abs(spectrum_mat(:)))) * 180 / pi
+
+function [spectrum_matrix, source_angle_matrix] = test_calculate_angle_from_spectra(in_file_name)
+
+  frame_length_sec = 0.075;
+  num_channels = 100;
+
+ [in_speech, sampling_rate] = wavread(in_file_name);
+  in_speech = in_speech * 32768;
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+  % TODO(chanwcom)
+  % Move it to another file defining the constsnts
+  speed_of_sound_meters_per_sec = 343.0;
+  microphone_distance_meters = 0.04;
+  angle_threshold = 30 / 180 * pi; % 10 degrees
+  angle_target_threshold = 30 / 180 * pi; % 10 degrees
+  angle_near_noise_threshold = 60 / 180 * pi; % 20 degrees
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ... 
+          'tested other than 16 kHz sampling rate case']);
+      % TODO(chanwcom)
+      % Don't know whether the following can process multiple columns.
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end 
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
+  % The problem is octave currently does not support classdef.
+  frame_length = floor(frame_length_sec * sampling_rate);
+  frame_period = floor(frame_period_sec * sampling_rate);
+  fft_size =  2 ^ceil(log(frame_length) / log(2));
+  [signal_length, num_microphones] = size(in_speech);
+
+  frame_spectrum = zeros(fft_size,  1); 
+  frame_half_spectrum = zeros(fft_size / 2, 1); 
+
+  % TODO(chanwcom)
+  % Instead of padding, consider the first and the last frame
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/export_fig/export_fig.m

@@ -1,0 +1,1057 @@
+function varargout = export_fig(varargin)
+%EXPORTFIG  Export a figure.
+%   EXPORTFIG(H, FILENAME) writes the figure H to FILENAME.  H is
+%   a figure handle and FILENAME is a string that specifies the
+%   name of the output file.
+%
+%   EXPORTFIG(H, FILENAME, OPTIONS) writes the figure H to FILENAME
+%   with options initially specified by the structure OPTIONS. The
+%   field names of OPTIONS must be legal parameters listed below
+%   and the field values must be legal values for the corresponding
+%   parameter. Default options can be set in releases prior to R12
+%   by storing the OPTIONS structure in the root object's appdata
+%   with the command 
+%      setappdata(0,'exportfigdefaults', OPTIONS) 
+%   and for releases after R12 by setting the preference with the
+%   command 
+%      setpref('exportfig', 'defaults', OPTIONS) 
+%
+%   EXPORTFIG(...,PARAM1,VAL1,PARAM2,VAL2,...) specifies
+%   parameters that control various characteristics of the output
+%   file. Any parameter value can be the string 'auto' which means
+%   the parameter uses the default factory behavior, overriding
+%   any other default for the parameter.
+%
+%   Format Paramter:
+%     'Format'  a string
+%          specifies the output format. Defaults to 'eps'. For a
+%          list of export formats type 'help print'.
+%     'Preview' one of the strings 'none', 'tiff'
+%          specifies a preview for EPS files. Defaults to 'none'.
+%
+%   Size Parameters:
+%     'Width'   a positive scalar
+%          specifies the width in the figure's PaperUnits
+%     'Height'  a positive scalar
+%          specifies the height in the figure's PaperUnits
+%     'Bounds' one of the strings 'tight', 'loose'
+%          specifies a tight or loose bounding box. Defaults to 'tight'.
+%     'BoundsCode' one of the strings 'internal', 'mcode'
+%          specifies whether to use the internal EPS code or
+%          general m-code for computing bounding boxes. Defaults to
+%          'internal'.
+%     'Reference' an axes handle or a string
+%          specifies that the width and height parameters
+%          are relative to the given axes. If a string is
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/plot/PlotData.m

@@ -1,0 +1,72 @@
+%
+% Add comments
+classdef PlotData
+  methods
+    % data should be given in columns
+    function [obj] = PlotData(obj)
+      obj.legend_sequence_ = cell(7, 1);
+      obj.legend_sequence_{1} = 'b^-';
+      obj.legend_sequence_{2} = 'gv:';
+      obj.legend_sequence_{3} = 'rs-.';
+      obj.legend_sequence_{4} = 'cd--';
+      obj.legend_sequence_{5} = 'mo-';
+      obj.legend_sequence_{6} = 'y+:';
+      obj.legend_sequence_{7} = 'kx-';
+    end
+
+    function [obj] = set_legend(obj, legend_sequence);
+      obj.legend_sequence_ = legend_sequence;
+    end
+
+    % It is allowed not to set the entire three elements.
+    function [obj] = set_title_and_xy_lables_(...
+        obj, title_and_xy_lables)
+      assert(length(title_and_xy_lables) == 3);
+      obj.title_and_xy_labels_
+    end
+
+    function [obj] = Plot(obj, data)
+      [num_points_in_line, number_of_lines] = size(data);
+
+      assert(number_of_lines <= length(obj.legend_sequence_));
+
+      figure
+      hold on
+      for i = 1 : number_of_lines
+        plot(data(:, i), ... 
+            sprintf('%s', obj.legend_sequence_(i)), ...
+            'LineWidth', obj.line_width_, ...
+            'MarkerSize', obj.marker_size_);
+      end
+      grid on;
+    end
+
+    function [obj] = PlotXY(obj, data)
+      [num_points_in_line, number_of_lines] = size(data);
+
+      assert(number_of_lines / 2 <= length(obj.legend_sequence_), ...
+          'The number of plots is more than the number of legends');
+
+      figure
+      hold on
+      m = 0;
+      % TODO(chanwcom) Update the code
+      for i = 1 : 2 : number_of_lines,
+        plot(data(:, i), data(:, i + 1), ... 
+            sprintf('%s', obj.legend_sequence_{m + 1}), ...
+            'LineWidth', obj.line_width_, ...
+            'MarkerSize', obj.marker_size_);
+        m = m + 1;
+      end
+      grid on;
+    end
+  end
+
+  properties (SetAccess = public)
+    legend_sequence_;
+    title_and_xy_labels_;
+    line_width_ = 2;
+    marker_size_ = 5;
+  end
+
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/set_path.m

@@ -1,0 +1,27 @@
+%
+% TODO(chanwcom)
+% 
+% Execute this script to set the path of Matlab libraries.
+%
+% TODO(chanwcom)Update the comment
+% TODO(chanwcom)Make a matlab comment template based on this.
+% 
+% History
+% Date          Author      Comment
+% Apr 5  2015   chanwcom    Add the voicebox.
+% Mar 18 2014   chanwcom    Created
+
+top_directory = '/google/src/cloud/chanwcom/chanwcom-speech/google3/experimental/chanwcom/matlab_lib';
+
+% TODO(chanwcom)
+% Are there any methods other than sprintf? Something like
+% strcat?
+path(path, sprintf('%s/speech/voice_activity_detection', top_directory))
+path(path, sprintf('%s/speech/normalization', top_directory))
+path(path, sprintf('%s/arithmetic', top_directory))
+path(path, sprintf('%s/dsp/filter', top_directory))
+path(path, sprintf('%s/dsp/multi_channel/phase_difference', top_directory))
+path(path, sprintf('%s/dsp/multi_channel/cross_correlation', top_directory))
+path(path, sprintf('%s/plot',       top_directory))
+path(path, sprintf('%s/export_fig', top_directory))
+path(path, sprintf('%s/third_party/voicebox', top_directory))

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/speech/normalization/energy_norm.m

@@ -1,0 +1,6 @@
+%
+%
+function [] = energy_norm(in_speech)
+
+
+end 

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/speech/normalization/power_norm.m

@@ -1,0 +1,11 @@
+%
+% TODO(chanwcom)
+% Make a unit test.
+%
+% This method scales the input speech to make it
+% have the specified Root Mean Square (RMS) power.
+function [in_speech] = power_norm(in_speech, rms_power)
+  rms_power_in_speech = sqrt(mean(in_speech .^ 2));
+  assert(rms_power_in_speech > 0.0);
+  in_speech = in_speech * (rms_power / rms_power_in_speech);
+end 

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/speech/short_time_processing/short_time_processing_mic_array_template.m

@@ -1,0 +1,117 @@
+%
+% Programmed by Chanwoo Kim
+%
+% This is the skeleton code for frame-by-frame
+% processing. Eventually, it will be replaced by
+% classdef version, but the problem is classdef is not
+% supported by octave as of now (Apr. 2014).
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+%
+% * Usage
+%     [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%         'out.wav', 0.1, 0.995, 0.01);
+%
+%  [out_speech] = main_process('sb01_Clean.in.wav', 'out.wav', 0.05, 0.99, 0.01);
+%
+% TODO(chanwcom) Try to combine it with the other "template" one.
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands.
+%
+% main_process(sb01_Clean.in.wav, 'sb01_Clean.out.wav', 0.1, 0.99, 0.01);
+function [out_speech] = main_process(...
+    in_file_name, out_file_name, frame_length_sec, num_channels)
+  set_path;
+
+  [in_speech, sampling_rate] = wavread(in_file_name);
+  in_speech = in_speech * 32768;
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+      % TODO(chanwcom)
+      % Don't know whether the following can process multiple columns.
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
+  % The problem is octave currently does not support classdef.
+  frame_length = floor(frame_length_sec * sampling_rate);
+  frame_period = floor(frame_period_sec * sampling_rate);
+  fft_size = 2 ^ceil(log(frame_length) / log(2));
+  [signal_length, num_microphones] = size(in_speech); 
+
+  frame_spectrum = zeros(fft_size,  1);
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/speech/short_time_processing/short_time_processing_template.m

@@ -1,0 +1,110 @@
+%
+% Programmed by Chanwoo Kim
+%
+% This is the skeleton code for frame-by-frame
+% processing. Eventually, it will be replaced by
+% classdef version, but the problem is classdef is not
+% supported by octave as of now (Apr. 2014).
+%
+% Parameters
+%
+% in_file_name  : Input file in wave file format
+% out_file_name : Output file in wave file format
+% frame_length_sec     : Use 0.05 or 0.075 (50 ms or 75 ms)
+%
+% * Usage
+%     [out_speech] = main_process('sb01_Reverb0P5sec.in.wav', ...
+%         'out.wav', 0.1, 0.995, 0.01);
+
+%
+% TODO(chanwcom)
+% Make the unit test. Before that time, let's test using the following
+% commands. Check whether the output is almost the same as the input.
+function [out_speech] = main_process(...
+    in_file_name, out_file_name, frame_length_sec)
+
+  set_path;
+
+  [in_speech, sampling_rate] = wavread(in_file_name);
+  in_speech = in_speech * 32768;
+  % TODO(chanwcom) Separate them as a separate class.
+  % The following are parameters.
+  frame_period_sec = 0.01;
+
+  if sampling_rate ~= 16000
+      disp(['[WARNING] this algorithm has not been' ...
+          'tested other than 16 kHz sampling rate case']);
+     in_speech = resample(in_speech, 16000, sampling_rate);
+  end
+
+  % TODO(chanwcom) Separate the program into three classes
+  % File read/processing/file write.
+  % The problem is octave currently does not support classdef.
+  frame_length = floor(frame_length_sec * sampling_rate);
+  frame_period = floor(frame_period_sec * sampling_rate);
+  fft_size = 2 ^ceil(log(frame_length) / log(2));
+  signal_length = length(in_speech);
+
+  frame_spectrum = zeros(fft_size,  1);
+  frame_half_spectrum = zeros(fft_size / 2, 1);
+
+  % TODO TODO(chanwcom)
+  % Instead of padding, consider the first and the last frame
+  % as special cases. Separate them as a function.
+  padded_in_speech ... 
+      = [zeros(round(frame_length / 2), 1); ...
+          in_speech; ...
+          zeros(round(frame_length / 2) , 1)];
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/speech/voice_activity_detection/simple_power_vad/config_vad_cut.pl

@@ -1,0 +1,20 @@
+$szMFuncName   = "VADCut";
+$iPartSize     = 1000;
+$szInExt       = "sph";
+$szOutExt      = "sph";
+$szParmFile    = "";
+$szParmVal     = "";
+
+$bPBS = 0;
+
+$szCurDir = `./pwd.pl`;
+chomp ($szCurDir);
+
+$szInTopDir    = "/net/katsura/work/chanwook/NOISY_DB_SPH/WSJ_ALL_Train";
+$szInCtlFile   = "/net/katsura/work/chanwook/NOISY_DB_SPH/WSJ_ALL_Train/CTL_si84";
+$szOutCtlFile  = $szInCtlFile;
+
+##### The above is copy and paste. but the below is not copy and paste...
+$szOutTopDir   = "/net/katsura/work/chanwook/NOISY_DB_SPH/WSJ_OFFLINE_VAD/WSJ_ALL_Train";
+@aszPath = ("$szCurDir");
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/speech/voice_activity_detection/simple_power_vad/single_wav_vad_speech_part.m

@@ -1,0 +1,23 @@
+%
+% It assumes the input 
+%
+% Originally made by Chanwoo Kim sometime in 2008 ~ 2009 
+% for Samsung project. 
+% Modified to support only the RIFF wavefile format.
+%
+% TODO(chanwcom) Implement a routine which is somewhat similar
+% to speech_mr. 
+%
+% Pass a command line argument which indicates which routine
+% to be runned.
+function [] = single_wav_vad_speech_part(in_file_name, out_file_name)
+  in_speech = wavread(in_file_name);
+  out_speech = vad_speech_part(in_speech);
+  wavwrite(out_speech / 32768.0, 16000, out_file_name);
+
+  figure
+  subplot(2, 1, 1)
+  plot(in_speech)
+  subplot(2, 1, 2)
+  plot(out_speech)
+end

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/matlab_lib/speech/voice_activity_detection/simple_power_vad/vad_speech_part.m

@@ -1,0 +1,254 @@
+% Retrun value is...
+%
+%
+% TODO(chanwcom) FRAME_PERIOD should be replaced by FRAME_PERIOD
+% TODO(chanwcom) Make a unit test for this VAD
+% VAD
+%
+% Return value:
+function [out_speech] = vad_speech_part(in_speech)
+  in_speech_org = in_speech;
+  in_speech = in_speech - mean(in_speech);
+  in_speech_orgStd = std(in_speech);
+
+  % TODO(chanwcom) Make it as a constant member variable.
+  PEAK   = 0.95;
+  BOTTOM = 0.2;
+
+  % This is very bad.
+  % There is no gaurantee that the input sampling rate is 
+  % 16 kHz.
+  FRAME_PERIOD = 160.0;
+  FRAME_LEN    = FRAME_PERIOD;
+
+  iNumFrames = floor((length(in_speech) - FRAME_LEN) / FRAME_PERIOD) + 1;
+  adSPL      = zeros(iNumFrames, 1);  
+  
+  % Compute the energy
+  % TODO(chanwcom)
+  % Can't we make it as a subclass of something like Process ?
+  iFrameIndex = 0;
+  for i = 0 : FRAME_PERIOD : length(in_speech) - 1 - FRAME_LEN
+    iFrameIndex = iFrameIndex + 1;
+
+    xFrame = in_speech(i + 1 : i + FRAME_LEN);
+
+    % Let's calculate the sound pressure level
+    % RMS power
+    dRMS  = sqrt(mean(xFrame .* xFrame));
+    adSPL(iFrameIndex) = 10 * log10(dRMS^2 / (2e-5)^2); 
+  end
+
+  adSortedSPL = sort(adSPL);
+
+  aTH1 = adSortedSPL(floor(length(adSortedSPL) * PEAK));
+  aTH2 = adSortedSPL(floor(length(adSortedSPL) * BOTTOM));
+  dTH = (aTH1 + aTH2) / 2
+
+  % Now, let's run the end detection algorithm
+  adVAD = HangOverVAD(adSPL, dTH);
+  [endResult iNumPart] =EndDetection(adVAD);
+  
+  iAcc = 0;
+  
+  for i = 1 : iNumPart,
+   endResult(i, 1) = max(endResult(i, 1) - 30, 1);
+   endResult(i, 2) = min(endResult(i, 2) + 30, length(adVAD));
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/run_octave_borg.pl

@@ -1,0 +1,32 @@
+#!/usr/bin/perl
+# Usual usage:
+#
+# First run copy_matlab_lib_here.pl. TODO(chanwcom)
+use strict;
+use warnings;
+
+use octave_util::octave_borg_util qw(RunOctaveOnBorg);
+
+my $octave_command
+    = "main_process('_SOURCE_FEATURE_FILE_', '_DEST_FEATURE_FILE_', 40, 0)\;";
+my $in_sstable = "/namespace/speech-team/ic-d/chanwcom/speech_database/rerecorded_database/iO4_85cm.random100.sstable-00000-of-00001";
+my $out_sstable = "/namespace/speech-team/ic-d/chanwcom/work/pdcm_experiments_june_2014/etsi_40_0_no_limit/output_iO4_85cm.sstable-00000-of-00001\@1";
+my $cell = "yh";
+my @octave_code_path = (".");
+
+RunOctaveOnBorg(
+    $octave_command,
+    $in_sstable,
+    $out_sstable,
+    $cell,
+    @octave_code_path);
+
+my $in_sstable = "/namespace/speech-team/ic-d/chanwcom/speech_database/rerecorded_database/iO4_74cm_driver_dashboard.random100.sstable-00000-of-00001";
+my $out_sstable = "/namespace/speech-team/ic-d/chanwcom/work/pdcm_experiments_june_2014/car_40_0_no_limit/output_iO4_74cm_driver_dashboard.sstable-00000-of-00001\@1";
+
+RunOctaveOnBorg(
+    $octave_command,
+    $in_sstable,
+    $out_sstable,
+    $cell,
+    @octave_code_path);

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/run_octave_borg_org.pl

@@ -1,0 +1,32 @@
+#!/usr/bin/perl
+# Usual usage:
+#
+# First run copy_matlab_lib_here.pl. TODO(chanwcom)
+use strict;
+use warnings;
+
+use octave_util::octave_borg_util qw(RunOctaveOnBorg);
+
+my $octave_command
+    = "main_process_4mic('_SOURCE_FEATURE_FILE_', '_DEST_FEATURE_FILE_')\;";
+my $in_sstable = "/namespace/speech-team/ic-d/thadh/rerecorded/keyed_properly/2014.03.14_DH20120424_CH0_adapt1/iO4_85cm.sstable-00000-of-00001";
+my $out_sstable = "/namespace/speech-team/ic-d/chanwcom/work/pdcm_2_mic_256_10_freq_offset_re/2014.03.14_DH20120424_CH0_adapt1/output_iO4_85cm.sstable-00000-of-00001\@1";
+my $cell = "yh";
+my @octave_code_path = (".");
+
+RunOctaveOnBorg(
+    $octave_command,
+    $in_sstable,
+    $out_sstable,
+    $cell,
+    @octave_code_path);
+
+my $in_sstable = "/cns/ic-d/home/speech-team/rs=6.3/thadh/rerecorded/2014.03.18_test201307_nissan_altima/iO4_74cm_driver_dashboard.sstable-00000-of-00001";
+my $out_sstable = "/namespace/speech-team/ic-d/chanwcom/work/pdcm_2_mic_256_10_freq_offset_re/2014.03.18_test201307_nissan_altima/output_iO4_74cm_driver_dashboard.sstable-00000-of-00001\@1";
+
+RunOctaveOnBorg(
+    $octave_command,
+    $in_sstable,
+    $out_sstable,
+    $cell,
+    @octave_code_path);

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/old_figures/test_data/pdcm_40_0_no_limit/set_path.m

@@ -1,0 +1,27 @@
+%
+% TODO(chanwcom)
+% 
+% Execute this script to set the path of Matlab libraries.
+%
+% TODO(chanwcom)Update the comment
+% TODO(chanwcom)Make a matlab comment template based on this.
+% 
+% History
+% Date          Author      Comment
+% Apr 5  2015   chanwcom    Add the voicebox.
+% Mar 18 2014   chanwcom    Created
+
+top_directory = './matlab_lib'
+
+% TODO(chanwcom)
+% Are there any methods other than sprintf? Something like
+% strcat?
+path(path, sprintf('%s/speech/voice_activity_detection', top_directory))
+path(path, sprintf('%s/speech/normalization', top_directory))
+path(path, sprintf('%s/arithmetic', top_directory))
+path(path, sprintf('%s/dsp/filter', top_directory))
+path(path, sprintf('%s/dsp/multi_channel/phase_difference', top_directory))
+path(path, sprintf('%s/dsp/multi_channel/cross_correlation', top_directory))
+path(path, sprintf('%s/plot',       top_directory))
+path(path, sprintf('%s/export_fig', top_directory))
+path(path, sprintf('%s/third_party/voicebox', top_directory))

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_mic_source_target_2d_asymmetric.py

@@ -1,0 +1,180 @@
+#!/usr/bin/python
+
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+import numpy as np
+
+plt.rc('text', usetex=True)
+font = {"family": "sans-serif", "size": 17}
+plt.rc("font", **font)
+
+
+fig = plt.figure()
+ax = fig.add_subplot(111, aspect = 'equal')
+
+def label(xy, text):
+    # shift x and y-value for label so that it's below right the artist
+    plt.text(xy[0] + 0.3, xy[1] - 0.3, text, ha="center", family='sans-serif', size=14)
+
+rect = mpatches.Rectangle(
+      (0.0, 0.0),
+      8.9,
+      6.8,
+      clip_on=False,
+      edgecolor='black',
+      facecolor='#c0c0ff',
+      fill=True,     # remove background
+      linewidth=4,
+)
+
+ax.add_patch(rect)
+
+#ax.grid(linestyle="--", linewidth=1)
+plt.plot(clip_on=False)
+
+microphone_pos = np.array([2.5, 1.5])
+
+
+x = np.linspace(2.5, 2.5, 10)
+y = np.linspace(0.0, 1.5, 10)
+plt.plot(x, y, '--', linewidth=2, color='k')
+
+x = np.linspace(0.0, 5.0, 10)
+y = np.linspace(1.5, 1.5, 10)
+plt.plot(x, y, '--', linewidth=2, color='k')
+
+
+angle_rad = np.deg2rad(30.0)
+dist_meters = 4.0
+target_pos = (microphone_pos +
+             dist_meters * np.array([np.cos(angle_rad), np.sin(angle_rad)]))
+
+print (target_pos)
+print ('===============')
+
+angle_rad = np.deg2rad(75.0)
+dist_meters = 4.0
+noise_pos = (microphone_pos +
+             dist_meters * np.array([np.cos(angle_rad), np.sin(angle_rad)]))
+
+
+circle = mpatches.Circle(target_pos, 0.1, color="black")
+ax.add_patch(circle)
+label(target_pos, 'Target')
+
+#circle = mpatches.Circle(noise_pos, 0.1, edgecolor='black',
+#                         facecolor="gray", linewidth=2)
+#ax.add_patch(circle)
+#label(noise_pos, 'Noise')
+
+#circle = mpatches.Circle(noise_pos, 0.1, edgecolor='black',
+#                         facecolor="gray", linewidth=2)
+ax.add_patch(circle)
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_mic_source_target_2d_symmetric.py

@@ -1,0 +1,179 @@
+#!/usr/bin/python
+
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+import numpy as np
+
+plt.rc('text', usetex=True)
+font = {"family": "sans-serif", "size": 17}
+plt.rc("font", **font)
+
+
+fig = plt.figure()
+ax = fig.add_subplot(111, aspect = 'equal')
+
+def label(xy, text):
+    # shift x and y-value for label so that it's below right the artist
+    plt.text(xy[0] + 0.1, xy[1] - 0.3, text, ha="center", family='sans-serif', size=14)
+
+rect = mpatches.Rectangle(
+      (0.0, 0.0),
+      4.9,
+      3.8,
+      clip_on=False,
+      edgecolor='black',
+      facecolor='#c0c0ff',
+      fill=True,     # remove background
+      linewidth=4,
+)
+
+ax.add_patch(rect)
+
+#ax.grid(linestyle="--", linewidth=1)
+plt.plot(clip_on=False)
+
+microphone_pos = np.array([1.5, 1.9])
+
+
+x = np.linspace(1.5, 1.5, 10)
+y = np.linspace(0.0, 1.9, 10)
+plt.plot(x, y, '--', linewidth=2, color='k')
+
+x = np.linspace(0.0, 1.5, 10)
+y = np.linspace(1.9, 1.9, 10)
+plt.plot(x, y, '--', linewidth=2, color='k')
+
+
+#angle_rad = np.deg2rad(30.0)
+angle_rad = np.deg2rad(0.0)
+dist_meters = 2.0
+target_pos = (microphone_pos +
+             dist_meters * np.array([np.cos(angle_rad), np.sin(angle_rad)]))
+
+#angle_rad = np.deg2rad(75.0)
+angle_rad = np.deg2rad(45.0)
+dist_meters = 2.0
+noise_pos = (microphone_pos +
+             dist_meters * np.array([np.cos(angle_rad), np.sin(angle_rad)]))
+
+
+circle = mpatches.Circle(target_pos, 0.1, color="black")
+ax.add_patch(circle)
+label(target_pos, 'Target')
+
+circle = mpatches.Circle(noise_pos, 0.1, edgecolor='black',
+                         facecolor="gray", linewidth=2)
+ax.add_patch(circle)
+label(noise_pos, 'Noise')
+
+circle = mpatches.Circle(noise_pos, 0.1, edgecolor='black',
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_microphone_magnitude_phase_difference.py

@@ -1,0 +1,148 @@
+#!/usr/bin/python
+
+import matplotlib.pyplot as plt
+import numpy as np
+import numpy.fft
+import os
+import os.path
+import sys
+import scipy.io.wavfile
+import scipy.signal
+
+from plot_util import data_list_plot
+from dsp.multi_channel import phase_difference_util
+
+
+def ObtainSpeechFrame(file_name):
+  assert(os.path.exists(file_name))
+
+  (sampling_rate_hz, audio_data) = scipy.io.wavfile.read(file_name)
+
+  length_in_sec = 0.10
+  length_in_samples = int(np.round(sampling_rate_hz * length_in_sec))
+
+  x_data = np.linspace(0.0, length_in_sec, length_in_samples)
+  y_data = audio_data[0 : int(length_in_samples)] / 32768.0
+
+  return (x_data, y_data, sampling_rate_hz)
+
+def GetMinFftSize(signal_length):
+  return 2 ** np.ceil(np.log2(signal_length))
+
+def MicrophoneResponseSpectrum(impulse_response, sampling_rate_hz):
+  (signal_length, num_channels) = np.shape(impulse_response)
+  if signal_length <= 0:
+    raise ValueError('single length must be positive.')
+
+  # Constructs the delay signal
+  impulse_data = np.zeros((signal_length, 1))
+  (sample_index, channel_index) = np.unravel_index(
+      impulse_response.argmax(), impulse_response.shape)
+  impulse_data[sample_index, 0] = 1.0
+  print sample_index
+
+  impulse_data = np.repeat(impulse_data, num_channels, axis=1)
+  window_signal = np.repeat(
+      np.expand_dims(
+          scipy.signal.hamming(signal_length), axis=1), num_channels, axis=1)
+
+  fft_size = int(GetMinFftSize(signal_length))
+  delay_spectrum = np.fft.fft(
+      impulse_data * window_signal, fft_size, axis=0)
+  spectrum = np.fft.fft(
+      impulse_response * window_signal, fft_size, axis=0)
+
+  # Compensates the delay component.
+  spectrum = spectrum / delay_spectrum
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_microphone_magnitude_phase_responses.py

@@ -1,0 +1,128 @@
+#!/usr/bin/python
+
+import matplotlib.pyplot as plt
+import numpy as np
+import numpy.fft
+import os
+import sys
+import scipy.io.wavfile
+import scipy.signal
+
+from plot_util import data_list_plot
+
+
+def ObtainSpeechFrame(file_name):
+  assert(os.path.exists(file_name))
+
+  (sampling_rate_hz, audio_data) = scipy.io.wavfile.read(file_name)
+  print sampling_rate_hz
+
+  length_in_sec = 0.10
+  length_in_samples = int(np.round(sampling_rate_hz * length_in_sec))
+
+  x_data = np.linspace(0.0, length_in_sec, length_in_samples)
+  y_data = audio_data[0 : int(length_in_samples), 1] / 32768.0
+
+  return (x_data, y_data, sampling_rate_hz)
+
+# Impulse response
+
+def PerformSTFT(speech_frame, sampling_rate_hz):
+  # Adds a routine to calculate FFT size.
+  fft_size = 2048
+  spectrum = numpy.fft.fft(
+      speech_frame * scipy.signal.hamming(len(speech_frame)), fft_size)
+  lower_half_spectrum = spectrum[0: int(np.floor(fft_size / 2))]
+
+  freq_data = np.linspace(0.0, sampling_rate_hz / 2.0, len(lower_half_spectrum))
+
+  return (freq_data, lower_half_spectrum)
+
+def GetMinFftSize(signal_length):
+  return 2 ** np.ceil(np.log2(signal_length))
+
+
+def MicrophoneResponseSpectrum(impulse_response, sampling_rate_hz):
+  signal_length = len(speech_frame)
+  if signal_length <= 0:
+    raise ValueError('single length must be positive.')
+
+  impulse_data = np.zeros((signal_length, ))
+  index = np.argmax(speech_frame)
+  impulse_data[index] = 1.0
+
+  # Constructs the delay signal
+  fft_size = int(GetMinFftSize(signal_length))
+  delay_spectrum = numpy.fft.fft(
+      impulse_data * scipy.signal.hamming(len(impulse_data)), fft_size)
+  spectrum = numpy.fft.fft(
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_mtr3.py

@@ -1,0 +1,37 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+plt.rc('text', usetex=True)
+
+sigma = np.array([0.0, 0.1, 0.4, 1.6, np.inf])
+
+# The phase distortion amount.
+x_data = np.sqrt(1.0 - np.exp(-sigma ** 2 / 2.0))
+
+
+# The data at 41.000 is problematic.
+data = []
+data.append((x_data, 100 - np.array([39.728, 38.888, 40.643, 43.247, 42.604]), "$\sigma_m = 0.0$"))
+data.append((x_data, 100 - np.array([40.049, 37.850, 39.744, 41.819, 42.728]), "$\sigma_m = 1.0$"))
+data.append((x_data, 100 - np.array([40.164, 40.057, 40.139, 42.400, 42.831]), "$\sigma_m = 2.0$"))
+
+# 41.904 is a false data. Rerun?
+data.append((x_data, 100 - np.array([41.904, 41.344, 41.780, 43.597, 43.470]), "$\sigma_m = 4.0$"))
+
+data_list_plot.PlotDiscreteData(data)
+fig = plt.gcf()
+plt.axis([0, 1.0, 50.0, 70.0])
+
+
+plt.title(r"\textit{Rerecorded noisy test set (13k mobile set)}")
+plt.ylabel(r'\textit{Accuracy (100 - WER \%)}')
+plt.xlabel(r'\textit{Circular standard deviation $s$}')
+fig.savefig("./test.eps")
+
+subprocess.check_call(shlex.split("evince test.eps"))
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_multitalker.py

@@ -1,0 +1,35 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+plt.rc('text', usetex=True)
+
+sigma = np.array([0.0, 0.1, 0.4, 1.6, np.inf])
+
+# The phase distortion amount.
+x_data = np.sqrt(1.0 - np.exp(-sigma ** 2 / 2.0))
+
+
+# The data at 41.000 is problematic.
+data = []
+data.append((x_data, 100 - np.array([52.568, 51.436, 55.331, 57.861, 52.955]), "$\sigma_m = 0.0$"))
+data.append((x_data, 100 - np.array([51.343, 48.775, 49.628, 55.675, 56.391]), "$\sigma_m = 1.0$"))
+data.append((x_data, 100 - np.array([49.571, 51.905, 51.509, 54.468, 52.893]), "$\sigma_m = 2.0$"))
+
+data_list_plot.PlotDiscreteData(data)
+fig = plt.gcf()
+plt.axis([0, 1.0, 40.0, 60.0])
+
+plt.title(r"\textit{Rerecorded multitalker test set (13k mobile set)}")
+plt.ylabel(r'\textit{Accuracy (100 - WER \%)}')
+plt.xlabel(r'\textit{Circular standard deviation $s$}')
+
+file_name = "mtr_multitalker.eps"
+fig.savefig(file_name)
+
+subprocess.check_call(shlex.split("evince {0}".format(file_name)))
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_mults.py

@@ -1,0 +1,57 @@
+#!/usr/bin/python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+def _GetMinFftSize(signal_length):
+  return int(2 ** np.ceil(np.log2(signal_length)))
+
+N_x = 116991.0
+B_array = np.arange(100, N_x + 1000, 100.0) # block_size
+M = 3893.0
+
+
+Mult_array = np.zeros(np.shape(B_array))
+
+index = 0
+N = float(_GetMinFftSize(N_x + M - 1))
+total = 6.0 * N * np.log2(N) + 2.0 * N
+for B in B_array:
+  N = float(_GetMinFftSize(B + M - 1))
+ # N = B + M - 1
+
+  mult =  np.ceil(float(N_x) / float(B)) * (4.0 * N * np.log2(N) + 2.0 * N)  + (2.0 * N * np.log2(N))
+
+  Mult_array[index] = mult
+  index = index + 1
+
+
+print (B_array[np.argmin(Mult_array)])
+print (np.min(Mult_array))
+print "=============="
+
+Mult_array2 = np.zeros(np.shape(B_array))
+
+index = 0
+N = float(_GetMinFftSize(N_x + M - 1))
+total = 6.0 * N * np.log2(N) + 2.0 * N
+for B in B_array:
+ # N = float(_GetMinFftSize(B + M - 1))
+  N = B + M - 1
+
+  mult =  np.ceil(float(N_x) / float(B)) * (4.0 * N * np.log2(N) + 2.0 * N)  + (2.0 * N * np.log2(N))
+
+  Mult_array2[index] = mult
+  index = index + 1
+
+
+print (min(Mult_array) / 1e7)
+
+Mult_array3 = total * np.ones(np.shape(B_array))
+
+plt.plot(B_array, Mult_array)
+plt.plot(B_array, Mult_array2)
+plt.plot(B_array, Mult_array3)
+plt.axis([0, N_x, 0, 1.5 * total])
+plt.show()

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_rir_cutoff_rerecorded_sets.py

@@ -1,0 +1,49 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+#plt.rc('text', usetex=True)
+
+x_data = np.array([5.0, 10.0, 20.0, float("inf")])
+
+
+# The data at 41.000 is problematic.
+data = []
+data.append((x_data, 100 - np.array([11.20, 10.75, 11.43, 11.95]),
+             "Original"))
+           #  "Original Set"))
+data.append((x_data, 100 - np.array([31.88, 24.19, 21.82, 21.87]),
+             "Relatively Clean"))
+
+data.append((x_data, 100 - np.array([51.12, 40.00, 35.83, 35.88]),
+             "Music"))
+data.append((x_data, 100 - np.array([58.30, 48.36, 46.22, 46.03]),
+             "Interfering Speakers"))
+
+
+#data.append((x_data, 100 - np.array([88, 40.643, 43.247, 42.604]), "Simulated Noise Set 1"))
+#data.append((x_data, 100 - np.array([88, 40.643, 43.247, 42.604]), "Simulated Noise Set 2"))
+
+
+data_list_plot.PlotSnrdbAccData(data)
+fig = plt.gcf()
+plt.axis([5, 25, 0, 100])
+
+
+#plt.title("\textit{Rerecorded Noisy Test Set \n (Mobile Voice Search Test Set)}")
+plt.title("Rerecorded Mobile \n Voice Search Test Set")
+#plt.ylabel('\textit{Accuracy (100 - WER \%)}')
+plt.xlabel('Room Impulse Response Cutoff Threshold (dB).')
+
+file_name = "./rir_cutoff_rerecorded_sets.eps"
+fig.set_size_inches(10.0, 6.0)
+fig.savefig(file_name,  bbox_inches='tight')
+
+
+subprocess.check_call(shlex.split("evince {0}".format(file_name)))
+
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_rir_cutoff_simulated_sets.py

@@ -1,0 +1,45 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+#plt.rc('text', usetex=True)
+
+x_data = np.array([5.0, 10.0, 20.0, float("inf")])
+
+
+# The data at 41.000 is problematic.
+data = []
+data.append((x_data, 100 - np.array([11.20, 10.75, 11.43, 11.95]),
+             "Original"))
+           #  "Original Set"))
+data.append((x_data, 100 - np.array([14.99, 13.59, 13.96, 14.88]),
+             "Simulated Noisy Set A"))
+
+data.append((x_data, 100 - np.array([28.27, 21.37, 19.58, 22.29]),
+             "Simulated Noisy Set B"))
+
+
+
+data_list_plot.PlotSnrdbAccData(data)
+fig = plt.gcf()
+plt.axis([5, 25, 0, 100])
+
+
+#plt.title("\textit{Rerecorded Noisy Test Set \n (Mobile Voice Search Test Set)}")
+plt.title("Simulated Noisy Mobile \n Voice Search Test Set")
+#plt.ylabel('\textit{Accuracy (100 - WER \%)}')
+plt.xlabel('Room Impulse Response Cutoff Threshold (dB).')
+
+file_name = "./rir_cutoff_simulated_sets.eps"
+fig.set_size_inches(10.0, 6.0)
+fig.savefig(file_name, bbox_inches='tight')
+
+
+
+subprocess.check_call(shlex.split("evince {0}".format(file_name)))
+
+

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/plot_wer_demand_speaker.py

@@ -1,0 +1,37 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+x_snr = np.array([0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9])
+
+data = []
+data.append((x_snr,
+             100 - np.array([14.5945949554,  20.5100955963,  30.3931980133,  27.3738231659,  30.1573429108,  31.6046962738,  36.9088821411,  39.9317398071,  37.4674758911,  33.8645401001]),
+                 
+             "RMS-PDCW"))
+data.append((x_snr,
+             100 - np.array([12.1081085205,  23.2731132507,  31.4558982849,  31.9931564331,  38.0244750977,  38.0626220703,  44.40599823,  47.2696228027,  46.9210739136,  43.6254997253]),
+             "PDCW"))
+data.append((x_snr,
+             100 - np.array([
+                 11.6756753922,  17.2157287598,  26.0361309052,  22.412317276,  24.5629367828,  26.2230911255,  28.8350639343,  31.3993167877,  31.6565475464,  25.1992034912, ]),
+             "MTR"))
+
+data.append((x_snr,
+             100 - np.array([
+                  20.4324321747,  34.2189178467,  50.2656745911,  52.2668952942,  58.0419578552,  60.6653633118,  69.0888137817,  72.3549499512,  70.0780563354,  73.8047790527 ]),
+             "Without MTR"))
+
+data_list_plot.PlotSnrdbAccData(data)
+fig = plt.gcf()
+plt.axis([0.0, 0.9, 0.0, 100])
+plt.title("Mobile search task \n 0 dB SNR DEMAND noise")
+plt.ylabel('Accuracy (100 - WER%)')
+plt.xlabel('Reverberation Time ($T_{60}$) in Seconds')
+fig.savefig("./demand_0db.eps")
+
+subprocess.check_call(shlex.split("evince demand_0db.eps"))

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/process.sh

@@ -1,0 +1,25 @@
+#!/bin/bash
+
+echo "["
+cat $1 | grep _00_ | perl -pe 's/.*://g; ' | sed -e '/====/d' | perl -pe 's/\n+/, /g'
+echo "]"
+
+echo "["
+cat $1 | grep _05_ | perl -pe 's/.*://g; ' | sed -e '/====/d' | perl -pe 's/\n+/, /g'
+echo "]"
+
+echo "["
+cat $1 | grep _10_ | perl -pe 's/.*://g; ' | sed -e '/====/d' | perl -pe 's/\n+/, /g'
+echo "]"
+
+echo "["
+cat $1 | grep _15_ | perl -pe 's/.*://g; ' | sed -e '/====/d' | perl -pe 's/\n+/, /g'
+echo "]"
+
+echo "["
+cat $1 | grep _20_ | perl -pe 's/.*://g; ' | sed -e '/====/d' | perl -pe 's/\n+/, /g'
+echo "]"
+
+echo "["
+cat $1 | grep _inf_ | perl -pe 's/.*://g; ' | sed -e '/====/d' | perl -pe 's/\n+/, /g'
+echo "]"

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/result.py

@@ -1,0 +1,67 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+x_snr = np.array([0, 5, 10, 15, 20])
+
+data = []
+data.append((x_snr,
+             100 - np.array([22.5, 19.7, 18.0, 16.9, 16.3]),
+             "PDCW"))
+data.append((x_snr,
+             100 - np.array([42.5, 32.7, 24.0, 21.9, 16.3]),
+             "OS-PDCW"))
+data.append((x_snr,
+             100 - np.array([79.5, 59.9, 40.1, 25.8, 19.1]),
+             "Baseline"))
+
+data_list_plot.PlotSnrdbAccData(data)
+plt.xlabel('SNR (dB)')
+plt.ylabel('Acc (100 - WER)')
+fig = plt.gcf()
+fig.savefig("./symmetric_noreverb.eps")
+subprocess.check_call('evince symmetric_noreverb.eps', shell=True)
+
+plt.figure()
+
+data = []
+data.append((x_snr,
+             100 - np.array([72.0, 55.0, 42.0, 35.0, 31.0]),
+             "PDCW"))
+data.append((x_snr,
+             100 - np.array([62.0, 49.0, 38.0, 32.0, 30.0]),
+             "OS-PDCW"))
+data.append((x_snr,
+             100 - np.array([82.0, 64.0, 49.0, 39.0, 32.0]),
+             "Baseline"))
+
+data_list_plot.PlotSnrdbAccData(data)
+plt.xlabel('SNR (dB)')
+plt.ylabel('Acc (100 - WER)')
+fig = plt.gcf()
+fig.savefig("./symmetric_reverb.eps")
+subprocess.check_call('evince symmetric_reverb.eps', shell=True)
+
+plt.figure()
+data = []
+data.append((x_snr,
+             100 - np.array([97.0, 79.0, 62.0, 49.0, 37.0]),
+             "PDCW"))
+data.append((x_snr,
+             100 - np.array([72.0, 54.0, 44.0, 38.0, 33.0]),
+             "OS-PDCW"))
+data.append((x_snr,
+             100 - np.array([83.0, 66.0, 51.0, 42.0, 33.0]),
+             "Baseline"))
+
+data_list_plot.PlotSnrdbAccData(data)
+plt.xlabel('SNR (dB)')
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/rir_plot.py

@@ -1,0 +1,176 @@
+#!/usr/bin/python
+
+import matplotlib
+import matplotlib.pyplot as plt
+import re
+import numpy as np
+
+from google3.experimental.users.chanwcom.my_pythonlib.plot_util import data_list_plot
+
+plt.rc('text', usetex=True)
+font = {"family": "sans-serif", "size": 17}
+plt.rc("font", **font)
+
+
+def ReturnFirstRIR():
+#  file_name = 'rir_data.txt'
+  file_name = 'samples_data.txt'
+  samples = []
+  with open(file_name) as fp:
+    for line in fp:
+
+      match = re.match("\s*sample:\s*\[(.*)\]\s*", line)
+
+      if match:
+        data =  match.group(1)
+        data = data.split(",")
+
+        rir_array = np.array([])
+        for elem in data:
+          rir_array = np.append(rir_array, float(elem))
+
+        return rir_array
+
+
+def DecibelToPowerRatio(decibel):
+  if decibel == -np.inf:
+    return 0.0
+
+  if decibel == np.inf:
+    return np.inf
+
+  return 10.0 ** (decibel / 10.0)
+
+
+def CutRirTailBelowThreshold(rir_array, threshold_db):
+  """ Threshold dB means that dB below the maximum"""
+
+  if threshold_db != np.inf:
+    power_signal = rir_array ** 2
+    max_power = np.max(power_signal)
+    threshold_level =  max_power * DecibelToPowerRatio(-threshold_db)
+
+    for i in np.arange(len(rir_array) - 1, -1, -1):
+      if power_signal[i] >= threshold_level:
+        break
+
+    cut_off_rir_array = rir_array[0 : i + 1]
+
+    if i + 1 <= len(rir_array) - 1:
+      ratio = 10.0 * np.log10(max_power / np.max(rir_array[i + 1 : ] ** 2))
+    else:
+      ratio = np.inf
+
+
+    print (ratio)
+
+  return cut_off_rir_array
+
+def main():
+  rir_array = ReturnFirstRIR()
+  sampling_rate_hz = 16000.0
+  time = np.linspace(0.0, len(rir_array) / sampling_rate_hz, len(rir_array))
+
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/rir_sample.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+
+
+# MTR3 room configurations
+input_sstable=/placer/prod/home/speech-placer/speech/mtr/room_configurations/mtr3/NOISY_TRAIN_3m_2mics/mtr3_3m_NOISY_TRAIN_room_config@300
+# Reverberation time should be .
+#
+# SNR 11.08 dB
+# T_60 = 0.48 seconds
+# 4000 samples
+gqui from $input_sstable proto speech.dsp.RoomConfiguration  limit 10 where 'target_source.impulse_response_at_microphone[0].sample.size_ > 3800 and target_source.impulse_response_at_microphone[0].sample.size_ < 4200' --outfile=sstable:sample_room_configuration@1

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/figures/tmp.py

@@ -1,0 +1,178 @@
+#!/usr/bin/python
+
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+import numpy as np
+
+plt.rc('text', usetex=True)
+font = {"family": "sans-serif", "size": 17}
+plt.rc("font", **font)
+
+
+fig = plt.figure()
+ax = fig.add_subplot(111, aspect = 'equal')
+
+def label(xy, text):
+    # shift x and y-value for label so that it's below right the artist
+    plt.text(xy[0] + 0.3, xy[1] - 0.3, text, ha="center", family='sans-serif', size=14)
+
+rect = mpatches.Rectangle(
+      (0.0, 0.0),
+      4.9,
+      3.8,
+      clip_on=False,
+      edgecolor='black',
+      facecolor='#c0c0ff',
+      fill=True,     # remove background
+      linewidth=4,
+)
+
+ax.add_patch(rect)
+
+#ax.grid(linestyle="--", linewidth=1)
+plt.plot(clip_on=False)
+
+microphone_pos = np.array([4.9, 3.8]) / 2.0
+
+
+x = np.linspace(1.5, 1.5, 10)
+y = np.linspace(0.0, 1.0, 10)
+plt.plot(x, y, '--', linewidth=2, color='k')
+
+x = np.linspace(0.0, 2.0, 10)
+y = np.linspace(1.0, 1.0, 10)
+plt.plot(x, y, '--', linewidth=2, color='k')
+
+
+#angle_rad = np.deg2rad(30.0)
+angle_rad = np.deg2rad(0.0)
+dist_meters = 1.5
+target_pos = (microphone_pos +
+             dist_meters * np.array([np.cos(angle_rad), np.sin(angle_rad)]))
+
+#angle_rad = np.deg2rad(75.0)
+angle_rad = np.deg2rad(45.0)
+dist_meters = 1.5
+noise_pos = (microphone_pos +
+             dist_meters * np.array([np.cos(angle_rad), np.sin(angle_rad)]))
+
+
+circle = mpatches.Circle(target_pos, 0.1, color="black")
+ax.add_patch(circle)
+label(target_pos, 'Target')
+
+circle = mpatches.Circle(noise_pos, 0.1, edgecolor='black',
+                         facecolor="gray", linewidth=2)
+ax.add_patch(circle)
+label(noise_pos, 'Noise')
+
+circle = mpatches.Circle(noise_pos, 0.1, edgecolor='black',
[…]

### 2018-06-17 room_simulator_comp_reduction_interspeech_2018/program/calculate_avg_utt_length_in_ah22m.py

@@ -1,0 +1,14 @@
+#!/usr/bin/python
+
+
+vs = 4.7
+vs_weighting = 11971984
+ime = 9.8
+ime_weighting = 6544952
+other = 3.7
+other_weighting = 980511
+
+avg = (vs * vs_weighting + ime * ime_weighting + other * other_weighting) / (vs_weighting + ime_weighting + other_weighting)
+
+print (avg)
+

### 2019-04-28 neural_frontend/doc/main.tex
updates gitignore

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2017
%
% to avoid loading the natbib package, add option nonatbib:
%\usepackage[nonatbib]{nips_2017}

\usepackage{nips_2017}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2017}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{tikz,placeins}
\usepackage{subcaption}
%\usepackage[caption = false]{subfig}
\usepackage{amssymb,amsmath,bm}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

\graphicspath{{../figures/}}

\title{WEVE: Weighted Enhancement Using Variance Estimation}

%\renewcommand{\vec}[1]{\mathbf{#1}}

\newcommand{\chanwcom}{{C. Kim}}
\renewcommand{\topfraction}{0.85}
\renewcommand{\textfraction}{0.1}
\renewcommand{\floatpagefraction}{0.85}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}
This paper presents a new robust neural frontend layer referred to as Power
Normalized Neural Frontend (PNNF) for robust speech recognition. PNNF
is implemented as a layer in an end-to-end all neural-network speech 
recognition system. For speech recognition, features such as Mel Filterbank
Cepstral Coefficient (MFCC) or log-Mel have been used very widely.
More recently, features motivated by human auditory processing have shown
improvement under certain conditions. Nevertheless, these auditory
features are constructed using signal processing blocks with hand-crafted
parameters for certain conditions. Therefore, the performance is not
always optimal for various kind of acoustic conditions.
 PNNF frontend layer is loosely motivated by human auditory system.
This processing uses the concept of the auditory masking and the auditory nonlinearity.
However, instead of directly using theories and parameters about human auditory masking,
neural networks make decision about it from the training data.
Even though the structure of the PNNF layer is very simple, this layer
significantly boosts the performance of the speech recognition system.
\end{abstract}

\section{Introduction}

\section{Feature enhancement}

In the feature enhancement process, we estimate a clean feature 
$\vec{y}$ given a corrupt feature $\vec{x}$.

In this case, the following $L_2$ norm is widely used:
\begin{align}
  l(\vec{y}, \vec{x}) = 
\end{align}

Feature mapping is a process of mapping noisy feature vectors
to clean feature vectors to enhance robustness
\cite{C_Kim_ASRU_2009_1, k_han_taslp_2015_00, k_han_icassp_2014_00}.
This procedure may be formulated by the following equation:
\begin{align}
  Y() = X()
\end{align}

From noisy features, we may infer 
Another

Masking and feature mapping are closely related techniques.
In feature mapping, enhanced features are predicted from
noisy features using machine learning models
The masking-based approaches with
Joint Adaptive Training (JAT) have been shown
to be effective to a large training set
\cite{a_narayanan_interspeech_2015_1}.

\section{Structure of the neural front-end}

\subsection{Neural nonlinearity}
In this section, we describe our neural nonlinearity algorithm. 
\begin{align}
  \vec{q[m, l]} = \vec{x[m, l]} ^ {\vec{\alpha}} 
\end{align}

\subsection{Neural background removal}
In this section, we describe our Neural Background Removal (NBR) approach.
Fig. \label{fig:nbr_diagram} shows the structure of the NBR processing.

$\vec{q}$ is the non-linearity output defined in

\begin{figure}
    \centering
    \resizebox{80mm}{!}{%
         \input{../figures/background_removal.tex}} %
    \caption {
      The structure of the Neural Background Removal (NBR) block.
      \label{fig:nbr_diagam}
    }
    %\end{center}
\end{figure}

\subsection{  }

NIPS requires electronic submissions.  The electronic submission site
is
\begin{center}
  \url{https://cmt.research.microsoft.com/NIPS2017/}
\end{center}

Please read carefully the instructions below and follow them
faithfully.

\section{The structure of the SPL algorithm}

Fig. \label{fig:entire_diagram} shows the block diagram for
enhancing the noisy feature.

%\begin{figure}
%    \centering
%    \resizebox{80mm}{!}{%
%         \input{../figures/entire_diagram.tex}} %
%    \caption {
%      The structure of feature enhancement using peak
%      value normalization and LSTMs.
%      \label{fig:entire_diagam}
%    }
%    %\end{center}
%\end{figure}

Fig. \ref{fig:entire_diagram} shows the structure for enhancing
noisy feature.

\subsection{Simulated utterance generation}
We use the room simulation system introduced in
\cite{C_Kim_INTERSPEECH_2017_1} to generate noisy speech
from clean speech.
\begin{align}
  y[n]
\end{align}
For 
\subsection{Review of the Room Simulator for Data Augmentation}
%
%
%\begin{figure}
%  \centering
%    \begin{subfigure}{\linewidth}
%      \centering
%      \includegraphics[width=70mm]{room_diagram.eps}
%      \caption{}
%      \label{fig:room_diagram}
%    \end{subfigure}
%   \\
%    \begin{subfigure}{\linewidth}
%      \centering
%      \includegraphics[width=70mm]{image_method.eps}
%      \caption{}
%      \label{fig:image_method}
%    \end{subfigure}
%    \caption{
%    (a) A simulated room: There may be multiple microphones, a single target
%    sound source, multiple noise sources in a cuboid-shape room with
%    acoustically reflective walls. (b) A diagram showing the location
%    of the real and the virtual sound sources assuming that the walls
%    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
%  \vspace{-10mm}
%\end{figure}
%
%
In this section, we briefly review the structure of the Google
Room Simulator for generating simulated utterances
to train acoustic models for speech recognition systems
\cite{C_Kim_INTERSPEECH_2017_1}. We assume a room of a
rectangular cuboid-shape as shown in Fig. \ref{fig:room_diagram}.
Assuming that all the walls of a room reflect acoustically uniformly,
we use the image method to model the Room Impulse Responses (RIRs)
\cite{J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007, S_G_McGovern_RIR}.

Fig. \ref{fig:image_method} shows how virtual sources
appearing as empty circles are constructed in the image method.
Even though the virtual rooms appear to be created in two-dimensions
in Fig. \ref{fig:image_method}, in the ``\emph{Room Simulator}",
they are constructed in three-dimensions. For example, in our
work for training the acoustic model for Google Home, we consider
$17 \times 17 \times 17 = 4913$ virtual rooms for RIR calculation
\cite{C_Kim_INTERSPEECH_2017_1}.
Following the image method, the impulse response is calculated
using the following equation
\cite{ J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007}:
\begin{align}
    h[n] = \sum_{i = 0}^{I-1} \frac{r^{g_i}}{d_i}
    \delta \left[n -\left \lceil{\frac{d_i f_s}{c_0}}\right \rceil \right],
      \label{eq:h_n_calculation}
\end{align}
where $i$ is the index of each virtual sound source, and $d_i$ is the distance
from that sound source to the microphone, $r$ is
the reflection coefficient of the wall, $g_i$ is
the number of the reflections
to that sound source, $f_s$ is the sampling rate of the RIR, and $c_0$ is the
speed of sound in the air. We use the value of $f_s = 16,000$ \textit{Hz} and
$c_0 = 343$ \textit{m/s} for the room simulator \cite{B_Li_INTERSPEECH_2017_1}.
For $d_i$, $r$, we use numbers created by a random number generator
following specified distributions for each impulse response \cite{C_Kim_INTERSPEECH_2017_1}.

Assuming that there are $I$ sound sources including one target
source and $J$ microphones, the received signal at microphone
$j$ is given by:
\begin{align}
  y_j[n] =  \sum_{i=0}^{I-1} \alpha_{ij} \left(h_{ij}[n] * x_i[n]\right).
  \label{eq:y_j_def}
\end{align}
Since we used a two-microphones system in
\cite{B_Li_INTERSPEECH_2017_1, C_Kim_INTERSPEECH_2017_1},
$J$ is two, and for the number noise sources, we used a value from zero
up to three \cite{C_Kim_INTERSPEECH_2017_1}.
%

\subsection{Feature extraction}

Even though the log-mel coefficients have been widely used
as features for speech recognition \cite{sbdavisandpm1980},
the log non-linearity has a disadvantage in that the value
diverges to negative infinity as the mel filterbank coefficient
approaches zero \cite{C_Kim_IEEETran_2016_1}.
Thus, we use the power-law nonlinearity
rather than the log-nonlinearity:
\begin{align}
  q[m, l] =  (p[m, l])^{\frac{1}{15}}
  \label{eq:power_law_nonlineartiy}
\end{align}
We use the power coefficient of $\frac{1}{15}$ as in
\cite{C_Kim_IEEETran_2016_1, C_Kim_ICASSP_2012_1}.

\subsection{Feature normalization using the peak-value}

The power-mel coefficients $q_x[m, l]$ and $q_y[m, l]$
are obtained from the clean and the simulated noisy
speech $x[n]$ and $y[n]$ respectively. $q_{x, \text{peak}}$
and $q_{y, \text{peak}}$

\section{Estimation of the expected value and the variance
  of the enhanced feature from the noisy feature}
\label{sec:estimation}

\begin{figure}
    \centering
    \resizebox{80mm}{!}{%
         \input{../figures/training.tex}} %
    \caption {
      Training of neural networks to estimate the clean feature and error ratio from corrupt feature
      \label{MFCCPNCCComparison}
    }
    %\end{center}
\end{figure}

In this section, we discuss how to predict the clean feature and the
error ratio from the corrupt feature. Let us denote the clean target feature,
the corrupt feature by $\boldsymbol{x}, \boldsymbol{y}$ respectively.

Using the room simulation system described in \cite{C_Kim_INTERSPEECH_2017_1},
we create a pair of clean and
corrupt utterances. Log-mel [XX] features are calculated from these original clean
and corrupt utterances. Let us denote the clean feature by $\boldsymbol{t}_i$ and
the simulated corrupt feature by $\boldsymbol{x}_i$, respectively where $i$ is the
utterance index. The training set is represented by the following set:
\begin{align}
  \mathcal{T} = \{<\boldsymbol{x}_i, \boldsymbol{t}_i>| 0 \le i \le N - 1\}
\end{align}
where $N$ is the number of training examples.

In the ECE algorithm, we first estimate the true target $\boldsymbol{t}_i$. The
estimation error is defined by the following equation:
\begin{align}
  \boldsymbol{e}_i =  \boldsymbol{t}_i - \boldsymbol{x}_i, \quad 0 \le i \le N - 1
\end{align}

The norm of the error vector $\boldsymbol{e}_i$ would be generally large when
the norm of the estimated clean feature is large.

Thus, instead of trying to estimate the error itself, the neural network tries to
estimate the error ratio given as follows:

\begin{align}
  r_i = {}{}
\end{align}

\section{Generation of simulated clean and noisy data sets}
\label{gen_inst}

To train neural networks described in section \ref{sec:estimation}, we
need a training set consisting of pairs of clean speech and noisy speech.
Unfortunately, it is not easy to have such a training set from real speech
utterances. Thus, we use the simulation system described in
\cite{C_Kim_INTERSPEECH_2017_1} to synthetically generate noisy speech
utterances from the clean speech utterances.

In our application, for clean training set, we used Wall Street Journal (WSJ)
si-284. For noise set, we used the Resource Management 1 (RM1)
\cite{price_p_ldc_1993} 50 \% of time 
and DEMAND noise [TODO(chanwcom) Adds reference] for the remaining 50 \% of time.

TODO(chanwcom) Cite DEMAND noise set.

%
%
%
%\begin{figure*}
%  \centering
%    \begin{subfigure}[\label{fig:randomly_selected_grid_coordinates}]{0.5\textwidth} {
%        \includegraphics[width=\textwidth]{target_estimation}}
%    \caption{Grid from random-sampling}
%    \end{subfigure}
%   % \begin{subfigure}[\label{fig:intersection_point}]{0.5\textwidth} {
%   %   \includegraphics[width=\textwidth]{intersection_point}}
%   % \caption{Calculation of grid coordinates}
%   % \end{subfigure}
%  \caption {Random Grid Sampling}
%\end{figure*}
%
%
%
\section{Estimation of the optimal weight in the EFW algorithm}
In this section, we describe the procedure of feature weighting approach.
Suppose that the feature before enhancement is represented by $\vec{x}$.
Let us represent the inference neural network to estimate the target by
$\mathcal{T}$.

\begin{align}
  \mathcal{X} = \{  \}
\end{align}

Instead of directly using the enhanced feature $\widehat{\vec{y}}$, we consider
the following interpolated feature $\bm{z}$ from the original corrupt
input $\bm{x}$ and .
\begin{align}
  \vec{z} = \vec{w} \odot \widehat{\vec{y}} \ + (1 - \vec{w}) \odot \vec{x} 
    \label{eq:vec_z}
\end{align}
where $\odot$ denotes the Hadamard product (entry-wise product).

Let us denote the estimated variance vector by $\hat{\vec{v}}$:
\begin{align}
  \hat{\vec{v}} & = \text{Var}[\widehat{\vec{y}}] \nonumber \\
                & = E[(y - y)^2 | \vec{x}[0], \vec{x}[1], ... \vec{x}[T]]
     \label{eq:vec_v}
\end{align}

In our discussion, let us assume that the expectation of $\hat{\vec{y}}$ is the
same as the true target $\vec{y}$.
\begin{align}
  E[\widehat{\vec{y}}] = \vec{y}  \label{eq:expectation_of_y}
\end{align}

Now, let us obtain the expected value of $\vec{z}$ from
\eqref{eq:vec_z} and \eqref{eq:expectation_of_y}
\begin{align}
  E[\vec{z}] = (1 - \vec{w}) \odot (\vec{x} - \vec{y})
\end{align}
Thus, the bias of $\vec{z}$ is given by:
\begin{align}
  Bias_{\vec{z}} & = E[\vec{z}] - t \nonumber \\
                 & = \vec{w} \odot (\widehat{\vec{y}} - \vec{y})
\end{align}

From \eqref{eq:vec_z} and \eqref{eq:vec_v}, the variance of $\vec{z}$ is given by:
\begin{align}
  Var_{\vec{z}} = \vec{v} \odot w \odot w.
\end{align}
The mean squared error of the $i$-th element of the $\vec{z}$ is given by:
\begin{align}
  MSE_{\vec{z_i}} & = Bias_{\vec{z_i}}^2 + Var_{\vec{z_i}} \nonumber \\
                 & =  \left[(\vec{x}_i - \vec{y}_i) ^ 2
                    + \vec{v}_i^2 \right] \vec{w}_i^{2}
                    - 2 (\vec{x}_i - \vec{y}_i)^{2}  \vec{w}_i
                    + (\vec{x}_i - \vec{y}_i)^{2}
 \label{eq:mse_z_i}
\end{align}
Since the above equation \eqref{eq:mse_z_i} is a quadratic equation with
respect to $\vec{w}_i$, we may find that the minimum value of $MSE_{\vec{z_i}}$
is obtained when $\vec{w}_i$ has the following value:
\begin{align}
  \vec{w}_i = \frac{(\vec{x}_i - \vec{y}_i)^2}{(\vec{x}_i - \vec{y}_i)^2 + \vec{v}_i}
\end{align}

Thus, the final form of the estimated vector $\widehat{\vec{z}}$ becomes:
\begin{align}
  \widehat{\vec{z}} = \widehat{\vec{w}} \odot \widehat{\vec{y}}
    \ + (1 - \widehat{\vec{w}}) \odot \vec{x}
\end{align}
where
\begin{align}
  \widehat{\vec{w}} = {(\vec{x} - \vec{y})^{\odot 2}}
    \left[(\vec{x} - \vec{y})^{\odot 2}+ \vec{v}\right]^{\odot -1}.
\end{align}

Sequence enhancement

The feature enhancement is to map a sequence of corrupt features $\mathbf{X}$.
\begin{subequations}
  \begin{align}
    \mathbf{X} = \left(\vec{x}[0], \vec{x}[1], \cdots, \vec{x}[M-1] \right)  \\
    \mathbf{Y} = \left(\vec{y}[0], \vec{y}[1], \cdots, \vec{y}[M-1] \right) 
  \end{align}
\end{subequations}

\subsubsection*{Acknowledgments}

\section*{References}

References follow the acknowledgments. Use unnumbered first-level
heading for the references. Any choice of citation style is acceptable
as long as you are consistent. It is permissible to reduce the font
size to \verb+small+ (9 point) when listing the references. {\bf
  Remember that you can go over 8 pages as long as the subsequent ones contain
  \emph{only} cited references.}
\medskip

\small

\clearpage
\newpage
\bibliographystyle{plain}
\bibliography{../../common_bib_file/common_bib_file}

\end{document}

### 2019-04-28 icml_2018_monolitic_end_to_end/doc/main.tex
Updates the paper

--- 2019-04-28 neural_frontend/doc/main.tex
@@
 
-\title{WEVE: Weighted Enhancement Using Variance Estimation}
+\title{A state of the art end-to-end speech recognition algorithm with
+a homogenous structure.}
 
@@
 \begin{abstract}
-This paper presents a new robust neural frontend layer referred to as Power
-Normalized Neural Frontend (PNNF) for robust speech recognition. PNNF
-is implemented as a layer in an end-to-end all neural-network speech 
-recognition system. For speech recognition, features such as Mel Filterbank
-Cepstral Coefficient (MFCC) or log-Mel have been used very widely.
-More recently, features motivated by human auditory processing have shown
-improvement under certain conditions. Nevertheless, these auditory
-features are constructed using signal processing blocks with hand-crafted
-parameters for certain conditions. Therefore, the performance is not
-always optimal for various kind of acoustic conditions.
- PNNF frontend layer is loosely motivated by human auditory system.
-This processing uses the concept of the auditory masking and the auditory nonlinearity.
-However, instead of directly using theories and parameters about human auditory masking,
-neural networks make decision about it from the training data.
-Even though the structure of the PNNF layer is very simple, this layer
-significantly boosts the performance of the speech recognition system.
+TODO(chanw.com) Revise the abstract.
+This paper proposes a new end-to-end speech recognition system referred to
+as Recurrent neural network Sequence Classification (RSC). Recently, end-to-end speech
+recognition systems have been gaining more attention from researchers and
+several different structures have been proposed. Typical examples  
+include Connectionist Temporal Classification (CTC), Recurrent Neural Network
+  Transducer (RNN-T), and Sequence-to-Sequence Modeling using the attention
+mechanism. The CTC-based approaches are using the CTC loss assuming the
+conditional independence property. Although the structure of CTC is simpler
+than other end-to-end systems, the performance is worse due to this conditional
+independence assumption. RNN-T and attention-based approaches have distinct
+components such as the prediction network  and encoder in RNN-T, and
+the encoder, the decoder, and the attention layer in the attention-based model.
+Compared to these models, SHC has a homogeneous structure from the bottom to 
+the top layer. LSTM and max-pooling layer are repeated followed by the top
+softmax layer. The embedded softmax output is fed back as input of each RNN
+layer. The training starts with flat initialization and alignment is made
+after every epoch. The loss is the Cross Entropy (CE) loss using this 
+alignment result. In our experimental results, SHC algorithm has shown 
+better performance than more complicated attention-based end-to-end speech
+recognition system. Another major advantage is training is significantly
+faster.
 \end{abstract}
@@
 
-\section{Feature enhancement}
+Recently, deep neural network has significantly improved the performance
+of speech recognition systems \cite{}.
 
-In the feature enhancement process, we estimate a clean feature 
-$\vec{y}$ given a corrupt feature $\vec{x}$.
-
-In this case, the following $L_2$ norm is widely used:
-\begin{align}
-  l(\vec{y}, \vec{x}) = 
-\end{align}
-
-Feature mapping is a process of mapping noisy feature vectors
-to clean feature vectors to enhance robustness
-\cite{C_Kim_ASRU_2009_1, k_han_taslp_2015_00, k_han_icassp_2014_00}.
-This procedure may be formulated by the following equation:
-\begin{align}
-  Y() = X()
-\end{align}
-
-From noisy features, we may infer 
-Another
-
-Masking and feature mapping are closely related techniques.
-In feature mapping, enhanced features are predicted from
-noisy features using machine learning models
-The masking-based approaches with
-Joint Adaptive Training (JAT) have been shown
-to be effective to a large training set
-\cite{a_narayanan_interspeech_2015_1}.
-
-\section{Structure of the neural front-end}
-
-\subsection{Neural nonlinearity}
-In this section, we describe our neural nonlinearity algorithm. 
-\begin{align}
-  \vec{q[m, l]} = \vec{x[m, l]} ^ {\vec{\alpha}} 
-\end{align}
-
-\subsection{Neural background removal}
-In this section, we describe our Neural Background Removal (NBR) approach.
-Fig. \label{fig:nbr_diagram} shows the structure of the NBR processing.
-
-$\vec{q}$ is the non-linearity output defined in
+\section{Review of end-to-end speech recognition systems}
 
@@
     \centering
-    \resizebox{80mm}{!}{%
-         \input{../figures/background_removal.tex}} %
+    \resizebox{40mm}{!}{%
+         \input{../figures/ctc.tex}} %
     \caption {
-      The structure of the Neural Background Removal (NBR) block.
-      \label{fig:nbr_diagam}
+      The entire structure of the sequence homogeneously-structured classifier
+      (SHC).
+      \label{fig:ctc_diagram}
+    }
+    %\end{center}
+\end{figure}
+Recently, there have been growing interests in end-to-end speech
+recognition systems.  [CITE] Fig. \ref{fig:ctc_diagram} shows the
+entire structure of the Connectionist Temporal Classification (CTC) 
+and the attention-based end-to-end speech recognition system.
+
+\section{Sequence Homogeneously-Structured Classifier}
+Figure \ref{} shows the entire structure of the SHC. Speech-recognition
+task can be also considered as a
+
+\subsection{The structure of the Sequence Homogeneously-Structured Classifier}
+
+Fig. \label{fig:entire_diagram} shows the block diagram for
+enhancing the noisy feature.
+
+\begin{figure}
+    \centering
+    \resizebox{50mm}{!}{%
+         \input{../figures/shc_diagram.tex}} %
+    \caption {
+      The entire structure of the sequence homogeneously-structured classifier
+      (SHC).
+      \label{fig:shc_diagram}
     }
@@
 
-\subsection{  }
+Fig. \ref{fig:shc_diagram} shows the structure of the SHC algorithm. The
+structure is very simple and somewhat similar to that of CTC shown in TODO
 
-NIPS requires electronic submissions.  The electronic submission site
-is
-\begin{center}
-  \url{https://cmt.research.microsoft.com/NIPS2017/}
-\end{center}
+\subsection{Training of the Sequence Homogeneously-Structured Classifier}
+In this section, we describe how to train SHC. The procedure is summarized
+in the following table.
 
-Please read carefully the instructions below and follow them
-faithfully.
-
-\section{The structure of the SPL algorithm}
-
-Fig. \label{fig:entire_diagram} shows the block diagram for
-enhancing the noisy feature.
-
-%\begin{figure}
-%    \centering
-%    \resizebox{80mm}{!}{%
-%         \input{../figures/entire_diagram.tex}} %
-%    \caption {
-%      The structure of feature enhancement using peak
-%      value normalization and LSTMs.
-%      \label{fig:entire_diagam}
-%    }
-%    %\end{center}
-%\end{figure}
-
-Fig. \ref{fig:entire_diagram} shows the structure for enhancing
-noisy feature.
-
-\subsection{Simulated utterance generation}
-We use the room simulation system introduced in
-\cite{C_Kim_INTERSPEECH_2017_1} to generate noisy speech
-from clean speech.
-\begin{align}
-  y[n]
-\end{align}
-For 
+\section{Structure of the Recurrent Sequence Recognizer}
 \subsection{Review of the Room Simulator for Data Augmentation}
@@
 %
-%\begin{figure}
-%  \centering
-%    \begin{subfigure}{\linewidth}
-%      \centering
-%      \includegraphics[width=70mm]{room_diagram.eps}
-%      \caption{}
-%      \label{fig:room_diagram}
-%    \end{subfigure}
-%   \\
-%    \begin{subfigure}{\linewidth}
-%      \centering
-%      \includegraphics[width=70mm]{image_method.eps}
-%      \caption{}
-%      \label{fig:image_method}
-%    \end{subfigure}
-%    \caption{
-%    (a) A simulated room: There may be multiple microphones, a single target
-%    sound source, multiple noise sources in a cuboid-shape room with
-%    acoustically reflective walls. (b) A diagram showing the location
-%    of the real and the virtual sound sources assuming that the walls
-%    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
-%  \vspace{-10mm}
-%\end{figure}
+\begin{figure}
+  \centering
+    \begin{subfigure}{\linewidth}
+      \centering
+      \includegraphics[width=70mm]{room_diagram.eps}
+      \caption{}
+      \label{fig:room_diagram}
+    \end{subfigure}
+   \\
+    \begin{subfigure}{\linewidth}
+      \centering
+      \includegraphics[width=70mm]{image_method.eps}
+      \caption{}
+      \label{fig:image_method}
+    \end{subfigure}
+    \caption{
+    (a) A simulated room: There may be multiple microphones, a single target
+    sound source, multiple noise sources in a cuboid-shape room with
+    acoustically reflective walls. (b) A diagram showing the location
+    of the real and the virtual sound sources assuming that the walls
+    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
+  \vspace{-10mm}
+\end{figure}
 %
 %
-In this section, we briefly review the structure of the Google
-Room Simulator for generating simulated utterances
-to train acoustic models for speech recognition systems
-\cite{C_Kim_INTERSPEECH_2017_1}. We assume a room of a
-rectangular cuboid-shape as shown in Fig. \ref{fig:room_diagram}.
-Assuming that all the walls of a room reflect acoustically uniformly,
-we use the image method to model the Room Impulse Responses (RIRs)
-\cite{J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007, S_G_McGovern_RIR}.
+%
+\subsection{Viterbi alignment and N-best alignment}
 
-Fig. \ref{fig:image_method} shows how virtual sources
-appearing as empty circles are constructed in the image method.
-Even though the virtual rooms appear to be created in two-dimensions
-in Fig. \ref{fig:image_method}, in the ``\emph{Room Simulator}",
-they are constructed in three-dimensions. For example, in our
-work for training the acoustic model for Google Home, we consider
-$17 \times 17 \times 17 = 4913$ virtual rooms for RIR calculation
-\cite{C_Kim_INTERSPEECH_2017_1}.
-Following the image method, the impulse response is calculated
-using the following equation
-\cite{ J_Allen_JASA_1979, E_A_Lehmann_ASPAA_2007}:
-\begin{align}
-    h[n] = \sum_{i = 0}^{I-1} \frac{r^{g_i}}{d_i}
-    \delta \left[n -\left \lceil{\frac{d_i f_s}{c_0}}\right \rceil \right],
-      \label{eq:h_n_calculation}
-\end{align}
-where $i$ is the index of each virtual sound source, and $d_i$ is the distance
-from that sound source to the microphone, $r$ is
-the reflection coefficient of the wall, $g_i$ is
-the number of the reflections
-to that sound source, $f_s$ is the sampling rate of the RIR, and $c_0$ is the
-speed of sound in the air. We use the value of $f_s = 16,000$ \textit{Hz} and
-$c_0 = 343$ \textit{m/s} for the room simulator \cite{B_Li_INTERSPEECH_2017_1}.
-For $d_i$, $r$, we use numbers created by a random number generator
-following specified distributions for each impulse response \cite{C_Kim_INTERSPEECH_2017_1}.
-
-Assuming that there are $I$ sound sources including one target
-source and $J$ microphones, the received signal at microphone
-$j$ is given by:
-\begin{align}
-  y_j[n] =  \sum_{i=0}^{I-1} \alpha_{ij} \left(h_{ij}[n] * x_i[n]\right).
-  \label{eq:y_j_def}
-\end{align}
-Since we used a two-microphones system in
-\cite{B_Li_INTERSPEECH_2017_1, C_Kim_INTERSPEECH_2017_1},
-$J$ is two, and for the number noise sources, we used a value from zero
-up to three \cite{C_Kim_INTERSPEECH_2017_1}.
-%
+In conventional frame-wise CE-training, forced-alignment 
+has been performed to obtain the frame-level acoustic unit  
+boundaries. TODO(chanwcom) Even though the Viterbi algorithm
+has advantages in simplicity and efficiency, it is based on
+the conditional independence assumption.
 
@@
 \cite{C_Kim_IEEETran_2016_1, C_Kim_ICASSP_2012_1}.
-
-\subsection{Feature normalization using the peak-value}
-
-The power-mel coefficients $q_x[m, l]$ and $q_y[m, l]$
-are obtained from the clean and the simulated noisy
-speech $x[n]$ and $y[n]$ respectively. $q_{x, \text{peak}}$
-and $q_{y, \text{peak}}$
-
-\section{Estimation of the expected value and the variance
-  of the enhanced feature from the noisy feature}
-\label{sec:estimation}
-
-\begin{figure}
-    \centering
-    \resizebox{80mm}{!}{%
-         \input{../figures/training.tex}} %
-    \caption {
-      Training of neural networks to estimate the clean feature and error ratio from corrupt feature
-      \label{MFCCPNCCComparison}
-    }
-    %\end{center}
-\end{figure}
 

### 2019-04-28 icml_2018_monolitic_end_to_end/doc/main.tex
Updates main file

@@
 \usepackage{subcaption}
+\usepackage{algpseudocode}
 %\usepackage[caption = false]{subfig}
@@
 
-\section{Structure of the Recurrent Sequence Recognizer}
-\subsection{Review of the Room Simulator for Data Augmentation}
-%
-%
-\begin{figure}
-  \centering
-    \begin{subfigure}{\linewidth}
-      \centering
-      \includegraphics[width=70mm]{room_diagram.eps}
-      \caption{}
-      \label{fig:room_diagram}
-    \end{subfigure}
-   \\
-    \begin{subfigure}{\linewidth}
-      \centering
-      \includegraphics[width=70mm]{image_method.eps}
-      \caption{}
-      \label{fig:image_method}
-    \end{subfigure}
-    \caption{
-    (a) A simulated room: There may be multiple microphones, a single target
-    sound source, multiple noise sources in a cuboid-shape room with
-    acoustically reflective walls. (b) A diagram showing the location
-    of the real and the virtual sound sources assuming that the walls
-    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
-  \vspace{-10mm}
-\end{figure}
-%
-%
-%
 \subsection{Viterbi alignment and N-best alignment}
 
-In conventional frame-wise CE-training, forced-alignment 
-has been performed to obtain the frame-level acoustic unit  
-boundaries. TODO(chanwcom) Even though the Viterbi algorithm
+In conventional frame-wise CE-training, Viterbi alignment 
+(a.k.a forced alignment) has been performed to obtain the frame-level 
+acoustic unit  boundaries TODO(chanwcom). Even though the Viterbi algorithm
 has advantages in simplicity and efficiency, it is based on
 the conditional independence assumption.
+
+In TFSC, we propose the following N-best alignment approach rather than
+the Viterbi alignment algorithm to find the alignment information.
+
+\begin{algorithmic}
+
+\For {$m = 0, . . . , M-1$}
+	\For {$l = 0, . . . , N_b-1$}
+		\State {$\pi^{(l)}[m]$}
+	\EndFor
+\EndFor
+
+\If {$i\geq maxval$}
+    \State $i\gets 0$
+\Else
+    \If {$i+k\leq maxval$}
+        \State $i\gets i+k$
+    \EndIf
+\EndIf
+\label{algorithm:n_best_alignment}
+\end{algorithmic}
 

### 2019-05-04 icml_2018_monolitic_end_to_end/doc/tex_to_pdf.sh
Removes deprecated template

@@ -1,7 +1,0 @@
-#!/bin/bash
-
-latex main
-bibtex main
-latex main
-latex main
-dvipdf main

### 2019-05-04 none_feedback_sequence_classifier/doc/main.tex
Updates the paper

--- 2019-04-28 icml_2018_monolitic_end_to_end/doc/main.tex
@@
 
-\usepackage{nips_2017}
+\usepackage{neurips_2019}
 
@@
 
-\newcommand{\chanwcom}{{C. Kim}}
+\newcommand{\chanwcom}{Chanwoo Kim}
 \renewcommand{\topfraction}{0.85}
@@
 the encoder, the decoder, and the attention layer in the attention-based model.
-Compared to these models, SHC has a homogeneous structure from the bottom to 
+Compared to these models, FSC has a homogeneous structure from the bottom to 
 the top layer. LSTM and max-pooling layer are repeated followed by the top
@@
 after every epoch. The loss is the Cross Entropy (CE) loss using this 
-alignment result. In our experimental results, SHC algorithm has shown 
+alignment result. In our experimental results, FSC algorithm has shown 
 better performance than more complicated attention-based end-to-end speech
@@
 \section{Introduction}
+Recently, there has been tremendous improvements in speech recognition
+systems fueled by advances in deep neural networks
+\cite{
+  Yu2013FeatureLearningDNN, 
+  g_hinton_ieee_signal_processing_mag_2012,
+  Seltzer2013DNNAurora4, 
+  t_sainath_taslp_2017_00,
+  t_sainath_book_chapter_2017_00,
+  v_vanhoucke_nips_workshop_2011_00}.
 
-Recently, deep neural network has significantly improved the performance
-of speech recognition systems \cite{}.
+TODO(chanw.com) Talk about the AI speakers.
 
-\section{Review of end-to-end speech recognition systems}
+TODO(chanw.com) Talk about the advancements of the end-to-end systems.
+
+Recently, it has been frequently observed that if 
+sequence-to-sequence end-to-end ASR systems are trained on sufficiently 
+large amounts of acoustic training data, they can outperform
+conventional HMM-DNN/RNN hybrid systems \cite{c_chiu_icassp_2018_00, 
+c_kim_interspeech_2019_00}.
+
+Recently, we observed that training with large-scale noisy data generated
+by a \textit{Room Simulator} \cite{C_Kim_INTERSPEECH_2017_1}
+improves speech recognition accuracy dramatically.
+This system has been successfully employed
+for training acoustic models for Google Home or Google voice
+search \cite{C_Kim_INTERSPEECH_2017_1}.
+
+\section{Review on sequence-to-sequence speech recognition algorithms}
+
+In this section, we review well-known {\it sequence-to-sequence} algorithms
+used in speech recognition.
+\cite{
+j_chorowski_nips_2015_00, 
+a_graves_corr_2012_00, 
+y_he_icassp_2019_00,
+r_prabhavalkar_interspeech_2017_00}. 
+A sequence-to-sequence
+model maps a sequence of input acoustic features into a sequence 
+of graphemes or words \cite{r_prabhavalkar_interspeech_2017_00}. 
+We denote a sequence of input acoustic feature vectors by 
+$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels by 
+$\mathcal{Y}_{0}^{L-1}$:
+\begin{subequations}
+  \begin{align}
+    \mathcal{X}_{0}^{}  =  
+      \left\{\vec{x}[0], \, \vec{x}[1], 
+        \, \cdots, \, \vec{x}[M-1] \right\},  \\
+    \mathcal{Y}_{0}^{}  =  
+      \left\{y_0, \, y_1, \,  \cdots, \, y_{L-1} \right\},
+  \end{align}
+\end{subequations}
+where $M$ is the number of frames in the input feature sequence and
+$L$ is the number of labels in the output target sequence. In Fig. 
+\ref{fig:ctc_diagram} $\sim$ \ref{fig:attention_diagram}, we show
+block diagrams of CTC \cite{a_graves_icml_2006_00}, 
+RNN-T \cite{a_graves_corr_2012_00, a_graves_icassp_2013_00}, and 
+the attention-based model 
+\cite{
+j_chorowski_nips_2015_00,
+w_chan_icassp_2016_00} respectively. CTC in Fig. \ref{fig:ctc_diagram} 
+and RNN-T in Fig. \ref{fig:rnn_t_diagram} are {\it frame-synchronous}, 
+which means that the ASR system generates the output target for each 
+input frame.
+
+\subsection{Connectionist Temporal Classification}
+
+Fig. \ref{fig:ctc_diagram} shows the entire structure of the 
+Connectionist Temporal Classification (CTC) 
+\cite{a_graves_icml_2006_00}. In CTC, we use the following CTC loss
+\cite{a_graves_icml_2006_00, y_he_icassp_2019_00}:
+\begin{align}
+  P\left(\mathcal{Y}_{0}^{L-1} | \mathcal{X}_{0}^{M-1}\right) = 
+    \sum_{\mathcal{Z}_{0}^{M-1} \in 
+      \mathcal{A}_{CTC} 
+        \left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1} \right)}
+          \Pi_{m=0}^{M-1}
+            P\left(\vec{z}[m] | \mathcal{X}_{0}^{M-1} \right),
+\end{align}
+where $\mathcal{A}_{CTC} \left(\mathcal{X}_{0}^{M-1}, 
+\mathcal{Y}_{0}^{L-1} \right)$ correspond to frame-level alignments
+of length $M$ such that removing blanks and repeated symbols from 
+$\mathcal{Z}_{0}^{M-1}$ yields $\mathcal{Y}_{0}^{L-1}$.
 
@@
   \centering
-    \resizebox{40mm}{!}{%
-         \input{../figures/ctc.tex}} %
+  \begin{subfigure}[b]{0.35\textwidth}
+    \centering
+    \resizebox{23mm}{!}{
+      \input{../figures/ctc_diagram.tex}
+    } 
     \caption {
-      The entire structure of the sequence homogeneously-structured classifier
-      (SHC).
+      Connectionist Temporal Classification (CTC) Model.
       \label{fig:ctc_diagram}
     }
-    %\end{center}
-\end{figure}
-Recently, there have been growing interests in end-to-end speech
-recognition systems.  [CITE] Fig. \ref{fig:ctc_diagram} shows the
-entire structure of the Connectionist Temporal Classification (CTC) 
-and the attention-based end-to-end speech recognition system.
+  \end{subfigure}
+  \begin{subfigure}[b]{0.60\textwidth}
+    \centering
+    \resizebox{78mm}{!}{
+      \input{../figures/rnn_t_diagram.tex}
+    }
+    \caption {
+      RNN-T Model.
+      \label{fig:rnn_t_diagram}
+    }
+  \end{subfigure}
 
-\section{Sequence Homogeneously-Structured Classifier}
-Figure \ref{} shows the entire structure of the SHC. Speech-recognition
-task can be also considered as a
+  \begin{subfigure}[b]{0.55\textwidth}
+    \centering
+    \resizebox{53mm}{!}{
+      \input{../figures/attention_diagram.tex}
+    }
+    \caption {
+      Attention-based Model.
+      \label{fig:attention_diagram}
+    }
+  \end{subfigure}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+    \resizebox{26mm}{!}{
+      \input{../figures/fsc_diagram.tex}
+    }
+    \caption {
+      Feedback Sequence Classifier (FSC) Model.
+      \label{fig:fsc_diagram}
+    }
+  \end{subfigure}
+  \caption{
+    Comparison of block diagrams of different sequence-to-sequence speech
+    recognition approaches.
+    The proposed Feedback Sequence Classifier (FSC) is shown in 
+    Fig. \ref{fig:fsc_diagram}.
+  }
 
-\subsection{The structure of the Sequence Homogeneously-Structured Classifier}
-
-Fig. \label{fig:entire_diagram} shows the block diagram for
-enhancing the noisy feature.
-
-\begin{figure}
-    \centering
-    \resizebox{50mm}{!}{%
-         \input{../figures/shc_diagram.tex}} %
-    \caption {
-      The entire structure of the sequence homogeneously-structured classifier
-      (SHC).
-      \label{fig:shc_diagram}
-    }
-    %\end{center}
 \end{figure}
 
-Fig. \ref{fig:shc_diagram} shows the structure of the SHC algorithm. The
-structure is very simple and somewhat similar to that of CTC shown in TODO
+\section{Feedback Sequence Classifier}
+\label{sec:feedback_sequence_classifier}
 
-\subsection{Training of the Sequence Homogeneously-Structured Classifier}
-In this section, we describe how to train SHC. The procedure is summarized
-in the following table.
+\subsection{Neural Network Structure}
+Fig. \ref{fig:fsc_diagram} shows the entire structure of the FSC. 
+As shown in this figure, LSTM layers and max-pool layers
+are interleaved from the bottom layer up to the third max-pool layer.
+
+In Fig. \ref{fig:fsc_diagram}, speech features $\vec{x}[m]$ are sampled 
+at every 10 {\it ms}, which is the usual speech feature frame rate  
+in speech recognition
+\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00},
+Using three two-to-one max-pool layers, $\vec{z}[p]$ has a frame period 
+of 80 {\it ms}.  
+The relationship between the temporal index $p$ in $\vec{z}[p]$ and 
+$m$ in $\vec{x}[m]$ is given by: 
+\begin{align}
+  p = \lceil m / 8 \rceil \label{eq:def_p}
+\end{align}
+
+The reason for using the one dimensional max-pool layer
+is to make the neural network output have a similar rate to the 
+that of each {\it phone} in utterances. Note that a {\it phone} 
+is any distinct speech sound serving as a phonetic unit.
+
+It has been observed that the average phone duration is between 50 {\it ms}
+\textasciitilde 100 {\it ms} \cite{x_wang_icslp_1996_00, z_bartosz_ltc_2009_00}.
+
+\subsection{Training of the Feedback Sequence Classifier}
+In this section, we describe how to train FSC. The first step is making an
+alignment using the N-best alignment. The second step is updating the
+neural network parameters using the Cross Entropy (CE) criterion.
+
+\subsection{Training procedure}
+
+The first step is finding the optimal frame-synchronous sequence
+$\mathcal{Z}$
+
+\begin{algorithmic}
+  \State {$\mathcal{Z} = A(\mathcal{X} | \Theta)$}
+  \State {Updates the model.}
+\end{algorithmic}
 
@@
 
-\subsection{Feature extraction}
-
-Even though the log-mel coefficients have been widely used
-as features for speech recognition \cite{sbdavisandpm1980},
-the log non-linearity has a disadvantage in that the value
-diverges to negative infinity as the mel filterbank coefficient
-approaches zero \cite{C_Kim_IEEETran_2016_1}.
-Thus, we use the power-law nonlinearity
-rather than the log-nonlinearity:
-\begin{align}
-  q[m, l] =  (p[m, l])^{\frac{1}{15}}
-  \label{eq:power_law_nonlineartiy}
-\end{align}
-We use the power coefficient of $\frac{1}{15}$ as in
-\cite{C_Kim_IEEETran_2016_1, C_Kim_ICASSP_2012_1}.
-
-In this section, we discuss how to predict the clean feature and the
-error ratio from the corrupt feature. Let us denote the clean target feature,
-the corrupt feature by $\boldsymbol{x}, \boldsymbol{y}$ respectively.
-
-Using the room simulation system described in \cite{C_Kim_INTERSPEECH_2017_1},
-we create a pair of clean and
-corrupt utterances. Log-mel [XX] features are calculated from these original clean
-and corrupt utterances. Let us denote the clean feature by $\boldsymbol{t}_i$ and
-the simulated corrupt feature by $\boldsymbol{x}_i$, respectively where $i$ is the
-utterance index. The training set is represented by the following set:
-\begin{align}
-  \mathcal{T} = \{<\boldsymbol{x}_i, \boldsymbol{t}_i>| 0 \le i \le N - 1\}
-\end{align}
-where $N$ is the number of training examples.
-
-In the ECE algorithm, we first estimate the true target $\boldsymbol{t}_i$. The
-estimation error is defined by the following equation:
-\begin{align}
-  \boldsymbol{e}_i =  \boldsymbol{t}_i - \boldsymbol{x}_i, \quad 0 \le i \le N - 1
-\end{align}
-
-The norm of the error vector $\boldsymbol{e}_i$ would be generally large when
-the norm of the estimated clean feature is large.
-
-Thus, instead of trying to estimate the error itself, the neural network tries to
-estimate the error ratio given as follows:
-
-\begin{align}
-  r_i = {}{}
-\end{align}
-
-\section{Generation of simulated clean and noisy data sets}
-\label{gen_inst}
-
-To train neural networks described in section \ref{sec:estimation}, we
-need a training set consisting of pairs of clean speech and noisy speech.
-Unfortunately, it is not easy to have such a training set from real speech
-utterances. Thus, we use the simulation system described in
-\cite{C_Kim_INTERSPEECH_2017_1} to synthetically generate noisy speech
-utterances from the clean speech utterances.
-
-In our application, for clean training set, we used Wall Street Journal (WSJ)
-si-284. For noise set, we used the Resource Management 1 (RM1)
-\cite{price_p_ldc_1993} 50 \% of time 
-and DEMAND noise [TODO(chanwcom) Adds reference] for the remaining 50 \% of time.
-
-TODO(chanwcom) Cite DEMAND noise set.
-
-%
-%
-%
-%\begin{figure*}
-%  \centering
-%    \begin{subfigure}[\label{fig:randomly_selected_grid_coordinates}]{0.5\textwidth} {
-%        \includegraphics[width=\textwidth]{target_estimation}}
-%    \caption{Grid from random-sampling}
-%    \end{subfigure}
-%   % \begin{subfigure}[\label{fig:intersection_point}]{0.5\textwidth} {
-%   %   \includegraphics[width=\textwidth]{intersection_point}}
-%   % \caption{Calculation of grid coordinates}
-%   % \end{subfigure}
-%  \caption {Random Grid Sampling}
-%\end{figure*}
-%
-%
-%
-\section{Estimation of the optimal weight in the EFW algorithm}
-In this section, we describe the procedure of feature weighting approach.
-Suppose that the feature before enhancement is represented by $\vec{x}$.
-Let us represent the inference neural network to estimate the target by
-$\mathcal{T}$.
-
-\begin{align}
-  \mathcal{X} = \{  \}
-\end{align}
-
-Instead of directly using the enhanced feature $\widehat{\vec{y}}$, we consider
-the following interpolated feature $\bm{z}$ from the original corrupt
-input $\bm{x}$ and .
-\begin{align}
-  \vec{z} = \vec{w} \odot \widehat{\vec{y}} \ + (1 - \vec{w}) \odot \vec{x} 
-    \label{eq:vec_z}
-\end{align}
-where $\odot$ denotes the Hadamard product (entry-wise product).
-
-Let us denote the estimated variance vector by $\hat{\vec{v}}$:
-\begin{align}
-  \hat{\vec{v}} & = \text{Var}[\widehat{\vec{y}}] \nonumber \\
-                & = E[(y - y)^2 | \vec{x}[0], \vec{x}[1], ... \vec{x}[T]]
-     \label{eq:vec_v}
-\end{align}
-
-In our discussion, let us assume that the expectation of $\hat{\vec{y}}$ is the
-same as the true target $\vec{y}$.
-\begin{align}
-  E[\widehat{\vec{y}}] = \vec{y}  \label{eq:expectation_of_y}
-\end{align}
-
-Now, let us obtain the expected value of $\vec{z}$ from
-\eqref{eq:vec_z} and \eqref{eq:expectation_of_y}
-\begin{align}
-  E[\vec{z}] = (1 - \vec{w}) \odot (\vec{x} - \vec{y})
-\end{align}
-Thus, the bias of $\vec{z}$ is given by:
-\begin{align}
-  Bias_{\vec{z}} & = E[\vec{z}] - t \nonumber \\
-                 & = \vec{w} \odot (\widehat{\vec{y}} - \vec{y})
-\end{align}
-
-From \eqref{eq:vec_z} and \eqref{eq:vec_v}, the variance of $\vec{z}$ is given by:
-\begin{align}
-  Var_{\vec{z}} = \vec{v} \odot w \odot w.
-\end{align}
-The mean squared error of the $i$-th element of the $\vec{z}$ is given by:
-\begin{align}
-  MSE_{\vec{z_i}} & = Bias_{\vec{z_i}}^2 + Var_{\vec{z_i}} \nonumber \\
-                 & =  \left[(\vec{x}_i - \vec{y}_i) ^ 2
-                    + \vec{v}_i^2 \right] \vec{w}_i^{2}
-                    - 2 (\vec{x}_i - \vec{y}_i)^{2}  \vec{w}_i
-                    + (\vec{x}_i - \vec{y}_i)^{2}
- \label{eq:mse_z_i}
-\end{align}
-Since the above equation \eqref{eq:mse_z_i} is a quadratic equation with
-respect to $\vec{w}_i$, we may find that the minimum value of $MSE_{\vec{z_i}}$
-is obtained when $\vec{w}_i$ has the following value:
-\begin{align}
-  \vec{w}_i = \frac{(\vec{x}_i - \vec{y}_i)^2}{(\vec{x}_i - \vec{y}_i)^2 + \vec{v}_i}
-\end{align}
-
-Thus, the final form of the estimated vector $\widehat{\vec{z}}$ becomes:
-\begin{align}
-  \widehat{\vec{z}} = \widehat{\vec{w}} \odot \widehat{\vec{y}}
-    \ + (1 - \widehat{\vec{w}}) \odot \vec{x}
-\end{align}
-where
-\begin{align}
-  \widehat{\vec{w}} = {(\vec{x} - \vec{y})^{\odot 2}}
-    \left[(\vec{x} - \vec{y})^{\odot 2}+ \vec{v}\right]^{\odot -1}.
-\end{align}
-
-Sequence enhancement
-
-The feature enhancement is to map a sequence of corrupt features $\mathbf{X}$.
-\begin{subequations}
-  \begin{align}
-    \mathbf{X} = \left(\vec{x}[0], \vec{x}[1], \cdots, \vec{x}[M-1] \right)  \\
-    \mathbf{Y} = \left(\vec{y}[0], \vec{y}[1], \cdots, \vec{y}[M-1] \right) 
-  \end{align}
-\end{subequations}
+\section{Experimental Results}
+\label{sec:experimental_results}
 

### 2019-05-13 none_feedback_sequence_classifier/doc/main.tex
Updates the paper

@@
 r_prabhavalkar_interspeech_2017_00}. 
-A sequence-to-sequence
-model maps a sequence of input acoustic features into a sequence 
-of graphemes or words \cite{r_prabhavalkar_interspeech_2017_00}. 
+A {\it sequence-to-sequence}
+speech recognizers maps a sequence of input acoustic features into a sequence 
+of graphemes  \cite{j_chorowski_nips_2015_00, w_chan_icassp_2016_00} or words 
+\cite{r_prabhavalkar_interspeech_2017_00}. 
 We denote a sequence of input acoustic feature vectors by 
-$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels by 
-$\mathcal{Y}_{0}^{L-1}$:
+$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels in 
+{\it one-hot vector} representation by 
+$\mathcal{Y}_{0}^{L-1}$ as shown below:
 \begin{subequations}
   \begin{align}
-    \mathcal{X}_{0}^{}  =  
-      \left\{\vec{x}[0], \, \vec{x}[1], 
-        \, \cdots, \, \vec{x}[M-1] \right\},  \\
-    \mathcal{Y}_{0}^{}  =  
-      \left\{y_0, \, y_1, \,  \cdots, \, y_{L-1} \right\},
+    \mathcal{X}_{0}^{M-1}  =  
+      \left\{\vec{x}[m]
+          \Big| 0 \le m \le M - 1, \; \vec{x}[m] \in \mathbb{R}^d \right\},  
+    \label{eq:input_seq} \\
+    \mathcal{Y}_{0}^{L-1}  =  
+      \left\{\vec{y}_l  \Big| 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
+    \label{eq:target_label}
   \end{align}
 \end{subequations}
-where $M$ is the number of frames in the input feature sequence and
-$L$ is the number of labels in the output target sequence. In Fig. 
-\ref{fig:ctc_diagram} $\sim$ \ref{fig:attention_diagram}, we show
-block diagrams of CTC \cite{a_graves_icml_2006_00}, 
-RNN-T \cite{a_graves_corr_2012_00, a_graves_icassp_2013_00}, and 
-the attention-based model 
+where $M$ is the number of frames in the input feature sequence,
+$d$ in \eqref{eq:input_seq} is the dimension of the input feature.
+$L$ is the number of labels in the output target sequence,
+ and $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
+labels, which may be graphemes 
+\cite{j_chorowski_nips_2015_00,
+w_chan_icassp_2016_00},
+subword units \cite{
+a_zeyer_interspeech_2018_00,
+c_chiu_icassp_2018_00},
+ and words \cite{h_soltau_interspeech_2017_00}.
+Note that the sequence index in \eqref{eq:input_seq} is a frame
+index, whereas the sequence index in \eqref{eq:target_label} is 
+label index. Depending on whether the neural network generates
+the inference output for every frame or not, there are following
+categories:
+
+\begin{itemize}
+  \item {\bf Label-synchronous inference} In this category, the 
+neural network generates the inference output $\widehat{\vec{y_l}}$ 
+only when a new label is expected. The loss function 
+$\mathbb{L}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1}\right)$ is 
+defined as follows:
+   \begin{align}
+     \mathbb{L}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1}\right) 
+        = \sum_{l=0}^{L-1}  y_l \odot \log\left( \circ \, \widehat{\vec{y_l}} \right)  
+          \label{eq:label_synchronous_ce_loss} 
+   \end{align}
+where $\odot$ and $\log \left(\circ \right)$ denote element-wise product 
+(a.k.a {\it Hadamard product}) and element-wise log, respectively.
+
+  \item {\bf Frame-synchronous inference} In this category, from the original 
+target label in \eqref{eq:target_label}, we either explicitly or 
+implicitly obtain the label boundaries.
+In the framewise Cross Entropy (CE) training 
+\cite{g_hinton_ieee_signal_processing_mag_2012_00, 
+C_Kim_INTERSPEECH_2017_1, 
+B_Li_INTERSPEECH_2017_1}, {\it Viterbi alignment}  
 \cite{
-j_chorowski_nips_2015_00,
-w_chan_icassp_2016_00} respectively. CTC in Fig. \ref{fig:ctc_diagram} 
-and RNN-T in Fig. \ref{fig:rnn_t_diagram} are {\it frame-synchronous}, 
-which means that the ASR system generates the output target for each 
-input frame.
+x_huang_prentice_hall_2001_00,
+l_r_rabiner_proceedings_of_ieee_1989_00} is usually employed. 
+Using these alignment algorithms, 
+we obtain corresponding {\it frame-synchronous }label sequences 
+$\vec{z}[m] \in \mathbb{V}$ for each frame index $m$. This
+latent label sequences are often called a {\it path}.
+  \begin{align}
+    \mathcal{Z}_{0}^{M-1}  =  
+      \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
+    \label{eq:frame_target_label}
+  \end{align}
+Fig. \ref{fig:path_alignment} shows one such example. 
+Such an alignment is usually called a {\it path}.
+
+  \begin{align}
+     l = \sum_{l=0}^{l=L-1}  y_l \log \left( \hat{y_l} \right)  
+          \label{eq:label_synchronous_ce_loss} 
+  \end{align}
+\end{itemize}
+
+Moreover, in almost all the large speech training database, the temporal boundray
+of each label is not marked. In the attention-based model described in 
+Sec. \ref{sec:attention_based_model} and shown in Fig. 
+\ref{fig:attention_diagram}, lack of the temporal alignment information
+in the training database is not a problem, since the {\it decoder} portion 
+of the attention-model directly generates the output label sequences.
+The loss function is also defined for each labels.
 
 \subsection{Connectionist Temporal Classification}
+\label{sec:ctc}
 
@@
 $\mathcal{Z}_{0}^{M-1}$ yields $\mathcal{Y}_{0}^{L-1}$.
+
+\subsection{RNN-Transducer}
+\label{sec:rnn_t}
+
+Fig. \ref{fig:rnn_t_diagram} shows the entire structure of the  
+RNN-T structure. The loss function used in RNN-T is given as follows:
+\begin{align}
+  P\left(\mathcal{Y}_{0}^{L-1} | \mathcal{X}_{0}^{M-1}\right) = 
+    \sum_{\mathcal{Z}_{0}^{M-1} \in 
+      \mathcal{A}_{CTC} 
+        \left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1} \right)}
+          \Pi_{m=0}^{M-1}
+            P\left(\vec{z}[m] | \mathcal{X}_{0}^{M-1} \right),
+\end{align}
+
+\subsection{Attention-based model}
+\label{sec:attention_based_model}
 
@@
 \subsection{Neural Network Structure}
+\label{sec:neural_network_structure}
 Fig. \ref{fig:fsc_diagram} shows the entire structure of the FSC. 
@@
 In Fig. \ref{fig:fsc_diagram}, speech features $\vec{x}[m]$ are sampled 
-at every 10 {\it ms}, which is the usual speech feature frame rate  
-in speech recognition
+at every 10 {\it ms}, which is the usual frame period in speech 
+recognition
 \cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00},
@@
   p = \lceil m / 8 \rceil \label{eq:def_p}
+\end{align}
+\begin{align}
+  \mathcal{Z}_{0}^{M-1}  =  
+    \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
+  \label{eq:frame_target_label}
 \end{align}
@@
 \subsection{Training of the Feedback Sequence Classifier}
-In this section, we describe how to train FSC. The first step is making an
+In this section, we describe how to train FSC. As mentioned in Sec. 
+\label{ref:neural_network_structure}, the FSC operates in the frame
+-synchronous way. Since we do not have the alignment information
+
+The first step is making an
 alignment using the N-best alignment. The second step is updating the
@@
 The first step is finding the optimal frame-synchronous sequence
-$\mathcal{Z}$
+$\mathcal{Z}_0^{M-1}$.
 
@@
 \subsection{Viterbi alignment and N-best alignment}
+
+\begin{figure}
+  \centering
+    \resizebox{100mm}{!}{
+      \input{../figures/path_alignment.tex}
+    } 
+    \caption {
+      An example of a path $\mathcal{Z}_{0}^{M-1}$ and the path movement 
+      constraint shown by TODO(chanw.com)[Check the latex arrow symbol] $P -> Q$ and $P -> R$. 
+      \label{fig:path_alignment}
+    }
+\end{figure}
+
+In CTC in Sec. \ref{sec:ctc} and in RNN-T in Sec. \ref{sec:rnn_t}, the 
+forward-backward algorithm is employed to update parameters. 
+TODO(chanw.com) cite HMM tutorial paper.
+
+For example in CTC, the forward algorithm is given by the following equation:
 

### 2019-05-13 none_feedback_sequence_classifier/doc/tex_to_pdf.sh
Updates the paper

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+pdflatex main
+bibtex main
+bibtex main
+pdflatex main
+pdflatex main

### 2019-05-13 none_feedback_sequence_classifier/doc/main.tex

@@
 
+ In Fig. 
+\ref{fig:ctc_diagram} $\sim$ \ref{fig:attention_diagram}, we show
+block diagrams of CTC \cite{a_graves_icml_2006_00}, 
+RNN-T \cite{a_graves_corr_2012_00, a_graves_icassp_2013_00}, and 
+the attention-based model 
+\cite{
+j_chorowski_nips_2015_00,
+w_chan_icassp_2016_00} respectively. CTC in Fig. \ref{fig:ctc_diagram} 
+and RNN-T in Fig. \ref{fig:rnn_t_diagram} are {\it frame-synchronous}, 
+which means that the ASR system generates the output target for each 
+input frame.
+
 \subsection{Connectionist Temporal Classification}
@@
 recognition
+at every 10 {\it ms}, which is the usual speech feature frame rate  
+in speech recognition
 \cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00},
@@
 The first step is making an
+In this section, we describe how to train FSC. The first step is making an
+>>>>>>> cf67f8b3ff96936469f82b1916daebe02799ed40
 alignment using the N-best alignment. The second step is updating the
@@
 $\mathcal{Z}_0^{M-1}$.   
+$\mathcal{Z}$
 

### 2019-05-15 none_feedback_sequence_classifier/doc/main.tex
Updates the paper

--- 2019-05-04 none_feedback_sequence_classifier/doc/main.tex
@@
 \usepackage{subcaption}
+\usepackage{algorithm}
 \usepackage{algpseudocode}
@@
 This paper proposes a new end-to-end speech recognition system referred to
-as Recurrent neural network Sequence Classification (RSC). Recently, end-to-end speech
+as Feedback Sequence Classifier (FSC). Recently, end-to-end speech
 recognition systems have been gaining more attention from researchers and
@@
   v_vanhoucke_nips_workshop_2011_00}.
+TODO(chanw.com) Describes history about starting using DNN, LSTM.
 
-TODO(chanw.com) Talk about the AI speakers.
+With widespread adoption of voice assistant speakers
+such as Google Home, Amazon Alexa
+\cite{B_Li_INTERSPEECH_2017_1, C_Kim_INTERSPEECH_2017_1},
+far-field speech recognition has become very important.
+Recently, approaches using data augmentation
+has been gaining popularity for far-field speech recognition
+\cite{R_Lippmann_icassp_1987_1,
+c_kim_interspeech_2018_00, w_hartmann_interspeech_2016_00}.
 
-TODO(chanw.com) Talk about the advancements of the end-to-end systems.
+TODO(chanw.com) Briefly describes CTC, RNN-T, and attention-based model.
 
-Recently, it has been frequently observed that if 
-sequence-to-sequence end-to-end ASR systems are trained on sufficiently 
+Recently, it has been observed that if 
+{\it sequence-to-sequence end-to-end} ASR systems are trained on sufficiently 
 large amounts of acoustic training data, they can outperform
@@
 c_kim_interspeech_2019_00}.
+These complete end-to-end systems have started surpassing the performance of
+the conventional WFST-based decoders with a improved training strategy
+such as label smoothing, Minimum Word Error Rate(MWER) training, 
+learning rate warming-up,
+and a better choice of target unit such as Byte Pair Encoded (BPE) 
+\cite {r_sennrich_acl_2016_00} subword units.
 
-Recently, we observed that training with large-scale noisy data generated
-by a \textit{Room Simulator} \cite{C_Kim_INTERSPEECH_2017_1}
-improves speech recognition accuracy dramatically.
-This system has been successfully employed
-for training acoustic models for Google Home or Google voice
-search \cite{C_Kim_INTERSPEECH_2017_1}.
+TODO(chanw.com) Briefly describes the motivation of FSC.
 
@@
 r_prabhavalkar_interspeech_2017_00}. 
-A sequence-to-sequence
-model maps a sequence of input acoustic features into a sequence 
-of graphemes or words \cite{r_prabhavalkar_interspeech_2017_00}. 
-We denote a sequence of input acoustic feature vectors by 
-$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels by 
-$\mathcal{Y}_{0}^{L-1}$:
+A {\it sequence-to-sequence}
+speech recognizers maps a sequence of input acoustic features into a sequence 
+of text labels  \cite{r_prabhavalkar_interspeech_2017_00}. 
+Mathematically, this model is 
+represented by the following transformation $\mathcal{T}$ 
+\cite{a_graves_icml_2006_00}:
+\begin{align}
+  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
+	\label{eq:transformation}
+\end{align}
+where the symbol ${*}$ denotes a sequence, $d$ is the dimension of the input 
+feature. $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
+labels, which may be graphemes 
+\cite{j_chorowski_nips_2015_00,
+w_chan_icassp_2016_00},
+subword units \cite{
+a_zeyer_interspeech_2018_00,
+c_chiu_icassp_2018_00},
+ and words \cite{h_soltau_interspeech_2017_00}.
+Let us denote a sequence of input acoustic feature vectors by 
+$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels in 
+{\it one-hot vector} representation or its label-smoothed 
+representation \cite{} by 
+$\mathcal{Y}_{0}^{L-1}$ as shown below:
 \begin{subequations}
   \begin{align}
-    \mathcal{X}_{0}^{}  =  
-      \left\{\vec{x}[0], \, \vec{x}[1], 
-        \, \cdots, \, \vec{x}[M-1] \right\},  \\
-    \mathcal{Y}_{0}^{}  =  
-      \left\{y_0, \, y_1, \,  \cdots, \, y_{L-1} \right\},
+    \mathcal{X}_{0}^{M-1}  =  
+      \left\{\vec{x}[m]
+          \Big| 0 \le m \le M - 1, \; \vec{x}[m] \in \mathbb{R}^d \right\},  
+    \label{eq:input_seq} \\
+    \mathcal{Y}_{0}^{L-1}  =  
+      \left\{\vec{y}_l  \Big| 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
+    \label{eq:target_label}
   \end{align}
 \end{subequations}
-where $M$ is the number of frames in the input feature sequence and
-$L$ is the number of labels in the output target sequence. In Fig. 
+where $M$ is the number of frames in the input feature sequence,
+$L$ is the number of labels in the output target sequence,
+ and $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
+Note that the sequence index in \eqref{eq:input_seq} is a frame
+index, whereas the sequence index in \eqref{eq:target_label} is 
+label index. Depending on whether the neural network generates
+the inference output for every frame or not, there are following
+categories:
+
+\subsection{Label-synchronous inference}
+In this class of models, the neural network generates the inference output 
+$\widehat{\vec{y_l}}$ 
+only when a new label is expected. The loss function 
+$\mathbb{L}_{\text{ls}}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1}\right)$ is 
+defined as follows:
+   \begin{align}
+     \mathbb{L}_{\text{ls}}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1}\right) 
+        = \sum_{l=0}^{L-1}  {\vec{y}_l}^{\;t}  \log\left( 
+            \circ \, \widehat{\vec{y_l}} \right)  
+          \label{eq:label_synchronous_ce_loss} 
+   \end{align}
+where $\log \left(\circ \right)$ and $^{t}$ denote element-wise log and 
+transpose operation, respectively.
+
+\subsection{Frame-synchronous inference}
+\label{sec:frame_synchronous_inference}
+In this class of inference,  we obtain
+the temporal boundaries of each label in \eqref{eq:target_label}.
+In the frame-wise Cross Entropy (CE) training 
+\cite{g_hinton_ieee_signal_processing_mag_2012_00, 
+C_Kim_INTERSPEECH_2017_1, 
+B_Li_INTERSPEECH_2017_1}, {\it Viterbi alignment}  
+\cite{
+x_huang_prentice_hall_2001_00,
+l_r_rabiner_proceedings_of_ieee_1989_00} is usually employed. 
+The FSC algorithm presented in this paper also obtains
+label boundaries using the {\it N-best alignment} which will
+be explained in Sec. \ref{sec:n_best_alignment}.
+
+Using these alignment algorithms, 
+we obtain corresponding {\it frame-synchronous} label sequences 
+$\vec{z}[m] \in \mathbb{V}$ for each frame index $m$. This
+latent label sequences are often called a {\it path}.
+  \begin{align}
+    \mathcal{Z}_{0}^{M-1}  =  
+      \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
+    \label{eq:latent_label_seq}
+  \end{align}
+Fig. \ref{fig:path_alignment} shows one such example. 
+Such an alignment is usually called a {\it path}.
+
+\begin{align}
+   \mathbb{L}_{\text{fs}}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Z}_{0}^{M-1}\right) 
+      = \sum_{l=0}^{M-1}  {\vec{z}[m]}^{\,t}  \log\left( 
+          \circ \, \widehat{\vec{z}}[m] \right)  
+        \label{eq:frame_synchronous_ce_loss} 
+\end{align}
+
+ In Fig. 
 \ref{fig:ctc_diagram} $\sim$ \ref{fig:attention_diagram}, we show
@@
 
-\subsection{Connectionist Temporal Classification}
+\subsubsection{Connectionist Temporal Classification}
+\label{sec:ctc}
 
@@
 $\mathcal{Z}_{0}^{M-1}$ yields $\mathcal{Y}_{0}^{L-1}$.
+
+To obtain derivatives required for back-propagation, CTC employs 
+the forward-backward algorithm.
+
+\subsubsection{RNN-Transducer}
+\label{sec:rnn_t}
+
+Fig. \ref{fig:rnn_t_diagram} shows the entire structure of the  
+RNN-T structure. The loss function used in RNN-T is given as follows:
+\begin{align}
+  P\left(\mathcal{Y}_{0}^{L-1} | \mathcal{X}_{0}^{M-1}\right) = 
+    \sum_{\mathcal{Z}_{0}^{M-1} \in 
+      \mathcal{A}_{CTC} 
+        \left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1} \right)}
+          \Pi_{m=0}^{M-1}
+            P\left(\vec{z}[m] | \mathcal{X}_{0}^{M-1} \right),
+\end{align}
 
@@
 \subsection{Neural Network Structure}
+\label{sec:neural_network_structure}
 Fig. \ref{fig:fsc_diagram} shows the entire structure of the FSC. 
+Speech features $\vec{x}[m]$ are sampled 
+at every 10 {\it ms}, which is the usual frame period in speech 
+\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00}.
 As shown in this figure, LSTM layers and max-pool layers
 are interleaved from the bottom layer up to the third max-pool layer.
-
-In Fig. \ref{fig:fsc_diagram}, speech features $\vec{x}[m]$ are sampled 
-at every 10 {\it ms}, which is the usual speech feature frame rate  
-in speech recognition
-\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00},
-Using three two-to-one max-pool layers, $\vec{z}[p]$ has a frame period 
-of 80 {\it ms}.  
-The relationship between the temporal index $p$ in $\vec{z}[p]$ and 
-$m$ in $\vec{x}[m]$ is given by: 
+Using three 2:1 max-pool layers, the softmax output $\vec{z}[u]$ has 
+a frame period of 80 {\it ms}.  Thus, the relationship between the original frame 
+index $m$ and the temporal sub-sampled index $u$ is given by \eqref{eq:def_u_U}.
+The relationship between the length of the softmax output sequence $U$
+and the length of the feature sequence $M$ is also given in the same way:
 	\begin{align}
-  p = \lceil m / 8 \rceil \label{eq:def_p}
+		u = \lceil m / 8 \rceil,  \; U = \lceil M / 8 \rceil \label{eq:def_u_U}.
 	\end{align}
 
-The reason for using the one dimensional max-pool layer
-is to make the neural network output have a similar rate to the 
-that of each {\it phone} in utterances. Note that a {\it phone} 
-is any distinct speech sound serving as a phonetic unit.
+FSC performs inference in a frame-synchronous way as described in 
+Sec. \ref{sec:frame_synchronous_inference}. 
+However, due to this temporal sub-sampling, the latent label sequence 
+in \eqref{eq:latent_label_seq} is slightly modified as shown below:
+\begin{align}
+  \mathcal{Z}_{0}^{U-1}  =  
+    \left\{\vec{z}[u]  \Big| 0 \le m \le U-1, \; \vec{z}[u] \in \mathbb{V} \right\}.
+  \label{eq:subsampled_latent_label_seq}
+\end{align}
 
+The loss function 
+$\mathbb{L}_{\text{fsc}}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Z}_{0}^{M-1}\right)$ 
+is also modified from the original one in 
+\eqref{eq:frame_synchronous_ce_loss}:
+\begin{align}
+	\mathbb{L}_{\text{fsc}}
+		\left(\mathcal{X}_{0}^{M-1}, \mathcal{Z}_{0}^{U-1}\right)
+      = \sum_{u=0}^{U-1}  {\vec{z}[u]}^{\,t}  \log\left( 
+          \circ \, \widehat{\vec{z}}[u] \right)  
+        \label{eq:fsc_ce_loss} 
+\end{align}
+The reason for performing the 8:1 temporal sub-sampling in \eqref{eq:def_u_U} is to 
+to make the period of the softmax output $\widehat{\vec{z}}[u]$ in \label{eq:fsc_ce_loss} 
+be similar to the shortest BPE duration. We assume that the {\it sequence-to-sequence}
+neural network models will be trained most efficiently when the period of neural 
+network output roughly matches the period of the target. In addition, this
+output periods must be equal to larger than the shortest target period to prevent
+missing some targets.
+The shortest duration of each BPE is similar to the average length of {\it phones}, 
+which is any distinct speech sound serving as a phonetic unit.
 It has been observed that the average phone duration is between 50 {\it ms}
 \textasciitilde 100 {\it ms} \cite{x_wang_icslp_1996_00, z_bartosz_ltc_2009_00}.
+Under this rationale, we chose the temporal sub-sampling factor of 8:1. 
+We also observe this sub-sampling factor is optimal in our experiments as well.
+
+\subsection{Target units of Feedback Sequence Classifier}
+\label{sec:target_units}
+
+In FSC, we use subword units created by BPE \cite{r_sennrich_acl_2016_00} for
+the output vocabulary $\mathbb{V}$ in 
+\eqref{eq:transformation} and \eqref{eq:subsampled_latent_label_seq}.
+
+When creating the latent frame-wise label sequence $\mathcal{Z}_{0}^{U-1}$ 
+in \eqref{eq:subsampled_latent_label_seq}, we distinguish the onset frame
+from other frames.  For example, if we have a BPE unit
+("{\it an}") in the vocabulary $\mathbb{V}$, then we define another
+target ("{\it an$_o$}") which marks the on-set frame of this BPE
+interval. Thus, when the number of BPE units is $B$, the total
+number of vocabularies in $\mathbb{V}$ becomes $2B$.
+We refer this approach to as {\it BPE with onset marking}.
+
+The reason for using this approach is two-folds. First, since FSC
+generates an inference output for each frame, if the same
+BPE symbol repeatedly appears, it is difficult to tell whether 
+this BPE is really expected to appear multiple times or whether 
+the a single BPE is continuing. For example, when we have 
+a sequence \{"{\it an}", "{\it an} "\}
+as the inference output, it is difficult to tell whether it should be a single
+"{\it an}" or two "{\it an}"s. With the onset marking,
+a decoder needs to print out the inference outputs with onset marking. 
+The blank symbol in CTC also plays a similar role. However this blank symbol
+is a common symbol following any labels. In the FSC algorithm, the information
+given by the feedback paths is crucial in performance. In this aspect,
+blank symbol is not very useful for this feedback structure. 
+Second, we have frequently observed that the on-set portion of sound
+has a very important role in human auditory perception 
+\cite{C_Kim_INTERSPEECH_2014_2}.
 
 \subsection{Training of the Feedback Sequence Classifier}
-In this section, we describe how to train FSC. The first step is making an
-alignment using the N-best alignment. The second step is updating the
+In this section, we describe how to train FSC.  Algorithm 
+\ref{algo:fsc_training} shows how FSC is trained using the 
+N-best alignment algorithm. N-best algorithm will be described 
+in Sec. \ref{sec:n_best_alignment} in detail.
+In Algorithm \ref{algo:fsc_training}  
+As mentioned in Sec. 
+\ref{sec:frame_synchronous_inference}, FSC performs inference
+in a frame-synchronous way.
+The first step is making an 
+In this section, we describe how to train FSC. The first step is 
+is to make an alignment using the N-best alignment. The second step is updating the
 neural network parameters using the Cross Entropy (CE) criterion.
 
-\subsection{Training procedure}
-
 The first step is finding the optimal frame-synchronous sequence
+$\mathcal{Z}_0^{M-1}$.   
 $\mathcal{Z}$
 
+\begin{algorithm}
+  \caption{Training procedure for the FSC algorithm}
+  \label{algo:fsc_training}
   \begin{algorithmic}
-  \State {$\mathcal{Z} = A(\mathcal{X} | \Theta)$}
-  \State {Updates the model.}
+    \State $\Theta^{(0)} \leftarrow$ initialize\_parameters()
+    \For {epoch index $i = 0, . . . , I-1$}
+      \For {each batch $\left\{\mathcal{X}_{0}^{M-1}  \right\}, 
+                        \left\{\mathcal{Y}_{0}^{L-1}  \right\}$}, 
+        \State $\left\{ {{\mathcal{Z}^{(i)}}_0^{U-1}} \right\}
+          \leftarrow
+          \text{n\_best\_align}
+          \left(
+            \left\{X_{0}^{M-1} \right\} \Big| \Theta^{(i)}
+          \right)$
+
+        \State {$\Theta^{(i)} \leftarrow$ update\_parameter 
+          $\left(
+            \left\{\mathcal{X}_{0}^{M-1} \right\},			
+            \left\{{\mathcal{Z}^{(i)}}_{0}^{U-1}\right\}
+          \right)$}
+
+    \EndFor
+    \State $\Theta^{(i+1)} := \Theta^{(i)}$
+  \EndFor
+  \label{algorithm:fsc_training}
   \end{algorithmic}
+\end{algorithm}
 
-\subsection{Viterbi alignment and N-best alignment}
+\subsection{N-best alignment}
+\label{sec:n_best_alignment}
+
+\begin{figure}
+  \centering
+    \resizebox{100mm}{!}{
+      \input{../figures/path_alignment.tex}
+    } 
+    \caption {
+      An example of a path $\mathcal{Z}_{0}^{M-1}$ and the path movement 
+      constraint shown by dashed arrows $P \rightarrow Q$ and $P \rightarrow R$. 
+      \label{fig:path_alignment}
+    }
+\end{figure}
+
+In CTC in Sec. \ref{sec:ctc} and in RNN-T in Sec. \ref{sec:rnn_t}, the 
+forward-backward algorithm is employed to update parameters. 
+For example in CTC, the forward-backward algorithm is based on the
+following assumption:
+\begin{align}
+  P \left(  \Big| \right) = \Pi
+\end{align}
 
@@
 has advantages in simplicity and efficiency, it is based on
-the conditional independence assumption.
+the following conditional independence assumption.
 
@@
 
+\begin{algorithm}
+  \caption{N-best alignment algorithm}
   \begin{algorithmic}
+
+  \Require {$\mathcal{X}_0^{M}$}
+  \Require {$\mathcal{Y}_0^{L}$}
 
@@
   \end{algorithmic}
+\end{algorithm}
 
@@
 \subsubsection*{Acknowledgments}
-
-\section*{References}
-
-References follow the acknowledgments. Use unnumbered first-level
-heading for the references. Any choice of citation style is acceptable
-as long as you are consistent. It is permissible to reduce the font
-size to \verb+small+ (9 point) when listing the references. {\bf
-  Remember that you can go over 8 pages as long as the subsequent ones contain
-  \emph{only} cited references.}
-\medskip
 

### 2019-05-19 none_feedback_sequence_classifier/doc/main.tex
Adds figures

@@
 \usepackage{amsfonts}       % blackboard math symbols
+\usepackage{amsmath}
 \usepackage{nicefrac}       % compact symbols for 1/2, etc.
@@
 \usepackage{algorithm}
+\usepackage{mathrsfs}
 \usepackage{algpseudocode}
@@
 \begin{document}
+
 % \nipsfinalcopy is no longer used
@@
     }
+  \label{fig:path_alignment}
 \end{figure}
@@
 
-In TFSC, we propose the following N-best alignment approach rather than
+In FSC, we propose the following N-best alignment approach rather than
 the Viterbi alignment algorithm to find the alignment information.
+
+TODO(chanw.com) Define $f$.
 
@@
 
-  \Require {$\mathcal{X}_0^{M}$}
-  \Require {$\mathcal{Y}_0^{L}$}
+  \Require {$\vec{\mathcal{X}}[0:M]$}
+  \Require {$\mathcal{\vec{Y}}_{0:L}$}
+  \Require {The neural network parameter $\Theta^{\left(i\right)}$ for calculating 
+      $p\left(\vec{z}[m] \big|
+      \mathcal{\vec{Z}}[0:m], \mathcal{\vec{X}}[0:m+1]\right)$}
 
-  \For {$m = 0, . . . , M-1$}
-    \For {$l = 0, . . . , N_b-1$}
-      \State {$\pi^{(l)}[m]$}
-    \EndFor
-  \EndFor
+  \State {\textbf{Initialization:}}
+  \State {Let $\vec{Z}_0[0:1] := \left\{ \vec{y}_0 \right\}  $}
+  \State {$\vec{Z}_b[0:1], 1 \le b < N_b$ are undefined.}
+  \State {Let $\mathcal{L}_{0} := \ln \left[ 
+        p \left(\vec{y}_{0} \big| 
+            \vec{\mathcal{X}}[0:1]\right)  \right]$}
+  \For {$m = 1, . . . , M-1$}
+    \For {$b = 0, . . . , N_b-1$}
+      \If {$\vec{\mathcal{Z}}_{b}[0:m]$ is defined}
+        \State {Let $\vec{y}_u := \mathcal{\vec{Z}}_{b}[m-1] $}
+        \State {Let $\vec{\mathcal{Z}}_{b, 0}[0:m+1] := \vec{\mathcal{Z}}_{b}[0:m] 
+                \cup \left\{ \vec{y}_u  \right\}  $} 
+            \Comment {A horizontal move $P \rightarrow Q$ in Fig. \ref{fig:path_alignment}}.
+        \State {
+              $\mathcal{L}_{b,0} := \ln \left[ 
+                  p \left(\vec{y}_{u} \big| 
+                      \vec{\mathcal{Z}}_b[0:m], 
+                      \vec{\mathcal{X}}[0:m+1], \Theta^{(i)}\right)  \right]
+                  + \mathcal{L}_b$}
 
-  \If {$i\geq maxval$}
-      \State $i\gets 0$
-  \Else
-      \If {$i+k\leq maxval$}
-          \State $i\gets i+k$
+        \If {$u+1 \le  L - 1$}
+          \State {Let $\vec{\mathcal{Z}}_{b, 1}[0:m+1] := \vec{\mathcal{Z}}_{b}[0:m] \cup \left\{ \vec{y}_{u+1}  \right\}  $} 
+              \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
+          \State  {
+              $\mathcal{L}_{b,1} := \ln \left[ 
+                  p \left(\vec{y}_{u+1} \big| 
+                      \vec{\mathcal{Z}}_b[0:m], \vec{\mathcal{X}}[0:m+1], \Theta^{(i)}\right)  \right] 
+                          + \mathcal{L}_b$}
       \EndIf
       \EndIf
+    \EndFor
+    \State {Sort a list of items
+    $\left\{\mathcal{L}_{b, i}, \vec{\mathcal{Z}}_{b, i}[0:m+1] \right\}, \; 0 \le b < B, i = 0, 1$ 
+    with respect to the log likelihood $\left\{\mathcal{L}_{b, i}\right\}$ 
+    in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
+    follows: 
+    $\left\{\mathcal{L}_{b}, \vec{\mathcal{Z}}_{b}[0:m+1] \right\}$, $0 \le b < N_b$}
+    where the first item in the sorted list is re-indexed to $b=0$, 
+    the second item is re-indexed to $b=1$, and so on.
+  \EndFor
   \label{algorithm:n_best_alignment}

### 2019-06-23 none_feedback_sequence_classifier/doc/main.tex
Updates main.tex

--- 2019-05-15 none_feedback_sequence_classifier/doc/main.tex
@@
   \begin{align}
-    \mathcal{X}_{0}^{M-1}  =  
+    \mathcal{X}[0:M]  =  
       \left\{\vec{x}[m]
@@
     \label{eq:input_seq} \\
-    \mathcal{Y}_{0}^{L-1}  =  
+    \mathcal{Y}_{0:L}  =  
       \left\{\vec{y}_l  \Big| 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
@@
 $L$ is the number of labels in the output target sequence,
- and $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
+ and $\mathbb{V}$ in \eqref{eq:target_label} is the set of outputs.
 Note that the sequence index in \eqref{eq:input_seq} is a frame
-index, whereas the sequence index in \eqref{eq:target_label} is 
-label index. Depending on whether the neural network generates
+index ({\it represented by} [m]), 
+whereas the sequence index in \eqref{eq:target_label} is 
+a label index ({\it represented by a subscript} $l$). 
+Depending on whether the neural network generates
 the inference output for every frame or not, there are following
@@
 only when a new label is expected. The loss function 
-$\mathbb{L}_{\text{ls}}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1}\right)$ is 
+$\mathbb{L}_{\text{ls}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ is 
 defined as follows:
    \begin{align}
-     \mathbb{L}_{\text{ls}}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1}\right) 
-        = \sum_{l=0}^{L-1}  {\vec{y}_l}^{\;t}  \log\left( 
-            \circ \, \widehat{\vec{y_l}} \right)  
+     \mathbb{L}_{\text{ls}}\left(\mathcal{X}[0:M], 
+        \mathcal{Y}_{0:L}\right) 
+        = \sum_{l=0}^{L-1} 
+          \sum_{v=0}^{V-1}
+          \left(\vec{y}_l\right)_v  \log ( 
+             \widehat{\vec{y_l}} )_{v}
           \label{eq:label_synchronous_ce_loss} 
    \end{align}
-where $\log \left(\circ \right)$ and $^{t}$ denote element-wise log and 
-transpose operation, respectively.
+where $V$ is the number of output labels in the set $\mathbb{V}$ 
+mentioned in \eqref{eq:target_label}, and ${(\vec{y}_l)}_v$  
+and ${(\widehat{\vec{y_l}})}_{v}$ are the $v$-th element of the 
+ground-truth vector $\vec{y}_l$ and the estimated vector by the 
+neural network ${\widehat{\vec{y_l}}}$.
 
@@
   \begin{align}
-    \mathcal{Z}_{0}^{M-1}  =  
+    \mathcal{Z}[0:M]  =  
       \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
@@
 Fig. \ref{fig:path_alignment} shows one such example.
-Such an alignment is usually called a {\it path}.
 
+The loss function in the frame-synchronous inference case
+$\mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ is 
+defined as follows:
 \begin{align}
-   \mathbb{L}_{\text{fs}}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Z}_{0}^{M-1}\right) 
-      = \sum_{l=0}^{M-1}  {\vec{z}[m]}^{\,t}  \log\left( 
-          \circ \, \widehat{\vec{z}}[m] \right)  
+  \mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Z}[0:M]\right) 
+      = \sum_{l=0}^{M-1} 
+          \sum_{v=0}^{V-1}  
+            (\vec{z}[m])_v  
+            \log (\widehat{\vec{z}}[m])_v  
         \label{eq:frame_synchronous_ce_loss} 
@@
 \begin{align}
-  P\left(\mathcal{Y}_{0}^{L-1} | \mathcal{X}_{0}^{M-1}\right) = 
+  P\left(\mathcal{Y}_{0:L} | \mathcal{X}[0:M]\right) = 
     \sum_{\mathcal{Z}_{0}^{M-1} \in 
@@
 \begin{align}
-  \mathcal{Z}_{0}^{U-1}  =  
+  \mathcal{Z}[0:U]  =  
     \left\{\vec{z}[u]  \Big| 0 \le m \le U-1, \; \vec{z}[u] \in \mathbb{V} \right\}.
@@
 The loss function 
-$\mathbb{L}_{\text{fsc}}\left(\mathcal{X}_{0}^{M-1}, \mathcal{Z}_{0}^{M-1}\right)$ 
+$\mathbb{L}_{\text{fsc}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ 
 is also modified from the original one in 
@@
 	\mathbb{L}_{\text{fsc}}
-		\left(\mathcal{X}_{0}^{M-1}, \mathcal{Z}_{0}^{U-1}\right)
-      = \sum_{u=0}^{U-1}  {\vec{z}[u]}^{\,t}  \log\left( 
-          \circ \, \widehat{\vec{z}}[u] \right)  
+    \left(\mathcal{X}[0:M], \mathcal{Z}_{0:U}\right)
+      = \sum_{u=0}^{U-1}  
+          \sum_{v=0}^{V-1}
+          {(\vec{z}[u])_v}  \log ( 
+             \widehat{\vec{z}}[u] )_v  
         \label{eq:fsc_ce_loss} 
@@
 
-When creating the latent frame-wise label sequence $\mathcal{Z}_{0}^{U-1}$ 
+When creating the latent frame-wise label sequence $\mathcal{Z}[0:U]$ 
 in \eqref{eq:subsampled_latent_label_seq}, we distinguish the onset frame
@@
 \ref{algo:fsc_training} shows how FSC is trained using the 
-N-best alignment algorithm. N-best algorithm will be described 
+$N$-best alignment algorithm and the cross entropy loss function. 
+$N$-best algorithm will be described 
 in Sec. \ref{sec:n_best_alignment} in detail.
@@
 In this section, we describe how to train FSC. The first step is 
-is to make an alignment using the N-best alignment. The second step is updating the
+is to make an alignment using the $N$-best alignment. The second step is updating the
 neural network parameters using the Cross Entropy (CE) criterion.
@@
 The first step is finding the optimal frame-synchronous sequence
-$\mathcal{Z}_0^{M-1}$.   
-$\mathcal{Z}$
+$\mathcal{Z}[0:M]$.
 
@@
     \For {epoch index $i = 0, . . . , I-1$}
-      \For {each batch $\left\{\mathcal{X}_{0}^{M-1}  \right\}, 
-                        \left\{\mathcal{Y}_{0}^{L-1}  \right\}$}, 
-        \State $\left\{ {{\mathcal{Z}^{(i)}}_0^{U-1}} \right\}
+      \For {each batch $\left\{\mathcal{X}[0:M],
+                        \mathcal{Y}_{0:L}  \right\}$}, 
+        \State $ {{\mathcal{Z}^{(i)}}[0:U]}
           \leftarrow
@@
           \left(
-            \left\{X_{0}^{M-1} \right\} \Big| \Theta^{(i)}
+            \mathcal{X}[0:M] \Big| \Theta^{(i)}
           \right)$
@@
           $\left(
-            \left\{\mathcal{X}_{0}^{M-1} \right\},			
-            \left\{{\mathcal{Z}^{(i)}}_{0}^{U-1}\right\}
+            \mathcal{X}[0:M],
+            \mathcal{Z}^{(i)}[0:U]
           \right)$}
@@
     \caption {
-      An example of a path $\mathcal{Z}_{0}^{M-1}$ and the path movement 
+      An example of a path $\mathcal{Z}[0:M]$ and the path movement 
       constraint shown by dashed arrows $P \rightarrow Q$ and $P \rightarrow R$. 
@@
 
-In TFSC, we propose the following N-best alignment approach rather than
+In FSC, we propose the following $N$-best alignment approach rather than
 the Viterbi alignment algorithm to find the alignment information.
 
+TODO(chanw.com) Define $f$.
+
 \begin{algorithm}
-  \caption{N-best alignment algorithm}
+  \caption{$N$-best alignment algorithm}
   \begin{algorithmic}
 
-  \Require {$\mathcal{X}_0^{M}$}
-  \Require {$\mathcal{Y}_0^{L}$}
+  \Require {$\mathcal{X}[0:M]$}
+  \Require {$\mathcal{Y}_{0:L}$}
+  \Require {The neural network parameter $\Theta^{\left(i\right)}$ 
+    for calculating 
+      $p\left(\vec{z}[m] \big|
+      \mathcal{Z}[0:m], \mathcal{X}[0:m+1]\right)$}
 
-  \For {$m = 0, . . . , M-1$}
-    \For {$l = 0, . . . , N_b-1$}
-      \State {$\pi^{(l)}[m]$}
-    \EndFor
-  \EndFor
+  \State {\textbf{Initialization:}}
+  \State {Let $\mathcal{Z}_0[0:1] := \left\{ \vec{y}_0 \right\}  $}
+  \State {Let $\mathcal{L}_{0} := \ln \left[ 
+        p \left(\vec{y}_{0} \big| 
+            {\mathcal{X}}[0:1]\right)  \right]$}
+  \State {$\mathcal{Z}_b[0:1], 1 \le b < N_b$ are undefined.}
+  \For {$m = 1, . . . , M-1$}
+    \For {$b = 0, . . . , N_b-1$}
+      \If {$\mathcal{Z}_{b}[0:m]$ is defined}
+        \State {Let $\vec{y}_u := \vec{z}_{b}[m-1] $}
+        \State {Let $\mathcal{Z}_{b, 0}[0:m+1] := \mathcal{Z}_{b}[0:m] 
+                \cup \left\{ \vec{y}_u  \right\}  $} 
+            \Comment {A horizontal move $P \rightarrow Q$ in 
+            Fig. \ref{fig:path_alignment}}.
+        \State {
+              $\mathcal{L}_{b,0} := \ln \left[ 
+                  p \left(\vec{y}_{u} \big| 
+                      \mathcal{Z}_b[0:m], 
+                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right]
+                  + \mathcal{L}_b$}
 
-  \If {$i\geq maxval$}
-      \State $i\gets 0$
-  \Else
-      \If {$i+k\leq maxval$}
-          \State $i\gets i+k$
+        \If {$u+1 \le  L - 1$}
+          \State {Let $\mathcal{Z}_{b, 1}[0:m+1] 
+          := {\mathcal{Z}}_{b}[0:m] \cup \left\{ \vec{y}_{u+1}  \right\}  $} 
+              \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
+          \State  {
+              $\mathcal{L}_{b,1} := \ln \left[ 
+                  p \left(\vec{y}_{u+1} \big| 
+                      \mathcal{Z}_b[0:m], 
+                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right] 
+                          + \mathcal{L}_b$}
       \EndIf
       \EndIf
+    \EndFor
+    \State {Sort a list of items
+    $\left\{\mathcal{L}_{b, i}, {\mathcal{Z}}_{b, i}[0:m+1] \right\}, \; 0 \le
+    b < N_b, i = 0, 1$ 
+    with respect to the log likelihood $\mathcal{L}_{b, i}$ 
+    in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
+    follows: 
+    $\left\{\mathcal{L}_{b}, \mathcal{Z}_{b}[0:m+1] \right\}$, $0 \le b < N_b$}
+    where the first item in the sorted list is re-indexed to $b=0$, 
+    the second item is re-indexed to $b=1$, and so on.
+  \EndFor
   \label{algorithm:n_best_alignment}

### 2019-06-23 none_cloud_post_processing_decoding/doc/main.tex
Updates the paper

--- 2019-06-23 none_feedback_sequence_classifier/doc/main.tex
@@
 
-\title{A state of the art end-to-end speech recognition algorithm with
-a homogenous structure.}
+\title{Enhancement of Speech Recognition Results Using Server-side
+Post-processing}
 
@@
 \section{Introduction}
+
+\section{Review on frame-synchronous speech recognition}
+
+Let us suppose that the sequence of the text stream is $T$  
+\begin{align}
+  X
+\end{align}
+
+A speech recognizers maps a sequence of input acoustic features into a sequence 
+of text labels  \cite{r_prabhavalkar_interspeech_2017_00}. 
+Mathematically, this model is 
+represented by the following transformation $\mathcal{T}$ 
+\cite{a_graves_icml_2006_00}:
+\begin{align}
+  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
+	\label{eq:transformation}
+\end{align}
+where the symbol ${*}$ denotes a sequence, $d$ is the dimension of the input 
+feature. $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
+labels, which may be graphemes 
+\cite{j_chorowski_nips_2015_00,
+w_chan_icassp_2016_00},
+subword units \cite{
+a_zeyer_interspeech_2018_00,
+c_chiu_icassp_2018_00},
+ and words \cite{h_soltau_interspeech_2017_00}.
+
+\section{The structure of the Server-side Post Processing System}
+
+Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
+system and the server-side post processing system. 
+The symbols used in this figure is defined as follows:
+%
+\begin{align}
+  \vec{x}[m]:& \quad \text{Acoustic feature vector from speech.}  \nonumber \\
+  \hat{y}_o[l]:& \quad \text{The frame-synchronous hypothesis from the
+  on-device speech recognizer.}   \nonumber \\
+       & \quad \hat{y}_o[l] \in \mathbb{V}.  \nonumber \\
+  \hat{y}_o[0:l+1]  : & \quad \text{The sequence of $y[l']$ where } 0 \le l'
+  \le l. \quad  \hat{y}_o[l'] \in \mathbb{V}.  \nonumber \\ 
+  \hat{y}_p[l]:& \quad \text{The frame-synchronous hypothesis for post-processing.}
+  \quad \hat{y}_p[l] \in \mathbb{V}.   \nonumber \\
+  W_i: & \quad \text{The word sequence. } W_i \in  \mathbb{D}.  \nonumber 
+\end{align}
+where $\mathbb{V}$ is the set of grapheme symbols, and $\mathbb{D}$ is the
+set of words. In Fig. \ref{fig:entire_system}, there are two top level
+blocks. The left and right blocks correspond to processing on the local
+device and the server side post processing respectively.
+
+\subsection{Label Likelihood Calculation}
+To perform decoding described in Section \ref{sec:decoding}, 
+we need to calculate likelihood $P(y[0:l+1] |z[l])$
+where $\mathcal{Y}[0:l]$ is the 
+In this block, the objective is to calculate the likelihood
+of the on-device ASR output $\mathcal{Y}[0:l]$ depending on 
+the label $z[l]$, which may be mathematically given
+by
+\begin{align}
+  P(\hat{y}_o[0:l+1] \big| \hat{y}_p[l]) 
+    = \frac{P(\hat{y}_p[l] \big| \hat{y}_o[0:l+1])
+        P\left(\hat{y}_o[0:l+1] \right)}{P(\hat{y}_p[l])}
+  \label{eq:post_prob}
+\end{align}
+
+\subsection{Decoding}
+\label{sec:decoding}
+The structure of the post-processing decoder is depicted in Fig.
+\ref{post_processing_decoder}. Using the dictionary and the
+language model, the hypothesis word sequence $W_i$ is obtained
+from the posterior probability in \eqref{eq:post_prob}.
+
+\begin{figure}
+  \centering
+    \centering
+    \resizebox{130mm}{!}{
+      \input{../figures/hybrid_on_device_cloud_asr.tex}
+    }
+    \caption {
+      The structure of an entire system consisting of the on-device speech 
+      recognition and the server-side post processing. 
+      \label{fig:entire_system}
+    }
+\end{figure}
+
+\begin{figure}
+  \centering
+    \centering
+    \resizebox{55mm}{!}{
+      \input{../figures/asr_system.tex}
+    }
+    \caption {
+      The on-device Automatic Speech Recognition (ASR) system.
+      \label{fig:asr_system}
+    }
+\end{figure}
+
+\begin{figure}
+    \centering
+    \resizebox{30mm}{!}{
+      \input{../figures/label_posteior_prob_estimation.tex}
+    } 
+    \caption {
+      Estimation of the label posterior probability
+      \label{fig:label_posterior_prob_estimation}
+    }
+\end{figure}
+
+\begin{figure}
+    \centering
+    \resizebox{70mm}{!}{
+      \input{../figures/post_processing_decoder.tex}
+    } 
+    \caption {
+      The post-processing decoder for generating the word sequence $W_i$
+      from the label likelihood $P(\hat{y}_o[0:l+1] | \hat{y}_p[l])$ in \eqref{eq:post_prob}, 
+      using the dictionary and the language model.
+      \label{fig:post_processing_decoder}
+    }
+\end{figure}
+
+\section{Introduction}
 Recently, there has been tremendous improvements in speech recognition
@@
 TODO(chanw.com) Describes history about starting using DNN, LSTM.
+
+\section{Review on sequence-to-sequence speech recognition algorithms}
+
+In this section, we review well-known {\it sequence-to-sequence} algorithms
+used in speech recognition.
+\cite{
+j_chorowski_nips_2015_00, 
+a_graves_corr_2012_00, 
+y_he_icassp_2019_00,
+r_prabhavalkar_interspeech_2017_00}. 
+where $M$ is the number of frames in the input feature sequence,
+$L$ is the number of labels in the output target sequence,
+ and $\mathbb{V}$ in \eqref{eq:target_label} is the set of outputs.
+Note that the sequence index in \eqref{eq:input_seq} is a frame
+index ({\it represented by} [m]), 
+whereas the sequence index in \eqref{eq:target_label} is 
+a label index ({\it represented by a subscript} $l$). 
+Depending on whether the neural network generates
+the inference output for every frame or not, there are following
+categories:
 
@@
 TODO(chanw.com) Briefly describes the motivation of FSC.
-
-\section{Review on sequence-to-sequence speech recognition algorithms}
-
-In this section, we review well-known {\it sequence-to-sequence} algorithms
-used in speech recognition.
-\cite{
-j_chorowski_nips_2015_00, 
-a_graves_corr_2012_00, 
-y_he_icassp_2019_00,
-r_prabhavalkar_interspeech_2017_00}. 
-A {\it sequence-to-sequence}
-speech recognizers maps a sequence of input acoustic features into a sequence 
-of text labels  \cite{r_prabhavalkar_interspeech_2017_00}. 
-Mathematically, this model is 
-represented by the following transformation $\mathcal{T}$ 
-\cite{a_graves_icml_2006_00}:
-\begin{align}
-  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
-	\label{eq:transformation}
-\end{align}
-where the symbol ${*}$ denotes a sequence, $d$ is the dimension of the input 
-feature. $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
-labels, which may be graphemes 
-\cite{j_chorowski_nips_2015_00,
-w_chan_icassp_2016_00},
-subword units \cite{
-a_zeyer_interspeech_2018_00,
-c_chiu_icassp_2018_00},
- and words \cite{h_soltau_interspeech_2017_00}.
-Let us denote a sequence of input acoustic feature vectors by 
-$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels in 
-{\it one-hot vector} representation or its label-smoothed 
-representation \cite{} by 
-$\mathcal{Y}_{0}^{L-1}$ as shown below:
-\begin{subequations}
-  \begin{align}
-    \mathcal{X}[0:M]  =  
-      \left\{\vec{x}[m]
-          \Big| 0 \le m \le M - 1, \; \vec{x}[m] \in \mathbb{R}^d \right\},  
-    \label{eq:input_seq} \\
-    \mathcal{Y}_{0:L}  =  
-      \left\{\vec{y}_l  \Big| 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
-    \label{eq:target_label}
-  \end{align}
-\end{subequations}
-where $M$ is the number of frames in the input feature sequence,
-$L$ is the number of labels in the output target sequence,
- and $\mathbb{V}$ in \eqref{eq:target_label} is the set of outputs.
-Note that the sequence index in \eqref{eq:input_seq} is a frame
-index ({\it represented by} [m]), 
-whereas the sequence index in \eqref{eq:target_label} is 
-a label index ({\it represented by a subscript} $l$). 
-Depending on whether the neural network generates
-the inference output for every frame or not, there are following
-categories:
 
@@
   \centering
-  \begin{subfigure}[b]{0.35\textwidth}
-    \centering
-    \resizebox{23mm}{!}{
-      \input{../figures/ctc_diagram.tex}
-    } 
-    \caption {
-      Connectionist Temporal Classification (CTC) Model.
-      \label{fig:ctc_diagram}
-    }
-  \end{subfigure}
   \begin{subfigure}[b]{0.60\textwidth}
@@
       \label{fig:attention_diagram}
-    }
-  \end{subfigure}
-  \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-    \resizebox{26mm}{!}{
-      \input{../figures/fsc_diagram.tex}
-    }
-    \caption {
-      Feedback Sequence Classifier (FSC) Model.
-      \label{fig:fsc_diagram}
     }
@@
 
-\begin{figure}
-  \centering
-    \resizebox{100mm}{!}{
-      \input{../figures/path_alignment.tex}
-    } 
-    \caption {
-      An example of a path $\mathcal{Z}[0:M]$ and the path movement 
-      constraint shown by dashed arrows $P \rightarrow Q$ and $P \rightarrow R$. 
-      \label{fig:path_alignment}
-    }
-  \label{fig:path_alignment}
-\end{figure}
-
 In CTC in Sec. \ref{sec:ctc} and in RNN-T in Sec. \ref{sec:rnn_t}, the 
@@
 
-\begin{algorithm}
-  \caption{$N$-best alignment algorithm}
-  \begin{algorithmic}
-
-  \Require {$\mathcal{X}[0:M]$}
-  \Require {$\mathcal{Y}_{0:L}$}
-  \Require {The neural network parameter $\Theta^{\left(i\right)}$ 
-    for calculating 
-      $p\left(\vec{z}[m] \big|
-      \mathcal{Z}[0:m], \mathcal{X}[0:m+1]\right)$}
-
-  \State {\textbf{Initialization:}}
-  \State {Let $\mathcal{Z}_0[0:1] := \left\{ \vec{y}_0 \right\}  $}
-  \State {Let $\mathcal{L}_{0} := \ln \left[ 
-        p \left(\vec{y}_{0} \big| 
-            {\mathcal{X}}[0:1]\right)  \right]$}
-  \State {$\mathcal{Z}_b[0:1], 1 \le b < N_b$ are undefined.}
-  \For {$m = 1, . . . , M-1$}
-    \For {$b = 0, . . . , N_b-1$}
-      \If {$\mathcal{Z}_{b}[0:m]$ is defined}
-        \State {Let $\vec{y}_u := \vec{z}_{b}[m-1] $}
-        \State {Let $\mathcal{Z}_{b, 0}[0:m+1] := \mathcal{Z}_{b}[0:m] 
-                \cup \left\{ \vec{y}_u  \right\}  $} 
-            \Comment {A horizontal move $P \rightarrow Q$ in 
-            Fig. \ref{fig:path_alignment}}.
-        \State {
-              $\mathcal{L}_{b,0} := \ln \left[ 
-                  p \left(\vec{y}_{u} \big| 
-                      \mathcal{Z}_b[0:m], 
-                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right]
-                  + \mathcal{L}_b$}
-
-        \If {$u+1 \le  L - 1$}
-          \State {Let $\mathcal{Z}_{b, 1}[0:m+1] 
-          := {\mathcal{Z}}_{b}[0:m] \cup \left\{ \vec{y}_{u+1}  \right\}  $} 
-              \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
-          \State  {
-              $\mathcal{L}_{b,1} := \ln \left[ 
-                  p \left(\vec{y}_{u+1} \big| 
-                      \mathcal{Z}_b[0:m], 
-                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right] 
-                          + \mathcal{L}_b$}
-      \EndIf
-      \EndIf
-    \EndFor
-    \State {Sort a list of items
-    $\left\{\mathcal{L}_{b, i}, {\mathcal{Z}}_{b, i}[0:m+1] \right\}, \; 0 \le
-    b < N_b, i = 0, 1$ 
-    with respect to the log likelihood $\mathcal{L}_{b, i}$ 
-    in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
-    follows: 
-    $\left\{\mathcal{L}_{b}, \mathcal{Z}_{b}[0:m+1] \right\}$, $0 \le b < N_b$}
-    where the first item in the sorted list is re-indexed to $b=0$, 
-    the second item is re-indexed to $b=1$, and so on.
-  \EndFor
-  \label{algorithm:n_best_alignment}
-  \end{algorithmic}
-\end{algorithm}
-
 \section{Experimental Results}

### 2019-06-23 none_cloud_post_processing_decoding/doc/main.tex
Updates figures

@@
 Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
-system and the server-side post processing system. 
-The symbols used in this figure is defined as follows:
+system and the server-side post processing system. In this figure,  
+the two top level blocks on the left and the right hand sides correspond
+to {\it speech recognition on the local device} and 
+{\it post processing on the server} respectively.  The symbols used in this 
+figure is defined as follows:
 %
@@
   \le l. \quad  \hat{y}_o[l'] \in \mathbb{V}.  \nonumber \\ 
-  \hat{y}_p[l]:& \quad \text{The frame-synchronous hypothesis for post-processing.}
+  y_p[l]:& \quad \text{The frame-synchronous hypothesis for post-processing.}
   \quad \hat{y}_p[l] \in \mathbb{V}.   \nonumber \\
@@
 To perform decoding described in Section \ref{sec:decoding}, 
-we need to calculate likelihood $P(y[0:l+1] |z[l])$
-where $\mathcal{Y}[0:l]$ is the 
-In this block, the objective is to calculate the likelihood
-of the on-device ASR output $\mathcal{Y}[0:l]$ depending on 
-the label $z[l]$, which may be mathematically given
-by
+we need to calculate likelihood $P(\hat{y}_o[0:l+1] | y_p[l])$
+where $\hat{y}_o[0:l+1]$ is the sequence of the frame-synchronous 
+label hypothesis.
+Using the Bayes rule, this likelihood is expressed in the following form:
 \begin{align}
-  P(\hat{y}_o[0:l+1] \big| \hat{y}_p[l]) 
-    = \frac{P(\hat{y}_p[l] \big| \hat{y}_o[0:l+1])
-        P\left(\hat{y}_o[0:l+1] \right)}{P(\hat{y}_p[l])}
-  \label{eq:post_prob}
+  P(\hat{y}_o[0:l+1] \big| y_p[l]) 
+    = \frac{P(y_p[l] \big| \hat{y}_o[0:l+1])
+        P\left(\hat{y}_o[0:l+1] \right)}{P(y_p[l])}.
+  \label{eq:likelihood_prob}
+\end{align}
+To calculate the above equation, the following three terms need to be
+calculated:
+\begin{align}
+  P(y_p[l] \big| \hat{y}_o[0:l+1]): & \text{ A posterior probability of } y_p[l]
+    \text{ given the frame-synchronous label sequence } \nonumber \\ 
+    & \hat{y}_o[0:l+1].
+    \nonumber \\
+  P\left(\hat{y}_o[0:l+1] \right): & 
+    \text{ A probability of the sequence of frame-synchronous labels } \hat{y}_o[0:l+1].
+      \nonumber \\
+  P(y_p[l]): & \text{ A prior probability of the label } y_p[l] \in \mathbb{V}.
+  \label{eq:prob_components_likelihood}
+\end{align}
+
+To calculate $P\left(\hat{y}_o[0:l+1] \right)$ in \eqref{eq:likelihood_prob}, 
+we use a either statistical n-gram or a RNN based Language Model (LM). 
+One notable difference of the LM used for this purpose compared 
+to a conventional LM is that this LM must be a frame-synchronous LM.
+and must be trained from frame-synchronous label corpus. 
+Thus, we first need to align transcribed speech corpus to obtain frame-synchronous 
+labels and train LM from this corpus. 
+Finally, we use this LM to calculate $P\left(\hat{y}_o[0:l+1] \right)$.
+
+Instead of calculating the likelihood of the whole sequence 
+$\hat{y}_o[0:l+1]$ described above, a simpler alternative is to ignore
+the past values of the original hypothesis $\hat{y}_o[0:l+1]$ and only to
+consider the current one $\hat{y}_o[l]$. Under this simplification,
+the likelihood in \eqref{eq:likelihood_prob} may be simplified as follows:
+\begin{align}
+  P(\hat{y}_o[l] \big| y_p[l]) 
+    = \frac{P (y_p[l] \big| \hat{y}_o[l]) P(\hat{y}_o[l])}{P(y_p[l])} 
 \end{align}
@@
 The structure of the post-processing decoder is depicted in Fig.
-\ref{post_processing_decoder}. Using the dictionary and the
+\ref{fig:post_processing_decoder}. Using the dictionary and the
 language model, the hypothesis word sequence $W_i$ is obtained
@@
 
-\section{Feedback Sequence Classifier}
-\label{sec:feedback_sequence_classifier}
-
-\subsection{Neural Network Structure}
-\label{sec:neural_network_structure}
-Fig. \ref{fig:fsc_diagram} shows the entire structure of the FSC. 
-Speech features $\vec{x}[m]$ are sampled 
-at every 10 {\it ms}, which is the usual frame period in speech 
-\cite{x_huang_prentice_hall_2001_00, c_kim_taslp_2016_00}.
-As shown in this figure, LSTM layers and max-pool layers
-are interleaved from the bottom layer up to the third max-pool layer.
-Using three 2:1 max-pool layers, the softmax output $\vec{z}[u]$ has 
-a frame period of 80 {\it ms}.  Thus, the relationship between the original frame 
-index $m$ and the temporal sub-sampled index $u$ is given by \eqref{eq:def_u_U}.
-The relationship between the length of the softmax output sequence $U$
-and the length of the feature sequence $M$ is also given in the same way:
-	\begin{align}
-		u = \lceil m / 8 \rceil,  \; U = \lceil M / 8 \rceil \label{eq:def_u_U}.
-	\end{align}
-
-FSC performs inference in a frame-synchronous way as described in 
-Sec. \ref{sec:frame_synchronous_inference}. 
-However, due to this temporal sub-sampling, the latent label sequence 
-in \eqref{eq:latent_label_seq} is slightly modified as shown below:
-\begin{align}
-  \mathcal{Z}[0:U]  =  
-    \left\{\vec{z}[u]  \Big| 0 \le m \le U-1, \; \vec{z}[u] \in \mathbb{V} \right\}.
-  \label{eq:subsampled_latent_label_seq}
-\end{align}
-
-The loss function 
-$\mathbb{L}_{\text{fsc}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ 
-is also modified from the original one in 
-\eqref{eq:frame_synchronous_ce_loss}:
-\begin{align}
-	\mathbb{L}_{\text{fsc}}
-    \left(\mathcal{X}[0:M], \mathcal{Z}_{0:U}\right)
-      = \sum_{u=0}^{U-1}  
-          \sum_{v=0}^{V-1}
-          {(\vec{z}[u])_v}  \log ( 
-             \widehat{\vec{z}}[u] )_v  
-        \label{eq:fsc_ce_loss} 
-\end{align}
-The reason for performing the 8:1 temporal sub-sampling in \eqref{eq:def_u_U} is to 
-to make the period of the softmax output $\widehat{\vec{z}}[u]$ in \label{eq:fsc_ce_loss} 
-be similar to the shortest BPE duration. We assume that the {\it sequence-to-sequence}
-neural network models will be trained most efficiently when the period of neural 
-network output roughly matches the period of the target. In addition, this
-output periods must be equal to larger than the shortest target period to prevent
-missing some targets.
-The shortest duration of each BPE is similar to the average length of {\it phones}, 
-which is any distinct speech sound serving as a phonetic unit.
-It has been observed that the average phone duration is between 50 {\it ms}
-\textasciitilde 100 {\it ms} \cite{x_wang_icslp_1996_00, z_bartosz_ltc_2009_00}.
-Under this rationale, we chose the temporal sub-sampling factor of 8:1. 
-We also observe this sub-sampling factor is optimal in our experiments as well.
-
-\subsection{Target units of Feedback Sequence Classifier}
-\label{sec:target_units}
-
-In FSC, we use subword units created by BPE \cite{r_sennrich_acl_2016_00} for
-the output vocabulary $\mathbb{V}$ in 
-\eqref{eq:transformation} and \eqref{eq:subsampled_latent_label_seq}.
-
-When creating the latent frame-wise label sequence $\mathcal{Z}[0:U]$ 
-in \eqref{eq:subsampled_latent_label_seq}, we distinguish the onset frame
-from other frames.  For example, if we have a BPE unit
-("{\it an}") in the vocabulary $\mathbb{V}$, then we define another
-target ("{\it an$_o$}") which marks the on-set frame of this BPE
-interval. Thus, when the number of BPE units is $B$, the total
-number of vocabularies in $\mathbb{V}$ becomes $2B$.
-We refer this approach to as {\it BPE with onset marking}.
-
-The reason for using this approach is two-folds. First, since FSC
-generates an inference output for each frame, if the same
-BPE symbol repeatedly appears, it is difficult to tell whether 
-this BPE is really expected to appear multiple times or whether 
-the a single BPE is continuing. For example, when we have 
-a sequence \{"{\it an}", "{\it an} "\}
-as the inference output, it is difficult to tell whether it should be a single
-"{\it an}" or two "{\it an}"s. With the onset marking,
-a decoder needs to print out the inference outputs with onset marking. 
-The blank symbol in CTC also plays a similar role. However this blank symbol
-is a common symbol following any labels. In the FSC algorithm, the information
-given by the feedback paths is crucial in performance. In this aspect,
-blank symbol is not very useful for this feedback structure. 
-Second, we have frequently observed that the on-set portion of sound
-has a very important role in human auditory perception 
-\cite{C_Kim_INTERSPEECH_2014_2}.
-
-\subsection{Training of the Feedback Sequence Classifier}
-In this section, we describe how to train FSC.  Algorithm 
-\ref{algo:fsc_training} shows how FSC is trained using the 
-$N$-best alignment algorithm and the cross entropy loss function. 
-$N$-best algorithm will be described 
-in Sec. \ref{sec:n_best_alignment} in detail.
-In Algorithm \ref{algo:fsc_training}  
-As mentioned in Sec. 
-\ref{sec:frame_synchronous_inference}, FSC performs inference
-in a frame-synchronous way.
-The first step is making an 
-In this section, we describe how to train FSC. The first step is 
-is to make an alignment using the $N$-best alignment. The second step is updating the
-neural network parameters using the Cross Entropy (CE) criterion.
-
-The first step is finding the optimal frame-synchronous sequence
-$\mathcal{Z}[0:M]$.
-
-\begin{algorithm}
-  \caption{Training procedure for the FSC algorithm}
-  \label{algo:fsc_training}
-  \begin{algorithmic}
-    \State $\Theta^{(0)} \leftarrow$ initialize\_parameters()
-    \For {epoch index $i = 0, . . . , I-1$}
-      \For {each batch $\left\{\mathcal{X}[0:M],
-                        \mathcal{Y}_{0:L}  \right\}$}, 
-        \State $ {{\mathcal{Z}^{(i)}}[0:U]}
-          \leftarrow
-          \text{n\_best\_align}
-          \left(
-            \mathcal{X}[0:M] \Big| \Theta^{(i)}
-          \right)$
-
-        \State {$\Theta^{(i)} \leftarrow$ update\_parameter 
-          $\left(
-            \mathcal{X}[0:M],
-            \mathcal{Z}^{(i)}[0:U]
-          \right)$}
-
-    \EndFor
-    \State $\Theta^{(i+1)} := \Theta^{(i)}$
-  \EndFor
-  \label{algorithm:fsc_training}
-  \end{algorithmic}
-\end{algorithm}
-
-\subsection{N-best alignment}
-\label{sec:n_best_alignment}
-
-In CTC in Sec. \ref{sec:ctc} and in RNN-T in Sec. \ref{sec:rnn_t}, the 
-forward-backward algorithm is employed to update parameters. 
-For example in CTC, the forward-backward algorithm is based on the
-following assumption:
-\begin{align}
-  P \left(  \Big| \right) = \Pi
-\end{align}
-
-In conventional frame-wise CE-training, Viterbi alignment 
-(a.k.a forced alignment) has been performed to obtain the frame-level 
-acoustic unit  boundaries TODO(chanwcom). Even though the Viterbi algorithm
-has advantages in simplicity and efficiency, it is based on
-the following conditional independence assumption.
-
-In FSC, we propose the following $N$-best alignment approach rather than
-the Viterbi alignment algorithm to find the alignment information.
-
-TODO(chanw.com) Define $f$.
-
 \section{Experimental Results}

### 2019-06-30 none_cloud_post_processing_decoding/doc/main.tex
Udpates the paper

@@
 
-\usepackage{neurips_2019}
+\usepackage[preprint]{neurips_2019}
 
@@
 \author{
-  David S.~Hippocampus\thanks{Use footnote for providing further
-    information about author (webpage, alternative
-    address)---\emph{not} for acknowledging funding agencies.} \\
-  Department of Computer Science\\
-  Cranberry-Lemon University\\
-  Pittsburgh, PA 15213 \\
-  \texttt{hippo@cs.cranberry-lemon.edu} \\
+  Chanwoo Kim  \\
+  Samsung Research \\
+  Seoul, Korea, 06765 \\
+  \texttt{chanw.com@samsung.com}  \\
+  \And
+  Kyungmin Lee  \\
+  Samsung Research \\
+  Seoul, Korea, 06765 \\
+  \texttt{k-m-lee@samsung.com} \\
+  \And
+  Eunhyang Kim  \\
+  Samsung Research \\
+  Seoul, Korea, 06765 \\
+  \texttt{sc.ehkim.jin@samsung.com} \\
+  \And
+  Kwangyoun Kim \\
+  Samsung Research \\
+  Seoul, Korea, 06765 \\
+  \texttt{sc.ehkim.jin@samsung.com} \\
+  \And
+  Dhananjaya Gowda \\
+  Samsung Research \\
+  Seoul, Korea, 06765 \\
+  \texttt{d.gowda@samsung.com} \\
   %% examples of more authors
@@
 
-\section{Review on frame-synchronous speech recognition}
+Recently, there has been tremendous improvements in speech recognition
+systems fueled by advances in deep neural networks
+\cite{
+  Yu2013FeatureLearningDNN, 
+  g_hinton_ieee_signal_processing_mag_2012,
+  Seltzer2013DNNAurora4, 
+  t_sainath_taslp_2017_00,
+  t_sainath_book_chapter_2017_00,
+  v_vanhoucke_nips_workshop_2011_00}.
+These improvements have come about from the shift from Gaussian Mixture Model
+(GMM) to the Feed-Forward Deep Neural Networks (FF-DNNs), FF-DNNs
+to Recurrent Neural Network (RNN) and in particular the Long Short-Term Memory
+(LSTM) networks.
+Thanks to these advances, voice assistant devices such as Google Home
+\cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}
+or Amazon Alexa or Samsung Bixby are being used at many homes and on personal devices.
 
-Let us suppose that the sequence of the text stream is $T$  
-\begin{align}
-  X
-\end{align}
+Recently there has been increasing interest in switching
+from the conventional Weighted Finite State Transducer (WFST)
+based decoder using an Acoustic Model (AM) and a Language Model (LM)
+to a complete end-to-end all-neural speech recognition systems
+\cite{w_chan_icassp_2016_00, r_prabhavalkar_interspeech_2017_00,
+j_chorowski_nips_2015_00}.
+These complete end-to-end systems have started surpassing the performance of
+the conventional WFST-based decoders with a very large training
+database, a better choice of target unit such as Byte Pair Encoded (BPE)
+subword units, and an improved training methodology such as Minimum
+Word Error Rate (MWER) training.
 
-A speech recognizers maps a sequence of input acoustic features into a sequence 
-of text labels  \cite{r_prabhavalkar_interspeech_2017_00}. 
-Mathematically, this model is 
-represented by the following transformation $\mathcal{T}$ 
-\cite{a_graves_icml_2006_00}:
-\begin{align}
-  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
-	\label{eq:transformation}
-\end{align}
-where the symbol ${*}$ denotes a sequence, $d$ is the dimension of the input 
-feature. $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
-labels, which may be graphemes 
-\cite{j_chorowski_nips_2015_00,
-w_chan_icassp_2016_00},
-subword units \cite{
-a_zeyer_interspeech_2018_00,
-c_chiu_icassp_2018_00},
- and words \cite{h_soltau_interspeech_2017_00}.
+Another important aspect of these recent improvements in speech
+recognition performance is data.
+To build high performance speech recognition systems for
+conversational speech, we need to use
+a large amount of speech data covering various domains. In
+\cite{h_soltau_interspeech_2017_00}, it has been shown
+that we need a very large training set ($\sim$125,000 hours of
+semi-supervised speech data) to achieve
+high speech recognition accuracy for difficult tasks like
+video captioning. To train neural networks using such large
+amounts of speech data, we usually need
+multiple Central Processing Units (CPUs) or Graphics
+Processing Units (GPUs) or GPU clusters
+\cite{E_Variani_INTERSPEECH_2017_01, p_goyal_arxiv_2018_00}.
 
-\section{The structure of the Server-side Post Processing System}
+\section{Overview of the Enhancement by Post-Processing}
 
@@
 to {\it speech recognition on the local device} and 
-{\it post processing on the server} respectively.  The symbols used in this 
-figure is defined as follows:
-%
+{\it post processing on the server} respectively.
+
+TODO(chanw.com) Describe the advantage of the server side post-processing.
+
+\begin{subequations}
+  \begin{align}
+    \text{On-Device Speech Recognition}   : 
+        & \quad \{ \, \cdots ,\, \vec{x}[m],     \cdots \, \} \rightarrow  
+                \{ \, \cdots ,\, \hat{z}_o[l],   \cdots \, \} \\
+    \text{Server-Side Post-Processing} : 
+        & \quad \{ \, \cdots ,\, \hat{z}_o[l],   \cdots \, \}  \rightarrow
+                \{ \, \cdots ,\, W_i,   \cdots \, \}
+  \end{align}
+\end{subequations}
+where $\vec{x}[m]$ is the speech feature vector with $m$ being the 
+frame index and $\hat{z}_o[l]$ is the frame-synchronous hypothesis 
+from the speech recognizer with $l$ being the frame index. More details
+about the frame-synchronous hypothesis will be covered in Sec. 
+\ref{sec:frame_synchronous_hypothesis}. The reason for using a different
+frame index $l$ for $\hat{z}_o[l]$ is that the frame period in hypothesis
+generation may be different from the frame period in feature extraction.
+As will be discussed in Sec \ref{sec:frame_synchronous_hypothesis}, 
+the sequence of $\hat{z}_o[l]$ is a stream of graphemes.
+
+When the server-side post processing is needed, the sequence of
+
+Before describing structures in detail in Sec.
+\ref{sec:frame_synchronous_hypothesis} and in Sec.
+\ref{sec:server_side_post_processing}, we will first define notational 
+conventions in this section. When representing a sequence consisting of 
+periodic elements we will use a bracket symbol to represent elements of
+such a sequence. For example, speech features are usually calculated 
+periodically at every frame interval (e.g. 10 ms). Thus, we use  
+the symbol $\vec{x}[m]$ in
+To represent sequences, we will use the bracket symbol
+to represent periodic data such as feature vector $\vec{x}[m]$. Usually
+speech features are usually sampled at around 10 ms intervals. TODO(chanw.com)
+Adds citation. To represent a sequence $\alpha$ starting from the index 
+$i$ and ending at $f-1$, we use the notation inspired by the python slice 
+notation 
+\begin{align}
+  \alpha[i:f] = \{ \alpha[m]| i \le m < f \} 
+\end{align}
+Using this notational convention, we summarize the symbols used in Fig
+\ref{fig:entire_system} as follows:
 \begin{align}
@@
 set of words. In Fig. \ref{fig:entire_system}, there are two top level
-blocks. The left and right blocks correspond to processing on the local
-device and the server side post processing respectively.
 
-\subsection{Label Likelihood Calculation}
-To perform decoding described in Section \ref{sec:decoding}, 
-we need to calculate likelihood $P(\hat{y}_o[0:l+1] | y_p[l])$
-where $\hat{y}_o[0:l+1]$ is the sequence of the frame-synchronous 
-label hypothesis.
-Using the Bayes rule, this likelihood is expressed in the following form:
-\begin{align}
-  P(\hat{y}_o[0:l+1] \big| y_p[l]) 
-    = \frac{P(y_p[l] \big| \hat{y}_o[0:l+1])
-        P\left(\hat{y}_o[0:l+1] \right)}{P(y_p[l])}.
-  \label{eq:likelihood_prob}
-\end{align}
-To calculate the above equation, the following three terms need to be
-calculated:
-\begin{align}
-  P(y_p[l] \big| \hat{y}_o[0:l+1]): & \text{ A posterior probability of } y_p[l]
-    \text{ given the frame-synchronous label sequence } \nonumber \\ 
-    & \hat{y}_o[0:l+1].
-    \nonumber \\
-  P\left(\hat{y}_o[0:l+1] \right): & 
-    \text{ A probability of the sequence of frame-synchronous labels } \hat{y}_o[0:l+1].
-      \nonumber \\
-  P(y_p[l]): & \text{ A prior probability of the label } y_p[l] \in \mathbb{V}.
-  \label{eq:prob_components_likelihood}
-\end{align}
+\section{Obtaining frame-synchronous hypothesis}
+\label{sec:frame_synchronous_hypothesis}
 
-To calculate $P\left(\hat{y}_o[0:l+1] \right)$ in \eqref{eq:likelihood_prob}, 
-we use a either statistical n-gram or a RNN based Language Model (LM). 
-One notable difference of the LM used for this purpose compared 
-to a conventional LM is that this LM must be a frame-synchronous LM.
-and must be trained from frame-synchronous label corpus. 
-Thus, we first need to align transcribed speech corpus to obtain frame-synchronous 
-labels and train LM from this corpus. 
-Finally, we use this LM to calculate $P\left(\hat{y}_o[0:l+1] \right)$.
-
-Instead of calculating the likelihood of the whole sequence 
-$\hat{y}_o[0:l+1]$ described above, a simpler alternative is to ignore
-the past values of the original hypothesis $\hat{y}_o[0:l+1]$ and only to
-consider the current one $\hat{y}_o[l]$. Under this simplification,
-the likelihood in \eqref{eq:likelihood_prob} may be simplified as follows:
-\begin{align}
-  P(\hat{y}_o[l] \big| y_p[l]) 
-    = \frac{P (y_p[l] \big| \hat{y}_o[l]) P(\hat{y}_o[l])}{P(y_p[l])} 
-\end{align}
-
-\subsection{Decoding}
-\label{sec:decoding}
-The structure of the post-processing decoder is depicted in Fig.
-\ref{fig:post_processing_decoder}. Using the dictionary and the
-language model, the hypothesis word sequence $W_i$ is obtained
-from the posterior probability in \eqref{eq:post_prob}.
-
-\begin{figure}
-  \centering
-    \centering
-    \resizebox{130mm}{!}{
-      \input{../figures/hybrid_on_device_cloud_asr.tex}
-    }
-    \caption {
-      The structure of an entire system consisting of the on-device speech 
-      recognition and the server-side post processing. 
-      \label{fig:entire_system}
-    }
-\end{figure}
-
-\begin{figure}
-  \centering
-    \centering
-    \resizebox{55mm}{!}{
-      \input{../figures/asr_system.tex}
-    }
-    \caption {
-      The on-device Automatic Speech Recognition (ASR) system.
-      \label{fig:asr_system}
-    }
-\end{figure}
-
-\begin{figure}
-    \centering
-    \resizebox{30mm}{!}{
-      \input{../figures/label_posteior_prob_estimation.tex}
-    } 
-    \caption {
-      Estimation of the label posterior probability
-      \label{fig:label_posterior_prob_estimation}
-    }
-\end{figure}
-
-\begin{figure}
-    \centering
-    \resizebox{70mm}{!}{
-      \input{../figures/post_processing_decoder.tex}
-    } 
-    \caption {
-      The post-processing decoder for generating the word sequence $W_i$
-      from the label likelihood $P(\hat{y}_o[0:l+1] | \hat{y}_p[l])$ in \eqref{eq:post_prob}, 
-      using the dictionary and the language model.
-      \label{fig:post_processing_decoder}
-    }
-\end{figure}
-
-\section{Introduction}
-Recently, there has been tremendous improvements in speech recognition
-systems fueled by advances in deep neural networks
-\cite{
-  Yu2013FeatureLearningDNN, 
-  g_hinton_ieee_signal_processing_mag_2012,
-  Seltzer2013DNNAurora4, 
-  t_sainath_taslp_2017_00,
-  t_sainath_book_chapter_2017_00,
-  v_vanhoucke_nips_workshop_2011_00}.
-TODO(chanw.com) Describes history about starting using DNN, LSTM.
-
-\section{Review on sequence-to-sequence speech recognition algorithms}
+In this section, we describe how to obtain frame-synchronous  
+hypothesis from a speech recognition decoder.
 
@@
   \centering
-  \begin{subfigure}[b]{0.60\textwidth}
+  \begin{subfigure}[b]{0.50\textwidth}
     \centering
-    \resizebox{78mm}{!}{
+    \resizebox{70mm}{!}{
       \input{../figures/rnn_t_diagram.tex}
@@
   \end{subfigure}
-
-  \begin{subfigure}[b]{0.55\textwidth}
+  \begin{subfigure}[b]{0.45\textwidth}
     \centering
-    \resizebox{53mm}{!}{
+    \resizebox{55mm}{!}{
       \input{../figures/attention_diagram.tex}
@@
   \caption{
-    Comparison of block diagrams of different sequence-to-sequence speech
-    recognition approaches.
-    The proposed Feedback Sequence Classifier (FSC) is shown in 
-    Fig. \ref{fig:fsc_diagram}.
+    Examples of a frame-synchronous decoding in \ref{fig:rnn_t_diagram}
+    and a label-synchronous decoding in \ref{fig:attention_diagram}.
   }
 
+\end{figure}
+
+Let us suppose that the sequence of the text stream is $T$  
+\begin{align}
+  X
+\end{align}
+
+A speech recognizers maps a sequence of input acoustic features into a sequence 
+of text labels  \cite{r_prabhavalkar_interspeech_2017_00}. 
+Mathematically, this model is 
+represented by the following transformation $\mathcal{T}$ 
+\cite{a_graves_icml_2006_00}:
+\begin{align}
+  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
+	\label{eq:transformation}
+\end{align}
+where the symbol ${*}$ denotes a sequence, $d$ is the dimension of the input 
+feature. $\mathbb{V}$ in \eqref{eq:target_label} is the set of output
+labels, which may be graphemes 
+\cite{j_chorowski_nips_2015_00,
+w_chan_icassp_2016_00},
+subword units \cite{
+a_zeyer_interspeech_2018_00,
+c_chiu_icassp_2018_00},
+ and words \cite{h_soltau_interspeech_2017_00}.
+
+\section{The structure of the Server-side Post Processing System}
+\label{sec:server_side_post_processing}
+
+Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
+system and the server-side post processing system. In this figure,  
+the two top level blocks on the left and the right hand sides correspond
+to {\it speech recognition on the local device} and 
+{\it post processing on the server} respectively.
+
+\subsection{Label Likelihood Calculation}
+To perform decoding described in Section \ref{sec:decoding}, 
+we need to calculate likelihood $P(\hat{y}_o[0:l+1] | y_p[l])$
+where $\hat{y}_o[0:l+1]$ is the sequence of the frame-synchronous 
+label hypothesis.
+Using the Bayes rule, this likelihood is expressed in the following form:
+\begin{align}
+  P(\hat{y}_o[0:l+1] \big| y_p[l]) 
+    = \frac{P(y_p[l] \big| \hat{y}_o[0:l+1])
+        P\left(\hat{y}_o[0:l+1] \right)}{P(y_p[l])}.
+  \label{eq:likelihood_prob}
+\end{align}
+To calculate the above equation, the following three terms need to be
+calculated:
+\begin{align}
+  P(y_p[l] \big| \hat{y}_o[0:l+1]): & \text{ A posterior probability of } y_p[l]
+    \text{ given the original frame-synchronous hypothesis } \nonumber \\ 
+    & \hat{y}_o[0:l+1].
+    \nonumber \\
+  P\left(\hat{y}_o[0:l+1] \right): & 
+    \text{ A probability of the original frame-synchronous hypothesis } \hat{y}_o[0:l+1].
+      \nonumber \\
+  P(y_p[l]): & \text{ A prior probability of the label } y_p[l] \in \mathbb{V}.
+  \label{eq:prob_components_likelihood}
+\end{align}
+%
+\begin{figure}
+    \centering
+    \resizebox{40mm}{!}{
+      \input{../figures/label_posteior_prob_estimation.tex}
+    } 
+    \caption {
+      Estimation of the label posterior probability
+      \label{fig:label_posterior_prob_estimation}
+    }
+\end{figure}
+%
+To calculate $P(y_p[l] \big| \hat{y}_o[0:l+1])$ in
+\eqref{eq:prob_components_likelihood}, we first train a neural network
+to predicting the distribution of $y_p[l]$ given the original 
+frame-synchronous hypothesis. Fig. \ref{fig:label_posterior_prob_estimation}
+shows the structure of such a neural network stack. To train this
+neural network stack, we need to have both the frame-level 
+original hypothesis $\hat{y}_o[l]$ and the corresponding the frame-level
+ground truth. Since the ground-truth labels are usually not given in the
+frame-level format, forced alignment needs to be applied to obtain
+the frame-synchronous ground truth.
+
+To calculate $P\left(\hat{y}_o[0:l+1] \right)$ in \eqref{eq:likelihood_prob}, 
+we use a either statistical n-gram or a RNN based Language Model (LM). 
+One notable difference of the LM used for this purpose compared 
+to a conventional LM is that this LM must be a frame-synchronous LM.
+and must be trained from frame-synchronous label corpus. 
+Thus, we first need to align transcribed speech corpus to obtain frame-synchronous 
+labels and train LM from this corpus. 
+Finally, we use this LM to calculate $P\left(\hat{y}_o[0:l+1] \right)$.
+
+Instead of calculating the likelihood of the whole sequence 
+$\hat{y}_o[0:l+1]$ described above, a simpler alternative is to ignore
+the past values of the original hypothesis $\hat{y}_o[0:l+1]$ and only to
+consider the current one $\hat{y}_o[l]$. Under this simplification,
+the likelihood in \eqref{eq:likelihood_prob} may be simplified as follows:
+\begin{align}
+  P(\hat{y}_o[l] \big| y_p[l]) 
+    = \frac{P (y_p[l] \big| \hat{y}_o[l]) P(\hat{y}_o[l])}{P(y_p[l])} 
+\end{align}
+
+\subsection{Decoding}
+\label{sec:decoding}
+The structure of the post-processing decoder is depicted in Fig.
+\ref{fig:post_processing_decoder}. Using the dictionary and the
+language model, the hypothesis word sequence $W_i$ is obtained
+from the posterior probability in \eqref{eq:post_prob}.
+
+\begin{figure}
+  \centering
+    \centering
+    \resizebox{130mm}{!}{
+      \input{../figures/hybrid_on_device_cloud_asr.tex}
+    }
+    \caption {
+      The structure of an entire system consisting of the on-device speech 
+      recognition and the server-side post processing. 
+      \label{fig:entire_system}
+    }
+\end{figure}
+
+\begin{figure}
+  \centering
+    \centering
+    \resizebox{55mm}{!}{
+      \input{../figures/asr_system.tex}
+    }
+    \caption {
+      The on-device Automatic Speech Recognition (ASR) system.
+      \label{fig:asr_system}
+    }
+\end{figure}
+
+\begin{figure}
+    \centering
+    \resizebox{70mm}{!}{
+      \input{../figures/post_processing_decoder.tex}
+    } 
+    \caption {
+      The post-processing decoder for generating the word sequence $W_i$
+      from the label likelihood $P(\hat{y}_o[0:l+1] | \hat{y}_p[l])$ in \eqref{eq:post_prob}, 
+      using the dictionary and the language model.
+      \label{fig:post_processing_decoder}
+    }
 \end{figure}

### 2019-06-30 none_cloud_post_processing_decoding/doc/main.tex
update the paper

@@
 
+\begin{figure}
+  \centering
+    \centering
+    \resizebox{130mm}{!}{
+      \input{../figures/hybrid_on_device_cloud_asr.tex}
+    }
+    \caption {
+      The structure of an entire system consisting of the on-device speech 
+      recognition and the server-side post processing. 
+      \label{fig:entire_system}
+    }
+\end{figure}
+
 Fig. \ref{fig:entire_system} shows the entire structure of the on-device ASR
@@
         & \quad \{ \, \cdots ,\, \vec{x}[m],     \cdots \, \} \rightarrow  
-                \{ \, \cdots ,\, \hat{z}_o[l],   \cdots \, \} \\
+                \{ \, \cdots ,\, \hat{y}_o[l],   \cdots \, \} \\
     \text{Server-Side Post-Processing} : 
-        & \quad \{ \, \cdots ,\, \hat{z}_o[l],   \cdots \, \}  \rightarrow
+        & \quad \{ \, \cdots ,\, \hat{y}_o[l],   \cdots \, \}  \rightarrow
                 \{ \, \cdots ,\, W_i,   \cdots \, \}
@@
 \ref{sec:frame_synchronous_hypothesis}. The reason for using a different
-frame index $l$ for $\hat{z}_o[l]$ is that the frame period in hypothesis
+frame index $l$ for $\hat{y}_o[l]$ is that the frame period in hypothesis
 generation may be different from the frame period in feature extraction.
 As will be discussed in Sec \ref{sec:frame_synchronous_hypothesis}, 
-the sequence of $\hat{z}_o[l]$ is a stream of graphemes.
+the sequence of $\hat{y}_o[l]$ is a stream of graphemes.
 
 When the server-side post processing is needed, the sequence of  
+of frame synchronous hypothesis
 
@@
 In this section, we describe how to obtain frame-synchronous  
-hypothesis from a speech recognition decoder.
+hypothesis from a speech recognition decoder. The function of a speech
+recognizer is to map a sequence of acoustic feature vectors into
+a sequence of graphemes or words. This transformation may be represented 
+by the following equation:
+\begin{align}
+  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
+	\label{eq:transformation}
+\end{align}
 
@@
 The loss function in the frame-synchronous inference case
-$\mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ is 
+$\mathbb{L}_{\text{fs}}\left(\vec{x}[0:M], y_{0:L}\right)$ is 
 defined as follows:
 \begin{align}
-  \mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Z}[0:M]\right) 
+  \mathbb{L}_{\text{fs}}\left(\vec{x}[0:M], z[0:M]\right) 
       = \sum_{l=0}^{M-1} 
@@
     \centering
-    \resizebox{130mm}{!}{
-      \input{../figures/hybrid_on_device_cloud_asr.tex}
-    }
-    \caption {
-      The structure of an entire system consisting of the on-device speech 
-      recognition and the server-side post processing. 
-      \label{fig:entire_system}
-    }
-\end{figure}
-
-\begin{figure}
-  \centering
-    \centering
     \resizebox{55mm}{!}{

### 2019-07-02 interspeech_2019_training_infra/doc/main.tex
Updates papers

% Template for ICASSP-2019 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass[a4paper]{article}

\usepackage{INTERSPEECH2019}
\usepackage{amsmath,graphicx}
\usepackage{amssymb,amsmath,bm}
\usepackage{textcomp}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{multirow}
%\usepackage{subcaption}
\usepackage[justification=centering]{caption}
\usepackage[caption = false]{subfig}

% Custom settings
\usepackage{tikz,placeins}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

\graphicspath{{../figures/}}

\newcommand{\specialcell}[2][c]{%
     \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcommand{\chanwcom}{{C. Kim}}
\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}
\renewcommand{\textfraction}{0.01}
\renewcommand{\floatpagefraction}{1.0}
\renewcommand{\dbltopfraction}{1.0}
\renewcommand{\floatpagefraction}{1.0}  % require fuller float pages
\renewcommand{\dblfloatpagefraction}{1.0} % require fuller float pages

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{End-to-end Training of a Large Vocabulary \\ End-to-end Speech Recognition System}
%\title{End-to-end training framework with on-the-fly data augmentation for building a large vocabulary end-to-end speech secognition system}
%
% Single address.
% ---------------
\name{Chanwoo Kim, Sungsoo Kim, Kwangyoun Kim, Mehul Kumar,
Jiyeon Kim, Kyungmin Lee, Changwoo Han, Abhinav Garg, Eunhyang Kim, Minkyoo
Shin, Shatrughan Singh, Larry Heck, Dhananjaya Gowda
\thanks{Thanks to Samsung
Electronics for funding this research. The authors are thankful to  
Executive Vice President Seunghwan Cho and members of Speech Processing Lab
 at Samsung Research.}}

\address{Samsung Research }
\email{\{chanw.com, ss216.kim, ky85.kim, mehul3.kumar, jstacey7.kim,
k.m.lee, cw1105.han, abhinav.garg, sc.ehkim.jin, mk0211.shin, shatrughan.s, 
larry.h, d.gowda\}@samsung.com }
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
\ninept
%
\maketitle
%
\begin{abstract}
In this paper, we present an end-to-end training framework and strategies for 
building state-of-the-art end-to-end (E2E) speech recognition systems.
Our training system utilizes a cluster of Central Processing Units 
  (CPUs) and Graphics Processing Units (GPUs).
The entire data reading, large scale data augmentation,
neural network parameter updates are all performed on-the-fly. 
  We use vocal tract length perturbation and an acoustic simulator 
for data augmentation. The processed features and labels are sent 
to the GPU cluster. Horovod {\tt allreduce} approach is employed to train
neural network parameters.
We evaluated the effectiveness of our system on the standard 
Librispeech corpus \cite{v_panayotov_icassp_2015_00} and 
  10,000-hr anonymized Bixby English dataset. 
Our end-to-end speech
recognition system built using this training infrastructure showed 
  2.85 \% WER on {\tt test-clean} for the LibriSpeech corpus 
 after shallow fusion with a recurrent neural network (RNN) language model (LM).
 For English Bixby open domain test set,
we obtained a WER of 7.92 \% using 
a bidirectional full attention (BFA) E2E model after shallow fusion with an RNN-LM.
When the monotonic chunckwise attention (MoCha) based approach is employed for 
streaming speech recognition, we obtained a WER of 9.95 \% 
  on the same Bixby open domain test set.
\end{abstract}
%
%\begin{keywords}
  \noindent{\bf Index Terms}: end-to-end speech recognition,
distributed training, example server, data augmentation, acoustic simulation
%\end{keywords}
%
%
\section{Introduction}
In recent years, deep learning techniques have significantly 
improved speech recognition accuracy \cite{Seltzer2013DNNAurora4, 
Yu2013FeatureLearningDNN, V_Vanhoucke_Deep_Learning_NIPS_Workshop_2011,
G_Hinton_IEEE_Signal_Process_Mag_2012,
T_Sainath_IEEETran_2017_1, T_Sainath_Book_Chapter_2017_1}.
This improvement has come about from the shift from Gaussian Mixture Model
(GMM) to the Feed-Forward Deep Neural Networks (FF-DNNs), FF-DNNs
to Recurrent Neural Network (RNN) and in particular the Long Short-Term Memory
(LSTM) networks. 
Thanks to these advances, voice assistant devices such as Google Home
\cite{C_Kim_INTERSPEECH_2017_1, B_Li_INTERSPEECH_2017_1}
or Amazon Alexa or Samsung Bixby are being used at many homes and on personal devices.

Recently there has been increasing interest in switching
from the conventional Weighted Finite State Transducer (WFST)
based decoder using an Acoustic Model (AM) and a Language Model (LM)
to a complete end-to-end all-neural speech recognition systems 
\cite{w_chan_icassp_2016_00, r_prabhavalkar_interspeech_2017_00, 
j_chorowski_nips_2015_00}. 
These complete end-to-end systems have started surpassing the performance of
the conventional WFST-based decoders with a very large training 
database, a better choice of target unit such as Byte Pair Encoded (BPE) 
subword units, and an improved training methodology such as Minimum
Word Error Rate (MWER) training.

Another important aspect of these recent improvements in speech
recognition performance is data. 
To build high performance speech recognition systems for
conversational speech, we need to use
a large amount of speech data covering various domains. In
\cite{h_soltau_interspeech_2017_00}, it has been shown
that we need a very large training set ($\sim$125,000 hours of 
semi-supervised speech data) to achieve
high speech recognition accuracy for difficult tasks like 
video captioning. To train neural networks using such large 
amounts of speech data, we usually need 
multiple Central Processing Units (CPUs) or Graphics
Processing Units (GPUs) or GPU clusters 
\cite{E_Variani_INTERSPEECH_2017_01, p_goyal_arxiv_2018_00}.

With widespread adoption of voice assistant speakers, far-field
speech recognition has become very important.
In far-field speech recognition, the impacts of reverberation and noise 
are much larger than those in near-field cases. 
Traditional approaches to far-field
speech recognition include noise robust feature extraction algorithms
\cite{C_Kim_IEEETran_2016_1, U_H_Yapanel_SpeechComm_2008},
or multi-microphone approaches
\cite{T_Nekatani_ICASSP_2017_1, T_Higuchi_ICASSP_2016_1,
H_Erdogan_INTERSPEECH_2016_1,
C_Kim_INTERSPEECH_2010_1, C_Kim_ICASSP_2012_2}.
More recently, approaches using data augmentation
has been gaining popularity for far-field speech recognition
\cite{R_Lippmann_icassp_1987_1,
c_kim_interspeech_2018_00, w_hartmann_interspeech_2016_00}. 
An ``acoustic simulator"  
\cite{C_Kim_INTERSPEECH_2017_1, c_kim_interspeech_2018_00}
is used to generate simulated speech utterances for
millions of different room dimensions, a wide distribution
of reverberation time and signal-to-noise ratio. In a similar 
spirit, Vocal Tract Length Perturbation (VTLP) has been proposed 
\cite{n_jaitly_icml_workshop_2013_00} to tackle the speaker variability issue.
As shown in our recent paper \cite{c_kim_interspeech_2019_00}, 
VTLP is especially useful when
the speaker variability in the training database is not sufficient. 
For these kinds of data augmentation, processing on CPUs is more
desirable than processing on GPUs. Due to this, we have proposed
an end-to-end training approach using Example Servers (ES)
 and workers. Example servers are typically run on the CPU
cluster performing data reading, data augmentation, and feature extraction
\cite{c_kim_interspeech_2018_00}.

%
%
\begin{figure*}[!tbp]
  \begin{center}
    \resizebox{\textwidth}{!}{\input{../figures/end_to_end_training_system.tex}}
      \caption { The Samsung Research end-to-end training framework for building an end-to-end
	speech recognition system with multi CPU-GPU clusters and on-the-fly data
	processing and augmentation pipeline.
     }   
     \label{fig:end_to_end_training_system}
  \end{center}
\vspace{-5mm}
\end{figure*}
%
%

In this paper, we describe the structure of our end-to-end training system
to train an end-to-end speech recognition system. This training system
has several advantages over previous systems described in
\cite{c_kim_interspeech_2018_00}. First, instead of using the {\tt QueueRunner},
we use a more efficient data queue using {\tt tf.data} in Tensorflow 
\cite{m_abadi_usenix_2016}.  Second, instead
of pre-calculating information about room configurations and 
room impulse responses in the acoustic simulator, these are
calculated on-the-fly. Thus, the entire training system runs on
-the-fly. Additionally, instead of using the parameter server-worker
structure, we use an {\tt allreduce} approach implemented in the Horovod
\cite{a_sergeev_arxiv_2018_00} distributed training framework, which
has been shown to be more efficient. The system described in 
\cite{E_Variani_INTERSPEECH_2017_01}, is designed
to train the acoustic model part of the speech recognition system where
as our training system trains the complete end-to-end speech recognition system.

The rest of the paper is organized as follows: We describe the entire
training system structure in detail in Sec. \ref{sec:training_cpu_gpu}.
The structure of the end-to-end speech recognition system 
is described in Sec. \ref{sec:end_to_end_speech_recognition}. 
Experimental results that demonstrates the effectiveness of our speech
recognition system is presented in Sec. \ref{sec:experimental_results}. 
We conclude in Sec.  \ref{sec:conclusions}.
%
\section{Overall structure of the end-to-end speech recognition}
\label{sec:training_cpu_gpu}
\vspace{-1mm}

In this section, we describe the overall structure of our 
end-to-end training system.  Fig. \ref{fig:end_to_end_training_system}
shows how the entire system is structured. Our system consists
of a cluster of CPUs and a cluster of GPUs. Each GPU node of 
the GPU cluster has eight nVidia\texttrademark P-40 GPUs and two 
Intel E5-2690 v4 CPUs. Each of these CPUs has 14 cores.
The large box on the left hand side of Fig. \ref{fig:end_to_end_training_system}
denoted ``GPU cluster'' shows a typical GPU node with $N$ GPUs.
The large box on the right shows a ``CPU cluster'' of $M$ CPUs,
each running an independent data pipeline.

\vspace{-1mm}
\subsection{Training job launch}
The main process of the training system runs on one of CPU cores 
of the GPU cluster. This CPU portion of the GPU node is represented
as a box in the right hand side of the GPU node box.
When the training job starts, this main training process launches
multiple example server jobs on the CPU cluster using the 
{\tt IBM Platform LSF} \cite{ibm_spectrum_lsf_2010}. In Fig. 
\ref{fig:end_to_end_training_system}, this launching process is represented
by a dashed arrow from the CPU portion of the GPU node to the 
CPU cluster.

\subsection{Data reading using an example queue}
In the CPU cluster, each CPU runs one example server
which reads speech utterance and transcript data from sharded 
{\tt TFRecords} defined in Tensorflow \cite{m_abadi_usenix_2016}.
The TFRecord format is a simple format in Tensorflow for storing 
a sequence of binary records. To support efficient reading using 
multiple CPUs, we use sharded {\tt TFRecords}.

To read large-scale data efficiently in parallel, we use an example queue
shown in the left side of Fig. \ref{fig:end_to_end_training_system}.  
The original speech waveform data, transcripts, and meta data are stored
in sharded {\tt TFRecords}. The data pipeline is implemented using
{\tt tf.data} in Tensorflow \cite{m_abadi_usenix_2016}, 
and contains the data augmentation and feature extraction blocks.
These {\tt tf.data} APIs are efficient in building complex pipelines
by applying a series of elementary operations. We perform data interleaving
and parallel reading using {\tt tf.contrib.data.parallel\_interleave}, 
shuffling using {\tt tf.data.Datatset.shuffle}, and padding using 
{\tt tf.data.Dataset.padded\_batch}.

\subsection{Data augmentation and feature extraction}
\label{sec:feature_extraction}
To improve robustness against speaker variability, we apply an
on-the-fly VTLP algorithm on the input waveform. The warping
factor is generated randomly for each input utterance. Unlike
conventional VTLP approaches in \cite{x_cui_taslp_2015_00,
n_jaitly_icml_workshop_2013_00}, we resynthesize the processed
speech. The purpose of doing this is to apply VTLP before applying
the acoustic simulator. One more advantage is that this
resynthesis approach enables us to use a window length 
optimal for VTLP different from that used in feature processing.
In the bilinear transformation, the relation between the input
and output discrete-time frequencies is given by: 
\begin{align}
  \omega_k'  = \omega_k + 2 \tan^{-1} \left(
                    \frac{ \left(1 - \alpha \right) \sin(\omega_k)} 
              {1 - (1 - \alpha) \cos(\omega_k) } \right)
                            \label{eq:bilinear_transformation}.
\end{align}
where $w_k= {2 \pi k}/{K}$ is the discrete-time frequency
 and $K$ is the DFT size. 
More details about our VTLP algorithm can be found
in our another paper \cite{c_kim_interspeech_2019_00}.
The acoustic simulator in Fig.~\ref{fig:end_to_end_training_system}
is similar to what we described in 
\cite{C_Kim_INTERSPEECH_2017_1, c_kim_interspeech_2018_00}.
One difference compared to our previous one in 
\cite{C_Kim_INTERSPEECH_2017_1} is that we do not pre-calculate
room impulse responses, but instead they are calculated on-the-fly.
For feature processing we use {\tt tf.data.Dataset.map} API. 
Instead of using the more conventional log-mel or 
MFCC features, we use the power mel filterbank energies,
since it shows slightly better performance \cite{c_kim_interspeech_2019_01}.

\subsection{Parameter calculation and update}
The features and the target label are sent to the GPU cluster
using the ZeroMQ \cite{zero_mq} asynchronous messaging queue.
Each example server sends these data asynchronously to the CPU portion
of the GPU node as shown in Fig \ref{fig:end_to_end_training_system}.
Using these data, neural network parameters are calculated and updated 
using an Adam optimizer and the
Horovod \cite{a_sergeev_arxiv_2018_00} {\tt allreduce} approach.

\section{Structure of the end-to-end speech recognition system}
\label{sec:end_to_end_speech_recognition}

\begin{figure}[tbp]
  \begin{center}
    \resizebox{65mm}{!}{\input{../figures/e2e_asr_block_diagram}}
      \caption {  The structure of the entire end-to-end
      speech recognition system. 
      %The LSTMs
      %in the encoder layers may be either bidirectional-LSTMs or
      %unidirectional-LSTMs. The attention may be either the full
      %attention or the MOnotonic CHunkwise Attention (MoCha)
      %\cite{c_chiu_iclr_2018_00}.
     }
     \label{fig:entire_diagram}
  \end{center}
\vspace{-5mm}
\end{figure}

We have adopted the RETURNN speech recognition system \cite{p_doetsch_icassp_2017_00,
a_zeyer_interspeech_2018_00} for training our end-to-end system with various modifications.
Some of the important modifications are: replacing the input data pipeline with our 
proposed on-the-fly example server based pipeline with support for VTLP
and acoustic simulation,
implementing the Monotonic Chunkwise Attention (MoChA) \cite{c_chiu_iclr_2018_00}
for online streaming E2E speech recognition, minimum Word Error Rate (mWER) training,
support for handling Korean language or script, our own scoring and Inverse Text 
Normalization modules, support for power mel filterbank features, Maximally Uniform Distribution (MUD) preprocessing of data, etc.

The structure of our entire end-to-end speech recognition system
with MUD processing \cite{c_kim_interspeech_2019_01} is shown 
in Fig.~\ref{fig:entire_diagram}.
 $\vec{x}[m]$ and $\vec{y}[n]$ are the input power mel 
filterbank energy vector and the output label,
respectively. $m$ is the input frame index and $n$ is the decoder output
step index. $\vec{c}[n]$ is the attention context vector calculated 
as a weighted sum of the encoder hidden state vectors denoted as $\vec{h}_{enc}[m]$.
The attention weights are computed as a softmax of energies computed as 
a function of the encoder hidden state $\vec{h}_{enc}[m]$, the decoder hidden state
$\vec{h}_{dec}[n]$, and the attention weight
feedback $\vec{\beta}[m, n]$  \cite{a_zeyer_interspeech_2018_00}.

In \cite{a_zeyer_interspeech_2018_00}, the peak value of the speech 
waveform is normalized to be one. However, since finding the peak sample value 
is not possible for online feature extraction, we do not perform this
normalization. We modified the input pipeline
so that the online feature generation can be performed. We disabled the 
clipping of feature range between -3 and 3, which is the default 
setting for the Librispeech experiment using MFCC 
features in \cite{a_zeyer_interspeech_2018_00}. 
We conducted experiments using both the 
uni-directional and bi-directional Long Short-Term Memories (LSTMs)
\cite{S_Hochreiter_neural_computation_1997_00} in the encoder.
However, uni-directional LSTMs are used in the decoder.
For online speech recognition experiments, we used the
MoChA models \cite{c_chiu_iclr_2018_00} with a chunk size of 2.
 For better stability in LSTM training, we use the gradient clipping by  
global norm \cite{r_pascanu_icml_2013}, which is implemented as  
{\tt tf.clip\_by\_global\_norm } API in Tensorflow  \cite{m_abadi_usenix_2016}.
We use six layers of encoders and one layer of decoder followed by a softmax
layer.

%
%
%
\section{Experimental Results}
\label{sec:experimental_results}
%
In this section, we present a summary of experimental results obtained
for our E2E speech recognition systems built using the proposed
Samsung Research end-to-end training framework.

\begin{table}[!tbhp]
  \renewcommand{\arraystretch}{1.3}
  \centering
        \caption{\label{tbl:power_law_result}
        Word Error Rates (WERs) obtained using MFCC implemented in
        \cite{b_mcfee_proc_scipy_2015_00} and power mel filterbank coefficients
        \\ on the Librispeech corpus \cite{v_panayotov_icassp_2015_00}. For
        each WER number, \\the same experiment was conducted twice and averaged.
        }
        %\vspace{-3mm}
        \begin{tabular}{| c | c  || c | c | c | c |}
          \hline
          \multicolumn{2}{| l ||}{Cell Size}
                                 & \specialcell{MFCC}
                                 & \specialcell{Power Mel \\ 
                                 Filterbank \\
                                 Coefficients} \\
          \hline
          \multirow{3}{*}{1536 cell}    
                  & test-clean  &   4.06  \% &  3.94 \%   \\
                  & test-other  &  13.97  \% & 13.56 \%   \\
                  & average     &   9.02  \% &  8.75 \%   \\
          \hline
       \end{tabular}
       \vspace{-2mm}
\end{table}
%
%
\begin{table}[!tbhp]
  \renewcommand{\arraystretch}{1.3}
  \centering
        \caption{\label{tbl:vtlp_result}
        Word Error Rates (WERs) obtained with VTLP processing
        with different warping factor $\alpha$ distribution, 
        and with and without an RNN LM. The warping factor $\alpha$
			  is the constant controlling warping in \eqref{eq:bilinear_transformation}.
        }
        %\vspace{-3mm}
        \begin{tabular}{| c | c  || c | c | c | c |}
          \hline
          \multicolumn{2}{| l ||}{Warping Factor}
                                 & \specialcell{ 0.7 $\sim$ 1.3 }
                                 & \specialcell{ 0.8 $\sim$ 1.2 }  
                                 & \specialcell{ 0.9 $\sim$ 1.1 }   \\
          \hline \hline
          \multirow{3}{*}{\specialcell{Without \\ RNN-LM}}
                  & test-clean  &   3.82  \% &  3.66  \%   &  3.86  \%  \\  
                  & test-other  &  12.50  \% & 12.39  \%   & 12.35  \%  \\  
                  & average     &   8.16  \% &  8.03  \%   &  8.11  \%  \\  
          \hline
          \multirow{3}{*}{\specialcell{With \\ RNN-LM}}
                  & test-clean  &   2.93  \% &  2.85  \%   &  2.96  \%  \\  
                  & test-other  &  10.40  \% & 10.25  \%   & 10.13  \%  \\  
                  & average     &   6.67  \% &  6.55  \%   &  6.55  \%  \\  
          \hline
       \end{tabular}
       \vspace{-2mm}
\end{table}
%
%
%
For near-field speech recognition experiments, we use the open source 
Librispeech database \cite{v_panayotov_icassp_2015_00}, as well as our in house
Bixby Usage training and test corpuses for English. 
The LibriSpeech dataset consists of around 960 hours of training data
consisting of 281,241 utterances. The evaluation set consists of the 
official 5.4 hours {\tt test-clean} and 5.1 hours {\tt test-other} data.
The Bixby Usage train corpus consists of approximately 10,000 hours of
anonymized Bixby usage data. The evaluation set consists of around 1000 
open domain utterances.

In Table \ref{tbl:power_law_result}, we compare the performance between
the baseline MFCC and the power-law of $(\cdot)^{\frac{1}{15}}$ features 
for a bidirectional full attention (BFA) E2E model with an encoder LSTM 
cell size of 1536. Especially for {\tt test-other}, which
is a more difficult task, the power mel filterbank coefficients 
shows better performance than the baseline MFCC.

In Table \ref{tbl:vtlp_result}, we show Word Error Rates (WERs) for a BFA model using 
different window sizes and warping coefficient distributions, with and without
using an external Recurrent Neural Network (RNN) Language Model (LM) 
\cite{a_zeyer_interspeech_2018_00} built using the standard LibriSpeech LM corpus.
The best performance was achieved when the window length is 50 {\it ms} and 
the warping coefficients are uniformly distributed between 0.8 and 1.2.
We obtained 3.66 \% WER on the {\it test-clean} database and 12.39 \%
WER on the {\it test-other} database without using an LM. 
To best of our knowledge, this is the
best result on this database without using any language models.
Using this shallow-fusion technique 
  with an RNN-LM, we achieved WERs of 2.85 \% and 10.25 \% 
  on the Librispeech {\tt test-clean} and {\tt test-other} databases, respectively.
To the best of our knowledge, the 2.85 \% WER on the {\tt test-clean} 
is the best result ever reported on this database using any approach, 
and 10.25 \% WER on the {\tt test-other} is the best result on this database using 
  an end-to-end recognition system.

In Table \ref{tbl:near_field_result}, we summarize our WER results for 
both the LibriSpeech and Bixby near-field E2E ASR models
with and without using an external RNN-LM trained using around 65GB of 
Bixby LM corpus with an architecture exactly similar to the
LibriSpeech LM model used in \cite{a_zeyer_interspeech_2018_00}.
All the models mentioned in the table have 1024 LSTM cells
in each encoder layer.
For comparison, the best WFST based conventional LSTM-HMM based ASR system
gives a WER of 8.85\% on the Bixby same open domain test set.
We can see that our current Bixby E2E BFA model is $\sim$10\% better, while
our MoChA streaming model is $\sim$10\% poorer compared to
the conventional WFST based DNN-HMM system.
%
\begin{table}[!tbhp]
  \renewcommand{\arraystretch}{1.3}
  \centering
        \caption{\label{tbl:near_field_result}
        Summary of Word Error Rates (WERs) obtained for different
        LibriSpeech and Bixby near-field E2E ASR models 
        with and without an RNN LM.
        }
        %\vspace{-3mm}
        \begin{tabular}{| c | c  || c | c |}
          \hline
          \multicolumn{2}{| l ||}{Models}
                                 & BFA
                                 & MOCHA \\
          \hline \hline
          \multirow{2}{*}{\specialcell{LibriSpeech}}
                  & w/o LM  &   3.66  \% &  6.78  \%  \\  
                  & RNN-LM  &   2.85  \% &  5.54  \%  \\  
          \hline
          \multirow{2}{*}{\specialcell{Bixby}}
                  & w/o LM  &   8.25  \% &  10.77  \% \\  
                  & RNN-LM  &   7.92  \% &   9.95  \% \\  
          \hline
       \end{tabular}
       \vspace{-2mm}
\end{table}
%

The performance our far-field E2E ASR model trained using the proposed
data pipeline with example servers and acoustic simulator is shown 
in Fig.~\ref{fig:plot_farfield_wer}. The performance of the far-field
models are evaluated on a English Commands test set with 900 utterances
and recorded at 4 different distances: 0.5m, 1m, 3m and 5m.
%
\begin{figure}[t]
            \begin{center}
                    {\includegraphics[width=80mm]{../figures/plot_farfield_wer}}
            \end{center}
  %\vspace{-6mm}
 \caption{\label{fig:plot_farfield_wer}
  Speech recognition accuracy with respect to the distance between 
  the microphone and the speaker.
 }
\end{figure}
%

%%
%
%
\section{Conclusions}
\label{sec:conclusions}
We presented a new end-to-end training framework and
 strategies for training 
state-of-the-art end-to-end speech recognition systems.
Our training system utilizes a cluster of Central Processing Units 
  (CPUs) and Graphics Processing Units (GPUs).
The entire data reading, large scale data augmentation,
neural network parameter updates are performed on-the-fly
using example servers and sharded {\tt TFRecords} and {\tt tf.data}. 
  We use vocal tract length perturbation and an acoustic simulator 
for data augmentation. Horovod {\tt allreduce} approach is employed 
to train the neural network parameters using Adam optimizer.
We evaluated the effectiveness of our system on the standard 
Librispeech corpus \cite{v_panayotov_icassp_2015_00} and 
  10,000-hr anonymized Bixby English training 
 and test sets both in near-field as well as
far-field scenarios.  
%\clearpage
%\newpage
\eightpt
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}

\end{document}

### 2019-08-25 none_feedback_sequence_classifier/doc/main.tex
update figures

@@
 \usepackage{amssymb,amsmath,bm}
+\usepackage[cal=boondox,scr=boondoxo]{mathalfa}
 \usetikzlibrary{arrows,decorations.markings}
@@
 Let us denote a sequence of input acoustic feature vectors by 
-$\mathcal{X}_{0}^{M-1}$ and a sequence of target labels in 
+$\vec{x}_{0}^{M-1}$ and a sequence of target labels in 
 {\it one-hot vector} representation or its label-smoothed 
 representation \cite{} by 
-$\mathcal{Y}_{0}^{L-1}$ as shown below:
+$\vec{y}_{0:L}$ as shown below:
 \begin{subequations}
   \begin{align}
-    \mathcal{X}[0:M]  =  
+    \vec{x}[0:M]  =  
       \left\{\vec{x}[m]
-          \Big| 0 \le m \le M - 1, \; \vec{x}[m] \in \mathbb{R}^d \right\},  
+          \, \big| \, 0 \le m \le M - 1, \; \vec{x}[m] \in \mathbb{R}^d \right\},  
     \label{eq:input_seq} \\
-    \mathcal{Y}_{0:L}  =  
-      \left\{\vec{y}_l  \Big| 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
+    \vec{y}_{0:L}  =  
+      \left\{\vec{y}_l \,  \big| \, 0 \le l \le L-1, \; \vec{y}_l \in \mathbb{V} \right\}, 
     \label{eq:target_label}
@@
 only when a new label is expected. The loss function 
-$\mathbb{L}_{\text{ls}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ is 
+$\mathbb{L}_{\text{ls}}\left(\vec{x}[0:M], \vec{y}_{0:L}\right)$ is 
 defined as follows:
    \begin{align}
-     \mathbb{L}_{\text{ls}}\left(\mathcal{X}[0:M], 
-        \mathcal{Y}_{0:L}\right) 
+     \mathcal{l}_{\text{ls}}\left(\vec{x}[0:M], 
+        \vec{y}_{0:L}\right) 
         = \sum_{l=0}^{L-1} 
@@
   \begin{align}
-    \mathcal{Z}[0:M]  =  
+    \vec{z}[0:m+1]  =  
       \left\{\vec{z}[m]  \Big| 0 \le m \le M-1, \; \vec{z}[m] \in \mathbb{V} \right\}, 
@@
 The loss function in the frame-synchronous inference case
-$\mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ is 
+$\mathbb{l}_{\text{fs}}\left(\vec{x}[0:M], \vec{y}_{0:L}\right)$ is 
 defined as follows:
 \begin{align}
-  \mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Z}[0:M]\right) 
-      = \sum_{l=0}^{M-1} 
+  \mathcal{l}_{\text{fs}}\left(x[0:M], z[0:M]\right) 
+      = - \sum_{l=0}^{M-1} 
           \sum_{v=0}^{V-1}  
-            (\vec{z}[m])_v  
-            \log (\widehat{\vec{z}}[m])_v  
+            (\vec{z}[m])_v  \log (\widehat{\vec{z}}[m])_v  
         \label{eq:frame_synchronous_ce_loss} 
@@
 \begin{align}
-  P\left(\mathcal{Y}_{0:L} | \mathcal{X}[0:M]\right) = 
-    \sum_{\mathcal{Z}_{0}^{M-1} \in 
+  P\left(\vec{y}_{0:L+1} | \vec{x}[0:M]\right) = 
+    \sum_{\vec{z}_{0}^{M-1} \in 
       \mathcal{A}_{CTC} 
-        \left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1} \right)}
+        \left(\vec{x}_{0}^{M-1}, \vec{y}_{0}^{L-1} \right)}
           \Pi_{m=0}^{M-1}
-            P\left(\vec{z}[m] | \mathcal{X}_{0}^{M-1} \right),
+            P\left(\vec{z}[m] | \vec{x}_{0}^{M-1} \right),
 \end{align}
-where $\mathcal{A}_{CTC} \left(\mathcal{X}_{0}^{M-1}, 
-\mathcal{Y}_{0}^{L-1} \right)$ correspond to frame-level alignments
+where $\mathcal{A}_{CTC} \left(\vec{x}_{0}^{M-1}, 
+\vec{y}_{0}^{L-1} \right)$ correspond to frame-level alignments
 of length $M$ such that removing blanks and repeated symbols from 
-$\mathcal{Z}_{0}^{M-1}$ yields $\mathcal{Y}_{0}^{L-1}$.
+$\vec{z}_{0}^{M-1}$ yields $\vec{y}_{0}^{L-1}$.
 
@@
 \begin{align}
-  P\left(\mathcal{Y}_{0:L} | \mathcal{X}[0:M]\right) = 
-    \sum_{\mathcal{Z}_{0}^{M-1} \in 
+  P\left(\vec{y}_{0:L} | \vec{x}[0:M]\right) = 
+    \sum_{\vec{z}_{0}^{M-1} \in 
       \mathcal{A}_{CTC} 
-        \left(\mathcal{X}_{0}^{M-1}, \mathcal{Y}_{0}^{L-1} \right)}
+        \left(\vec{x}_{0}^{M-1}, \vec{y}_{0}^{L-1} \right)}
           \Pi_{m=0}^{M-1}
-            P\left(\vec{z}[m] | \mathcal{X}_{0}^{M-1} \right),
+            P\left(\vec{z}[m] | \vec{x}_{0}^{M-1} \right),
 \end{align}
@@
 
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.35\textwidth}
+    \centering
+    \resizebox{50mm}{!}{
+      \input{../figures/structure_for_inference.tex}
+    } 
+  \caption {
+    \label{fig:structure_for_inference}
+  } 
+  \end{subfigure}
+  \begin{subfigure}[b]{0.35\textwidth}
+    \centering
+    \resizebox{43mm}{!}{
+      \input{../figures/structure_for_training.tex}
+    } 
+  \caption {
+    \label{fig:structure_for_training}
+  }
+  \end{subfigure}
+  \caption{
+    Structures of sequential hypothesis classifier for inference (a) 
+    and for training (b).
+  }
+
+\end{figure}
+
 \subsection{Neural Network Structure}
@@
 \begin{align}
-  \mathcal{Z}[0:U]  =  
+  \vec{z}[0:U]  =  
     \left\{\vec{z}[u]  \Big| 0 \le m \le U-1, \; \vec{z}[u] \in \mathbb{V} \right\}.
@@
 The loss function 
-$\mathbb{L}_{\text{fsc}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ 
+$\mathbb{L}_{\text{fsc}}\left(\vec{x}[0:M], \vec{y}_{0:L}\right)$ 
 is also modified from the original one in 
@@
 	\mathbb{L}_{\text{fsc}}
-    \left(\mathcal{X}[0:M], \mathcal{Z}_{0:U}\right)
+    \left(\vec{x}[0:M], \vec{z}_{0:U}\right)
       = \sum_{u=0}^{U-1}  
@@
 
-When creating the latent frame-wise label sequence $\mathcal{Z}[0:U]$ 
+When creating the latent frame-wise label sequence $\vec{z}[0:U]$ 
 in \eqref{eq:subsampled_latent_label_seq}, we distinguish the onset frame
@@
 The first step is finding the optimal frame-synchronous sequence
-$\mathcal{Z}[0:M]$.
+$\vec{z}[0:M]$.
 
@@
   \begin{algorithmic}
-    \State $\Theta^{(0)} \leftarrow$ initialize\_parameters()
+    \State $\Theta^{(0)} \leftarrow$ \texttt{initialize\_parameters}()
     \For {epoch index $i = 0, . . . , I-1$}
-      \For {each batch $\left\{\mathcal{X}[0:M],
-                        \mathcal{Y}_{0:L}  \right\}$}, 
-        \State $ {{\mathcal{Z}^{(i)}}[0:U]}
+      \For { \texttt{example} $ \left\{\vec{x}[0:M],  \,
+                        \vec{y}_{0:L}  \right\} $} 
+        \State $ {\vec{z}^{(i)}}[0:U] 
           \leftarrow
-          \text{n\_best\_align}
+          \texttt{n\_best\_align}
           \left(
-            \mathcal{X}[0:M] \Big| \Theta^{(i)}
+            \vec{x}[0:M] \, \big|\, \Theta^{(i)}
           \right)$
 
-        \State {$\Theta^{(i)} \leftarrow$ update\_parameter 
+        \State {$\Theta^{(i)} \leftarrow$  \texttt {update\_parameter}
           $\left(
-            \mathcal{X}[0:M],
-            \mathcal{Z}^{(i)}[0:U]
+            \vec{x}[0:M] \, ,  \,
+            \vec{z}^{(i)}[0:U]
           \right)$}
@@
     \caption {
-      An example of a path $\mathcal{Z}[0:M]$ and the path movement 
-      constraint shown by dashed arrows $P \rightarrow Q$ and $P \rightarrow R$. 
-      \label{fig:path_alignment}
+      An example of the path function $\vec{z}[0:M]$ and the path movement 
+      constraint represented by two dashed arrows 
+      $P \rightarrow Q$ and $P \rightarrow R$.  \label{fig:path_alignment}
     }
@@
 \begin{algorithm}
-  \caption{$N$-best alignment algorithm}
+  \caption{Teacher forced alignment}
   \begin{algorithmic}
 
-  \Require {$\mathcal{X}[0:M]$}
-  \Require {$\mathcal{Y}_{0:L}$}
+  \Require {$\vec{x}[0:M]$}
+  \Require {$\vec{y}_{0:L}$}
+  \Require {The beam size $N_b$}
   \Require {The neural network parameter $\Theta^{\left(i\right)}$ 
-    for calculating 
-      $p\left(\vec{z}[m] \big|
-      \mathcal{Z}[0:m], \mathcal{X}[0:m+1]\right)$}
+    for calculating $\vec{z}[u] = f(\vec{x}[0:m+1],\,z[0:u])$}
 
   \State {\textbf{Initialization:}}
-  \State {Let $\mathcal{Z}_0[0:1] := \left\{ \vec{y}_0 \right\}  $}
-  \State {Let $\mathcal{L}_{0} := \ln \left[ 
-        p \left(\vec{y}_{0} \big| 
-            {\mathcal{X}}[0:1]\right)  \right]$}
-  \State {$\mathcal{Z}_b[0:1], 1 \le b < N_b$ are undefined.}
+  \State {Let $z_0[0:1] := \left( \vec{y}_0 \right)  $}
+  \State {$z_b[0:1], 1 \le b < N_b$ are undefined.}
+  \State {Let $\mathcal{l}_{0} := \ln \left[ 
+        p \left(\vec{y}_{0} \, \big|  \,
+            {\vec{x}}[0:1]\right)  \right]$}
   \For {$m = 1, . . . , M-1$}
     \For {$b = 0, . . . , N_b-1$}
-      \If {$\mathcal{Z}_{b}[0:m]$ is defined}
-        \State {Let $\vec{y}_u := \vec{z}_{b}[m-1] $}
-        \State {Let $\mathcal{Z}_{b, 0}[0:m+1] := \mathcal{Z}_{b}[0:m] 
-                \cup \left\{ \vec{y}_u  \right\}  $} 
+      \If {$z_{b}[0:m]$ is defined}
+        \State {Let $\vec{y}_u := z_{b}[m-1] $}
+        \State {Let $z_{b, 0}[0:m+1] := z_{b}[0:m] 
+                \frown \left\{ \vec{y}_u  \right\}  $} 
             \Comment {A horizontal move $P \rightarrow Q$ in 
@@
         \State {
-              $\mathcal{L}_{b,0} := \ln \left[ 
+              $\mathcal{l}_{b,0} := \ln \left[ 
                   p \left(\vec{y}_{u} \big| 
-                      \mathcal{Z}_b[0:m], 
-                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right]
-                  + \mathcal{L}_b$}
+                      z_b[0:m], 
+                      \vec{x}[0:m+1], \Theta^{(i)}\right)  \right]
+                  + \mathcal{l}_b$}
 
         \If {$u+1 \le  L - 1$}
-          \State {Let $\mathcal{Z}_{b, 1}[0:m+1] 
-          := {\mathcal{Z}}_{b}[0:m] \cup \left\{ \vec{y}_{u+1}  \right\}  $} 
+          \State {Let $z_{b, 1}[0:m+1] 
+          := z_{b}[0:m] \frown \left\{ \vec{y}_{u+1}  \right\}  $} 
               \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
           \State  {
-              $\mathcal{L}_{b,1} := \ln \left[ 
+              $\mathcal{l}_{b,1} := \ln \left[ 
                   p \left(\vec{y}_{u+1} \big| 
-                      \mathcal{Z}_b[0:m], 
-                      \mathcal{X}[0:m+1], \Theta^{(i)}\right)  \right] 
-                          + \mathcal{L}_b$}
+                      z_b[0:m], 
+                      \vec{x}[0:m+1], \Theta^{(i)}\right)  \right] 
+                          + \mathcal{l}_b$}
       \EndIf
@@
     \State {Sort a list of items
-    $\left\{\mathcal{L}_{b, i}, {\mathcal{Z}}_{b, i}[0:m+1] \right\}, \; 0 \le
+    $\left\{\mathcal{l}_{b, i}, z_{b, i}[0:m+1] \right\}, \; 0 \le
     b < N_b, i = 0, 1$ 
-    with respect to the log likelihood $\mathcal{L}_{b, i}$ 
+    with respect to the log likelihood $\mathcal{l}_{b, i}$ 
     in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 
     follows: 
-    $\left\{\mathcal{L}_{b}, \mathcal{Z}_{b}[0:m+1] \right\}$, $0 \le b < N_b$}
+    $\left\{\mathcal{l}_{b}, z_{b}[0:M] \right\}$, $0 \le b < N_b$}
     where the first item in the sorted list is re-indexed to $b=0$, 

### 2019-08-25 none_feedback_sequence_classifier/doc/tex_to_pdf.sh

@@ -2,6 +2,5 @@
 
 pdflatex main
 bibtex main
-bibtex main
 pdflatex main
 pdflatex main

### 2019-08-25 asru_2019_sound_source_separation/doc/main.tex

\documentclass{article}

%\usepackage{INTERSPEECH2019}
\usepackage{spconf}

\usepackage{graphicx}
\usepackage{amssymb,amsmath,bm}
\usepackage{textcomp}
%\usepackage{spconf,amsmath,graphicx,amssymb,epsfig, graphicx, url}
\usepackage[tight,footnotesize]{subfigure}
\usepackage{url}
\def\vec#1{\ensuremath{\bm{{#1}}}}
\def\mat#1{\vec{#1}}

\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}
\renewcommand{\textfraction}{0.01}
\renewcommand{\floatpagefraction}{1.0}
\renewcommand{\dbltopfraction}{1.0}
\renewcommand{\floatpagefraction}{1.0}  % require fuller float pages
\renewcommand{\dblfloatpagefraction}{1.0} % require fuller float pages

\newcommand{\etal}{\emph{et al.} }
\newcommand{\eg}{\emph{e.g.} }
\newcommand{\ie}{\emph{i.e.} }

\sloppy % better line breaks
\ninept

\title{Sound Source Separation Using Inter-Microphone Delay, Cross-Correlation,
and Cross-Covariance}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% If multiple authors, uncomment and edit the lines shown below.       %%
%% Note that each line must be emphasized {\em } by itself.             %%
%% (by Stephen Martucci, author of spconf.sty).                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\makeatletter
%\def\name#1{\gdef\@name{#1\\}}
%\makeatother
%\name{{\em Firstname1 Lastname1, Firstname2 Lastname2, Firstname3 Lastname3,}\\
%      {\em Firstname4 Lastname4, Firstname5 Lastname5, Firstname6 Lastname6,
%      Firstname7 Lastname7}}
%%%%%%%%%%%%%%% End of required multiple authors changes %%%%%%%%%%%%%%%%%

\makeatletter
\def\name#1{\gdef\@name{#1\\}}
\makeatother \name{{\em Chanwoo Kim$^1$, Anjali Menon$^2$, and Richard M. Stern$^2$\thanks{\textbf{
Thanks to Samsung Electronics for funding this research. The authors are thankful 
to Executive Vice President Seunghwan Cho and speech processing Lab. members at Samsung Research.
}}}}

\address{$^{1}$ Samsung Research \\ $^{2}$ Carnegie Mellon University \\
{\small \tt chanw.com@samsung.com, \{anjalim, rms\}@cmu.edu}}
%
%\twoauthors{Karen Sp\"{a}rck Jones.}{Department of Speech and Hearing \\
%  Brittania University, Ambridge, Voiceland \\
%  {\small \tt Karen@sh.brittania.edu} }
%  {Rose Tyler}{Department of Linguistics \\
%  University of Speechcity, Speechland \\
%  {\small \tt RTyler@ling.speech.edu} }

%
%
\graphicspath{{../figures/}}
%
\newcommand{\chanwcom}{{C. Kim}}
%
\begin{document}
%
  \maketitle
  %
  \begin{abstract}
In this paper, we present a two-microphone algorithm for sound source separation 
    referred to as Minimum Normalized Cross-Correlation and Minimum Normalized 
    Cross-coVariance (MNCC-MNCV).  
    The MNCC-MNCV algorithm automatically selects the ``Inter-Microphone
    Delay (IMD) threshold," which separates time-frequency segments that are believed to
    belong to the target from components that are dominated by noise sources.
    In this work, we develop an algorithm which considers both the
    normalized correlation and the correlation coefficient of the target and
    interfering signal signals, after a compressive nonlinearity. 
We demonstrate that the use of the MNCC-MNCV method of estimating IMD
    thresholds  provides significantly better recognition accuracy in the
    presence of   interfering speech sources, omni-directional noise, and
    reverberation than several other approaches including ZCAE
    \cite{H_Park_SpeechComm_2009}, PDCW \cite{C_Kim_INTERSPEECH_2009_1}, and
    our previous automatic IMD threshold selection approach
    \cite{C_Kim_INTERSPEECH_2010_1}. 
  \end{abstract}
%  
  \noindent{\bf Index Terms}: Robust speech recognition, signal separation, phase difference analysis,  cross-correlation, normalized correlation
%
%
\section{Introduction}
%
\begin{figure*}[t]
            \begin{center}
                    {\includegraphics[width=170mm]{../figures/PDCW_AUTO_BlockDiagram}}
            \end{center}
	%\vspace{-6mm}
 \caption{\label{fig:PDCW_AUTO_BlockDiagram}
       \emph{ Block diagram of a sound source separation system using the
       MNCC-MNCV algorithm. }
       }	\vspace{-6mm}
\end{figure*}
%
\label{sec:intro}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
%
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
%
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
%
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
%
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
% Below is an example of how to insert images. Delete the ``\vspace'' line,
% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
% with a suitable PostScript file name.
% -------------------------------------------------------------------------

% To start a new column (but not a new page) and help balance the last-page
% column length use \vfill\pagebreak.
% -------------------------------------------------------------------------
%\vfill
%\pagebreak
\label{BinaryMaskGenerationForTimeFreqBin}
%
Recently, improvement in deep learning technology
\cite{Seltzer2013DNNAurora4, Yu2013FeatureLearningDNN, V_Vanhoucke_Deep_Learning_NIPS_Workshop_2011,
G_Hinton_IEEE_Signal_Process_Mag_2012,
T_Sainath_IEEETran_2017_1, T_Sainath_Book_Chapter_2017_1}
has helped to commercialize voice assistant speakers
\cite{B_Li_INTERSPEECH_2017_1, C_Kim_INTERSPEECH_2017_1}.
In far-field speech recognition environments, the impact of
noise and reverberation is much larger than near-field cases.
To enhance robustness of speech recognition systems,
data augmentation techniques have been
widely used with notable success  \cite{R_Lippmann_icassp_1987_1, w_hartmann_interspeech_2016_00, C_Kim_INTERSPEECH_2017_1,
c_kim_interspeech_2018_00, c_kim_icassp_2018_00,
n_jaitly_icml_workshop_2013_00, C_Kim_ASRU_2009_2}. 
Multi-microphone approaches  
have been also frequently used to select the target sound source while 
suppressing noisy sources \cite{T_Nekatani_ICASSP_2017_1, T_Higuchi_ICASSP_2016_1,
H_Erdogan_INTERSPEECH_2016_1, C_Kim_INTERSPEECH_2015_1}. Various variations
of Minimum Variance Distortionless Response (MVDR) beam-formers
have been used with success \cite{e_habets_taslp_2010_00,
p_chevalier_icassp_2009_00, p_chevalier_ieee_trans_signal_process_2007_00,
j_zhang_ieee_taslp_2018_00}.
 Many algorithms have been proposed that segregate signals on the basis  of
 differences in arrival time (\emph{e.g.} \cite{y_zhang_icassp_2018_00,
 PalomakiBrownWang04,SrinivasanEtAl06,H_Park_SpeechComm_2009, c_kim_icassp_2018_01}).  It is well documented that the human
binaural system has a remarkable ability to separate speech that arrives from different azimuths
(\emph{e.g.} \cite{Grantham95,SternWangBrown06}) using
various types of acoustical cues are used to segregate the target signal from 
interfering sources.
 Motivated by these observations, a number of models and algorithms
have been developed  that separate signals according to Inter-Microphone Delays
(IMDs) (\emph{e.g.} \cite{SrinivasanEtAl06, H_Park_SpeechComm_2009}), inter-microphone intensity difference (IIDs), inter-microphone
phase differences (IPDs) (\emph{e.g.} \cite{P_Aarabi_IEEETranSysManCyber_2005}, \cite{D_Halupka_ICASSP_2005}), as well as other cues.  IMDs can be estimated using either phase differences (\emph{e.g.}
\cite{C_Kim_INTERSPEECH_2009_1}), cross-correlation, or zero-crossings (\emph{e.g.} \cite{H_Park_SpeechComm_2009}).  Typically these algorithms compare IMDs or IPDs in each spectro-temporal segment of an input  to a fixed threshold, in order to select those IMDs or IPDs that are   consistent with the azimuth of the desired target speaker.  In \cite{C_Kim_INTERSPEECH_2010_1}, we proposed an algorithm that selects the     IMD threshold automatically by minimizing the correlation coefficient of power signals after the peripheral auditory nonlinearities. While this algorithm was found to be more robust than algorithms using fixed thresholds (\eg \cite{C_Kim_INTERSPEECH_2009_1}),   this algorithm is not very effective for practical environments that include   multiple noisy sources. In the present work, by considering both the cross-correlation and
cross-covariance between the masked and unmasked channels, with additional
Channel Weighting (CW), we obtain significant improvements for various conditions.
%
%
%
%
%\vspace{-2mm}
\section{Structure of the\\MNCC-MNCV Algorithm}
	\label{Sec:OverviewPDCWAUTO}
	%\vspace{-2mm}
In this section, we explain the structure of our binaural sound source separation system. While the detailed
description below assumes a sampling rate of 16 kHz, this algorithm is easily modified to accommodate other sampling frequencies. Our approach is based on Phase Difference Channel Weighting (PDCW) \cite{C_Kim_INTERSPEECH_2009_1}. If the automatic threshold selection algorithm  described in Sec. \ref{sec:optimalIMDthresholdSelection}  is employed to obtain the target IMD threshold,  we refer to the entire system as Minimum Normalized
Cross-Correlation and Minimum Normalized Cross-coVariance (MNCC-MNCV). In this paper, we consider three different ways of selecting the IMD threshold: the  Minimum Normalized Cross-coVariance (MNCV)  which had been introduced in \cite{C_Kim_INTERSPEECH_2010_1}, a
Minimum Normalized Cross-Correlation (MNCC), and a combination of these two approaches (MNCC-MNCV). These approaches will be explained in   detail in Sec. \ref{sec:optimalIMDthresholdSelection}.
A block diagram of the MNCC-MNCV system is shown in Fig.  \ref{fig:PDCW_AUTO_BlockDiagram}.  The system first  performs a short-time Fourier transform (STFT) which decomposes the two input signals in time and in frequency. We use Hamming windows of duration 75 ms with 37.5 ms between frames, and a DFT size of 2048.  The  IMD is estimated indirectly by comparing the phase information from the two microphones at each frequency. The time-frequency mask identifying the subset of IMDs that are ``close'' to the IMD of the target speaker is obtained
using the IMD threshold selection algorithm described in Sec. \ref{sec:optimalIMDthresholdSelection}.   To obtain better speech recognition accuracy in noisy environments, we apply a gammatone channel-weighting approach as described in \cite{C_Kim_INTERSPEECH_2009_1}
instead of directly applying the binary mask. This step is another improvement
over our previous approach in \cite{C_Kim_INTERSPEECH_2010_1}. Finally, the
time domain signal is obtained using the IFFT and the OverLap-Add (OLA) method.  
%
%\vspace{-2mm}
\subsection{Source Separation Using IMDs}
	\label{sec:sourceSeparation}
	%\vspace{-2mm}
	In   binaural sound source separation systems we usually assume that we have \emph{a priori}
knowledge about the target location. In this paper  we assume that the target is located along the 
perpendicular bisector to the line connecting two microphones. Hence, the 
decision criteria can be expressed as follows:
\begin{align}
	\begin{cases}
		\text{considered to be a target:} \qquad & |\tau[m, k]| < \tau_0 \\
        \text{considered to be a noise source:} \qquad & |\tau[m, k]| \ge \tau_0 \\	
	\end{cases}
		\label{eq:decCriterionTau}
\end{align}
where $m$ is the frame index, $k$ is the frequency index,   $\tau[m, k]$ is the estimated IMD for a time-frequency bin represented by $[m, k]$, and $\tau_0$ is the threshold IMD.  Thus, if we obtain a suitable
IMD threshold   using  \eqref{eq:decCriterionTau}, we can make a binary decision.
In this sound-source separation system the IMD is obtained for each time-frequency bin using phase information according to \eqref{eq:decCriterionTau}.  In our previous work (\emph{e.g.} \cite{C_Kim_INTERSPEECH_2010_1}), it has been shown that the IMD $\tau[m, k]$
for each time-frequency bin can be obtained by:
\begin{align} \label{eq:IMD_Estimate}
|\tau[m, k]|  & \approx  \frac{1}{|w_{k}|}   \min_r \Big|\angle{X_R[m, e^{-j w_k } ]} \nonumber \\
              & \qquad  - \angle{X_L[m, e^{-j w_k }]} - 2 \pi r \Big|, \; 0 \le k \le \frac{K}{2}
\end{align}
where $m$ is the frame index, $k$ is the frequency index, $X_L[m, e^{-j w_k }]$ and $X_R[m, e^{-j w_k } ]$ are
STFTs of the signals from the left and right microphones, receptively.
$\omega_k$ is the discrete-time frequency defined to be $\omega_k = \frac{2 \pi
k}{K}$, and $K$ is the DFT size. Using an IMD threshold $\tau_0$, we construct
a binary mask as in \cite{C_Kim_INTERSPEECH_2010_1}. The procedure of obtaining an automatic threshold is described in Sec. \ref{sec:optimalIMDthresholdSelection}. 
%The mask $\mu[m, k | \tau_0]$  obtained in this way may be directly applied to   $X_{A}[m, e^{j \omega_k}]$, the averaged signal
%spectrogram from the two microphones: %, and speech is reconstructed from the $\tilde{X}(k,m)$ where

%As mentioned above,  the Phase Difference (PD) approach refers to the direct application of   $\mu[m, k | \tau_0]$ to the spectrum, while the use of the  gammatone channel weighting introduced in \cite{C_Kim_INTERSPEECH_2009_1} to obtain a smoothed mask $\mu_s[m, k| \tau_0]$ is referred to as Phase Difference Channel Weighting (PDCW).
% The reconstructed spectrum is given by:
%\begin{align}
%   Y [m, e^{j \omega k})  = \max\left[\mu_s[m, k], \eta\right] \, X_{A} [m, e^{j \omega k}),
%                         \; 0 \le k \le \frac{N}{2} \label{XcmResyn}
%\end{align}
%where again  we use $\eta=0.01$ as in \cite{C_Kim_INTERSPEECH_2009_1}, and $X_{A} [m, e^{j \omega k})$ is the averaged
%spectrum defined in  \eqref{eq:averageSpec}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Section:	 Optimal IMD threshold selection using complementary masks
%
%\vspace{-2mm}
\subsection{Optimal IMD threshold selection using complementary masks}
\label{sec:optimalIMDthresholdSelection}
%\vspace{-2mm}
%
%
To find   the optimal IMD threshold, computation is performed in discrete fashion, considering  a set  $\mathcal{T}$ of a finite number  of possible IMD threshold candidates. The set $\mathcal{T}$ is defined by the following minimum and maximum values
of the IMD threshold: $\tau_{min}  =   d \sin(\theta_{0, min})f_s/c$ and $\tau_{max}  =  d \sin(\theta_{0, max}) f_s / c$, where $d$ is the distance between two microphones, $c$ is the speed of sound,   $f_s$ is the sampling frequency, and  
$\theta_{0, min}$ and $\theta_{0, max}$  are the minimum and the maximum values
of the threshold angle. In the present implementation, we use  values of $\theta_{0, min} = 5 ^{\circ}$ and 
$\theta_{0, max} = 45 ^{\circ}$. We use a set of candidate IMD thresholds $\mathcal{T}$ that consist of the 20   linearly-spaced values of $\theta_{0}$ between $\theta_{0, min}$ and $\theta_{0, max}$.
%
%
\begin{figure}[t]
       \begin{center}
  %     \begin{tabular}{c c c}
 %     \subfigure[\label{fig:PDCW_AUTO_3IntSNR_Rev_0ms_Angle_30}]
 %         {\includegraphics[width=65mm]{../figures/PDCW_AUTO_CorrTypes_IntSNR_Rev_0ms_Angle_30_ICASSP}}    \\
%            \subfigure[\label{fig:PDCW_AUTO_CorrTypes_IntSNR_Rev_0ms_Angle_30}]
%          {\includegraphics[width=65mm]{../figures/PDCW_AUTO_CorrTypes_IntSNR_Rev_100ms_Angle_30_ICASSP}}  \\
          \subfigure[\label{fig:PDCW_AUTO_3IntSNR_Rev_200ms_Angle_30}]
          {\includegraphics[width=65mm]{../figures/plot_mncc_mcc_wer_200ms}}   \vspace{-2mm} \\
           \subfigure[\label{fig:PDCW_AUTO_CorrTypes_Omni}]
           {\includegraphics[width=65mm]{../figures/plot_mncc_mcc_wer_omni}}
          \vspace{-2mm}%
  %    \end{tabular}
       {\caption{\label{fig:PDCW_AUTO_CorrTypes_IntSNR}
             \emph{Comparison of recognition accuracy for the DARPA RM database (a) corrupted by an interfering speaker located at 30 degrees under the reverberation of $T_{60} = 200 ms $, and (b) in the presence of natural real-world noise.}
   }}
   \end{center}
   \vspace{-8mm}
\end{figure}
%
%
%
We determine which element
of this set is the most appropriate IMD threshold by performing an exhaustive search over the set $\mathcal{T}$. Let us consider one element of this set, $\tau_0 =   d \sin(\theta_{0}) f_s / c$.
%But these masks are two noisy too be directly used, so we need to use some smoothing in the frequency domain.
%For smoothing method, we can consider the gammatone channel weighting approach \cite{C_Kim_ASRU_2009_2}
%\cite{C_Kim_INTERSPEECH_2009_1} or simple smoothing across frequency indexes.
%The following is one example of obtaining smoothed mask
Using the procedure described in Sec. \ref{sec:sourceSeparation}, we obtain the target spectrum $X_T[m, e^{j \omega_k} | \tau_0], \quad 0 \le k \le \frac{K}{2}$  as shown below:
\begin{align}
        X_T[m, e^{j \omega_k} | \tau_0] = X_{A}[m, e^{j \omega_k}] \mu[m, k | \tau_0]
\end{align}
where $X_{A}[m, e^{j \omega_k}]$ is the averaged signal spectrogram from the two microphones defined by
\begin{equation}
  X_{A}[m,  e^{j \omega_k}] = (X_L[m, e^{j \omega_k} ]  + X_R[m, e^{j
  \omega_k}])/2.
\end{equation}
$\mu[m, k | \tau_0]$ is the binary mask obtained by \eqref{eq:decCriterionTau}.
In the above equation we explicitly include $\tau_0$ to show that the masked spectrum depends on
the IMD threshold. Using this spectrum $X_T[m, e^{j \omega_k}]$, we obtain the target power
and the power of the interfering sources. Since everything which is not the target is considered to be an interfering source,
the power associated with the target and interfering sources can be obtained by the following equations:
\begin{subequations}
    \begin{align}
    P_T[m|\tau_0] & =  \sum_{k=0}^{K-1} \Big|X_T[m, e^{j \omega_k} | \tau_0]\Big|^2 \\
    P_I[m|\tau_0] & =  \sum_{k=0}^{K-1} \Big|X_{A}[m, e^{j \omega_k}]\Big|^2 - P_T[m|\tau_0]
     \end{align}
     \label{P_TandP_I}
\end{subequations}
 As in \cite{C_Kim_INTERSPEECH_2010_1, C_Kim_IEEETran_2016_1, C_Kim_ICASSP_2012_1}, a compressive nonlinearity is invoked:
 \begin{subequations}
\begin{align}
    R_T[m|\tau_0]  =  P_T[m|\tau_0] ^ {a_0}  \qquad    R_I[m|\tau_0]  =  P_I[m|\tau_0] ^ {a_0}
\end{align}
 \label{NonlinearityOuput}
\end{subequations}
where   $a_0 = 1 / 15$ is the power coefficient as in
\cite{C_Kim_INTERSPEECH_2010_1, C_Kim_IEEETran_2016_1}.

In general, the optimal IMD threshold is determined by identifying the value of $\tau_0$ that minimizes the cross-correlation between the signals $R_T[m|\tau_0]$ and $R_I[m|\tau_0]$ from  \eqref{NonlinearityOuput}, but there are several plausible ways of computing this cross-correlation.  The first method considered, which was used in an earlier paper \cite{C_Kim_INTERSPEECH_2010_1}, is based on 
the normalized cross-covariance of the signals in  \eqref{NonlinearityOuput}:
\begin{align}
    \rho_{T,I}(\tau_0) = \frac{\frac{1}{K}\sum_{m=1}^{M} R_T[m|\tau_0]  R_I[m|\tau_0] - \mu_{R_T}\mu_{R_I}}{\sigma_{R_T} \sigma_{R_I}}
    \label{eq:TypeI}
\end{align}
where $\mu_{R_1}$ and $\mu_{R_2}$, and $\sigma_{R_T}$ and $\sigma_{R_I}$, are the means and standard deviations of $R_T[m|\tau_0]$ and $R_I[m|\tau_0]$, respectively.  (This statistic   is also known as the Pearson product-moment correlation.)

The optimal IMD threshold $\tau_0$ is selected to minimize the absolute value
of the cross-covariance:
\begin{align}
    \hat{\tau}_1 = \arg \min_{\tau_0} |\rho_{T,I}(\tau_0)| \label{eq:minCrossCor}
\end{align}
 Again, we refer to this approach
as the MNCV statistic, and 
  it has provided good speech recognition accuracy as shown in Fig. \ref{fig:PDCW_AUTO_CorrTypes_IntSNR}, especially at low SNRs such as 0 or 5 dB. Nevertheless, at moderate SNRs such 10   or 15 dB, the speech recognition accuracies obtained using MNCV processing are   worse than those obtained using the PDCW algorithm.  MNCC-MNCV processing using the MNCV statistic also provides poor recognition accuracy in the presence of omnidirectional 
natural noise, as   shown in Fig. \ref{fig:PDCW_AUTO_CorrTypes_Omni}. 
We have also found in pilot studies that the MNCV statistic in  \eqref{eq:TypeI} is not a helpful measure in situations where there is a single interfering source with power that is comparable to that of the target, or where there are multiple interfering sources.

To address this problem, we consider a second related statistic,    the   normalized cross-correlation:
\begin{align}
    r_{T,I}(\tau_0)  = \frac{\frac{1}{K}\sum_{m=1}^{M} R_T[m|\tau_0]  R_I[m|\tau_0]}{\sigma_{R_T} \sigma_{R_I}} \\
    \hat{\tau}_2  = \arg \min_{\tau_0} | r_{T,I}(\tau_0) |
\end{align}
We refer to implementations using $\hat{\tau}_2$   as Minimum Normalized Cross-correlation (MNCC) systems.

The final IMD threshold  $\hat{\tau}_3$ is obtained easily by calculating the minimum of $\hat{\tau}_1$ and $\hat{\tau}_2$ as shown below:
\begin{align}
    \hat{\tau}_3 = \min(\hat{\tau}_1, \hat{\tau}_2) 
    \label{eq:tau3_eq}
\end{align}
We refer to implementations using $\hat{\tau}_3$   as  MNCC-MNCV systems.
As can be seen in Figs. \ref{fig:PDCW_AUTO_CorrTypes_IntSNR}($a$) and \ref{fig:PDCW_AUTO_CorrTypes_Omni}, systems using the MNCC-MNCV
stastistic consistently provide recognition accuracy that is similar to or better than that obtained using either the     MNCV or MNCC approaches.  For these reasons we adopt MNCC-MNCV processing as the default approach, unless some other approach is stated explicitly. 
Instead of directly applying the mask $\mu[m, k | \hat{\tau}_3]$, 
we obtain a smoothed mask $\mu_s[m, k| \hat{\tau}_3]$ using the Channel Weighting
(CW) technique in \cite{C_Kim_INTERSPEECH_2009_1}. By applying $\mu_s[m, k| \hat{\tau}_3]$ to the averaged spectrum $X_{A}[m, e^{j \omega_k}]$, we obtain the enhanced spectrum $Y[m, e^{j \omega_k}]$ as follows:
\begin{align}
        Y[m, e^{j \omega_k}]= X_{A}[m, e^{j \omega_k}] \mu_s[m, k| \hat{\tau}_3]
\end{align}
% The reconstructed spectrum is given by:
%\begin{align}
%   Y [m, e^{j \omega k})  = \max\left[\mu_s[m, k], \eta\right] \, X_{A} [m, e^{j \omega k}),
%                         \; 0 \le k \le \frac{N}{2} \label{XcmResyn}
%\end{align}
%where again  we use $\eta=0.01$ as in \cite{C_Kim_INTERSPEECH_2009_1}, and $X_{A} [m, e^{j \omega k})$ is the averaged
%spectrum defined in  \eqref{eq:averageSpec}.
%In the discussion up to now  we have considered spectral components for frequency indicies $0 \le k \le \frac{N}{2} $. For $\frac{N}{2} + 1 \le k \le N - 1$, we obtain $X_T [m, e^{j \omega k} | \hat{\tau}_3)$ using the Hermition symmetry property of Fourier transforms of real time functions.  [THIS IS NOT SO IMPORTANT AND COMMONLY USED IN ANY CASE]
%
%\vspace{-2mm}
\subsection{Spectral flooring}
\label{sec:spectral_flooring}
%\vspace{-2mm}
%
In our previous work (\emph{e.g.}  \cite{C_Kim_IEEETran_2016_1} ), it has been frequently observed that an appropriate flooring helps in improving 
  noise robustness. For this reason we also
apply a flooring level to the spectrum, which is described by the   equation:
\begin{align}
Y_{f} = \delta_f \sqrt{\frac{1}{N_f K}  \sum_{m=0}^{N_f - 1} \sum_{k = 0}^{K - 1}  \big|Y[m, e^{j \omega_k}]\big|^2 }
\end{align}
where $\delta_f$ is the flooring coefficient, $N_f$ is the number of frames in the utterance,  $K$
is the FFT size, and $Y_{f}$ is the obtained threshold. We use a value of 0.01 for the flooring
coefficient $\delta_f$.
Using the flooring level $Y_{f}$, the floored spectrum $Z [m, e^{j \omega k}], 0 \le k \le K$ is obtained as follows:
	\begin{align}
    Z[m, e^{j \omega k}] =  \max\left[  \big| Y[m, e^{j \omega_k}] \big|
     , Y_f\right] e^ {j \angle Y[m, e^{j \omega_k}] }
	\end{align}
%The above equations mean that the magnitude spectrum is floored by a minimum value of $Y_f$ while 
 % the phase remains unchanged. 
Using $Z [m, e^{j \omega k}]$, speech is resynthesized using IFFT and the
overlap-add method (OLA). While the improved threshold optimization 
criteria in Sec. \ref{sec:optimalIMDthresholdSelection} is the most important 
improvement over our previous approach in \cite{C_Kim_INTERSPEECH_2010_1},
Channel Weighting (CW) and this spectral flooring are also additional
improvements.
%%
%\begin{figure}
%       \begin{center}
%          {\includegraphics[width=65mm]{../figures/PDCW_AUTO_CorrTypes_Omni_ICASSP}}  
%           \vspace{-6mm}%
%       {\caption{\label{fig:PDCW_AUTO_CorrTypes_Omni}
%            Speech recognition accuracy obtained using different algorithms in the presence of natural real-world noise.  \vspace{-6mm}%
%   }}
%   \end{center}
%\end{figure}
%%
\begin{figure}
       \begin{center}
    %   \begin{tabular}{c c c}
      \subfigure[\label{fig:PDCW_AUTO_IntSNR_Rev_0ms_Angle_30}]
           {\includegraphics[width=65mm]{../figures/plot_comparison_0ms.eps}
           }
           \vspace{-2mm}
      %      \subfigure[\label{fig:PDCW_AUTO_IntSNR_Rev_100ms_Angle_30}]
     %     {\includegraphics[width=65mm]{../figures/PDCW_AUTO_IntSNR_Rev_100ms_Angle_30_ICASSP}} &
           \subfigure[\label{fig:PDCW_AUTO_IntSNR_Rev_200ms_Angle_30}]
           {\includegraphics[width=65mm]{../figures/plot_comparison_200ms.eps}}
           \vspace{-2mm}
            \subfigure[\label{fig:ATIS_PDCW_PD_AUTO_FIXED_Omni}]
           {\includegraphics[width=65mm]{../figures/plot_comparison_omni.eps}}
          \vspace{-2mm}
    %  \end{tabular}
       {\caption{\label{fig:PDCW_AUTO_IntSNR}
        \emph{Comparison of recognition accuracy for the DARPA RM database (a) corrupted by an interfering speaker located at 30 degrees, (b) corrupted by an interfering speaker located at 30 degrees under the reverberation of $T_{60} = 200   $ ms, and (c) in the presence of natural real-world noise.}    
   }}
   \end{center}
   \vspace{-8mm}
\end{figure}
%
\begin{figure}
       \begin{center}
     %  \begin{tabular}{c c c}
         % \subfigure[\label{fig:PDCW_AUTO_IntLoc_Rev_0ms_Angle_45}]
         % {\includegraphics[width=65mm]{../figures/PDCW_AUTO_IntLoc_Rev_0ms_Angle_45_ICASSP}}   \vspace{-3mm} \\
       %     \subfigure[\label{fig:PDCW_AUTO_IntLoc_Rev_100ms_Angle_45}]
         {\includegraphics[width=65mm]{../figures/plot_comparison_angle}}
      %    \subfigure[\label{fig:PDCW_AUTO_IntLoc_Rev_200ms_Angle_45}]
      %    {\includegraphics[width=65mm]{../figures/PDCW_AUTO_IntLoc_Rev_200ms_Angle_45_ICASSP}} 
          % \vspace{-6mm}
    %  \end{tabular}
       {\caption{\label{fig:PDCW_AUTO_IntLoc}
                \emph{Comparison of recognition accuracy for the DARPA RM database corrupted by an interfering speaker   at different locations in a simulated room with 100 {\it ms} different reverberation time. (SIR) is fixed at 0 dB. } 
	       }}
   \end{center}
   \vspace{-8mm}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Section:	 Experimental results
%
%\vspace{-2mm}
\section{Experimental results}
%\vspace{-2mm}
	\label{sec:experimentalResults}
In this section, we present experimental results using the MNCC-MNCV algorithms 
described in this paper, focussing on the performance of the new methods that
were developed to estimate blindly the IMD threshold parameter. To evaluate the
effectiveness of this MNCC-MNCV algorithm, we performed
comparison with the source separation algorithm developed in  \cite
{C_Kim_INTERSPEECH_2010_1}, which is referred to as 
``Auto-ITD-Th" in this section. To see the additional benefit of Channel
Weighting (CW), we also compared the performance
when the Channel Weighting (CW) approach is not employed in
MNCC-MCVN.

 We also  compare our approach with an earlier  technique, the ZCAE algorithm
 described in  \cite{H_Park_SpeechComm_2009} 
using binary masking as in \cite{C_Kim_INTERSPEECH_2010_1}. In all speech recognition experiments described in this paper we perform feature extraction using  the version of MFCC processing implemented in  \texttt{sphinx\_fe} in \texttt{sphinxbase 0.4.1}.
For acoustic model training, we used \texttt{SphinxTrain 1.0}, and decoding was
performed using the  \texttt{CMU Sphinx 3.8}, all of which are readily available in Open Source form.
 We used subsets of 1600 utterances and 600 utterances, respectively, from the DARPA Resource Management (RM1) database for training and testing.
A bigram language model was used in all experiments. In all experiments, we used feature vectors
of length of 39 including delta and delta-delta features. We assumed that the distance between two microphones is 4 cm.

We conducted three different sets of experiments in this section.
The first two sets of experiments involve   simulated reverberant environments in which the target speaker is
masked by a single interfering speaker. 
 The reverberation simulations were accomplished using the \emph{Room Impulse Response} open source software package \cite{RIR} based on the image method.
   In these experiments, we assume a room of
dimensions 5 m x 4 m x 3 m, with microphones that are located at the center of the room.
Both the target and interfering sources are 1.5 m away from the microphone.
For the ZCAE algorithm, we used a threshold angle of  $\theta_{TH} = 20 ^ {\circ}$.

In the first set of experiments, we assume that the target is located along the perpendicular bisector of the 
line between two microphones, which means $\theta_T = 0^{\circ}$. We assume
that the interfering source is located at $\theta_I = 30^{\circ}$. We repeated the
experiments by changing the Signal-to-Interference Ratio (SIR) and reverberation time.
As shown in Fig. \ref{fig:PDCW_AUTO_IntSNR_Rev_0ms_Angle_30}, in the absence of
reverberation at 0-dB SIR, both the fixed-IMD system (ZCAE) and the automatic-IMD
systems (MNCC-MCNV, Auto-ITD-Th) provide comparable performance.   If   reverberation is present, however, 
MNCC-MNCV provides substantially better performance than the ZCAE signal separation system. 
In the second set of the experiments we changed the location of the interfering speaker while maintaining
the SIR   at 0 dB. As shown in Fig. \ref{fig:PDCW_AUTO_IntLoc}, even if the SIR is the same as in the calibration environment,
the performance of the fixed-IMD threshold system (ZCAE) becomes significantly degraded   if the actual interfering speaker
location is different from the location used in the calibration environment.   The MNCC-MNCV selection system
provides recognition results that are much more robust with respect to the locations of the interfering sources compared to ZCAE and the basic MNCC-MNCV/Auto-ITD-Th algorithm described in \cite{C_Kim_INTERSPEECH_2010_1}.  %Based on the results of Fig. 2 we believe that the differences between the results obtained with the

 % In this figure we observe that as the interfering speaker moves
%toward the target,  the fixed-IMD threshold PD system provides   increased word error rate. %We repeated
%this   experiment with different reverberation times. As shown in Fig. \ref{fig:PDCW_AUTO_IntLoc}, the automatic-threshold-selection algorithm provides %consistently
%better recognition accuracy than the fixed threshold system, as expected. 
%
%
%\begin{figure}
%   \begin{center}
%            {\includegraphics[width=65mm]{../figures/ATIS_PDCW_PD_AUTO_FIXED_Omni_ICASSP}}           
%   \end{center}
%    \vspace{-6mm}%
%         {\caption{\label{fig:ATIS_PDCW_PD_AUTO_FIXED_Omni}
%         Speech recognition accuracy using different algorithms in the presence of natural real-world noise.       }
%    \vspace{-6mm}
%     }  
%\end{figure}
%
%
In the third set of experiments we added noise recorded with two microphones in real environments  such as a public  market, a food court,   a city street and a bus stop.  These real noise sources surround the two microphones, and the signals from these recordings are digitally added to clean speech from the   test set of the RM database.  Fig.
\ref{fig:ATIS_PDCW_PD_AUTO_FIXED_Omni} shows speech recognition accuracy for this configuration. 
Again we observe that  MNCC-MNCV provides the best performance by a significant
margin, while the  Auto-ITD-Th, MNCC-MCNV without CW, and ZCAE show similar performance to each other.
%
%In this paper, we conducted experiments in various configurations, and we observed that MNCC-MNCV provides significant 
%improvement in speech recognition accuracy for speech in various types of interfering noise sources and reverberation, compared to state-of-the-art algorithms that rely on a fixed IMD threshold.  The use of the automatic IMD threshold selection is particularly helpful in the presence of multiple interfering sources or reverberation, or when the location of the target source is not estimated properly.
%
\section{Summary}
 In this paper, we present a two-microphone algorithm for sound source separation 
    referred to as Minimum Normalized Cross-Correlation and Minimum Normalized 
    Cross-coVariance (MNCC-MNCV).  
We demonstrate that the use of the MNCC-MNCV method of estimating IMD
    thresholds  provides significantly better recognition accuracy in the
    presence of   interfering speech sources, omni-directional noise, and
    reverberation than several other approaches including ZCAE
    \cite{H_Park_SpeechComm_2009}, PDCW \cite{C_Kim_INTERSPEECH_2009_1}, and
    our previous automatic IMD threshold selection approach
    \cite{C_Kim_INTERSPEECH_2010_1}. 
% While the PDCW algorithm itself is not patent protected, a US patent has been applied for the automatic IMD threshold selection algorithm.
%
%
%\section{Summary}
%
%In this paper we introduce power-normalized cepstral coefficients (PNCC), which we characterize as a feature set that provides better recognition accuracy than MFCC and RASTA-PLP processing in the presence of common types of additive noise and reverberation.  PNCC processing is motivated by the desire to develop computationally efficient feature extraction for automatic speech recognition that is based on a pragmatic abstraction of various attributes of auditory processing including the rate-level nonlinearity, temporal and spectral integration, and temporal masking.  The processing also includes a
%component that implements suppression of various types of common additive noise.
%Further details about the motivation for and implementation of PNCC processing are available in \cite{ChanwooKimPhDThesis, C_Kim_IEEETran_2016_1}.
%This thesis also includes additional relevant experimental findings including results obtained for PNCC processing using multi-style training 
%and in combination  with speaker-by-speaker MLLR.
%Open Source MATLAB code for PNCC may be found at
%{\small\texttt{http://www.cs.cmu.edu/ \\
%\ \ \~{}robust/archive/algorithms/PNCC\_IEEETran}}.  The code in this directory was used for obtaining the results for this paper.
%
%
%  \newpage
 % \eightpt
\bibliographystyle{IEEEtran}
   %  \bibliographystyle{IEEEbib}
%
\bibliography{../../common_bib_file/common_bib_file}
%
%
%
%  \begin{thebibliography}{9}
%    \bibitem[1]{Davis80-COP}
%      S.\ B.\ Davis and P.\ Mermelstein,
%      ``Comparison of parametric representation for monosyllabic word recognition in continuously spoken sentences,''
%      \textit{IEEE Transactions on Acoustics, Speech and Signal Processing}, vol.~28, no.~4, pp.~357--366, 1980.
%    \bibitem[2]{Rabiner89-ATO}
%      L.\ R.\ Rabiner,
%      ``A tutorial on hidden Markov models and selected applications in speech recognition,''
%      \textit{Proceedings of the IEEE}, vol.~77, no.~2, pp.~257-286, 1989.
%    \bibitem[3]{Hastie09-TEO}
%      T.\ Hastie, R.\ Tibshirani, and J.\ Friedman,
%      \textit{The Elements of Statistical Learning -- Data Mining, Inference, and Prediction}.
%      New York: Springer, 2009.
%    \bibitem[4]{YourName15-XXX}
%      F.\ Lastname1, F.\ Lastname2, and F.\ Lastname3,
%      ``Title of your INTERSPEECH 2015 publication,''
%      in \textit{Interspeech 2015 -- 16\textsuperscript{th} Annual Conference of the International Speech Communication Association, September 06--10, Dresden, Germany, Proceedings}, 2015, pp.~100--104.
%  \end{thebibliography}

\end{document}

### 2019-09-02 cv_chanwcom/cv_chanwcom.tex
Updates the CV

% generated with the docstrip utility.
%
% The original source files were:
%
% currvita.dtx  (with options: `testfile')
%
% LaTeX sample file for the currvita package
%
% Copyright (C) 1999 Axel Reichert
% See the files README and COPYING.
%
% \CharacterTable
%   {Upper-case    \A\B\C\D\E\F\G\H\I\J\K\L\M\N\O\P\Q\R\S\T\U\V\W\X\Y\Z
%   Lower-case    \a\b\c\d\e\f\g\h\i\j\k\l\m\n\o\p\q\r\s\t\u\v\w\x\y\z
%   Digits        \0\1\2\3\4\5\6\7\8\9
%   Exclamation   \!     Double quote  \"     Hash (number) \#
%   Dollar        \$     Percent       \%     Ampersand     \&
%   Acute accent  \'     Left paren    \(     Right paren   \)
%   Asterisk      \*     Plus          \+     Comma         \,
%   Minus         \-     Point         \.     Solidus       \/
%   Colon         \:     Semicolon     \;     Less than     \<
%   Equals        \=     Greater than  \>     Question mark \?
%   Commercial at \@     Left bracket  \[     Backslash     \\
%   Right bracket \]     Circumflex    \^     Underscore    \_
%   Grave accent  \`     Left brace    \{     Vertical bar  \|
%   Right brace   \}     Tilde         \~}
\documentclass[10pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% packages
\usepackage{color}
\usepackage{currvita}
\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{hyperref}
\usepackage{mdwlist}
\usepackage[resetlabels]{multibib}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[margin=1.2in]{geometry}

\definecolor{red}{RGB}{128,0,0}
\definecolor{dark_blue}{RGB}{0,0,128}
\hypersetup{
  colorlinks=true,
  linkcolor=dark_blue,
  filecolor=dark_blue,
  urlcolor=dark_blue,
}
\newcommand{\chanwcom}{\color{dark_blue} \underline{\textbf{C. Kim}}}
\newcommand{\lineunder}{
    \vspace*{-15pt}\par\hspace*{-6pt}\color{dark_blue}\hrulefill\\\color{black}}
%\newcites{pubs,intjourn,bookchap,intconf,domconf,thesis,uspatents,uspatentsapp,koreapatents}
\newcites{intjourn,bookchap,intconf,domconf,thesis,uspatents,uspatentsapp,koreapatents}
    {
     %{Peer-reviewed International Journal/Conference Papers \\
     %     \lineunder \vspace{-5mm}},
     {International Jounral Papers \\
       \lineunder \vspace{-5mm}},
     {Book Chapter \\
       \lineunder \vspace{-5mm}},
     {Peer-reviewed International Conference Papers \\
       \lineunder \vspace{-5mm}},
     {Domestic Conference Papers \\ \lineunder \vspace{-5mm}},
     {Theses \\ \lineunder \vspace{-5mm}},
     {US Patents Issued \\ \lineunder \vspace{-5mm}},
     {US Patents Application \\ \lineunder \vspace{-5mm}},
     {Korea Patents Issued \\ \lineunder \vspace{-5mm}}}
\titleformat{\section}[block]{\color{dark_blue}\Large\bfseries\filcenter}{}{1em}{}
\titleformat{\subsection}[hang]{\bfseries}{}{1em}{}

\newenvironment{packed_itemize}{
  \begin{itemize}
    \setlength{\itemsep}{1pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}
  }{\end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
\begin{flushright}
  {\footnotesize \it    Curriculum Vitae-Chanwoo Kim}
\end{flushright}
%
\section*{\filleft \LARGE \it  \href{https://scholar.google.com/citations?user=pJoZXxYAAAAJ&hl=en}{Chanwoo Kim} \filleft}
\lineunder
{  \it
56 Seongchon-Gil, Seoul R \& D campus, Seocho-gu, Seoul, 06765, South Korea \\
Cell: +82-10-4043-3996, E-mail:
\href{mailto:chanw.com@samsung.com}{chanw.com@samsung.com} \\ \\
Profile Page at Google Research : \href{https://research.google.com/pubs/105202.html}
  {\url{https://research.google.com/pubs/105202.html}} \\ \\
Google Scholar page : \href{https://scholar.google.com/citations?user=pJoZXxYAAAAJ&hl=en}
  {Link to the page} {\color{red} (h-index :22, citations: 1616)} \\ \\
Personal homepage: \href{
  http://www.cs.cmu.edu/~chanwook}{\url{http://www.cs.cmu.edu/~chanwook}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\section*{Education}
\lineunder
{\sl  Ph. D.} \\
{\color{dark_blue} \href{http://lti.cs.cmu.edu}{Language Technologies Institute},
\href{http://cs.cmu.edu}{School of Computer Science}\\
Carnegie Mellon University}, Pittsburgh, PA \hfill Sept. 2005 - Dec. 2010 \\
Advisor: Prof. Richard Stern \\
THESIS - \href{http://www.lti.cs.cmu.edu/research/thesis/2011/chanwoo_kim.pdf}{Signal Processing for Robust Speech Recognition Motivated by
Auditory Processing} \\ \\
%
{\sl  M. S.} \\
{\color{dark_blue} School of Electrical Engineering and Computer Science} \\
\href{http://www.snu.ac.kr}{Seoul National University}, Seoul, Korea \hfill March 1998 - Feb. 2001 \\
Advisor: Prof. Wonyong Sung \\
THESIS - \href{http://library.snu.ac.kr/search/DetailView.ax?sid=6&cid=925773}{Implementation of an Intonation and Pronunciation Checking System for Embedded Systems} \\ \\
%
{\sl  B. S.} \\
{\color{dark_blue} School of Electrical Engineering} \\
\href{http://www.snu.ac.kr}{Seoul National University}, 
Seoul, Korea \hfill March 1994 - Feb. 1998 \\
Thesis advisor: Prof. Min-Koo Han \\ \\
%
{\sl  High School} \\
\href{http://www.sshs.hs.kr/}{Seoul Science High School}, Seoul, Korea \hfill March 1991 - Feb. 1994 \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Interests
\section*{Research Interests}
\lineunder
\begin{packed_itemize}
\item Automatic speech recognition
\item Machine Learning and deep learning for signal processing
\item Training deep-learning system using simulated data
\item Speech enhancement (using a single microphone, dual microphones, and multiple microphones)
\item Human auditory processing
\end{packed_itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Award
\section*{Award}
\lineunder
\begin{packed_itemize}
\item {\color {dark_blue} Google spot bonus},
    Acoustic modeling for Google Home. Dec. 2016.
\item {\color {dark_blue} Google peer bonus},
    Member of the summit squad for the Google Pittsburgh Ph. D. summit 2014, Google, Jan. 2014.
\item {\color{dark_blue} Google peer bonus},
    Design and implementation of the room simulator and robustness training and evaluation using it, Google, Dec, 2013
\item {\color {dark_blue} 17-th Samsung Humantech Thesis Bronze prize},
    {\color{dark_blue} C. Kim} and R. M. Stern,
    "Power-Normalized cepstral coefficients for robust speech recognition",
     Feb. 2011
\item {\color {dark_blue} 16-th Samsung Hamantech Thesis Honour prize},
    {\color{dark_blue} C. Kim} and R. M. Stern,
    "Small power boosting and spectral subtraction for robust speech
     recognition",  Feb. 2010
\item {\color{dark_blue} Research fellowship for Ph. D. study} 2005 - 2010, Carnegie Mellon University, Jan. 2005.
\item {\color{dark_blue} Scholarship for studying abroad 2005 - 2006},
    Korea Institute of Energy Evaluation and Planning, July, 2005.
\item {\color{dark_blue} Graduate cum laude} with a bachelor’s degree, Seoul National University, Feb. 1998
\end{packed_itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Employment
\section*{Employment}
\lineunder
%
{\color{dark_blue} Samsung Research} Speech Processing Lab. \hfill Feb. 2018
- Current \\
56 Seongchon-Gil Seoul R \& D Campus, Seoul, 06765, Korea \\
Corporate Vice President \\
\vspace{-5mm}
\begin{itemize*}
  \item
    {\color{dark_blue} On-device and server neural end-to-end speech recognition} \\
  \item
    {\color{dark_blue} Wake-up engine} \\
  \item
    {\color{dark_blue} Far-field processing} \\
  \item
    {\color{dark_blue} Neural Text-to-speech engine development} \\
\end{itemize*}
%
{\color{dark_blue} Google} Google Speech \hfill Feb. 2013 - Feb. 2018 \\
1600 Amphitheatre Pkwy Mountain View, CA, 94043  \\
Senior Software Engineer \\
\vspace{-5mm}
\begin{itemize*}
  \item
    {\color{dark_blue} Room simulation system for acoustic model simulation} \\
      Designed and implemented the room acoustics simulation system using
      the image method for various kinds of real room environments. Using
      deep learning techniques, acoustic models were trained using data generated by this
      room acoustics simulator. This system has reduced Word Error Rate to half [C. Kim. et. al., Interspeech 2017]. This system is used for commercialized Google
      speech recognition systems. \\

  \item
    {\color{dark_blue} Developing next-generation voice-assistant devices for Google}
     Have participated and lead efforts for the future voice assistant
     devices at Google. Currently under development. \\

  \item
    {\color{dark_blue} Robust speech recognition for Google Home} \\
      Have participated in the Google Home project by generating
      simulated training sets and performing training and evaluation.
      This system was launched and commercialized. \\

  \item
    {\color{dark_blue} Noise robustness for speech recognition using deep learning} \\
      Developed a system which learns the mapping from noisy feature to clean feature using
      deep learning techniques for feature enhancement and noise robustness
      of speech recognition systems.  \\

  \item
    {\color{dark_blue} Multi-style training for speech recognition systems} \\
      Trained acoustic models for speech recognition systems using various
      machine learning techniques and the aforementioned room simulator.
      Using this Multi-style TRaining (MTR) approach, we obtained remarkable
      improvement under noisy environments. \\

  \item
    {\color{dark_blue} Development of the PAINT algorithm for robust speech recognition} \\
      Developed a sound source separation algorithm using
      multi-microphones named the Power Angle Information Near
      Target (PAINT) algorithm for future Internet Of Things
      (IOT) products \\
  \item
    {\color{dark_blue} Development of the TMT algorithm for robust speech recognition} \\
      Developed the Temporal Masking and Threshold (TMT)algorithm motivated by the on-set enhancement
      techniques for robust speech recognition under reverberant environment. \\

  \item
    {\color{dark_blue} Development of a Signal-to-Noise Ratio (SNR) estimation algorithm} \\
      Developed a modified Waveform Amplitude Distribution Analysis (WADA)
      algorithm as a Mapper in MapReduce at Google. It has been a valuable
      tool at Google speech.

\end{itemize*}
\vspace{5mm}
%
{\color{dark_blue} Microsoft} Microsoft Speech  \hfill Jan. 2011 - Jan. 2013\\
One Microsoft Way, Redmond, WA, 98052  \\
Speech Scientist \\
\vspace{-5mm}
\begin{itemize*}
  \item
    {\color{dark_blue} Development of the SMAD algorithm} \\
      Developed a sound source separation algorithm named Statistical
      Modeling of Angle Distribution (SMAD) for multi-microphone
      sound source separation \\
  \item
  {\color{dark_blue} Distributed processing for speech recognition} \\
      Participating in developing the infrastructure for processing big data
      for speech recognition using Cosmos. \\
  \item
    {\color{dark_blue} Post-processing of Gaussian Mixture Model (GMM)} \\
      Introducing an approach to balance deletion/insertion errors
      by modifying the mixture components of GMM. \\
  \item
    {\color{dark_blue} {Audio-Video (AV) capture pipeline for Microsoft Windows Phone}} \\
      Audio/Video capturing using Microsoft media foundation for Windows Phone 8. \\

  \item
    {\color{dark_blue} Media Foundation Transforms (MFTs)}
        Design and implementation of several Media Foundation Transforms
      (SW Jpeg Encoder MFT, Demux MFT, etc). \\
  \item
    {\color{dark_blue} Camera pipeline} \\
      Working for EXIF processing, meta data handling etc.
\end{itemize*}
\vspace{5mm}
%
{\color{dark_blue} LG Electronics } \hfill June 2003 - Aug. 2005 \\
128, Yeoui-daero Yeongdeungpo-gu, Seoul, Korea, 150-721  \\
Senior Research Engineer, VoIP Phone Conference Call Development Team Leader \\
\vspace{-5mm}
\begin{itemize*}
  \item {\color{dark_blue} VoIP handset project}
      Manging the conference-call part using the Session Initiation Protocol (SIP). \\

  \item {\color{dark_blue} Video On Demand (VOD) system project}
      Participating in the VOD project working on streaming protocols such as
      Real-Time Protocol (RTP), Real-Time Control Protocol (RTCP), and
      Real-Time Streaming Protocol (RTSP). \\

  \item {\color{dark_blue} Development of an audio/video synchronization algorithm}
      Developing an audio/video synchronization algorithm for
      Video Telephony (VT) using Network Time Protocol (NTP). \\

  \item {\color{dark_blue} Testing and evaluation of multimedia codes}
      H.263, H.264, AAC, AAC+, and H.323 \\

  \item {\color{dark_blue} Multimedia platform survey}
      Texas Instruments (TI) Open Multimedia Application Platform (OMAP), Neomagic MiMagic6, Renesas SH-Mobile V. etc
\end{itemize*}
\vspace{5mm}
%
{\color{dark_blue} SK Teletech } \hfill June 2003 - Aug. 2005 \\
Research Engineer \\
\\
{\color{dark_blue} Edumediatek } \hfill June 2000 - July 2002 \\
Research Engineer \\
A research venture company established by Prof. Wonyong Sung at Seoul National University
\begin{itemize*}
  \item {\color{dark_blue} Computer Aided Language Learning (CALL) System} Intonation and vowel checking
system for embedded systems \\
  \item {\color{dark_blue} Development of a robust formant extraction algorithm} Combination of the spectral \\
 peak picking and root solving \\
  \item {\color{dark_blue} Development of a robust pitch extraction algorithm}
\end{itemize*}
\vspace{5mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Graduate research
\section*{Graduate research}
\lineunder

\begin{itemize*}
  \item {\color{dark_blue} Power Normalized Central Coefficients (PNCC)}
      Motivated by human auditory processing, this new feature set
      incorporates modulation frequency, temporal masking, and
      rate-nonlinearity concepts. The features require low computation
      and on-line implementation is possible. \\

  \item {\color{dark_blue} Small Power Boostin (SPB) Algorithm}
      Developed the SPB algorithm motivated by the human rate-intensity
      as well as temporal and spectral smoothing. This algorithm works
      especially well for non-stationary noise such as music noise. \\

  \item {\color{dark_blue} Dual-microphone speech enhancement systems}
      Developed the Phase Difference Channel Weighting (PDCW) algorithm
      which performs sound source separation without a priori knowledge
      of source locations. \\

  \item {\color{dark_blue} Single-microphone speech enhancement system}:
      Developed the Power-function-based Power Distribution Normalization
      (PPDN) algorithm which enhances speech. \\

  \item {\color{dark_blue} Automatic speech recognition with
      low computational cost}
      Focused on developing online algorithms, which are robust against
      noise with low computational complexity. \\

  \item {\color{dark_blue} SNR Estimation algorithm for speech}:
      Developed a new algorithm which estimates Signal-to-
      Noise Ratio (SNR) more accurately than the standard NIST STNR algorithm. \\

  \item {\color{dark_blue} Automatic ITD threshold detection algorithm}:
      Developed a new algorithm which can obtain the optimal ITD threshold
      for spatial separation of signals. \\

  \item {\color{dark_blue} Dereverberation algorithm}
      Developed Suppression of Slowly-varying and Falling edges (SSF): a
      simple algorithm for robust speech recognition that is highly effective
      in reverberant environments. \\

  \item {\color{dark_blue} HLab C++ automatic speech recognition system}
      Developed a C++ HMM (Hidden Markov Model) speech recognition system from
      scratch. \\

  \item {\color{dark_blue} Power Normalized Voice Activity Detection (PN-VAD)}
      Developed a new voice activity detection algorithm that is very accurate
      and computationally efficient. \\

  \item {\color{dark_blue} DARPA GALE project}
      Robust front end for the DARPA GALE project. Applied a new feature set
      that we developed for the 180-hr training set and the large vocabulary
      Broadcast News test set. \\

  \item {\color{dark_blue} NSF auditory signal processing project}
      Developed features motivated by auditory processing, binaural processing,
      and poly-aural processing. \\

  \item {\color{dark_blue}Samsung speech-to-speech translator project}
      Developed low-complexity online algorithms for embedded processors.
      Developed an on-line noise-robustness feature extraction algorithm,
      a binaural source-separation algorithm, an online VAD, an online MVN,
      and supporting technologies.
      Applied the algorithm to a 64,000-word database with a 500-hour training set. \\

  \item {\color{dark_blue} Voice activity detector project}
      Designed a robust VAD which requires very low computation.

\end{itemize*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Invited talk
\section*{Invited Talks}
\lineunder
\begin{itemize*}
  \item ``Introduction to contemporary speech recognition systems and recent advances from deep-learning and human auditory processing techniques," Korea Aerospace University, Goyang, Korea, May. 2015.
  \item ``Research direction for robust speech recognition," Samsung Advanced Institute of Technology, Suwon, Korea, Dec. 2014.
  \item ``Speech recognition research using neural networks," Seoul National University, Seoul Korea, Sept. 2014.
  \item ``Speech Noise Robustness for Intelligent Cars and Home Appliances," Yonsei University, Wonju, Korea, Sept. 2014.
  \item ``TMT, SSF, and PAINT algorithms for far-field speech recognition," Sogang University, July, 2014.
  \item ``Speech Recognition Infrastructure and Noise Robustness Efforts," Seoul National University. July, 2014.
  \item ``Signal Processing for Robust Speech Recognition Motivated by Auditory Processing," Sogang University, Sept. 2012.
\end{itemize*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Invited talk
\section*{Teaching Experience}
\lineunder
\begin{itemize*}
  \item Teaching Assistant, 18-792 Advanced Digital Signal Processing,
    Electrical and Computer Engineering Department, Carnegie Mellon University, Spring, 2010.
  \item Teaching Assistant, including weekly recitations,
    15-211 fundamental data structures and algorithms,
    School of Computer Science, Carnegie Mellon University, Fall, 2009.
\end{itemize*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publications
% 2019
\nociteintconf{d_gowda_interspeech_2019_00}
\nociteintconf{c_kim_interspeech_2019_00}
\nociteintconf{a_menon_icassp_2019_00}

% 2018 
\nociteintconf{c_kim_interspeech_2018_00}
\nociteintconf{x_zhou_isnn_2018_00},
\nociteintconf{c_kim_icassp_2018_00}
\nociteintconf{c_kim_icassp_2018_01}
%\nociteintconf{r_nongpiur_icassp_2018_00}
%\nociteintconf{a_menon_icassp_2018_00}
% 2017
\nociteintconf{a_menon_asru_2017_00}
\nociteintconf{C_Kim_INTERSPEECH_2017_1}
\nociteintconf{B_Li_INTERSPEECH_2017_1}
\nociteintconf{A_Menon_INTERSPEECH_2017_1}
\nociteintjourn{T_Sainath_IEEETran_2017_1}
\nocitebookchap{T_Sainath_Book_Chapter_2017_1}
% 2016
\nociteintjourn{C_Kim_IEEETran_2016_1}
\nociteintjourn{B_Cho_SigProcLetters_2016_1}

% 2015
\nociteintconf{C_Kim_INTERSPEECH_2015}

% 2014
\nociteintconf{C_Kim_INTERSPEECH_2014_2}
\nociteintconf{C_Kim_INTERSPEECH_2014_1}

% 2013

% 2012
\nociteintconf{C_Kim_ICASSP_2012_2}
\nociteintconf{C_Kim_ICASSP_2012_1}

% 2011
\nociteintconf{C_Kim_ICASSP_2011_3}
\nociteintconf{C_Kim_ICASSP_2011_2}

% 2010
\nociteintconf{C_Kim_ICASSP_2010_1}
\nociteintconf{C_Kim_INTERSPEECH_2010_2}
\nociteintconf{C_Kim_INTERSPEECH_2010_1}

% 2009
\nociteintconf{C_Kim_ASRU_2009_2}
\nociteintconf{C_Kim_ASRU_2009_1}
\nociteintconf{C_Kim_INTERSPEECH_2009_2}
\nociteintconf{C_Kim_INTERSPEECH_2009_1}

% 2008
\nociteintconf{C_Kim_INTERSPEECH_2008}
\nociteintconf{R_M_Stern_HSCMA_2008}

% 2007

% 2006
\nociteintjourn{C_Kim_EurasipJourn_2006}
\nociteintjourn{C_Kim_IEICE_2006}
\nociteintconf{C_Kim_INTERSPEECH_2006}
\nociteintconf{C_Kim_ICCE_2006}

% 2005
\nociteintjourn{C_Kim_TransCE_2005}
\nociteintconf{C_Kim_ICCE_2005}

% 2004

% 2003

% 2002
\nociteintconf{C_Kim_INTERSPEECH_2002}

% 2001
\nociteintconf{C_Kim_ICSP_2001}

\bibliographystyleintjourn{ieee_tran}
\bibliographyintjourn{../common_bib_file/common_bib_file}

\bibliographystylebookchap{ieee_tran}
\bibliographybookchap{../common_bib_file/common_bib_file}

\bibliographystyleintconf{ieee_tran}
\bibliographyintconf{../common_bib_file/common_bib_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Domestic conference
\nocitedomconf{C_Kim_KCC_2005}

\bibliographystyledomconf{ieee_tran}
\bibliographydomconf{../common_bib_file/common_bib_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Theses
\nocitethesis{C_Kim_PhDThesis_2010}
\nocitethesis{C_Kim_MSThesis_2001}

\bibliographystylethesis{ieee_tran}
\bibliographythesis{../common_bib_file/common_bib_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% US Patents Issued
% 2016
\nociteuspatents{C_Khwand_USPatent_Issued_2016_1}

% 2015
\nociteuspatents{C_Kim_USPatent_Issued_2015_1}

% 2014
\nociteuspatents{C_Kim_USPatent_Issued_2014_1}

% 2011
\nociteuspatents{C_Kim_USPatent_Issued_2011_1}

% 2010
\nociteuspatents{C_Kim_USPatent_Issued_2010_2}
\nociteuspatents{C_Kim_USPatent_Issued_2010_1}

% 2009
\nociteuspatents{C_Kim_USPatent_Issued_2009_4}
\nociteuspatents{C_Kim_USPatent_Issued_2009_3}
\nociteuspatents{C_Kim_USPatent_Issued_2009_2}
\nociteuspatents{C_Kim_USPatent_Issued_2009_1}

% 2008
\nociteuspatents{C_Kim_USPatent_Issued_2008_1}

\bibliographystyleuspatents{ieee_tran}
\bibliographyuspatents{../common_bib_file/common_bib_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% US Patents Application

% 2016
\nociteuspatentsapp{A_Narayanan_USPatent_Application_2016_1}
\nociteuspatentsapp{A_Misra_USPatent_Application_2016_1}

% 2014
%\nociteuspatentsapp{C_Kim_USPatent_Application_2014_1}
%\nociteuspatentsapp{C_Khawand_USPatent_Application_2014_1}

% 2012
\nociteuspatentsapp{C_Kim_USPatent_Application_2012_1}

% 2006
\nociteuspatentsapp{C_Kim_USPatent_Application_2006_5}
\nociteuspatentsapp{C_Kim_USPatent_Application_2006_4}
\nociteuspatentsapp{C_Kim_USPatent_Application_2006_3}
\nociteuspatentsapp{C_Kim_USPatent_Application_2006_1}

% 2005
\nociteuspatentsapp{C_Kim_USPatent_Application_2005_3}
\nociteuspatentsapp{C_Kim_USPatent_Application_2005_1}

\bibliographystyleuspatentsapp{ieee_tran}
\bibliographyuspatentsapp{../common_bib_file/common_bib_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Korea Patents Issued

% 2007
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2007_1}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2007_2}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2007_3}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2007_4}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2007_5}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2007_6}

% 2006
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2006_1}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2006_2}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2006_3}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2006_4}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2006_5}
% The following has become void.
%\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2006_6}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2006_7}
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2006_8}

% 2005
\nocitekoreapatents{C_Kim_KoreaPatent_Issued_2005_1}

\bibliographystylekoreapatents{ieee_tran}
\bibliographykoreapatents{../common_bib_file/common_bib_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Technical skills
\section*{Technical skills}
\lineunder
\begin{itemize*}
  \item Programming Language :
      C, C++, Pyhon, Perl, Java, Matlab, various shell scripts, etc.
  \item Programming Environments :
      Win32 API, Microsoft Foundation Class (MFC), NumPy/SciPy, MapReduce, and various Linux environments.
  \item Speech Recognition Engine :
      Sphinx, Hidden markov model Tool Kit (HTK), Janus, etc.
  \item Development Tool : Various Linux tools including gcc. Microsoft visual studio,
      Arm Developer Suite (ADS), Code Composer Studio (CCS), etc.
  \item Real-time OS : Rex, Nucleus
\end{itemize*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References
\section*{References}
\lineunder

\begin{itemize*}
  \item
    {\color{dark_blue} Prof. Richard M. Stern} (Ph. D. study advisor 2005-2010)\\
    Department of Electrical and Computer Engineering,
    Carnegie Mellon University, \\
    B24 Porter Hall \\
    5000 Forbes Ave, Pittsburgh, PA 15213, USA (Tel: +1-412-268-2535) \\
    E-mail: \href{mailto:rms@cs.cmu.edu}{rms@cs.cmu.edu} \\

  \item
    {\color{dark_blue} Prof. Wonyong Sung} (M. S. study advisor 1999-2001) \\
    Department of Electrical and Computer Engineering, Seoul National Univ. \\
    1 Gwanangno, Gwanak-gu, Seoul, Korea, 151-744 (Tel: +82-2-880-1816)  \\
    E-mail: \href{mailto:wysung@dsp.snu.ac.kr}{wysung@dsp.snu.ac.kr} \\

  \item
    {\color{dark_blue} Prof. Bhiksha Raj} (Collaborating professor) \\
    Language Technologies Institute, School of Computer Science,
    Carnegie Mellon University, \\
    6705 Gates-Hillman Center,
    5000 Forbes Ave, Pittsburgh, PA 15213  (Tel: +1-412-268-9826) \\
    E-mail: \href{mailto:bhiksha@cs.cmu.edu}{bhiksha@cs.cmu.edu} \\

  \item {\color{dark_blue} Prof. Rita Singh} \\
    Language Technologies Institute, School of Computer Science,
    Carnegie Mellon University, \\
    6723 Gates-Hillman Center,
    5000 Forbes Ave, Pittsburgh, PA 15213  (Tel: +1-412-268-9859) \\
    E-mail: \href{mailto:rsingh@cs.cmu.edu}{rsingh@cs.cmu.edu} \\

  \item {\color{dark_blue} Prof. Kwang-deok Seo} (Manager at LG 2003-2005) \\
    Computer\&Telecommunications Engineering Division,
    Yonsei University, \\
    1 Yonseidae-gil, Wonju, Gangwon-do, 220-710, Korea, (Tel: +1-33-760-2788) \\
    E-mail: \href{mailto:kdseo@yonsei.ac.kr}{kdseo@yonsei.ac.kr}
\end{itemize*}
\vspace{10mm}
\begin{flushright}
    Updated Sept. 1st , 2017
\end{flushright}
\end{document}
\endinput
%%
%% End of file `cvtest.tex'.

### 2019-09-14 nips_2018_neural_front_end/doc/Template.tex
update the papers

% Template for ASRU-2017 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{AUTHOR GUIDELINES FOR ASRU 2017 PROCEEDINGS MANUSCRIPTS}
%
% Single address.
% ---------------
\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
The abstract should appear at the top of the left-hand column of text, about
0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
beginning of the main text.  The abstract should contain about 100 to 150
words, and should be identical to the abstract text submitted electronically
along with the paper cover sheet.  All manuscripts must be in English, printed
in black ink.
\end{abstract}
%
\begin{keywords}
One, two, three, four, five
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

These guidelines include complete descriptions of the fonts, spacing, and
related information for producing your proceedings manuscripts. Please follow
them and if you have any questions, direct them to Conference Management
Services, Inc.: Phone +1-979-846-6800 or email
to \\\texttt{papers@asru2017.org}.

\section{Formatting your paper}
\label{sec:format}

All printed material, including text, illustrations, and charts, must be kept
within a print area of 7 inches (178 mm) wide by 9 inches (229 mm) high. Do
not write or print anything outside the print area. The top margin must be 1
inch (25 mm), except for the title page, and the left margin must be 0.75 inch
(19 mm).  All {\it text} must be in a two-column format. Columns are to be 3.39
inches (86 mm) wide, with a 0.24 inch (6 mm) space between them. Text must be
fully justified.

\section{PAGE TITLE SECTION}
\label{sec:pagestyle}

The paper title (on the first page) should begin 1.38 inches (35 mm) from the
top edge of the page, centered, completely capitalized, and in Times 14-point,
boldface type.  The authors' name(s) and affiliation(s) appear below the title
in capital and lower case letters.  Papers with multiple authors and
affiliations may require two or more lines for this information. Please note
that papers should not be submitted blind; include the authors' names on the
PDF.

\section{TYPE-STYLE AND FONTS}
\label{sec:typestyle}

To achieve the best rendering both in printed proceedings and electronic proceedings, we
strongly encourage you to use Times-Roman font.  In addition, this will give
the proceedings a more uniform look.  Use a font that is no smaller than nine
point type throughout the paper, including figure captions.

In nine point type font, capital letters are 2 mm high.  {\bf If you use the
smallest point size, there should be no more than 3.2 lines/cm (8 lines/inch)
vertically.}  This is a minimum spacing; 2.75 lines/cm (7 lines/inch) will make
the paper much more readable.  Larger type sizes require correspondingly larger
vertical spacing.  Please do not double-space your paper.  TrueType or
Postscript Type 1 fonts are preferred.

The first paragraph in each section should not be indented, but all the
following paragraphs within the section should be indented as these paragraphs
demonstrate.

\section{MAJOR HEADINGS}
\label{sec:majhead}

Major headings, for example, "1. Introduction", should appear in all capital
letters, bold face if possible, centered in the column, with one blank line
before, and one blank line after. Use a period (".") after the heading number,
not a colon.

\subsection{Subheadings}
\label{ssec:subhead}

Subheadings should appear in lower case (initial word capitalized) in
boldface.  They should start at the left margin on a separate line.

\subsubsection{Sub-subheadings}
\label{sssec:subsubhead}

Sub-subheadings, as in this paragraph, are discouraged. However, if you
must use them, they should appear in lower case (initial word
capitalized) and start at the left margin on a separate line, with paragraph
text beginning on the following line.  They should be in italics.

\section{PRINTING YOUR PAPER}
\label{sec:print}

Print your properly formatted text on high-quality, 8.5 x 11-inch white printer
paper. A4 paper is also acceptable, but please leave the extra 0.5 inch (12 mm)
empty at the BOTTOM of the page and follow the top and left margins as
specified.  If the last page of your paper is only partially filled, arrange
the columns so that they are evenly balanced if possible, rather than having
one long column.

In LaTeX, to start a new column (but not a new page) and help balance the
last-page column lengths, you can use the command ``$\backslash$pagebreak'' as
demonstrated on this page (see the LaTeX source below).

\section{PAGE NUMBERING}
\label{sec:page}

Please do {\bf not} paginate your paper.  Page numbers, session numbers, and
conference identification will be inserted when the paper is included in the
proceedings.

\section{ILLUSTRATIONS, GRAPHS, AND PHOTOGRAPHS}
\label{sec:illust}

Illustrations must appear within the designated margins.  They may span the two
columns.  If possible, position illustrations at the top of columns, rather
than in the middle or at the bottom.  Caption and number every illustration.
All halftone illustrations must be clear black and white prints.  Colors may be
used, but they should be selected so as to be readable when printed on a
black-only printer.

Since there are many ways, often incompatible, of including images (e.g., with
experimental results) in a LaTeX document, below is an example of how to do
this \cite{Lamp86}.

\section{FOOTNOTES}
\label{sec:foot}

Use footnotes sparingly (or not at all!) and place them at the bottom of the
column on the page on which they are referenced. Use Times 9-point type,
single-spaced. To help your readers, avoid using footnotes altogether and
include necessary peripheral observations in the text (within parentheses, if
you prefer, as in this sentence).

% Below is an example of how to insert images. Delete the ``\vspace'' line,
% uncomment the preceding line ``\centerline...'' and replace ``imageX.ps''
% with a suitable PostScript file name.
% -------------------------------------------------------------------------
\begin{figure}[htb]

\begin{minipage}[b]{1.0\linewidth}
  \centering
  \centerline{\includegraphics[width=8.5cm]{image1}}
%  \vspace{2.0cm}
  \centerline{(a) Result 1}\medskip
\end{minipage}
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{image3}}
%  \vspace{1.5cm}
  \centerline{(b) Results 3}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{image4}}
%  \vspace{1.5cm}
  \centerline{(c) Result 4}\medskip
\end{minipage}
%
\caption{Example of placing a figure with experimental results.}
\label{fig:res}
%
\end{figure}

% To start a new column (but not a new page) and help balance the last-page
% column length use \vfill\pagebreak.
% -------------------------------------------------------------------------
%\vfill
%\pagebreak

\section{COPYRIGHT FORMS}
\label{sec:copyright}

You must include your fully completed, signed IEEE copyright release form when
form when you submit your paper. We {\bf must} have this form before your paper
can be published in the proceedings.

\section{REFERENCES}
\label{sec:ref}

List and number all bibliographical references at the end of the
paper. The references can be numbered in alphabetic order or in
order of appearance in the document. When referring to them in
the text, type the corresponding reference number in square
brackets as shown at the end of this sentence \cite{C2}. An
additional final page (the fifth page, in most cases) is
allowed, but must contain only references to the prior
literature.

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{strings,refs}

\end{document}

### 2019-09-14 nips_2018_neural_front_end/doc/main.tex
update the papers

--- 2019-04-28 neural_frontend/doc/main.tex
@@
 
-%\begin{figure}
-%    \centering
-%    \resizebox{80mm}{!}{%
-%         \input{../figures/entire_diagram.tex}} %
-%    \caption {
-%      The structure of feature enhancement using peak
-%      value normalization and LSTMs.
-%      \label{fig:entire_diagam}
-%    }
-%    %\end{center}
-%\end{figure}
+\begin{figure}
+    \centering
+    \resizebox{80mm}{!}{%
+         \input{../figures/entire_diagram.tex}} %
+    \caption {
+      The structure of feature enhancement using peak
+      value normalization and LSTMs.
+      \label{fig:entire_diagam}
+    }
+    %\end{center}
+\end{figure}
 
@@
 %
-%\begin{figure}
-%  \centering
-%    \begin{subfigure}{\linewidth}
-%      \centering
-%      \includegraphics[width=70mm]{room_diagram.eps}
-%      \caption{}
-%      \label{fig:room_diagram}
-%    \end{subfigure}
-%   \\
-%    \begin{subfigure}{\linewidth}
-%      \centering
-%      \includegraphics[width=70mm]{image_method.eps}
-%      \caption{}
-%      \label{fig:image_method}
-%    \end{subfigure}
-%    \caption{
-%    (a) A simulated room: There may be multiple microphones, a single target
-%    sound source, multiple noise sources in a cuboid-shape room with
-%    acoustically reflective walls. (b) A diagram showing the location
-%    of the real and the virtual sound sources assuming that the walls
-%    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
-%  \vspace{-10mm}
-%\end{figure}
+\begin{figure}
+  \centering
+    \begin{subfigure}{\linewidth}
+      \centering
+      \includegraphics[width=70mm]{room_diagram.eps}
+      \caption{}
+      \label{fig:room_diagram}
+    \end{subfigure}
+   \\
+    \begin{subfigure}{\linewidth}
+      \centering
+      \includegraphics[width=70mm]{image_method.eps}
+      \caption{}
+      \label{fig:image_method}
+    \end{subfigure}
+    \caption{
+    (a) A simulated room: There may be multiple microphones, a single target
+    sound source, multiple noise sources in a cuboid-shape room with
+    acoustically reflective walls. (b) A diagram showing the location
+    of the real and the virtual sound sources assuming that the walls
+    reflects acoustic wave like a mirror \cite{C_Kim_INTERSPEECH_2017_1}.}
+  \vspace{-10mm}
+\end{figure}
 %

### 2019-09-14 nips_2018_neural_front_end/doc/main_bak.tex
update the papers

%% bare_jrnl.tex
%% V1.4
%% 2102/12/27
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8 or later) with an IEEE journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/10 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex,
%%                    bare_jrnl_transmag.tex
%%*************************************************************************

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% IEEEtran contains the IEEEalign family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{dsfont}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% New commands
\newcommand{\chanwcom}{{C. Kim}}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Phase Difference Smoothing for Sound Source Separation Under Reverberant Environment}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{
        %Chanwoo~Kim,~\IEEEmembership{Member,~IEEE,}
        %and~M~Bacciani,~\IEEEmembership{Member,~IEEE,}% <-this % stops a space
\thanks{M. Shell is with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised December 27, 2102.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2102}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2102 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
This paper presents a new algorithm for normalizing multi-microphone
signals under reverberation. In this study, we observe that in
reverberant environments, Interaural Time Delay (ITD) or Phase
Difference (PD) estimation may be distorted due to reflections. We
propose a method referred to as Multi-Microphone Signals Normalization (MMSN) 
to model this distortion as a transfer function 
between multi-microphone signals and to compensate this distortion.
We combine this MMSN algorithm with our previous sound source separation 
algorithm referred to as Phase Difference Channel Weighting (PDCW). 
Speech recognition experiment shows that MMSN algorithm significantly 
enhances robustness of sound source separation algorithms under 
reverberant environments.

\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Multi-microphone signal processing, masking, reverberation,
interaural time delay, phase difference, beam forming,
robust speech recognition
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results.}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

\section{Introduction}
\cite{J_Allen_JASA_1979}
\IEEEPARstart{S}{peech} recognition systems have significantly improved
these days, and we have been widespread usage of them
for hand-held devices like smart phones. 
Recent advances in machine learning techniques such 
as Deep Neural Network \cite{G_Hinton_IEEE_Signal_Process_Mag_2012}
and enhanced computational power \cite{V_Vanhoucke_Deep_Learning_NIPS_Workshop_2011}
have made tremendous contribution for improving speech recognition accuracy.
In spite of these success with close-talking applications
 like smart phones, they have been less successful for 
far-field applications such as
speech recognition inside a car or speech recognition for
home appliance devices. The major problem is that under
noisy or reverberant environments, speech recognition
accuracy is quite adversely affected.

Thus far, many researchers have proposed various kinds of algorithms
to address this problem  \cite{P_J_Moreno_ICASSP_1996,
R_M_Stern_ETRW_1997, C_Kim_ASRU_2009_2, C_Kim_ICASSP_2012_1,
C_Kim_ICASSP_2012_2}. To some degrees, these efforts have brought
some improvement. Nevertheless for highly non-statioary noise
or reverberent speech, the improvment has been still limited.
For these environments, recent work motivated by human 
auditory processing seems to be more promising
\cite{C_Kim_ICASSP_2012_1, C_Kim_INTERSPEECH_2010_2, 
C_Kim_ICASSP_2010_1, C_Kim_INTERSPEECH_2006}.

TODO(chanwcom) Revise the introduction
An alternative approach is signal separation based on anal-
ysis of differences in arrival time [8], [9], [10]. It
is well documented that the human binaural system has a
remarkable ability to separate speech and other sounds that
arrive from different azimuths [11]. It has been observed
that various types of cues are used to segregate the target signal
from interfering sources. Motivated by these observations,
many models and algorithms have been developed using
inter-microphone time differences (ITDs), inter-microphone
intensity difference (IIDs), inter-microphone phase differences
(IPDs), and other cues [8], [9], [12], [13]. IPD and ITD
have been extensively used in binaural processing because
this information can be easily obtained by spectral analysis
[12] [14] [15]. ITD can be estimated using either phase
differences [15], cross-correlation [16], [17], or
zero-crossings  [9].

Research on signal separation based on analysis of 
differences in arrival time has be conducted for a long time
by many researchers
\cite{SrinivasanEtAl06, H_Park_SpeechComm_2009, 
P_Aarabi_IEEETranSysManCyber_2005}.

signal separation based on analysis of differences in arrival time 
[1, 2]. It is well known that the human binaural system is remark-
able in its ability to separate speech from interfering sources (e.g.
[3]). Motivated by these observations, many models and algorithms
have been developed using interaural time differences (ITDs), inter-
aural intensity difference (IIDs), interaural phase differences (IPDs),
and other cues [1, 2, 4]. IPD and ITD have been extensively
used in binaural processing because this information can be easily
obtained by spectral analysis [5].

TODO(chanwcom) Mention the frequency smoothing.
PNCC, my thesis, other binaural papers.

In PDS altorithm, 
In MMSN algorithm, to capture the effect of reverberation, we use
a longer window than those used for speech feature extraction.
Based on experimental results, we use a medium-duration window as in
\cite{C_Kim_ASRU_2009_1, C_Kim_ASRU_2009_2, 
C_Kim_PhDThesis_2010, C_Kim_ICASSP_2012_1}.

This paper is organized as follows:

In our previous work TODO[XX] \cite{}, we have frequently assumed that the
each microphone in a microphone array has exactly the same frequency 
response.

TODO
however, this is not true with real-recordings since each microphone
in a multi-microphone array does not have exactly the same

[CWP]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Section
\section{Background theory}

\subsection {Near-field effect}

In this work, we assume that we do not have prior knowledge about the
target sound source location. However, based on our

We use ILD, but if we directly use ILDs, then it will

Thus, we try the following feature combinations.

Smoothed

We try the following different features.

log(A / B)
(A / B) ^ (p)

As will be described in TODO(chanwcom)

However, along with this, based on discussion... We assume that
log(A) log(B)
log(A / B)
(A / B) ^ (p)

[CWP]

\subsection {PDCW algorithm}

\subsection {Image method to model reverberation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Section
\section{The effects of reverberation on multi-microphone signals}

\subsection{Virtual sources in symmetric and asymmetric target location configuration}

\subsection{The effect of reverberation on the target source}

\begin{figure}[!t]
  \centering
    \resizebox{60mm}{!}{\input{../figures/symmetric_room.tex}}
    \caption {
      A target source and its mirrored image   
    }   
\label{fig:symmetric_configuration}
\end{figure}

\begin{figure}[!t]
  \centering
    \resizebox{60mm}{!}{\input{../figures/asymmetric_room.tex}}
    \caption {
      A target source and its mirrored image   
    }   
\label{fig:asymmetric_configuration}
\end{figure}

\begin{figure}[!t]
  \centering
    \resizebox{60mm}{!}{\input{../figures/one_source_one_wall.tex}}
    \caption {
      A target source and its mirrored image   
    }   
\label{fig:one_target_one_virtual}
\end{figure}

\begin{figure}[!t]
  \centering
    \resizebox{60mm}{!}{\input{../figures/one_source_in_room.tex}}
    \caption {
      A target source and its mirrored image   
    }   
\label{fig:one_target_one_virtual}
\end{figure}

Suppose that we place two microphones inside a room as shown in Fig. XXX.
We refer the two signals received by these microphones as 
$x_0[n]$ and $x_1[n]$, and the target signal as $x[n]$.
Let us further assume that the reflection coefficients of the walls
of the room is a constant. Under this assumption, the effect of 
reflection is frequently modeled by the image method. XXXX

In the image method \cite{J_Allen_JASA_1979}, the RIR from the
source to the receiver is obtained by considering images
sources on an infinite grid of mirrored rooms. In Fig. XX, 
we show a 3 x 3 subset of

In Fig. XXX, we represent a true sound source by a solid circle and
virtual sound sources that are mirrored images of the target source 
by a circle with dashed patterns.

For all sound sources including both the original sound source 
and the virtual sound sources, the impulse response for the
microphone 0 and the microphone 1 may be represented by  
the following equation:

\cite{E_A_Lehmann_ASPAA_2007},

In this case, the signal from the left and right microphones 
$x_l[n]$ and $x_r[n]$ may be represented by the following 
equations:

In Fig. XX, we assume that the mirrored source $\mathcal{M}$
is located along a line with a angle of $\theta_M$ with respect to
the line connecting the target and the center of two microphones. 
In this case, the Intermicrophone Time Difference is given by TODO(chanwcom) [XX][XX]
\begin{align}
  d = \frac{A}{B} 
\end{align}
As a specific example, if the $d_t$ is two meters, and the distance 
then, $d_m$ is

When the reflection coefficient is $r$, after the sound wave hits
the wall, the amplitude of the reflected wave becomes $r$ times 
the original waveform [XX].
The amplitude of the waveform is inversely proportional to 
the distance. Thus, the 
\begin{align}
  \alpha = \frac{d_l}{d_m}  
\end{align}

The ratio of the amplitude from the mirrored source to the target
source $\gamma$ is given by:

\begin{subequations}
  \begin{align}
    x_0[n] & = x_t[n] + r \frac{d_l}{d_m} x_t[n - \tau_0] \\
    x_1[n] & = x_t[n] + r \frac{d_l}{d_m} x_t[n - \tau_1]
  \end{align}
\end{subequations}

Performing STFT, we obtain the following equations:
\begin{subequations}
  \begin{align}
    X_0[m, e^{j \omega_k}] 
    = \left(1  + \gamma e^{-j \omega_k d_0} \right) X_t[m, e^{j \omega_k}] \label{eq:target_left_spec}\\
%
    X_1[m, e^{j \omega_k}] 
    = \left(1  + \gamma e^{-j \omega_k d_1} \right) X_t[m, e^{j \omega_k}] \label{eq:target_right_spec}
  \end{align}
\end{subequations}
where $r$ is the reflection coefficient.

\subsection{The effects of mirrored sources on phase difference}

The relationship between the $T_{60}$ and the reflection coefficient may
be approximated by Eryling's empiricial equation [XX]:
\begin{align}
  \alpha & = 1 - \exp \left(\frac{- 0.16 V}{S T_{60}}  \right) \\
  r & = \sqrt{1 - \alpha^2}
\end{align}
where $\alpha$ and $r$ are an absorption coefficient and a reflection coefficient
respectively, and where $V$ is the volume of the room and $S$ is the total
surface area of the room.  As a specific example, for a typical room of a size 
of 5 m x 4 m x 3 m and and a reverberation time $T_{60}$ of 300 $ms$, the reflection
coefficient $r$ is 0.9575.

When there is only one target without noise, the phase difference between
\eqref{eq:target_left_spec} and \eqref{eq:target_right_spec} is given by:
%
%
\begin{align}
  \Delta \phi[m, e^{j \omega_k}] = \angle \left( 1  + \gamma e^{-j \omega_k \tau_0}\right)
    - \angle \left( 1  + \gamma e^{-j \omega_k \tau_0}\right)
\end{align}
%

Let us define 
\begin{align}
  \tau_{ave} = \frac{\tau_0 + \tau_1}{2}
\end{align}

\begin{align}
  \Delta \phi[m, e^{j \omega_k}] 
        = \tan^{-1}\left( \frac{\gamma \sin \left(\omega_k d_0 \right)}
        {1 + \gamma \cos \left( \omega_k d_0 \right)} \right) \nonumber  \\
        - \tan^{-1}\left( \frac{\gamma \sin \left(\omega_k d_1 \right)}
        {1 + \gamma \cos \left( \omega_k d_1 \right)} \right) 
          \label{eq:phase_diff_one_target_one_mirror}
\end{align}
If the argument $x$ of $\tan^{-1}$ is small enough, then it may be approximated 
by $\tan^{1}(x) \approx x$. In this case, \eqref{eq:phase_diff_one_target_one_mirror},
may be approximated by the following equation:
\begin{align}
  \Delta \phi[m, e^{j \omega_k}] & \approx 
    \gamma \left[ \sin \left(\omega_k d_0 \right) 
    - \sin \left(\omega_k d_1 \right) \right]  \nonumber \\
        & = \gamma \sin \left(\frac{\omega_k \left(d_0 + d_1 \right) }{2}  \right)
    \sin \left( \frac{ \omega_k \left(d_0 - d_1 \right) }{2} \right)
      \label{eq:approx_phase_diff_one_target_one_mirror}
\end{align}

%
From the equation \eqref{eq:approx_phase_diff_one_target_one_mirror}, we observe
that the high frequency component is due to the following term: 
\begin{align}
  \Delta = \sin \left( \frac{\omega_k \left(d_0 + d_1\right)}{2} \right)
\end{align}
With respect to the $\omega$ the period is $x$ given by:
\begin{align}
  \frac{2 \pi}{\tau_{ave}} \label{eq:frequency_domain_period}
\end{align}
From \eqref{eq:frequency_domain_period}, we observe that the period depends on the 
distance between ... . Thus, it is safe to say that 
As distance of the becomes farther, the period becomes smaller.
We assume that $d_{ave}  = \frac{d_0 - d_1}{2}$ is at least 1 meter.

In the real situation of far-field speech recognition,

\subsection{The effects of mirrored sources when the target is inside a room}

where $\omega_k$ is the discrete-frequency index defined by
\begin{align}
  \omega_k = \frac{2 \pi k}{N}, \qquad 0 \le k \le N - 1
\end{align}
where $N$ is the DFT size. Typical reverberation time in terms of
$T_{60}$ is between 100 ms and 400 ms, so when performing the STFT
, the window length should be sufficiently long to capture at least 
the early reflections.

In our previous work XXXX we had assumed that if the target 
sound source is located along the perpendicular bisector to the
line connecting two microphones, the ITD and phase difference
should be zero. However, as may be seen in \eqref{eq:microphone_signals_stft}

\subsection{The effect on the reverberation on the target and the noise source}

In this section, we consider the case where there is a target and 
a noise source inside the room simultaneously.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Section
\section{Normalization of multi-microphone signals}

\subsection{Off-line normalization algorithm}

Since $a_{[u, v]}$ and $b_{[u, v]}$ are constants
as long as the target is stationary,  $H_{01}[e^{j\omega_k}]$
is also a constant if the target is stationary. However,
if we calculate $H_{01}[m, e^{j\omega_k}]$ for each frame 
independently for multi-channel signal compensation, 
then as will be seen in XXXX, it might be affected by other noisy components.

\subsection{On-line normalization algorithm}

We perform an on-line estimation of $H_{01}[e^{j\omega_k}]$ as follows.

Initialization: \\
\begin{align}
  H_u[0, e^{j\omega_k}] = \frac{X_0[0, e^{j\omega_k}]} 
        {X_u[0, e^{j\omega_k}]}  
\end{align}

However, we might need to apply a weighting based on the power.
Let $p[m, e^{\omega_k}]$ represent the power spectrum defined by
$p[m, e^{\omega_k}] = |X[m, e^{\omega_k}]|^2$

If we use the same forgetting factor $\lambda$ for 
$H_{01}[m, e^{j \omega_k}]$ to obtain the smoothed transfer function
$\hat{H}_{01}[m, e^{j \omega_k}]$:
\begin{align}
            \label{eq:h_smoothing}
  \hat{H}_u[m, e^{j\omega_k}] 
      = &  \lambda \hat{H}_u[m - 1, e^{j \omega_k}]  \\ \nonumber 
        &  \qquad + (1 - \lambda) H_{01}[m, e^{j \omega_k}] 
\end{align}

However, the problem with \eqref{eq:h_smoothing} is that
it does not consider the relative intensity at each frame.
More specifically, if the current spectrum at the $m$-th frame is
strong, then s 
of the previous smoothed transfer function $\hat{H}[m, e^{j \omega_k}]$ 
and the current transfer function $H[m, e^{j \omega_k}]$, and 
each of them are weighted by $\lambda$ and $1 - \lambda$, respectively.

The smoothed power $\hat{p}[m, e^{\omega_k}]$ is

We interpret the weighting is, so when the power

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.

\section{Deviation Masking}
After normalizing spectra in the frequency domain, the most straightforward
way is just averaging spectra.
The section in Sec. TODO(chanwcom) based on the assumption that there
is only the target source. If we have both the target and noise source,
the equations becomes as follows:

\begin{subequations}
  \begin{align}
    X_0[m, e^{j\omega_k}]     & = H_0[m, e^{j\omega_k}] X[m, e^{j \omega_k}] + N_0[m, e^{j\omega_k}] \\
                              &  \qquad  \vdots \nonumber \\
    X_u[m, e^{j\omega_k}]     & = H_{u-1}[m, e^{j\omega_k}] X[m, e^{j \omega_k}] + N_u[m, e^{j\omega_k}]\\
                              &  \qquad  \vdots \nonumber \\
      X_{U-1}[m, e^{j\omega_k}] & = H_{U-1}[m, e^{j\omega_k}] X[m, ^{j \omega_k}]+ N_U[m, e^{j\omega_k}]
  \end{align}
  \label{eq:microphone_signals_stft}
\end{subequations}

\section{Experimental Results}
%
TODO(chanwcom) 
% Improve database description and add experimental results.
In this section we describe experimental results obtained
on the DARPA Resource Management 1 (RM1) database and the large scale
English and Icelandic databases used in Google. For the RM1 experiment
we use the Sphinx 3 speech recognition system for acoustic modeling
and decoding, and for the Google speech recognition databases, we
used the state-of-the-art DNN training system, and the GRECO3
decoder. 
TODO(chanwcom)
% Add reference about Google speech recognition system.

\section{Conclusion}
In this paper, we presented an algorithm for microphone compensation.
We have observed that under reverberation, even if the target is placed
at the 
In this paper, we presented an algorithm for phase offset compensation.
Many of the previous algorithms are based on the assumption that if
the target is along the perpendicular bisector to the line connecting
two microphones, the ITD or the phase difference needs to be zero.
However, in the real environments, this assumption usually does not hold.
This discrepancy might occur due to either non-ideal hardware, or
deviation of the target source location.
This POC algorithm can significantly compensate the distortion and
enhance speech recognition accuracy in the real environment.

% use section* for acknowledgement
\section*{Acknowledgements}
This research was supported by Google.

\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2019-09-14 none_feature_mapping_weve/doc/main.tex
update the papers

--- 2019-09-14 nips_2018_neural_front_end/doc/main.tex
@@
 \begin{abstract}
-This paper presents a new robust neural frontend layer referred to as Power
-Normalized Neural Frontend (PNNF) for robust speech recognition. PNNF
-is implemented as a layer in an end-to-end all neural-network speech 
-recognition system. For speech recognition, features such as Mel Filterbank
-Cepstral Coefficient (MFCC) or log-Mel have been used very widely.
-More recently, features motivated by human auditory processing have shown
-improvement under certain conditions. Nevertheless, these auditory
-features are constructed using signal processing blocks with hand-crafted
-parameters for certain conditions. Therefore, the performance is not
-always optimal for various kind of acoustic conditions.
- PNNF frontend layer is loosely motivated by human auditory system.
-This processing uses the concept of the auditory masking and the auditory nonlinearity.
-However, instead of directly using theories and parameters about human auditory masking,
-neural networks make decision about it from the training data.
-Even though the structure of the PNNF layer is very simple, this layer
-significantly boosts the performance of the speech recognition system.
+TODO(chanw.com) Revise the abstract.
+This paper presents a new enhacement algorithm using neural networks 
+refered to as WEVE (Weighted Enhancement Using Variance Estimation).
+The conventional way of feature enhacement is to directly estimate the clean
+feature from the corrupt feature. This mapping from the corrupt feature
+to the corresponding clean feature is learned using a training database
+consisting of a large number of such pairs of corrupt and clean features
+usually with the Mean Squared Error (MSE) loss. The problem of such 
+conventional techniques is that they do consider the reliablity of enhancement.
+We have frequently observed that this enhancement mapping actually degrades
+performance rather than enhacing the classification or recognition
+performance under certain conditions.  In WEVE, we estimate both the enhanced 
+feature and the variance of this estimation. The final output of the enhancement 
+block is a linear combination of the original feature and the 
+enhanced feature. The weighting is given by the Minimum Mean
+Sqaured Error (MMSE) criterion. This process is very simple nontheless
+shows significant improvements in our experiments.
 \end{abstract}
@@
 In the feature enhancement process, we estimate a clean feature 
-$\vec{y}$ given a corrupt feature $\vec{x}$.
+$\vec{y}$ given a corrupt feature $\vec{x}$. Suppose that
+we have
 
@@
 \cite{a_narayanan_interspeech_2015_1}.
-
-\section{Structure of the neural front-end}
-
-\subsection{Neural nonlinearity}
-In this section, we describe our neural nonlinearity algorithm. 
-\begin{align}
-  \vec{q[m, l]} = \vec{x[m, l]} ^ {\vec{\alpha}} 
-\end{align}
-
-\subsection{Neural background removal}
-In this section, we describe our Neural Background Removal (NBR) approach.
-Fig. \label{fig:nbr_diagram} shows the structure of the NBR processing.
-
-$\vec{q}$ is the non-linearity output defined in
-
-\begin{figure}
-    \centering
-    \resizebox{80mm}{!}{%
-         \input{../figures/background_removal.tex}} %
-    \caption {
-      The structure of the Neural Background Removal (NBR) block.
-      \label{fig:nbr_diagam}
-    }
-    %\end{center}
-\end{figure}
-
-\subsection{  }
 

### 2019-09-14 none_feedback_sequence_classifier/doc/main.tex
update the papers

@@
 
-  \Require {$\vec{x}[0:M]$}
-  \Require {$\vec{y}_{0:L}$}
+  \Require {A sequence of feature vectors $\vec{x}[0:M]$}
+  \Require {A sequence of corresponding labels $\vec{y}_{0:L}$}
   \Require {The beam size $N_b$}
   \Require {The neural network parameter $\Theta^{\left(i\right)}$ 
-    for calculating $\vec{z}[u] = f(\vec{x}[0:m+1],\,z[0:u])$}
+    for calculating $\vec{z}[u]
+    = f^{\left(\Theta^{(i)}\right)}(\vec{x}[0:m+1],\,z[0:u])$} 
+    where $m$ is the index of the feature and $u$ is the index of
+    time-synchronous label.
 
@@
   \State {Let $z_0[0:1] := \left( \vec{y}_0 \right)  $}
-  \State {$z_b[0:1], 1 \le b < N_b$ are undefined.}
+  \State {$z_b[0:1],\, 1 \le b < N_b$ are undefined.}
   \State {Let $\mathcal{l}_{0} := \ln \left[ 
-        p \left(\vec{y}_{0} \, \big|  \,
-            {\vec{x}}[0:1]\right)  \right]$}
+        f^{\left(\Theta^{(i)}\right)}(\vec{x}[0:1],\,z_{<sos>})  \right] $}
   \For {$m = 1, . . . , M-1$}
     \For {$b = 0, . . . , N_b-1$}
-      \If {$z_{b}[0:m]$ is defined}
-        \State {Let $\vec{y}_u := z_{b}[m-1] $}
-        \State {Let $z_{b, 0}[0:m+1] := z_{b}[0:m] 
-                \frown \left\{ \vec{y}_u  \right\}  $} 
+      \If {$z_{b}[0:u]$ is defined}
+        \State {Let $y_u := z_{b}[u-1] $}
+        \State {Let $z_{b, 0}[0:u+1] := z_{b}[0:u] \oplus (y_u)   $} 
             \Comment {A horizontal move $P \rightarrow Q$ in 
@@
               $\mathcal{l}_{b,0} := \ln \left[ 
-                  p \left(\vec{y}_{u} \big| 
-                      z_b[0:m], 
-                      \vec{x}[0:m+1], \Theta^{(i)}\right)  \right]
+                  f^{\left(\Theta^{(i)}\right)}_{y_u} 
+                  \left(\vec{x}[0:m+1],\, z_b[0:u] \right)  \right]
                   + \mathcal{l}_b$}
-
         \If {$u+1 \le  L - 1$}
-          \State {Let $z_{b, 1}[0:m+1] 
-          := z_{b}[0:m] \frown \left\{ \vec{y}_{u+1}  \right\}  $} 
+          \State {Let $z_{b, 1}[0:u+1] 
+          := z_{b}[0:u] \oplus (y_{u+1})  $} 
               \Comment {A diagonal move $P \rightarrow R$ in Fig. \ref{fig:path_alignment}}.
@@
               $\mathcal{l}_{b,1} := \ln \left[ 
-                  p \left(\vec{y}_{u+1} \big| 
-                      z_b[0:m], 
-                      \vec{x}[0:m+1], \Theta^{(i)}\right)  \right] 
+                  f^{\left(\Theta^{(i)}\right)}_{y_{u+1}}
+                  \left(\vec{x}[0:m+1],\, z_b[0:u]\right)  \right]
                   + \mathcal{l}_b$}
@@
     \State {Sort a list of items
-    $\left\{\mathcal{l}_{b, i}, z_{b, i}[0:m+1] \right\}, \; 0 \le
-    b < N_b, i = 0, 1$ 
-    with respect to the log likelihood $\mathcal{l}_{b, i}$ 
+    $\left\{\mathcal{l}_{b, k}, z_{b, k}[0:m+1] \right\}, \; 0 \le
+    b < N_b,\, k = 0, 1$ 
+    with respect to the log likelihood $\mathcal{l}_{b, k}$ 
     in the decreasing order. The top $N_b$ of this sorted list is chosen and re-indexed as 

### 2019-10-31 cv_chanwcom/cv_chanwcom.tex
Update the CV
update the cv

@@
 Google Scholar page : \href{https://scholar.google.com/citations?user=pJoZXxYAAAAJ&hl=en}
-  {Link to the page} {\color{red} (h-index :22, citations: 1616)} \\ \\
+  {Link to the page} {\color{red} (h-index :22, citations: 1682)} \\ \\
 Personal homepage: \href{
@@
 % 2019
+\nociteintconf{c_kim_interspeech_2019_00}
 \nociteintconf{d_gowda_interspeech_2019_00}
-\nociteintconf{c_kim_interspeech_2019_00}
 \nociteintconf{a_menon_icassp_2019_00}
@@
 \nociteintconf{c_kim_icassp_2018_01}
-%\nociteintconf{r_nongpiur_icassp_2018_00}
-%\nociteintconf{a_menon_icassp_2018_00}
+
 % 2017
@@
 \nociteintconf{C_Kim_INTERSPEECH_2014_2}
-\nociteintconf{C_Kim_INTERSPEECH_2014_1}
+\nociteintconf{h_park_interspeech_2014_00}
 
@@
 \begin{itemize*}
+  \item Machine Learning Toolkits:
+      Tensorflow, Keras
   \item Programming Language :

### 2019-12-15 asru_2019_training_infra/doc/main.tex
Update the ASRU infra paper

% Template for ICASSP-2019 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}

\usepackage{spconf}
\usepackage{amsmath,graphicx}
\usepackage{amssymb,amsmath,bm}
\usepackage{textcomp}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage[justification=centering]{caption}
%\usepackage[caption = false]{subfig}

% Custom settings
\usepackage{tikz,placeins}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

\graphicspath{{../figures/}}

\newcommand{\specialcell}[2][c]{%
     \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcommand{\chanwcom}{{C. Kim}}
\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}
\renewcommand{\textfraction}{0.01}
\renewcommand{\floatpagefraction}{1.0}
\renewcommand{\dbltopfraction}{1.0}
\renewcommand{\floatpagefraction}{1.0}  % require fuller float pages
\renewcommand{\dblfloatpagefraction}{1.0} % require fuller float pages

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{End-to-end Training of a Large Vocabulary \\ End-to-end Speech Recognition System}
%
% Single address.
% ---------------
\name{Chanwoo Kim, Sungsoo Kim, Kwangyoun Kim, Mehul Kumar,  Jiyeon Kim,
Kyungmin Lee, Changwoo Han, 
\thanks{Thanks to Samsung
Electronics for funding this research. The authors are thankful to  
Executive Vice President Seunghwan Cho, Ravichander Vipperla, Nicholas Lane,
and members of Speech Processing Lab
 at Samsung Research.}
}
\secondlinename{Abhinav Garg, Eunhyang Kim,  Minkyoo Shin, Shatrughan Singh,
Larry Heck, Dhananjaya Gowda}

\address{Samsung Research \\
{\small \tt \{chanw.com, ss216.kim, ky85.kim, mehul3.kumar, jstacey7.kim,
k.m.lee, cw1105.han} \\ \small \tt {abhinav.garg, sc.ehkim.jin, mk0211.shin, shatrughan.s,
larry.h, d.gowda\}@samsung.com }}

%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
\ninept
%
\maketitle
%
\begin{abstract}
In this paper, we present an end-to-end training framework for 
building state-of-the-art end-to-end speech recognition systems.
Our training system utilizes a cluster of Central Processing Units 
  (CPUs) and Graphics Processing Units (GPUs).
The entire data reading, large scale data augmentation,
neural network parameter updates are all performed ``on-the-fly". 
  We use vocal tract length perturbation \cite{c_kim_interspeech_2019_00} 
  and an acoustic simulator \cite{c_kim_interspeech_2017_00}
for data augmentation. The processed features and labels are sent 
to the GPU cluster. The Horovod {\tt allreduce} approach is employed to train
neural network parameters.
We evaluated the effectiveness of our system on the standard 
Librispeech corpus \cite{v_panayotov_icassp_2015_00} and 
  the 10,000-hr anonymized Bixby English dataset. 
Our end-to-end speech
recognition system built using this training infrastructure showed 
  a 2.44 \% WER on {\tt test-clean} of the LibriSpeech test set 
 after applying shallow fusion with a Transformer language model (LM).
 For the proprietary English Bixby open domain test set,
we obtained a WER of 7.92 \% using 
a Bidirectional Full Attention (BFA) end-to-end model after applying shallow fusion with an RNN-LM.
When the monotonic chunckwise attention (MoCha) based approach is employed for 
streaming speech recognition, we obtained a WER of 9.95 \% 
  on the same Bixby open domain test set.
\end{abstract}
%
%\begin{keywords}
  \noindent{\bf Index Terms}: end-to-end speech recognition,
distributed training, example server, data augmentation, acoustic simulation
%\end{keywords}
%
%
\section{Introduction}
In recent years, deep learning techniques have significantly 
improved speech recognition accuracy \cite{Seltzer2013DNNAurora4, 
Yu2013FeatureLearningDNN, V_Vanhoucke_Deep_Learning_NIPS_Workshop_2011,
G_Hinton_IEEE_Signal_Process_Mag_2012,
T_Sainath_IEEETran_2017_1}.
This improvement has come about from the shift from Gaussian Mixture Model
(GMM) to the Feed-Forward Deep Neural Networks (FF-DNNs), FF-DNNs
to Recurrent Neural Network (RNN) and in particular the Long Short-Term Memory
(LSTM) networks \cite{S_Hochreiter_neural_computation_1997_00}. 
Thanks to these advances, voice assistant devices such as Google Home
\cite{c_kim_interspeech_2017_00, B_Li_INTERSPEECH_2017_1}
, Amazon Alexa or Samsung Bixby \cite{samsung_bixby} are being used at 
many homes and on personal devices.

Recently there has been increasing interest in switching
from the conventional Weighted Finite State Transducer (WFST)
based decoder using an Acoustic Model (AM) and a Language Model (LM)
to a complete end-to-end all-neural speech recognition systems 
\cite{w_chan_icassp_2016_00, r_prabhavalkar_interspeech_2017_00, 
j_chorowski_nips_2015_00}. 
These complete end-to-end systems have started surpassing the performance of
the conventional WFST-based decoders with a very large training 
database \cite{c_chiu_icassp_2018_00}, a better choice of target unit 
such as Byte Pair Encoded (BPE) subword units, and an improved 
training methodology such as Minimum
Word Error Rate (MWER) training \cite{r_Prabhavalkar_icassp_2018_00}.

Another important aspect in building high-performance 
speech recognition systems is the amount
and the coverage of the training data.
To build high performance speech recognition systems for
conversational speech, we need to use
a large amount of speech data covering various domains
\cite{a_narayanan_slt_2018_00}. In \cite{h_soltau_interspeech_2017_00}, 
it has been shown that we need a very large training set ($\sim$125,000 hours of 
semi-supervised speech data) to achieve
high speech recognition accuracy for difficult tasks like 
video captioning. To train neural networks using such large 
amounts of speech data, we usually need 
multiple Central Processing Units (CPUs) or Graphics
Processing Units (GPUs)
\cite{E_Variani_INTERSPEECH_2017_01, p_goyal_arxiv_2018_00}.

With widespread adoption of voice assistant speakers, far-field
speech recognition has become very important.
In far-field speech recognition, the impacts of reverberation and noise 
are much larger than those in near-field cases. 
Traditional approaches to far-field
speech recognition include noise robust feature extraction algorithms
\cite{C_Kim_IEEETran_2016_1, U_H_Yapanel_SpeechComm_2008, c_kim_interspeech_2014_00},
or multi-microphone approaches
\cite{T_Nekatani_ICASSP_2017_1, T_Higuchi_ICASSP_2016_1,
H_Erdogan_INTERSPEECH_2016_1,
C_Kim_INTERSPEECH_2010_1, C_Kim_ICASSP_2012_2, C_Kim_INTERSPEECH_2015_1, c_kim_icassp_2018_01}.
More recently, approaches using data augmentation
has been gaining popularity for far-field speech recognition
\cite{R_Lippmann_icassp_1987_1,
c_kim_icassp_2018_00, w_hartmann_interspeech_2016_00, 
s_park_interspeech_2019_00, C_Kim_ASRU_2009_2}. 
An ``acoustic simulator"  
\cite{c_kim_interspeech_2017_00, c_kim_interspeech_2018_00}
is used to generate simulated speech utterances for
millions of different room dimensions, a wide distribution
of reverberation time and signal-to-noise ratio. In a similar 
spirit, Vocal Tract Length Perturbation (VTLP) has been proposed 
\cite{n_jaitly_icml_workshop_2013_00} to tackle the speaker variability issue.
As shown in our recent paper \cite{c_kim_interspeech_2019_00}, 
VTLP is especially useful when
the speaker variability in the training database is not sufficient. 
For these kinds of data augmentation, processing on CPUs is more
desirable than processing on GPUs. Due to this, we have proposed
an end-to-end training approach using Example Servers (ES)
 and workers. Example servers are typically run on the CPU
cluster performing data reading, data augmentation, and feature extraction
\cite{E_Variani_INTERSPEECH_2017_01, c_kim_interspeech_2018_00}.
%
%
%
\begin{figure*}[!tbp]
  \begin{center}
    \resizebox{\textwidth}{!}{\input{../figures/end_to_end_training_system.tex}}
      \caption { The Samsung Research end-to-end training framework for building an end-to-end
	speech recognition system with multi CPU-GPU clusters and on-the-fly data
	processing and augmentation pipeline.
     }   
     \label{fig:end_to_end_training_system}
  \end{center}
\vspace{-5mm}
\end{figure*}
%
%
%
In this paper, we describe the structure of our end-to-end training system
to train an end-to-end speech recognition system. This training system
has several advantages over previous systems described in
\cite{c_kim_interspeech_2018_00}. First, instead of using the {\tt QueueRunner},
we use a more efficient data queue using {\tt tf.data} in Tensorflow 
\cite{m_abadi_usenix_2016}.  Second, instead
of pre-calculating information about room configurations and 
room impulse responses in the acoustic simulator, these are
calculated {\it on-the-fly}. Thus, the entire training system runs 
{\it on-the-fly}. Additionally, instead of using the parameter server-worker
structure, we use an {\tt allreduce} approach implemented in the Horovod
\cite{a_sergeev_arxiv_2018_00} distributed training framework, which
has been shown to be more efficient. The system described in 
\cite{E_Variani_INTERSPEECH_2017_01}, is designed
to train the acoustic model part of the speech recognition system where
as our training system trains the complete end-to-end speech recognition system.

The rest of the paper is organized as follows: We describe the entire
training system structure in detail in Sec. \ref{sec:training_cpu_gpu}.
The structure of the end-to-end speech recognition system 
is described in Sec. \ref{sec:end_to_end_speech_recognition}. 
Experimental results that demonstrates the effectiveness of our speech
recognition system is presented in Sec. \ref{sec:experimental_results}. 
We conclude in Sec.  \ref{sec:conclusions}.
%
\section{Overall structure of the end-to-end speech recognition}
\label{sec:training_cpu_gpu}
\vspace{-1mm}

In this section, we describe the overall structure of our 
end-to-end training system.  Fig. \ref{fig:end_to_end_training_system}
shows how the entire system is structured. Our system consists
of a cluster of CPUs and a cluster of GPUs. Each GPU node of 
the GPU cluster has eight Nvidia\texttrademark P-40, P-100 or V-100 GPUs and two 
Intel E5-2690 v4 CPUs. Each of these CPUs has 14 cores.
The large box on the left hand side of Fig. \ref{fig:end_to_end_training_system}
denoted ``GPU cluster'' shows a typical GPU node with $N$ GPUs.
The large box on the right shows a ``CPU cluster'' of $M$ CPUs,
each running an independent data pipeline.

\vspace{-1mm}
\subsection{Training job launch}
The main process of the training system runs on one of CPU cores 
of the GPU cluster. This CPU portion of the GPU node is represented
as a box in the right hand side of the GPU node box.
When the training job starts, this main training process launches
multiple example server jobs on the CPU cluster using the 
{\tt IBM Platform LSF} \cite{ibm_spectrum_lsf_2010}. In Fig. 
\ref{fig:end_to_end_training_system}, this launching process is represented
by a dashed arrow from the CPU portion of the GPU node to the 
CPU cluster.

\subsection{Data reading using an example queue}
In the CPU cluster, each CPU runs one example server
which reads speech utterance and transcript data from sharded 
{\tt TFRecords} defined in Tensorflow \cite{m_abadi_usenix_2016}.
The TFRecord format is a simple format in Tensorflow for storing 
a sequence of binary records. To support efficient reading using 
multiple CPUs, we use sharded {\tt TFRecords}.

To read large-scale data efficiently in parallel, we use an example queue
shown in the left side of Fig. \ref{fig:end_to_end_training_system}.  
The original speech waveform data, transcripts, and meta data are stored
in sharded {\tt TFRecords}. The data pipeline is implemented using
{\tt tf.data} in Tensorflow \cite{m_abadi_usenix_2016}, 
and contains the data augmentation and feature extraction blocks.
These {\tt tf.data} APIs are efficient in building complex pipelines
by applying a series of elementary operations. We perform data interleaving
and parallel reading using {\tt tf.contrib.data.parallel\_interleave}, 
shuffling using {\tt tf.data.Datatset.shuffle}, and padding using 
{\tt tf.data.Dataset.padded\_batch}.

\subsection{Data augmentation and feature extraction}
\label{sec:feature_extraction}
To improve robustness against speaker variability, we apply an
on-the-fly VTLP algorithm on the input waveform
\cite{c_kim_interspeech_2019_00}. The warping
factor is generated randomly for each input utterance. Unlike
conventional VTLP approaches in \cite{n_jaitly_icml_workshop_2013_00,   
x_cui_taslp_2015_00}, we resynthesize the processed
speech. The purpose of doing this is to apply VTLP before applying
the acoustic simulator to the input waveform.  This is quite 
natural that data augmentation to model speaker variability 
should be performed before the data augmentation to model
acoustic variability.
One more advantage is that this
resynthesis approach enables us to use a window length 
optimal for VTLP different from that used in feature processing.
We apply a blinear transformation \cite{p_zhan_cmu_tech_report_1997_00} 
to perform frequency warping
to model speaker variability due to the difference in the vocal tract length.
In the bilinear transformation, the relation between the input
and output discrete-time frequencies is given by: 
\begin{align}
  \omega_k'  = \omega_k + 2 \tan^{-1} \left(
                    \frac{ \left(1 - \alpha \right) \sin(\omega_k)} 
              {1 - (1 - \alpha) \cos(\omega_k) } \right)
                            \label{eq:bilinear_transformation}.
\end{align}
where $\omega_k = \frac{2 \pi k}{K}$ is the input discrete-time frequency
, $\omega_k' = \frac{2 \pi k'}{K}$ is the output discrete-time frequency, and
  $K$ is the DFT size. 
More details about our VTLP algorithm is described 
in detail in \cite{c_kim_interspeech_2019_00}.
The acoustic simulator in Fig.~\ref{fig:end_to_end_training_system}
is similar to what we described in 
\cite{c_kim_interspeech_2017_00, c_kim_interspeech_2018_00}.
One difference compared to our previous one in 
\cite{c_kim_interspeech_2017_00} is that we do not pre-calculate
room impulse responses, but instead they are calculated on-the-fly.
For feature processing we use {\tt tf.data.Dataset.map} API. 
Instead of using the more conventional log-mel or 
MFCC features, we use the power mel filterbank energies,
since it shows slightly better performance \cite{c_kim_interspeech_2019_00,
c_kim_asru_2019_00}. Motivated by our previous research of
using power-law nonlinearity with a power coefficient between 
$\frac{1}{15}$ \cite{C_Kim_ICASSP_2010_1, C_Kim_ICASSP_2012_1, C_Kim_PhDThesis_2010} and 
$\frac{1}{10}$ \cite{C_Kim_INTERSPEECH_2009_2}, we apply the 
power-law nonlinearity of $(\cdot)^{\frac{1}{15}}$ to the mel filterbank 
coefficients. We refer to this feature as {\it power-mel filterbank
coefficients}.

\begin{figure}[tbp]
  \begin{center}
    \resizebox{80mm}{!}{\input{../figures/e2e_asr_block_diagram}}
      \caption {  The structure of the entire end-to-end
      speech recognition system. 
      %The LSTMs
      %in the encoder layers may be either bidirectional-LSTMs or
      %unidirectional-LSTMs. The attention may be either the full
      %attention or the MOnotonic CHunkwise Attention (MoCha)
      %\cite{c_chiu_iclr_2018_00}.
     }
     \label{fig:entire_diagram}
  \end{center}
\vspace{-5mm}
\end{figure}

\subsection{Parameter calculation and update}
\label{sec:parameter_update}
The features and the target labels are sent to the GPU cluster
using the ZeroMQ \cite{zero_mq} asynchronous messaging queue.
Each {\it example server } sends these data asynchronously to the CPU portion
of the GPU node as shown in Fig \ref{fig:end_to_end_training_system}.
Using these data, neural network parameters are calculated and updated 
using an Adam optimizer and the
Horovod \cite{a_sergeev_arxiv_2018_00} {\tt allreduce} approach.

Fig. \ref{fig:plot_example_server_performance} shows how many CPUs
in the {\it  example server } per GPU are required to provide sufficient 
data to the GPU cluster. In this experiment, we used a 10,000-hr
anonymized {\texttt Bixby} English training set. 
We trained a streaming end-to-end model using the Monotonic CHunkwise
Attention (MoCha) algorithm \cite{c_chiu_iclr_2018_00}. The details
about our MoCha implemention are discussed in \cite{k_kim_asru_2019_00}.
In the {\it  example server}, we ran the
VTLP data augmentation \cite{c_kim_interspeech_2019_00}, 
{\it acoustic simulator} \cite{c_kim_interspeech_2017_00} and 
feature extraction modules shown in Fig. \ref{fig:entire_diagram}.
In this experiment, we used four Nvidia\texttrademark V-100 GPUs with 32-GB
memory in the 
GPU cluster. Fig. \ref{fig:plot_example_server_time} shows how much
time is required to finish one epoch of training. When data augmentation
is not applied, 65.6-hours were required to finish one epoch of training.
Fig. \ref{fig:plot_example_server_time} shows us that three CPUs per GPU 
(total 12 CPUs for 4 GPUs) are required to obtain a comparable throughput. 
If we use four or five CPUs per GPU, as shown in Fig.
\ref{fig:plot_example_server_time}, the training is even slightly 
faster than the case without the {\it  example-server}-based data-augmentation.
We think that this happened because of more efficient data processing
with the {\it example server}. When we do not perform data augmentation
using {\it example servers}, feature extraction and data reading are performed
on a limited numbers of CPUs inside the GPU cluster, which might add some
latency during the training. 
Thus, it is possible that the training with data augmentation
using {\it example servers} may be even slightly faster than the 
baseline case without data-augmentation using {\it example servers}.

Fig. \ref{fig:plot_gpu_time_percentage} shows the portion of the time
used for{\tt Tensorflow } computation. This portion of time is defined
by:
\begin{align}
  t_{\text{session}} =  \frac{\text{Time Spent in {\tt Tensorflow}
  Session}}{\text{Elapsed Time}}.
  \label{eq:session_time_portion}
\end{align}
If GPUs in the GPU cluster are not given sufficient amount 
of data, these GPUs will remain idle. Thus, $t_{\text{session}}$ in
\eqref{eq:session_time_portion} is a good indicator to 
see whether the {\it example server } 
provides sufficient 
amount of processed features. From this figure, we may conclude that
three $\sim$ four CPUs per GPU (total 12 $\sim$ 16 CPUs for 4 GPUs) 
are required to keep GPUs busy enough. In our experiments using
the 10,000-hr Bixby training set in Sec. \ref{sec:experimental_results},
we used 8 GPUs and 40 CPUs (5 CPUs per GPU) during the training.

\begin{figure}
  \captionsetup[subfigure]{justification=centering}
    \centering
    \begin{subfigure}[5]{0.5\textwidth}
      {\includegraphics[width=80mm]{../figures/plot_example_server_time}}
      \caption{
          \label{fig:plot_example_server_time}
      }
    \end{subfigure}

    \begin{subfigure}[b]{0.5\textwidth} 
      {\includegraphics[width=80mm]{../figures/plot_gpu_time_percentage}}
    \caption{
      \label{fig:plot_gpu_time_percentage}
    }
    \end{subfigure}
  \caption{\label{fig:plot_example_server_performance}
  The efficiency of the {\it example server} with respect to
  the number of CPUs per GPU: (a) The required time to 
  process a single epoch during the training phase and (b) 
  the percentage of {\tt Tensorflow } computation time defined by 
  \eqref{eq:session_time_portion}. 
  The blue horizontal dotted lines in each figure represent the case
  when data augmentation with example servers is not employed.
  }
\end{figure}

\section{Structure of the end-to-end speech recognition system}
\label{sec:end_to_end_speech_recognition}

We have adopted the RETURNN speech recognition system \cite{p_doetsch_icassp_2017_00,
a_zeyer_interspeech_2018_00} for training our end-to-end system with various modifications.
Some of the important modifications are: replacing the input data pipeline with our 
proposed on-the-fly example server based pipeline with support for VTLP
and acoustic simulation,
implementing the Monotonic Chunkwise Attention (MoChA) \cite{c_chiu_iclr_2018_00}
for online streaming end-to-end speech recognition, minimum Word Error Rate (mWER) 
training, support for handling Korean language or script, our own scoring and Inverse Text 
Normalization (ITN) modules, support for power mel filterbank features
\cite{c_kim_interspeech_2019_00, c_kim_asru_2019_00}, etc. We have tried
various types of training strategies for better performance
\cite{d_gowda_interspeech_2019_00, a_garg_asru_2019_00}.
Our MoCha implementation and optimization are described in very detail in our
another paper \cite{k_kim_asru_2019_00}.

The structure of our entire end-to-end speech recognition system
 is shown in Fig.~\ref{fig:entire_diagram}.
 $\vec{x}[m]$ and $\vec{y}_l$ are the input power mel 
filterbank energy vector and the output label,
respectively. $m$ is the input frame index and $l$ is the decoder output
step index. $\vec{c}_l$ is the context vector calculated 
as a weighted sum of the encoder hidden state vectors denoted as $\vec{h}^{enc}[m]$.
The attention weights are computed as a softmax of energies computed as 
a function of the encoder hidden state $\vec{h}^{enc}[m]$, the decoder hidden state
$\vec{h}^{dec}_l$, and the attention weight
feedback $\vec{\beta}_l[m]$  \cite{a_zeyer_interspeech_2018_00}.

In \cite{a_zeyer_interspeech_2018_00}, the peak value of the speech 
waveform is normalized to be one. However, since finding the peak sample value 
is not possible for online feature extraction, we do not perform this
normalization. We modified the input pipeline
so that the online feature generation can be performed. We disabled the 
clipping of feature range between -3 and 3, which is the default 
setting for the Librispeech experiment using MFCC 
features in \cite{a_zeyer_interspeech_2018_00}. 
We conducted experiments using both the 
uni-directional and bi-directional Long Short-Term Memories (LSTMs)
\cite{S_Hochreiter_neural_computation_1997_00} in the encoder.
However, only the uni-directional LSTMs are used in the decoder.
For online speech recognition experiments, we used the
MoChA models \cite{c_chiu_iclr_2018_00} with a chunk size of 2.
In MoCha experiments, we used only the uni-directional LSTMs 
both in the encoder and the decoder to enable streaming recognition.
 For better stability in LSTM training, we use the gradient clipping by  
global norm \cite{r_pascanu_icml_2013}, which is implemented as  
{\tt tf.clip\_by\_global\_norm } API in Tensorflow  \cite{m_abadi_usenix_2016}.
We use six layers of encoders and one layer of decoder followed by a softmax
layer.

In performing shallow-fusion with an external LM, our approach is slightly 
different from the previously known approaches 
\cite{c_gulcehre_corr_2015_00, s_toshniwal_slt_2018_00} to obtain better 
performance.
we used the following equation:
\begin{align}
  y_{0:L}^{*} = & \argmax_{y_{0:L}} \sum_{l=0}^{L-1} \Big[ \log P \left(y_l
  |\vec{x}[0:M], y_{0:l} \right)
  \nonumber \\
                           & \qquad - \lambda_p \log P(y_l) 
                           + \lambda_{\text{lm}} \log P \left(y_l   |y_{0:l} \right)  \Big],
                           \label{eq:lm_fusion}
\end{align}
where we have an additional term $\lambda_p \log P(y_l) $ for subtracting 
the {\it prior bias} that the model has learned from the training corpus. 
In \eqref{eq:lm_fusion} $L$ is the 
length of the output label hypothesis. $\lambda_p$ and $\lambda_{\text{lm}}$ are 
weights for the prior probability and the LM prediction probability, 
respectively.
In \eqref{eq:lm_fusion}, we represented sequences following the Python slice
notation. For example, $\vec{x}[0:M]$ denotes the sequence of the input acoustic
features of length $M$, and $y_{0:L}$ is a sequence of output labels  of length $L$.
%
%
%
%
\section{Experimental Results}
\label{sec:experimental_results}
%
%
%
In this section, we present a summary of experimental results obtained
with our end-to-end speech recognition systems built using the proposed
Samsung Research end-to-end training framework.
%
For near-field speech recognition experiments, we use the open source 
Librispeech database \cite{v_panayotov_icassp_2015_00}, as well as our in-house
{\it Bixby} \cite{samsung_bixby} usage training and test sets for English. 
The LibriSpeech dataset consists of around 960 hours of training data
consisting of 281,241 utterances. The evaluation set consists of the 
official 5.4 hours {\tt test-clean} and 5.1 hours {\tt test-other} data.
The Bixby training set consists of approximately 10,000 hours of
anonymized Bixby usage data. The evaluation set consists of around 1,000 
open domain utterances. As mentioned in Sec. 
%
\ref{sec:parameter_update}, we used 8 GPUs in a GPU cluster and 
40 CPUs in an example server when training the model using the 
Bixby training set.
\begin{table}[!tbhp]
  \renewcommand{\arraystretch}{1.3}
  \centering
        \caption{\label{tbl:power_law_result}
        Word Error Rates (WERs) obtained using MFCC implemented in
        \cite{b_mcfee_proc_scipy_2015_00} and power mel filterbank coefficients
        \\ on the Librispeech corpus \cite{v_panayotov_icassp_2015_00}. For
        each WER number, \\the same experiment was conducted twice and averaged.
        }
        %\vspace{-3mm}
        \begin{tabular}{| c | c  || c | c | c | c |}
          \hline
          \multicolumn{2}{| l ||}{Cell Size}
                                 & \specialcell{MFCC}
                                 & \specialcell{Power Mel \\ 
                                 Filterbank \\
                                 Coefficients} \\
          \hline
          \multirow{3}{*}{1536 cell}    
                  & test-clean  &   4.06  \% &  \textcolor{blue}{\bf 3.94 } \%   \\
                  & test-other  &  13.97  \% &  \textcolor{blue}{\bf 13.56} \%   \\
                  & average     &   9.02  \% &  \textcolor{blue}{\bf 8.75 } \%   \\
          \hline
       \end{tabular}
       \vspace{-2mm}
\end{table}
%
%
\begin{table}[!tbhp]
  \renewcommand{\arraystretch}{1.3}
  \centering
        \caption{\label{tbl:vtlp_result}
        Word Error Rates (WERs) obtained with VTLP processing
        with different warping factor $\alpha$ distribution, 
        and with and without an RNN LM. The warping factor $\alpha$
			  is the constant controlling warping in \eqref{eq:bilinear_transformation}.
        }
        %\vspace{-3mm}
        \begin{tabular}{| c | c  || c | c | c | c |}
          \hline
          \multicolumn{2}{| l ||}{Warping Factor}
                                 & \specialcell{ 0.7 $\sim$ 1.3 }
                                 & \specialcell{ 0.8 $\sim$ 1.2 }  
                                 & \specialcell{ 0.9 $\sim$ 1.1 }   \\
          \hline \hline
          \multirow{3}{*}{\specialcell{Without \\ RNN-LM}}
                  & test-clean  &   3.82  \% &  3.66  \%   &  3.86  \%  \\  
                  & test-other  &  12.50  \% & 12.39  \%   & 12.35  \%  \\  
                  & average     &   8.16  \% &  8.03  \%   &  8.11  \%  \\  
          \hline
          \multirow{3}{*}{\specialcell{With \\ RNN-LM}}
                  & test-clean  &   2.93  \% &  \textcolor{blue}{\bf 2.85}  \%   &  2.96  \%  \\  
                  & test-other  &  10.40  \% & 10.25  \% & \textcolor{blue}{\bf10.13}  \%  \\  
                  & average     &   6.67  \% &  \textcolor{blue} {\bf 6.55}  \%
                  &  \textcolor{blue}{\bf 6.55}  \%  \\  
          \hline
       \end{tabular}
       \vspace{-2mm}
\end{table}
%
%
%

In Table \ref{tbl:power_law_result}, we compare the performance between
the baseline MFCC and the power-law of $(\cdot)^{\frac{1}{15}}$ features 
for a Bidirectional Full Attention (BFA) end-to-end model with 
an LSTM cell size of 1536 on the LibriSpeech database \cite{v_panayotov_icassp_2015_00}. 
Especially for {\tt test-other}, which
is a more difficult task, the power mel filterbank coefficients 
shows better performance than the baseline MFCC. Thus, we use 
the power-mel filterbank coefficients as the default feature in 
our end-to-end system. All the following results in this section
were obtained using the power-mel filterbank coefficients.

In Table \ref{tbl:vtlp_result}, we show Word Error Rates (WERs) on the same
LibriSpeech corpus for a BFA model using 
different window sizes and warping coefficient distributions, with and without
using an external Recurrent Neural Network (RNN) Language Model (LM) 
\cite{a_zeyer_interspeech_2018_00} built using the standard LibriSpeech LM corpus.
The best performance was achieved when the window length is 50 {\it ms} and 
the warping coefficients are uniformly distributed between 0.8 and 1.2.
We obtained 3.66 \% WER on the {\tt test-clean} database and 12.39 \%
WER on the {\tt test-other} database without using an LM. 
Using this shallow-fusion technique 
  with an RNN-LM, we achieved WERs of 2.85 \% and 10.25 \% 
  on the Librispeech {\tt test-clean} and {\tt test-other} databases, respectively.
%
%
%

\begin{table}[!htbp]
  \renewcommand{\arraystretch}{1.3}
  \centering
        \caption{\label{tbl:vtlp_result_with_trans_lm}
        Word Error Rates (WERs) obtained with VTLP processing
        using shallow-fusion with a Transformer LM with different beam sizes.
        The window length is 50 ms, and the warping factor distribution is
        $0.8 \sim 1.2$.
        }
        %\vspace{-2mm}
        \begin{tabular}{| c || c | c | c | c |}
        %\begin{tabular}{| c || c | c | }
          \hline
                                 {Beam Size}
                                 & \specialcell{ 12 }
                                 & \specialcell{ 24 }   
                                 & \specialcell{ 36 }   
                                 & \specialcell{ 48 }   \\  
          \hline \hline
              \specialcell{ $\lambda_p$ \\ $ \lambda_{\text{lm}}$ } &   
              \specialcell{ 0.005\\ 0.45}  &
              \specialcell{ 0.004\\ 0.46}  &   
              \specialcell{ 0.003\\ 0.48}  &   
              \specialcell{ 0.002\\ 0.48} \\
              \hline

              test-clean  &   2.49  \% & 2.45 \%  &  \textcolor{blue}{\bf 2.44 \%} & 2.45 \%  \\  
              test-other  &   8.76  \% & 8.40 \%  &   8.29 \%
              & \textcolor{blue}{\bf 8.22
              \%} \\
              average     &   5.63  \% & 5.43  \% &   5.37 \%
              & \textcolor{blue}{\bf 5.34 \%} \\
          %    test-clean  &   2.55  \% &  2.51 \%   &   2.51 \% & 2.52 \%  \\  
          %    test-other  &   8.59  \% &  8.42 \%   &   8.33 \% & 8.33 \%  \\  
          %    average     &   5.57  \% &  5.47  \%  &   5.42 \% & 5.42 \%  \\  
          \hline
       \end{tabular}
       \vspace{-2mm}
\end{table}
%
%
%
\begin{figure}
  \captionsetup[subfigure]{justification=centering}
    \centering
    \begin{subfigure}[5]{0.5\textwidth}
      {\includegraphics[width=75mm]{../figures/plot_farfield_wer_tv}}
      \caption{
          \label{fig:tv_noise}
      }
    \end{subfigure}

    \begin{subfigure}[b]{0.5\textwidth} 
      {\includegraphics[width=75mm]{../figures/plot_farfield_wer_music}}

    \caption{
          \label{fig:music_noise}
    }
    \end{subfigure}

    \begin{subfigure}[b]{0.5\textwidth} 
      {\includegraphics[width=75mm]{../figures/plot_farfield_wer_babble}}
    \caption{
          \label{fig:babble_noise}
    }
    \end{subfigure}

  %\vspace{-6mm}
 \caption{\label{fig:plot_farfield_wer}
  Speech recognition accuracy at different Signal-to-Noise Ratios (SNRs)
  under three different noisy conditions: direct TV noise (a)
  , music noise (b), and babble noise (c). NBF, VTLP, and AS
  stand for Neural Beam Former (NBF) \cite{j_heymann_icassp_2016_00}, 
  Vocal Tract Length Perturbation (VTLP) \cite{c_kim_interspeech_2019_00} , and
  Acoustics Simulator (AS) \cite{c_kim_interspeech_2017_00,
  c_kim_interspeech_2018_00},
  respectively.
  \vspace{-2mm}
 }
\end{figure}
%
%
%
Table \ref{tbl:vtlp_result_with_trans_lm} shows word error rates on the
  LibriSpeech testsets obtained 
  by applying shallow-fusion with a Transformer LM 
  \cite{a_vaswani_nips_2017_00, c_luscher_arxiv_2019_00} using
  \eqref{eq:lm_fusion}. As shown in this table, we conducted experiments with
  different beam sizes, $\lambda_p$ and $\lambda_{\text{lm}}$ parameters in
  \eqref{eq:lm_fusion}. The best result we obtained using a Transformer LM
  in Table \ref{tbl:vtlp_result_with_trans_lm} is significantly better than the result we obtained with a LSTM LM in 
  Table \ref{tbl:vtlp_result}.

%
%
%
In Table \ref{tbl:near_field_result}, we summarize our WER results for 
both the LibriSpeech and Bixby end-to-end ASR models.
In the case of the Bixby model, we optionally used an external RNN-LM 
trained using around 65GB of 
the Bixby LM corpus with an architecture exactly similar to the
LibriSpeech LM model used in \cite{a_zeyer_interspeech_2018_00}.
The cell sizes of the LibriSpeech model and the Bixby model 
in Table \ref{tbl:near_field_result} are 1536 and 1024 respectively.
For comparison, the best WFST based conventional LSTM-HMM based ASR system
gives a WER of 8.85\% on the Bixby same open domain test set.
We can see that our current Bixby end-to-end BFA model is $\sim$10\% better, while
our MoChA streaming model is $\sim$10\% poorer compared to
the conventional WFST based DNN-HMM system.
%
\begin{table}[!tbhp]
  \renewcommand{\arraystretch}{1.3}
  \centering
        \caption{\label{tbl:near_field_result}
        Summary of Word Error Rates (WERs) obtained for different
        LibriSpeech and Bixby near-field end-to-end ASR models 
        with and without an RNN LM.
        }
        %\vspace{-3mm}
        \begin{tabular}{| c | c  || c | c |}
          \hline
          \multicolumn{2}{| l ||}{Models}
                                 & BFA
                                 & MoChA \\
          \hline \hline
          \multirow{3}{*}{\specialcell{LibriSpeech \\ (1536-cell) \\ test-clean}}
                  & w/o LM  &   3.66  \% &  6.78  \%  \\  
                  & RNN-LM  &   2.85  \% &  5.54  \%  \\  
                  & Transformer LM  &   2.44  \% &   -   \\  
          \hline
          \multirow{2}{*}{\specialcell{Bixby \\ (1024-cell) }}
                  & w/o LM  &   8.25  \% &  10.77  \% \\  
                  & RNN-LM  &   7.92  \% &   9.95  \% \\  
          \hline
       \end{tabular}
       \vspace{-2mm}
\end{table}
%
%
The performance of our far-field end-to-end ASR model trained using the proposed
structure in Fig. \ref{fig:entire_diagram} is shown 
in Fig. \ref{fig:plot_farfield_wer}. In this experiment, we used
the same anonymized 10,000 hours of the English Bixby training set.
The performance of the far-field
models were evaluated on the English Bixby command test set.
The Bixby command test set
include utterancesare sampled from the anonymized Bixby usage log. 
Examples in this
test set include ``Set an alarm for tomorrow at 6 a.m", 
``Tell me remaining time of my timers", ``Play the most latest added 
song", and so on.

Far-field recording using this Bixby command set was performed
by playing back utterances using a loud speaker at 5-meter distance 
in a real room.
The reverberation time in this
recording room was measured to be $T_{60}=430 ms$. We used two microphones
on a prototype {\it Galaxy Home Mini} to record this far-field speech.
The distance between two microphones is 6.8 cm. We simulated 
far-field additive noise by playing back three different types of noise using loud speakers.
In Fig. \ref{fig:tv_noise}, we used a single loud speaker located at 
1-meter distance from the microphone to simulate direct noise from 
a television. In Figs. \ref{fig:music_noise} and \ref{fig:babble_noise},
we used four loud speakers oriented to different directions to simulate
diffuse noise. On the prototype {\it Galaxy home Mini} device, 
the two-microphone signals are enhanced using a beamformer 
based on the Neural Network supported
Generalized Eigenvalue (NN-GEV) algorithm \cite{j_heymann_icassp_2016_00}. 
In Fig.  \ref{fig:plot_farfield_wer}, we evaluated speech recognition accuracy
using three different systems. {\tt NBP+VTLP+AS} denotes a system
which uses the VTLP system and the acoustic simulator described in this paper for 
data augmentation in model training, and additionally uses this NN-GEV-based 
beamformer for signal enhancement. {\it NBF} in this future stands for
this Neural Beam Former (NBF).  {\tt VTLP+AS} denotes a system employing
the VTLP system and the acoustic simulator without using this beamformer.
{\tt baseline} denotes a system which was trained using utterances
recorded in close-talking environments without any further processing. 
As can be seen in these figures,
data augmentation technique significantly enhances speech recognition
accuracy under the far-field environments. We also observe that
the data augmentation algorithm described in Sec. \ref{sec:training_cpu_gpu}
does not harm the clean performance, thus we may use the same 
data augmentation both for the close-talking and the far-field environments.
In case of the direct
TV noise in Fig. \ref{fig:tv_noise} and babble noise in Fig.
\ref{fig:babble_noise}, we observe that further improvement is 
achieved by employing a NN-GEV-based beamformer.
%
%
%
%%
%
%
\section{Conclusions}
\label{sec:conclusions}
We presented a new end-to-end training framework and
 strategies for training 
state-of-the-art end-to-end speech recognition systems.
Our training system utilizes a cluster of Central Processing Units 
  (CPUs) and Graphics Processing Units (GPUs).
The entire data reading, large scale data augmentation,
neural network parameter updates are performed on-the-fly
using example servers and sharded {\tt TFRecords} and {\tt tf.data}. 
  We use vocal tract length perturbation and an acoustic simulator 
for data augmentation. Horovod {\tt allreduce} approach is employed 
to train the neural network parameters using Adam optimizer.
We evaluated the effectiveness of our system on the standard 
Librispeech corpus \cite{v_panayotov_icassp_2015_00} and 
  10,000-hr anonymized Bixby English training 
 and test sets both in near-field as well as
far-field scenarios.  
%\clearpage
%\newpage
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}

\end{document}

### 2019-12-15 asru_2019_training_infra/figures/plot_example_server_time.py

@@ -1,0 +1,38 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from util.plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+plt.rc('text', usetex=True)
+
+dist = np.array([1.0, 2.0, 3.0, 4.0, 5.0])
+
+data = []
+
+# The data at 41.000 is problematic.
+data.append((dist, [163.7, 82.4, 62.0, 58.8, 53.7]))
+plt.plot([0.0, 5.2], [65.6, 65.6], '--',  linewidth=2)
+
+data_list_plot.PlotDiscreteData(data)
+fig = plt.gcf()
+plt.axis([0.8, 5.2, 0.0, 180.0])
+
+fig = plt.gcf()
+fig.set_size_inches(5,3)
+
+
+ax = plt.gca()
+ax.get_legend().remove()
+
+plt.ylabel(r'\textit{Elapsed Time per Epoch (in Hr)}')
+plt.xlabel(r"\textit{Number of CPUs in the Example Server per GPU}")
+plt.tight_layout()
+
+file_name = "plot_example_server_time.eps"
+fig.savefig(file_name)
+
+#subprocess.check_call(shlex.split("evince {0}".format(file_name)))
+

### 2019-12-15 asru_2019_training_infra/figures/plot_farfield_noisy_wer.py

@@ -1,0 +1,86 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from util.plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+plt.rc('text', usetex=True)
+
+data = []
+x_snr = np.array([0.0, 5.0, 10.0, 15.0, 20.0])
+
+# The data at 41.000 is problematic.
+data.append((x_snr, 100 - np.array([3.07, 1.54, 0.92, 1.84, 1.53]),
+    "NBF + VTLP + AS"))
+data.append((x_snr, 100 - np.array([22.46, 4.29, 1.53, 1.53, 1.53]),
+    "VTLP + AS"))
+data.append((x_snr, 100 - np.array([84.91, 31.37, 5.21, 2.76, 1.84]),
+    "baseline"))
+
+data_list_plot.PlotSnrdbAccData(data)
+fig = plt.gcf()
+
+plt.title(r"\textit{Commmand Set (Babble Noise)}")
+plt.tight_layout()
+plt.ylabel(r'\textit{Accuracy (100 - WER \%)}')
+plt.xlabel(r'\textit{SNR (dB)}')
+plt.axis([-1.0, 21.0, 0.0, 100.0])
+
+file_name = "plot_farfield_wer_babble.eps"
+fig.savefig(file_name)
+
+#subprocess.check_call(shlex.split("evince {0}".format(file_name)))
+
+
+# TV_direct
+plt.figure()
+
+data = []
+x_snr = np.array([0.0, 5.0, 10.0, 15.0, 20.0])
+
+data.append((x_snr, 100 - np.array([3.99, 2.15, 1.53, 1.86, 0.92]),
+    "NBF + VTLP + AS"))
+data.append((x_snr, 100 - np.array([26.23, 10.15, 1.53, 1.53, 0.92]),
+    "VTLP + AS"))
+data.append((x_snr, 100 - np.array([68.55, 51.26, 16.77, 6.44, 2.15]),
+    "baseline"))
+
+data_list_plot.PlotSnrdbAccData(data)
+fig = plt.gcf()
+
+plt.title(r"\textit{Commmand Set (TV Noise)}")
+plt.tight_layout()
+plt.ylabel(r'\textit{Accuracy (100 - WER \%)}')
+plt.xlabel(r'\textit{SNR (dB)}')
+plt.axis([-1.0, 21.0, 0.0, 100.0])
+
[…]

### 2019-12-15 asru_2019_training_infra/figures/plot_gpu_time_percentage.py

@@ -1,0 +1,37 @@
+#!/usr/bin/python
+
+import shlex
+import subprocess
+import numpy as np
+from util.plot_util import data_list_plot
+import matplotlib.pyplot as plt
+
+plt.rc('text', usetex=True)
+
+dist = np.array([1.0, 2.0, 3.0, 4.0, 5.0])
+
+data = []
+
+# The data at 41.000 is problematic.
+data.append((dist, [35.0, 85.7, 91.8, 92.8, 96.6]))
+plt.plot([0.0, 5.2], [94.8, 94.8], '--',  linewidth=2)
+
+data_list_plot.PlotDiscreteData(data)
+fig = plt.gcf()
+plt.axis([0.8, 5.2, 0.0, 100.0])
+
+fig = plt.gcf()
+fig.set_size_inches(5,3)
+
+ax = plt.gca()
+ax.get_legend().remove()
+
+plt.ylabel(r'\textit{Tensorflow Session Time (\%)}')
+plt.xlabel(r"\textit{Number of CPUs in the Example Server per GPU}")
+plt.tight_layout()
+
+file_name = "plot_gpu_time_percentage.eps"
+fig.savefig(file_name)
+
+#subprocess.check_call(shlex.split("evince {0}".format(file_name)))
+

### 2019-12-15 asru_2019_maximizing_uniformity_of_distribution/doc/asru_2019_reviewer_rebuttal.txt
udpate ASRU MUD

Summary:
We would like to thank all the reviewers for sparing time out of their busy schedule to provide very useful comments on our paper. The major novelty of this paper is that we proposed a new way of deriving a suitable compressive nonlinearty from the data themselves. In case of the previous power-law nonlinearty of 1/15, it was obtained by curve-fitting from the rate-intensity curve of the human auditory system and additionally by performing speech recognition experiments with various power coefficients to find out the best value. These steps require a lot of time for obtaining the best power-coefficient. Because of this problem, we couldn’t fine tune the power coefficient for each filter bank channel when we first presented this work in our previous PNCC paper in 2012 and in 2016. In this new MUD approach, we  obtain suitable coefficients for each filterbank channel “without” actually running speech recognition experiments. This is a huge benefit compared to the previous hand-crafted fine tuning. In addition, we believe that this approach can be extended to other domains like vision. The  previous power coefficient of 1/15 was already hand-optimized by performing experiments with  different parameters. This it is quite natural that the additional improvement over this previous optimized system with a power coefficient of 1/15 is relatively small. However, the major importance of this work is that we proposed a new way of designing the compressive nonlinearity from data themselves, and this approach is much more flexible and may be extended to other domains as well.

To the reviewer #0D85

First, thank you very for carefully reviewing the paper. We greatly thank your complimentary ratings and giving very helpful comments.
We reply to your comments as follows:

1. About using an external LM.
We recently performed an experiment using a Transformer LM with a shallow-fusion technique. This approach showed around 30 % additional relative improvement in Word Error Rate (WER).  If this paper is accepted, we will include this result as well.

2. About performance improvement over the power-law nonlinearty of 1/15.
It is indeed true that the additional improvement over the previous power coefficient of 1/15 is not  large. However, as mentioned in the summary part of this rebuttal, the importance of this work is that we suggested a completely new way of obtaining the compressive non-linearity. Unlike our previous PNCC paper, we didn’t need to conduct speech recognition experiments with different power-law coefficients to obtain the optimal coefficient. This is a huge benefit compared to the previous hand-crafted fine tuning. In addition, we believe that this approach can be extended to other domains like vision. The  previous power coefficient of 1/15 was already hand-optimized by performing experiments with  different parameters. This it is quite natural that the additional improvement over this previous optimized system with a power coefficient of 1/15 is relatively small. When we come up with the power coefficient of 1/15, we couldn’t optimize the power coefficient for different filter bank channel, since it will take too much time for doing such an experiment. In the new MUD approach, we could easily optimize power coefficient for different filterbank channel very easily using a new criterion. In the future, we believe that this algorithm can be applied to other domains (such as vision) as well.

3. The meaning of “easier”
If the features are difficult to learn, parameter convergence usually becomes more difficult due to the erratic error function surface. In this case, we usually have hard time in fine-tuning learning rates and hyper parameters to obtain converged parameters. In this paper, “easier” means that the neural network may be trained well without too much fine-tuning because of the well-behaved feature distribution and the error surface.

Again, thank you and we really appreciate your complimentary remarks!

To the reviewer #0c9#

First, thank you very much for carefully reviewing the paper. We greatly appreciate your review comments. If this paper is accepted, we will include experimental results obtained using 10,000-hr Bixby training set.
Thank you very much for your complimentary review!

To the reviewer #0DF3.

First, thank you very much for carefully reviewing the paper. We greatly appreciate your review comments. Thank you for mentioning the Spec-Augment paper. We checked that spec-Augment shows better performance. Once this paper is accepted, we will modify the content mentioning that this is the best result without using data-augmentation. After submitting this work, we could reduce WER  relatively by 30% by using a transformer LM.

To the reviewer #0D3A

First, thank you very for carefully reviewing the paper. We greatly thank your complimentary ratings and giving very helpful comments.
We reply to your comments as follows:

1. About performance improvement over the power-law nonlinearty of 1/15.
It is indeed true that the additional improvement over the previous power coefficient of 1/15 is not  large. However, as mentioned in the summary part of this rebuttal, the importance of this work is that we suggested a completely new way of obtaining the compressive non-linearity. Unlike our previous PNCC paper, we didn’t need to conduct speech recognition experiments with different power-law coefficients to obtain the optimal coefficient. This is a huge benefit compared to the previous hand-crafted fine tuning. In addition, we believe that this approach can be extended to other domains like vision. The  previous power coefficient of 1/15 was already hand-optimized by performing experiments with  different parameters. This it is quite natural that the additional improvement over this previous optimized system with a power coefficient of 1/15 is relatively small. When we come up with the power coefficient of 1/15, we couldn’t optimize the power coefficient for different filter bank channel, since it will take too much time for doing such an experiment. In the new MUD approach, we could easily optimize power coefficient for different filterbank channel very easily using a new criterion. In the future, we believe that this algorithm can be applied to other domains (such as vision) as well.

2. About the statistical significance of the improvement over the previous power-law coefficient of 1/15.
 For the Libri speech test-other, we checked that the WER difference is statistically significant.

### 2019-12-15 asru_2019_maximizing_uniformity_of_distribution/doc/main.tex
udpate ASRU MUD

% Template for ICASSP-2019 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass[a4paper]{article}

%\usepackage{INTERSPEECH2019}
\usepackage{spconf}
\usepackage{amsmath,graphicx}
\usepackage{amssymb,amsmath,bm}
\usepackage{textcomp}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{multirow}
%\usepackage{subcaption}
\usepackage[justification=centering]{caption}
\usepackage[caption = false]{subfig}

% Custom settings
\usepackage{tikz,placeins}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\large]

\graphicspath{{../figures/}}

\newcommand{\specialcell}[2][c]{%
     \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcommand{\chanwcom}{C. {Kim}}
\renewcommand{\topfraction}{1.0}
\renewcommand{\bottomfraction}{1.0}
\renewcommand{\textfraction}{0.01}
\renewcommand{\floatpagefraction}{1.0}
\renewcommand{\dbltopfraction}{1.0}
\renewcommand{\floatpagefraction}{1.0}  % require fuller float pages
\renewcommand{\dblfloatpagefraction}{1.0} % require fuller float pages

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

% Example definitions.
% --------------------
\def\x{{\mathbf x}} 
\def\L{{\cal L}}

\title{Power-law nonlinearity with maximally uniform distribution criterion for
improved neural network training in automatic speech recognition}
%
% Single address.
% ---------------
\name{{Chanwoo Kim, Mehul Kumar, Kwangyoun Kim, and Dhananjaya Gowda} 
  \thanks{Thanks to Samsung
Electronics for funding this research. The authors are thankful to 
Executive Vice President Seunghwan Cho and speech processing Lab.
members at Samsung Research.}}

%\address{BLIND}
\address{Samsung Research \\
  {\small \tt \{chanw.com, mehul3.kumar, ky85.kim, d.gowda\}@samsung.com }}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
In this paper, we describe the Maximum Uniformity of Distribution 
(MUD) algorithm with the power-law nonlinearity. In this approach, 
  we hypothesize that neural network training will become more stable
 if feature distribution is not too much skewed.
We propose two different types of MUD approaches: power function-based MUD 
and histogram-based MUD. In these approaches, we first obtain the mel filterbank
coefficients and apply nonlinearity functions for each filterbank channel.
With the power function-based MUD, we apply a power-function based
nonlinearity where power function coefficients are chosen to maximize the 
likelihood assuming that nonlinearity outputs follow the uniform distribution.
With the histogram-based MUD, the empirical Cumulative Density Function (CDF) 
from the training database is employed to transform the original distribution
 into a uniform distribution.
In MUD processing, we do not use any prior knowledge (e.g. logarithmic
relation) about the energy of the incoming signal and the perceived intensity 
by a human. Experimental results using an end-to-end speech recognition system
demonstrate that power-function based MUD shows better result than the 
 conventional Mel Filterbank Cepstral Coefficients (MFCCs).  On the LibriSpeech
  database, we could achieve 4.02 \% WER on {\tt test-clean} and 13.34 \% WER on
  {\tt test-other } without using any Language Models (LMs). The major
  contribution of this work is that we developed a new algorithm for designing
  the compressive nonlinearity in a {\it data-driven} way, which is much more
  flexible than the previous approaches and may be extended to other domains as
  well.
\end{abstract}
%

%
%\begin{keywords}
  \noindent{\bf Index Terms}:  Deep-Neural Network Model, end-to-end speech recognition, feature distribution,  nonlinearity function, power function
%\end{keywords}

%
%
\section{Introduction}
After the breakthrough of deep learning technology
\cite{Seltzer2013DNNAurora4, Yu2013FeatureLearningDNN,
V_Vanhoucke_Deep_Learning_NIPS_Workshop_2011,
G_Hinton_IEEE_Signal_Process_Mag_2012, h_hadian_interspeech_2018_00, 
s_karita_interspeech_2019_00, c_chiu_icassp_2018_00, r_prabhavalkar_interspeech_2017_00}, 
speech recognition accuracy has
improved dramatically. Recently, speech recognition systems
are widely used not only in smart phones and Personal Computers
(PCs) but also in standalone devices in far-field environments.
Examples include voice assistant systems such as Amazon Alexa
, Google Home \cite{c_kim_interspeech_2017_00, B_Li_INTERSPEECH_2017_1}, and
Samsung Bixby \cite{samsung_bixby}.

In the era of deep neural networks, it has been frequently
observed that the amount and coverage of the training data 
seem to be one of the most important factors to obtain better 
speech recognition accuracy 
\cite{h_soltau_interspeech_2017_00, a_narayanan_slt_2018_00}.
However, it is very difficult to gather sufficient amount of
transcribed data from various domains. To overcome this problem,
data augmentation has been very popular these days 
\cite{w_hartmann_interspeech_2016_00, x_cui_taslp_2015_00, s_park_interspeech_2019_00, c_kim_icassp_2018_00, 
c_kim_interspeech_2019_00}. Small Power Boosting (SPB) technique
may be considered as a variation of data augmentation techniques
\cite{C_Kim_ASRU_2009_2}. These kinds of data augmentation techniques
have significantly improved speech recognition accuracy for commercial
products such as Google Home \cite{
c_kim_interspeech_2017_00, B_Li_INTERSPEECH_2017_1, c_kim_interspeech_2018_00}.
However, a still remaining question is what would be the best way to
obtain features as inputs to the neural network.

Using the capabilities of neural networks,
researchers have explored raw-waveform features
\cite{T_Sainath_IEEETran_2017_1}
or complex Fast Fourier Transform (FFT) features
\cite{c_kim_interspeech_2017_00, B_Li_INTERSPEECH_2017_1}.
However, log-mel filterbank coefficients or Mel Filterbank Cepstral Coefficients 
(MFCCs) \cite{pmermelstein1975} still remains the dominant form as 
features of the automatic speech recognition systems 
\cite{h_hadian_interspeech_2018_00, d_amodei_pmlr_2016_00,
c_kim_icassp_2018_01, c_kim_interspeech_2014_00}. This is because the conventional
features such as MFCC or log-mel filterbank coefficients requires
less computation than the neural network-based features 
such as raw-waveform features \cite{T_Sainath_INTERSPEECH_2015_1} while 
showing comparable performance.  In log-mel filterbank coefficients and MFCC, the
log-nonlinearity is employed to represent the relationship
between the perceived sound intensity by human and
the filterbank energy \cite{C_Kim_PhDThesis_2010}. In more recent
features such as Power Normalized Cepstral Coefficients (PNCCs), 
the power-law nonlinearity with the power coefficient of $\frac{1}{15}$
is employed \cite{C_Kim_IEEETran_2016_1, C_Kim_ICASSP_2012_1}. In our previous study 
\cite{C_Kim_ICASSP_2010_1, C_Kim_INTERSPEECH_2009_2} 
this power-law nonlinearity has been shown 
to be more robust against additive noise. Both the log-law nonlinearity
and the power-law nonlinearity with this specific coefficient of $\frac{1}{15}$
 were 
motivated by {\it the rate-intensity relation} of the human auditory system
\cite{C_Kim_PhDThesis_2010, C_Kim_IEEETran_2016_1}.

In this paper, we take a completely different approach. Instead of trying to model
the human auditory system directly, we try to find a nonlinearity function
which maximizes the uniformity of distribution.
We refer this approach to Maximum Uniformity of Distribution (MUD) approach.
This approach is based on the assumption that even though 
neural networks have remarkable capabilities in classifying input features,
training would be easier
 if feature distribution is not too much 
skewed and features are not too much concentrated in an extremely narrow
interval. More specifically, we assume that if the distributions of features 
are difficult to learn, parameter convergence usually becomes more difficult due to the
erratic surfaces of error functions. In this case, we might have hard time 
in fine-tuning learning rates and hyper parameters to obtain converged 
parameters. In this paper, ``easier" training means that the neural network may be
trained well without too much fine-tuning thanks to the well-behaved feature
distribution and the error function surface. 
It has been known that the distribution of amplitudes \cite{C_Kim_INTERSPEECH_2008} and 
filterbank energies  \cite{C_Kim_ASRU_2009_1}
is very sharp and skewed.
Thus, it is usually not possible to use  mel filterbank energy as features
without using any compressive nonlinearity.
We proposed two different types of MUD approaches: power function-based MUD 
and histogram-based MUD. In these approaches, we first obtain the mel filterbank
energy. 
With the power function-based MUD, we apply a power-function based
nonlinearity where the power function coefficient is chosen to maximize the 
likelihood assuming that the nonlinearity output is the uniform distribution.
  With the histogram-based MUD, the empirical Cumulative Density Function (CDF) 
  is obtained from the training database to transform the original distribution
 into a uniform distribution.
In these two approaches, unlike our previous study 
\cite{C_Kim_IEEETran_2016_1, C_Kim_PhDThesis_2010}, we do not use any prior knowledge 
about {\it the rate-intensity relationship} which is the relation between 
the energy of the incoming signal and the perceived intensity 
by a human \cite{C_Kim_PhDThesis_2010}. However, as will be discussed in Sec.  
\ref{sec:end_to_end_speech_recognition}, we may obtain 
surprisingly similar coefficients  to those obtained from human
auditory systems in a {\it data-driven} way.  A major contribution of this 
work is that we developed a new algorithm for designing
the compressive nonlinearity in a {\it data-driven} way, which is much more
flexible than the previous approaches and may be extended to other domains as
well.
Experimental results with an end-to-end speech recognition system
demonstrate that Power-function based MUD shows better result than the 
  conventional Mel Filterbank Cepstral Coefficients (MFCCs) while Histogram-based
  MUD shows comparable results to the MFCC processing.

The rest of the paper is organized as follows: We develop the theory of
maximizing the uniformity in Sec. \ref{sec:mud_theory}. We describe
the MUD nonlinearity estimation and the entire end-to-end speech
recognition system in Sec. \ref{sec:end_to_end_speech_recognition}.
Experimental results that demonstrates the effectiveness of the MUD processing
is presented in Sec.  \ref{sec:experimental_results}. We conclude in Sec.
\ref{sec:conclusion}.
%
%
%
\section{Maximization of Distribution Uniformity}
\label{sec:mud_theory}
%
\subsection{Power-function based maximization of distribution uniformity}
\label{sec:power_function_based_mud}
%
Consider a random variable $\mathbf{X}$ whose range is a closed interval
$I_{\mathbf{X}} = \left[x_{\text{min}}, x_{\text{max}} \right]$. 
$x_{\text{min}}$ and  $x_{\text{max}}$ are the minimum and maximum
values of the random variable $\mathbf{X}$ respectively.

Our objective is to apply a nonlinearity $\sigma_{p}(\cdot)$ 
in the form of \eqref{eq:power_mud} to $X$  so that the transformed
random variable $Y$ closely follows a uniform distribution:
\begin{align}
  \mathbf{Y} = \sigma_{p} \left(\mathbf{X} \right) = (X - x_{\text{min}})^{\alpha}.
    \label{eq:power_mud}
\end{align}
We chose the power function as the nonlinearity, partly because
it has been shown that this function is quite effective as
a compressive nonlinearity in speech feature processing 
\cite{C_Kim_IEEETran_2016_1,C_Kim_ICASSP_2012_1,
C_Kim_ICASSP_2010_1, C_Kim_INTERSPEECH_2009_2}.
We subtract $X$ by $x_{\text{min}}$, since this will simplify
the maximum likelihood estimation of $\alpha$, which will be
explained shortly.
From \eqref{eq:power_mud}, the range of $Y$ is given by
$I_{\mathbf{Y}} = \left[0, \left(x_{\text{max}} - x_{\text{min}} \right)
    ^{\alpha}\right]$. 
Thus, we expect $Y$ to follow the following uniform distribution:
\begin{align}
  \mathbf{Y} \sim 
  \mathcal{U}(0, \left(x_{\text{max}} - x_{\text{min}} \right)^{\alpha} ).
    \label{eq:pdf_y}
\end{align}
The PDF of $Y$ is given by:
%
\begin{align}
  p_{\mathbf{Y}}(y) =             
    \begin{cases}
      \frac{1}{\left(x_{\text{max}} - x_{\text{min}} \right)^{\alpha}} ,
          & 0 \le y \le \left(x_{\text{max}} - x_{\text{min}} \right)^{\alpha}   \\
      0, \qquad                    & \text{otherwise}.
    \end{cases}
\end{align}
%
Using the property of the PDFs of the transformed random variables
\cite{A_Papoulis_McGrawHill_2002},
we obtain the PDF of the random variable $\mathbf{X}$ by:
%
%
\begin{align}
  p_{\mathbf{X}}(x)
                & = p_{\mathbf{Y}}(y) \frac{dy}{dx}   \nonumber \\
                & = p_{\mathbf{Y}}(y) \left[ \alpha 
                    \left(x - x_{\text{min}}\right)^{\alpha-1} \right]
                    \nonumber \\
                & = 
                \begin{cases}
                  \frac{\alpha \left(x - x_{\text{min}}\right)  ^{\alpha-1}}
                    {\left(x_{\text{max}} - x_{\text{min}}\right)^{\alpha}},  
                      \qquad &  x_{\text{min}} \le x \le x_{\text{max}} \\ 
                  0,         &\text{otherwise}.
                \end{cases}
  \label{eq:pdf_x}
\end{align}
Now, suppose that we have the following $N$ samples from 
the random variable $\mathbf{X}$:
\begin{align}
  X = \left\{x_0, x_1, \cdots, x_{N-1}\right\}.
    \label{eq:x_samples}
\end{align}
Using \eqref{eq:pdf_x}, we obtain the $\alpha$ value which maximizes 
the data likelihood $p(X|\alpha)$.
The log likelihood of the data $X$ assuming the PDF in \eqref{eq:pdf_y}
is given by:
%
\begin{align}
  \mathcal{L}\left(\alpha ; X\right) 
      & = \sum_{i=0}^{N-1} \ln p_{\mathbf{X}} \left( x_i \right)  \nonumber \\
      & = \sum_{i=0}^{N-1} 
              \ln \left[ \frac{ \alpha (x_i - x_{\text{min}} )^{\alpha-1}}  
              {\left(x_{\text{max}} - x_{\text{min}} \right)^{\alpha}} \right]  \nonumber \\
      & = N \ln(\alpha) + \left(\alpha-1 \right) \sum_{i=0}^{N-1}
        \ln \left(x_i - x_{\text{min}} \right)  \nonumber \\
      & \qquad - N \alpha \ln \left(x_{\text{max}} - x_{\text{min}} \right).
        \label{eq:x_likelihood}
\end{align}
%
In \eqref{eq:x_likelihood}, the term $\ln \left(x_i - x_{\text{min}}
\right)$ is not defined when $x_i = x_{\text{min}}$. Thus, we apply flooring as
shown below:
\begin{align}
  \mathcal{L}\left(\alpha ; X\right) & =  
    N \ln(\alpha) \nonumber \\
     & \quad  + \left(\alpha-1 \right) \sum_{i=0}^{N-1}
        \ln \left(\max \left\{x_i - x_{\text{min}}, \delta \right\} \right)
          \nonumber \\
      & \quad - N \alpha \ln \left(x_{\text{max}} - x_{\text{min}} \right),
        \label{eq:x_likelihood}
\end{align}
where $\delta$ is a flooring coefficient. We use $\delta = 10^{-100}$ in our
experiments.
%
By differentiating $\mathcal{L}\left(\alpha | X\right)$ with respect to 
$\alpha$, we obtain $\hat{\alpha}$, which maximizes the likelihood as below:
\begin{align}
  \hat{\alpha} = \frac{1}{
    \ln \left(\max \left\{x_i - x_{\text{min}}, \delta \right\} \right)
    - \frac{1}{N} \sum_{i=0}^{N-1} \ln \left(x_i - x_{\text{min}}\right)}.
  \label{eq:alpha_estimation}
\end{align}
%
%
\subsection{Histogram-based maximization of distribution uniformity}
\label{sec:histogram_based_mud}
%
Instead of using the power-function based parametric approach to
maximize the uniformity of distribution, we may also consider the
non-parametric approach. In this approach, we estimate the 
Cumulative Distribution Function (CDF) from the samples in 
\eqref{eq:x_samples}. This CDF estimation is achieved by 
sorting the samples $x_i$ in \eqref{eq:x_samples} and performing
interpolation. The relation between the original random variable
$\mathbf{X}$ and the transformed random variable $\mathbf{Y}$
is given by the following equation:
\begin{align}
  \mathbf{Y} = \sigma_{np}(\mathbf{X}) 
      = F_u^{-1} \left(\hat{F}_x(\mathbf{X})\right)
  \label{eq:histogram_mud}
\end{align}
where $F_u(\cdot)$ is the CDF of the uniform distribution.
$\hat{F}_x(\mathbf{X})$ in \eqref{eq:histogram_mud} is the 
estimated CDF of $\mathbf{X}$ that is mentioned above.
In the special case of the uniform distribution of 
$\mathcal{U}(0, 1)$, the inverse of this CDF 
is given by  $F_u^{-1}(x) = x, \;\; 0 \le x \le 1$. Under this
assumption, the above equation \eqref{eq:histogram_mud} may be 
simplified to:
\begin{align}
  \mathbf{Y} = \sigma_{np}(\mathbf{X}) 
      = \hat{F}_x(\mathbf{X}).
  \label{eq:histogram_mud_simple}
\end{align}

\section{End-to-End speech recognition with the maximization of feature 
distribution uniformity}
\label{sec:end_to_end_speech_recognition}
%
%
\begin{figure}[tbp]
  \begin{center}
    \resizebox{80mm}{!}{\input{../figures/e2e_asr_block_diagram}}
      \caption {  The structure of the entire end-to-end 
      speech recognition system with MUD processing. The LSTMs
      in the encoder layers may be either bidirectional-LSTMs or
      unidirectional-LSTMs. The attention may be either the full
      attention or the MOnotonic CHunkwise Attention (MoCha) 
      \cite{c_chiu_iclr_2018_00, k_kim_asru_2019_00}. 
     }   
     \label{fig:entire_diagram}
  \end{center}
%\vspace{-5mm}
\end{figure}
%
%
In this section, we explain how to use  the theories we developed in
Sec. \ref{sec:power_function_based_mud} and \ref{sec:histogram_based_mud}
to train an end-to-end speech recognition system. The entire block diagram
of the system is shown in Fig. \ref{fig:entire_diagram}. 
We used two different attention structures: Bidirectional LSTMs with 
Full Attention (BFA)  \cite {d_bahdanau_iclr_2015_00} and 
MOnotonic CHunkwise Attention (MoCha) 
\cite{c_chiu_iclr_2018_00}. Our MoCha implementation is described
in very detail in our another paper \cite{k_kim_asru_2019_00}.

We apply either the 
power function-based MUD nonlinearity in \eqref{eq:power_mud} or the 
histogram-based MUD nonlinearity to each mel filterbank energy as the first
step as depicted in Fig. \ref{fig:entire_diagram}.
The mel filterbank energy is defined by the following equation:
\begin{align}
  p[m, l] & = 
    \sum_{k=0}^{K/2} \left|X[m, e^{j \omega_k}]\right|^2  M_l[\omega_k] 
  \label{eq:mel_filterbank_energy}
\end{align}
where $M_l[\omega_k]$ is the triangular mel response for the $l$-th
filterbank channel, $m$ is the frame index, and $K$ is the Fast Fourier
Transform (FFT) size. $\omega_k$ is the discrete-time frequency defined
by $\omega_k = \frac{2 \pi k}{K} \;\; 0 \le k \le K - 1$. 
The input feature vector $\vec{x}[m]$ in 
Fig. \ref{fig:entire_diagram} is therefore given by:
\begin{align}
  \vec{x}[m] = \left[p[m, 0], \; p[m, 1], \; \cdots, \; p[m, C-1] \right].
\end{align}
where $C$ is the number of mel filter bank channels. In our experiments, we
used the value of $C = 40$. For the power function-based MUD, we use 
\eqref{eq:alpha_estimation} for each mel filterbank channels from the 
randomly selected 1,000 utterances from the training set. In order not to
be affected by the silence portion, we removed non-speech portion using
a simple energy-based Voice Activity Detector (VAD).

Fig.  \ref{fig:estimated_power_coeff} shows the estimated $\hat{\alpha}$ 
using \eqref{eq:alpha_estimation} for each mel filterbank channel.
From this Fig. \ref{fig:estimated_power_coeff}, we observe that 
$\hat{\alpha}$ values are surprisingly close to the power 
coefficient of $\frac{1}{15}$ which we obtained by modeling the rate-intensity 
curve using a human auditory system \cite{C_Kim_PhDThesis_2010,
C_Kim_IEEETran_2016_1}. 
For the histogram-based
MUD, we also used the same randomly selected 1,000 utterances from the 
training set, applied a VAD, and constructed the empirical CDF to
obtain the nonlinearity function in \eqref{eq:histogram_mud}.

Fig. \ref{fig:pdf_mud} shows the Probability Density Functions (PDFs)
of the  mel filterbank energy in (a), those of the nonlinearity output using 
the power-based MUD in (b), and those of the nonlinearity output
using the histogram-based MUD in (c). In plotting these PDFs in Fig.
\ref{fig:pdf_mud}, we used another 1,000 utterances which are not 
included in estimating the MUD nonlinearities. These plots are for the
third filterbank channel $l=3$ in \eqref{eq:mel_filterbank_energy}.
As shown in Fig. \ref{fig:power_function_based_mud_output_histogram}, 
if we use the power function-based MUD, the PDF becomes much smoother
compared to the original PDF in Fig. \ref{fig:mel_filterbank_energy_histogram}.
However, this PDF is not as uniform as the one in Fig.  
\ref{fig:histogram_based_mud_output_histogram}. In Fig.
\ref{fig:nonlinearity_comparison}, we compared the Power-law nonlinearity 
of the form of $(\cdot)^{\frac{1}{15}}$ used in PNCC
\cite{C_Kim_IEEETran_2016_1, C_Kim_ICASSP_2012_1},
power function-based MUD in \eqref{eq:power_mud}, 
and histogram-based MUD \eqref{eq:histogram_mud} for the
third mel filterbank channel $l=3$ in \eqref{eq:mel_filterbank_energy}. 
Note that in case of power function-based MUD and histogram-based MUD, the nonlinearity
functions are different for different filterbank channels.
%
%
\begin{figure}[tbp]
  \begin{center}
    \includegraphics[width=70mm]{estimated_power_coeff} 
    \caption {
      \label{fig:estimated_power_coeff}
      The estimated power coefficients for each mel filterbank channels using
      \eqref{eq:alpha_estimation}.
    }
  \end{center}
  \vspace{-7mm}
\end{figure}
%
%
\begin{figure}[tbp]
  \begin{center}
    \subfloat[] {
      \includegraphics[width=70mm]{mel_filterbank_energy_histogram}
      \label{fig:mel_filterbank_energy_histogram}
  \vspace{-2mm}
    }   
    \\  
    \subfloat[] {
      \includegraphics[width=70mm]{power_function_based_mud_output_histogram}
      \label{fig:power_function_based_mud_output_histogram}
    }   
  \vspace{-2mm}
		\\
    \subfloat[] {
      \includegraphics[width=70mm]{histogram_based_mud_output_histogram}
      \label{fig:histogram_based_mud_output_histogram}
    }   
  \vspace{-2mm}
    \caption {
      The Probability Density Functions for the third filterbank channel
       of (a): the mel filterbank energy $p[m, l], l = 3$ in 
       \eqref{eq:mel_filterbank_energy}, (b): the power-function based MUD
      output of this mel filterbank energy in \eqref{eq:power_mud}, (c)
      the histogram based-MUD in \eqref{eq:histogram_mud}. 
      \label{fig:pdf_mud}
    }   
   \vspace{-7mm}
  \end{center}
\end{figure}
%
%
%
\begin{figure}[tbp]
  \begin{center}
    \includegraphics[width=70mm]{nonlinearity_comparison}
      \caption { 
      \label{fig:nonlinearity_comparison}
      Comparison of different nonlinearities:
      Power-law nonlinearity of the form of $(\cdot)^{\frac{1}{15}}$
      used in PNCC \cite{C_Kim_IEEETran_2016_1, C_Kim_ICASSP_2012_1},
      power function-based MUD in \eqref{eq:power_mud}, 
      and histogram-based MUD \eqref{eq:histogram_mud} for the
      third mel filterbank channel. 
      }
  \vspace{-7mm}
  \end{center}
\end{figure}
%
%
\begin{table*}[!htbp]
  \renewcommand{\arraystretch}{1.3}
  \centering
      \caption{\label{tbl:result} 
      Word Error Rates (WERs) obtained with MFCC, Power Mel filterbank
      coefficients, \\ power function-based MUD processing, and
      histogram-based MUD Processing on the LibriSpeech corpus 
      \cite{v_panayotov_icassp_2015_00}. \\ For each WER number, the same 
      experiment was conducted twice and the results were averaged. \\ All these 
      results were obtained \textbf{without} using a Language Model (LM).
      }
      %\vspace{-3mm}
      \begin{tabular}{| c | c  || c | c | c | c |}
        \hline
        \multicolumn{2}{| l ||}{Neural Network Structure}
                               & \specialcell{MFCC}
                               & \specialcell{$ ( \cdot ) ^ {\frac{1}{15}}$}
                               & \specialcell{Power Function- \\ Based MUD}
                               & \specialcell{Histogram- \\ Based MUD}   \\
        \hline \hline
        \multirow{3}{*}{\specialcell{1024 cell \\ ULSTM \\ MoCha}}    
                & test-clean  &   7.09  \% & \textcolor{blue}{\textbf{ 7.04 }} \%   &   7.10 \%  &  7.13 \%  \\
                & test-other  &  20.60  \% & 19.76 \%
                &  \textcolor{blue}{\textbf{19.64}} \%  & 20.03 \%  \\
                & average     &  13.85  \% & 13.40 \%
                &  \textcolor{blue}{\textbf{13.37}} \%  & 13.58 \%  \\
        \hline \hline
     %   \multirow{3}{*}{\specialcell{256 cell  \\ BLSTM \\ Full-Attention}}    
     %           & test-clean  &   5.32  \% &  5.25 \%   &   5.32 \% &  5.53 \%  \\
     %           & test-other  &  16.82  \% & 16.40 \%   &  16.49 \% & 17.05 \%  \\
     %           & average     &  11.07  \% & 10.83 \%   &  10.91 \% & 11.29 \%  \\
     %   \hline
     %   \multirow{3}{*}{\specialcell{1024 cell \\ BLSTM \\ Full-Attention}}
     %           & test-clean  &   4.19  \% &   4.21 \%   &  4.24  \% &  4.20  \%  \\
     %           & test-other  &  14.19  \% &  13.80 \%   & 13.88  \% & 14.14  \%  \\
     %           & average     &   9.19  \% &   9.01 \%   &  9.06  \% &  9.17  \%  \\
     %   \hline
        \multirow{3}{*}{\specialcell{1536 cell \\ BLSTM \\ Full-Attention}}
                & test-clean  &   4.06  \% & \textcolor{blue}{\textbf{3.94}} \%   &   4.02 \%  &  4.11 \%  \\
                & test-other  &  13.97  \% & 13.56 \%
                & \textcolor{blue}{\textbf{13.34}} \%  & 14.10 \%  \\
                & average     &   9.02  \% &  8.75 \%
                & \textcolor{blue}{\textbf{8.68}} \%  &  9.11 \%  \\
        \hline
     \end{tabular}
     \vspace{-4mm}
\end{table*}
%
%
We used the RETURNN speech recognition system \cite{p_doetsch_icassp_2017_00,
a_zeyer_interspeech_2018_00, c_luscher_interspeech_2019_00}.
We have tried various modifications to the training stratgegy
(\emph{e.g} \cite{d_gowda_interspeech_2019_00, a_garg_asru_2019_00}).
$\vec{x}[n]$ and 
$\vec{y}_l$ are the input mel filterbank energy vector and the output label
, respectively. $m$ is the input frame index and $l$ is the decoder output
step index. $\vec{c}_l$ is the attention context vector calculated as
a weighted sum of the encoder hidden state vectors $\vec{h}_{enc}[m]$. The 
weights used in this procedure is called the attention weights. They are
calculated by applying softmax to the attention energies 
\cite{d_bahdanau_iclr_2015_00, a_zeyer_interspeech_2018_00}.
$\vec{h}^{enc}[m]$ and $\vec{h}^{dec}_l$ are the encoder and the decoder
hidden state vectors, respectively. $\vec{\beta}_l[m]$ is the attention weight
feedback \cite{a_zeyer_interspeech_2018_00}.
In \cite{a_zeyer_interspeech_2018_00}, the peak value of the speech 
waveform is normalized to be one. However, since finding the peak sample value 
is not possible for on-line feature extraction, we did not perform this
normalization. We modified the input pipeline
so that the on-line feature generation can be performed. We disabled the
clipping of feature range between -3 and 3, which is the default setting in 
their LibriSpeech experiment in \cite{a_zeyer_interspeech_2018_00}. 
We conducted experiments using both the
uni-directional and bi-directional Long Short-Term Memories  (LSTMs)
\cite{S_Hochreiter_neural_computation_1997_00}. 
For on-line processing, we used the MOnotonic CHunkwise Attention 
(MoCha) \cite{c_chiu_iclr_2018_00}. 
In online speech recognition experiments using MoCha, we used the chunk
size of 2.
 For better 
stability in the LSTM training, we used the gradient clipping by 
global norm \cite{r_pascanu_icml_2013}, which is implemented as 
{\tt tf.clip\_by\_global\_norm } API in Tensorflow  \cite{m_abadi_usenix_2016}.
We used six layers of encoders and one layer of decoder followed by a softmax 
layer. The training infrastructure we used is described in more detail in 
our another paper \cite{c_kim_asru_2019_01}.
%
%
\section{Experimental Results}
\label{sec:experimental_results}
%\begin{table*}[htbp]
%  \renewcommand{\arraystretch}{1.3}
%  \centering
%        \caption{\label{tbl:final_sdtr_mtr_result} 
%        Word Error Rates (WERs) obtained with MFCC, Power Mel filterbank
%        coefficients, \\ power function-based MUD processing, and
%        histogram-based MUD Processing on the Librispeech corpus 
%        \cite{v_panayotov_icassp_2015_00}. \\ For each WER number, the same 
%        experiment was conducted twice and averaged.
%        }
%        %\vspace{-3mm}
%        \begin{tabular}{| c | c  || c | c | c | c |}
%          \hline
%          \multicolumn{2}{| l ||}{Cell Size}
%                                 & \specialcell{MFCC}
%                                 & \specialcell{$ ( \cdot ) ^ {\frac{1}{15}}$}
%                                 & \specialcell{Power Function- \\ Based MUD}
%                                 & \specialcell{Histogram- \\ Based MUD}   \\
%          \hline \hline
%          \multirow{3}{*}{256 cell}    
%                  & test-clean  &   5.92  \% &  5.87 \%   &   5.91 \% &  6.15 \%  \\
%                  & test-other  &  17.58  \% & 17.11 \%   &  17.22 \% & 17.79 \%  \\
%                  & average     &  11.75  \% & 11.49 \%   &  11.57 \% & 11.97 \%  \\
%          \hline
%          \multirow{3}{*}{1024 cell}    
%                  & test-clean  &   4.70  \% &   4.72 \%   &   4.75 \% &  4.70  \%  \\
%                  & test-other  &  14.87  \% &  14.48 \%   &  14.53 \% & 14.82 \%  \\
%                  & average     &   9.79  \% &   9.60 \%   &   9.64 \% &  9.76 \%  \\
%          \hline
%          \multirow{3}{*}{1536 cell}    
%                  & test-clean  &   4.58  \% &  4.43 \%   &   4.54 \%  &  4.61 \%  \\
%                  & test-other  &  14.63  \% & 14.14 \%   &  13.98 \%  & 14.73 \%  \\
%                  & average     &   9.61  \% &  9.29 \%   &   9.26 \%  &  9.67 \%  \\
%          \hline
%       \end{tabular}
%       \vspace{-4mm}
%\end{table*}
%

\label{sec:experimental_results}
%
For speech recognition experiments, we used the Librispeech database
\cite{v_panayotov_icassp_2015_00}
for training and evaluation. For training, we used the entire 960 hours training
set consisting of 281,241 utterances. For evaluation, we used the 
official 5.4 hours {\tt test-clean} and 5.1 hours {\tt test-other} databases.
We conducted experiments
using the 40-th order MFCC feature implemented in
\cite{b_mcfee_proc_scipy_2015_00}, power-law nonlinearity of
$(\cdot)^{\frac{1}{15}}$ applied to the mel filterbank energy, 
power function based MUD processing, and histogram-based MUD processing.
We conducted experiments using both the online ULSTM/MoCha 
\cite{c_chiu_iclr_2018_00} structure and the BLSTM with the full-attention 
structure. We have conducted Bidirectional Long Short-Term Memory (BLSTM) 
experiments with the cell size of 1536.
For the on-line MoCha experiment, we used the Uni-directional 
Long Short-term Memory (ULSTM) with the cell size of 1024. 
Our MoCha implementation is described in very detail in \cite{k_kim_asru_2019_00}.
In all of our experiments in this section, we did not use any external Language 
Models (LMs). We observed that external LMs can significantly enhance the 
speech recognition accuracy of our end-to-end speech recognition system, which 
is shown in our other papers
\cite{c_kim_interspeech_2019_00, c_kim_asru_2019_01}. However, in this paper,
just to focus on the effects of nonlinearity, we did not employ external LMs.

These results are summarized in Table \ref{tbl:result}. For
each WER number in this table, the same experiment was conducted twice and 
these results were averaged to reduce the effect of random fluctuation
in each trial.
The best 
performance was achieved when we used the power function-based MUD with 
the 1536-cell BLSTM layers in the encoder and the full attention.
For the {\tt test-clean} and test {\tt test-other} test sets
\cite{v_panayotov_icassp_2015_00} , we 
obtained 4.02 \% Word Error Rate (WER) and 13.34 \% WER, respectively.
On average, the WER was 8.68 \%, which is relatively 3.77 \% improvement   
over the baseline MFCC with 9.02 \% WER.
From Table. \ref{tbl:result},
we note that usually there is no improvement over the baseline MFCC on
the {\tt test-clean} set. However, improvement on the {\tt test-other}
was usually more substantial. For the 1536-cell BLSTM full-attention case,
the relative improvement over the baseline MFCC on the {\tt test-other} 
is 4.51 \%.
 The performance difference between
the power-law nonlinearity of $(\cdot)^{\frac{1}{15}}$ and the power
function-based MUD is usually very small. This was expected since
the estimated parameters using \eqref{eq:alpha_estimation} are not
very different from $\frac{1}{15}$ as shown in Fig.
\ref{fig:estimated_power_coeff}.  However, for the {\tt test-other}
database, which is more a difficult set, the improvement over 
the power-law nonlinearity of $(\cdot)^{\frac{1}{15}}$ is {\bf statistically
significant}.
Histogram-based MUD shows somewhat worse 
performance compared to power function-based MUD. However, this histogram-
based MUD still shows comparable results to the conventional MFCC processing.
For the histogram-based MUD, we also tried to transform the PDF into a Gaussian
distribution. However, that system showed slightly worse results than the 
Histogram-based MUD in Table \ref{tbl:result}.
We hypothesize that the reason why histogram-based MUD does slightly worse
than the power-function based MUD is that it somewhat obscured the
energy boundary between speech vs non-speech. If we can employ a very sharp VAD
to select only the speech portion very accurately, we think the performance
of the histogram-based MUD will be comparable to that of the power-funcation
based MUD.

%
%%
%
%
\section{Conclusions}
\label{sec:conclusion}
In this paper, we described the Maximum Uniformity of Distribution 
(MUD) algorithm. This approach is based on the assumption that
neural-network training would be easier and the converged parameters would show better
performance when feature distribution is not too much 
skewed or too much concentrated in an extremely narrow interval. We proposed
two different types of MUD approaches: power function-based MUD and histogram
-based MUD. In these approaches, we first obtain the Mel filterbank
coefficients. The estimated parameters using the power function-based MUD 
using \eqref{eq:alpha_estimation} are surprisingly close to the power 
coefficient of $\frac{1}{15}$ which we obtained by modeling the rate-intensity 
curve using a human auditory system \cite{C_Kim_PhDThesis_2010,
C_Kim_IEEETran_2016_1}. The histogram-based MUD shows comparable performance
to the conventional MFCC processing, but it was worse than the performacne
of the power function-based MUD. In the end-to-end speech recognition
experiments on the LibriSpeech databases \cite{v_panayotov_icassp_2015_00},
we obtained 4.02 \%  WER and 13.34 \% WER on the  {\tt test-clean} and 
test {\tt test-other} test sets respectively using the power function-based
MUD processing.

The major novelty of this paper is that we proposed a new way of deriving 
a suitable nonlinearty from the training data themselves in a 
{\it data-driven} way. 
In the case of the previous power-law nonlinearty with the power coefficients of 
$\frac{1}{10}$ \cite{C_Kim_INTERSPEECH_2009_2} or $\frac{1}{15}$ \cite{C_Kim_ICASSP_2012_1}, 
they were obtained either by curve-fitting from {\it the rate-intensity curve } of the 
human auditory system \cite{C_Kim_IEEETran_2016_1}
or by performing speech recognition experiments with various power coefficients 
to find out the optimal value \cite{C_Kim_PhDThesis_2010}. 
Since these steps require significant amount time, 
we could not fine-tune the power coefficient for 
each filter bank channel in our previous work \cite{C_Kim_IEEETran_2016_1}. 
In this new MUD approach, we obtain suitable coefficients for 
each filterbank channel ``without" actually running speech recognition experiments. 
This is a significant advantage compared to the previous hand-crafted fine-tuning. 
In addition, we believe that this approach is not only limited to speech
recognition, but it can be applied to other domains in the future. 
Since the  previous power coefficient of $\frac{1}{15}$ was already hand-optimized 
by performing experiments with different coefficients, it is quite natural 
that the additional improvement of MUD over the previous power-law nonlinearity
is relatively small, which is also shown in Section 
\ref{sec:experimental_results}.
Nevertheless, the major contribution of this work is that we proposed 
a new way of designing the compressive nonlinearity in a {\it data-driven } way,
and this approach is much more flexible and may be extended to other domains 
as well.
%
%
%
%
%\clearpage
\ninept
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}

\end{document}

### 2019-12-15 asru_2019_maximizing_uniformity_of_distribution/poster/main.tex
udpate ASRU MUD

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% a0poster Landscape Poster
% LaTeX Template
% Version 1.0 (22/06/13)
%
% The a0poster class was created by:
% Gerlinde Kettl and Matthias Weiser (tex@kettl.de)
% 
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a0,portrait]{a0poster}
%\documentclass[a4]{article}

\usepackage{multicol} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster

\usepackage[svgnames]{xcolor} % Specify colors by their 'svgnames', for a full list of all colors available see here: http://www.latextemplates.com/svgnames-colors

\usepackage{times} % Use the times font
%\usepackage{palatino} % Uncomment to use the Palatino font

\usepackage{float}
\usepackage{graphicx} % Required for including images
\usepackage{booktabs} % Top and bottom rules for table
\usepackage[export]{adjustbox}
\usepackage[font=large,labelfont=bf]{caption} % Required for specifying captions to tables and figures
%\usepackage{tikzpagenodes}
\usepackage{amsfonts, amsmath, amsthm, amssymb, bm} % For math fonts, symbols and environments
\usepackage{wrapfig} % Allows wrapping text around tables and figures
\usepackage{multirow}
\usepackage[justification=centering]{caption}
\usepackage[caption = false]{subfig}

\DeclareMathOperator*{\argmax}{arg\,max}

\usepackage{tikz,placeins}
\usetikzlibrary{arrows,decorations.markings}
\tikzstyle{every picture}+=[font=\rmfamily\it\bfseries\tiny]
\usetikzlibrary{positioning, shapes}
%\usepackage{xcolor} %already loaded by tikz
%
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}

\graphicspath{{../figures/}}

\newcommand{\specialcell}[2][c]{%
     \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\newcommand{\chanwcom}{{C. Kim}}

\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

\begin{document}

%----------------------------------------------------------------------------------------
%	POSTER HEADER 
%----------------------------------------------------------------------------------------

% The header is divided into three boxes:
% The first is 55% wide and houses the title, subtitle, names and university/organization
% The second is 25% wide and houses contact information
% The third is 19% wide and houses a logo for your university/organization or a photo of you
% The widths of these boxes can be easily edited to accommodate your content as you see fit

\begin{minipage}[t]{1.0\linewidth}
\begin{center}
  \begin{minipage}[t]{0.1\textwidth}
    \centering
    \vspace{0pt}
    \includegraphics[width=10cm, valign=t]{samsung_research} % Logo or a photo of you, adjust its dimensions here
  \end{minipage} \hfill
  \begin{minipage}[t]{0.7\textwidth}
    \begin{center}
  \huge \color{NavyBlue} 
      \textbf{Power-law nonlinearity with maximally uniform distribution criterion for
      improved neural network training in automatic speech recognition} \\
      \LARGE \textbf{Chanwoo Kim, Mehul Kumar, Kwangyoun Kim, and Dhananjaya Gowda}
  \\
\LARGE Samsung Research, Seoul, South Korea\\ % University/organization
\large \{chanw.com, mk0211.shin, ky85.kim, d.gowda\}@samsung.com
    \end{center}
  \end{minipage}
  \begin{minipage}[t]{0.1\textwidth}
    \begin{center}
    \includegraphics[width=10cm]{samsung_research} % Logo or a photo of you, adjust its dimensions here
    \end{center}
  \end{minipage} \hfill
\end{center}
\end{minipage}
%
%\begin{minipage}[b]{0.25\linewidth}
%\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
%Department Name\\ % Address
%University Name\\
%123 Broadway, State, Country\\\\
%Phone: +1 (000) 111 1111\\ % Phone number
%Email: \texttt{john@LaTeXTemplates.com}\\ % Email address
%\end{minipage}
%

\vspace{1cm} % A bit of extra whitespace between the header and poster content

%----------------------------------------------------------------------------------------

\begin{multicols}{2} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\large

\color{Navy} % Navy color for the abstract

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\color{SaddleBrown} % SaddleBrown color for the introduction

\section{Motivation}

\begin{enumerate}
  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
    training database \cite{n_jaitly_icml_workshop_2013_00}.
  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
    \begin{itemize}
        \item We can apply the acoustic simulator after performing the VTLP
          processing.
        \item We may use a different window length for the frequency warping from
          the one used in feature processing for performance optimization.
    \end{itemize}
\end{enumerate}

\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
  \section{Maximization of Distribution Uniformity}

\begin{Figure}
  \begin{center}
    {
      \includegraphics[width=170mm]{mel_filterbank_energy_histogram}
      \label{fig:mel_filterbank_energy_histogram}
    }   
    \\  
    {
      \includegraphics[width=170mm]{power_function_based_mud_output_histogram}
      \label{fig:power_function_based_mud_output_histogram}
    }   
  \vspace{-2mm}
    \\  
    {
      \includegraphics[width=170mm]{histogram_based_mud_output_histogram}
      \label{fig:histogram_based_mud_output_histogram}
    }   
  \vspace{-2mm}
    \captionof{figure} {
      The Probability Density Functions for the third filterbank channel
       of (a): the mel filterbank energy $p[m, l], l = 3$ in  
       \eqref{eq:mel_filterbank_energy}, (b): the power-function based MUD 
      output of this mel filterbank energy in \eqref{eq:power_mud}, (c) 
      the histogram based-MUD in \eqref{eq:histogram_mud}. 
      \label{fig:pdf_mud}
    }   
   \vspace{-7mm}
  \end{center}
\end{Figure}

%\begin{center}
%  \includegraphics[width=0.2\linewidth]{power_function_based_mud_output_histogram}

%\captionof{figure}{
%  \label{fig:bilinear_transform}
%      The relation between the input frequency and the
%      warped frequency using the bilinear transformation
%      \eqref{eq:bilinear_transformation}.}
%
%\end{center}

%\item \textbf{IFFT and OverLap Addition (OLA)} Re-synthesize the waveform.
%\end{enumerate}

%\begin{figure}%[!tbp]
%\end{figure}

\section{End-to-End Speech recognition}

\begin{minipage}{1.0\linewidth}
  {
    \normalsize
  \begin{center}
  \resizebox{180mm}{!}{\input{../figures/e2e_asr_block_diagram_poster.tex}}
  \end{center}
\captionof{figure}{ 
  The structure of the entire end-to-end speech recognition system.}
  }
\end{minipage}

  We used the RETURNN speech recognition system
  \cite{a_zeyer_interspeech_2018_00} with various modifications:
    \begin{itemize}
      \item{Gradient clipping and learning-late warm-up.}
      \item{Power-mel feature} Motivated by the power-law nonlinearity of ($(\cdot)^{\frac{1}{15}}$) in PNCC \cite{C_Kim_IEEETran_2016_1}.
      \item{Modified shallow fusion with a Transformer LM}

        \begin{align}
  y_{0:L}^{*} = & \argmax_{y_{0:L}} \sum_{l=0}^{L-1} \Big[ \log P \left(y_l
  |\vec{x}[0:M], y_{0:l} \right)
  \nonumber \\
                           & \qquad - \lambda_p \log P(y_l)
                           + \lambda_{\text{lm}} \log P \left(y_l   |y_{0:l} \right)  \Big],
                           \label{eq:lm_fusion}
\end{align}

    \end{itemize}

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	MATERIALS AND METHODS
%----------------------------------------------------------------------------------------

\section{Experimental Results}
\begin{itemize}
  \item For training, we used { \bf the Librispeech train-clean and
    train-other}.
  \item For evaluation, we used { \bf the test-clean and test-other of this Libri
    Speech database. }
\end{itemize}

\begin{minipage}[b]{1.0\linewidth}
  %\begin{table*}[!htbp]
  \renewcommand{\arraystretch}{1.3}
  \centering
      \captionof{table}{\label{tbl:result}
      Word Error Rates (WERs) obtained with MFCC, Power Mel filterbank
      coefficients,  power function-based MUD processing, and
      histogram-based MUD Processing on the LibriSpeech corpus
      \cite{v_panayotov_icassp_2015_00}. 
      }
      %\vspace{-3mm}
      \begin{tabular}{| c | c  || c | c | c | c |}
        \hline
        \multicolumn{2}{| l ||}{Neural Network Structure}
                               & \specialcell{MFCC}
                               & \specialcell{$ ( \cdot ) ^ {\frac{1}{15}}$}
                               & \specialcell{Power Function- \\ Based MUD}
                               & \specialcell{Histogram- \\ Based MUD}   \\
        \hline \hline
        \multirow{3}{*}{\specialcell{1024 cell \\ ULSTM \\ MoCha}}
                & test-clean  &   7.09  \% & \textcolor{blue}{\textbf{ 7.04 }} \%   &   7.10 \%  &  7.13 \%  \\
                & test-other  &  20.60  \% & 19.76 \%
                &  \textcolor{blue}{\textbf{19.64}} \%  & 20.03 \%  \\
                & average     &  13.85  \% & 13.40 \%
                &  \textcolor{blue}{\textbf{13.37}} \%  & 13.58 \%  \\
        \hline \hline

            \multirow{3}{*}{\specialcell{1536 cell \\ BLSTM \\ Full-Attention}}
                & test-clean  &   4.06  \% & \textcolor{blue}{\textbf{3.94}} \%   &   4.02 \%  &  4.11 \%  \\
                & test-other  &  13.97  \% & 13.56 \%
                & \textcolor{blue}{\textbf{13.34}} \%  & 14.10 \%  \\
                & average     &   9.02  \% &  8.75 \%
                & \textcolor{blue}{\textbf{8.68}} \%  &  9.11 \%  \\
        \hline
     \end{tabular}
     \vspace{-4mm}
\end{minipage}
 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

%\nocite{*} % Print all references regardless of whether they were cited in the poster or not
%\bibliographystyle{plain} % Plain referencing style
%\bibliography{sample} % Use the example bibliography file sample.bib

%
\color{SaddleBrown} % SaddleBrown color for the introduction
\section{Conclusions}
%
{ \color{red}
We achieved 2.44 \% WER and 8.29 \% WER
  on the Librispeech {\it test-clean} and {\it test-other} databases.
To the best of our knowledge, the 2.44 \% WER on the {\it test-clean}
is the best result ever reported on this database
}
%
%
\begin{enumerate}
  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
    training database. \cite{n_jaitly_icml_workshop_2013_00}
  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
    \begin{itemize}
        \item We can apply the acoustic simulator after performing the VTLP
          processing.
        \item We may use a different window length (50 {\it ms}) for the frequency warping from
          the one used in feature processing (25 {\it ms}).
    \end{itemize}
  \item Applies the power-mel feature.
  \item Applies a modified shallow-fusion with a Transformer LM.
\end{enumerate}
\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
%----------------------------------------------------------------------------------------
\bibliographystyle{IEEEtran}
\bibliography{../../common_bib_file/common_bib_file}
\end{multicols}
\end{document}

### 2019-12-16 asru_2019_training_infra/poster/main.tex
Update the poster

--- 2019-12-15 asru_2019_maximizing_uniformity_of_distribution/poster/main.tex
@@
   \end{minipage} \hfill
-  \begin{minipage}[t]{0.7\textwidth}
+  \begin{minipage}[t]{0.79\textwidth}
     \begin{center}
   \huge \color{NavyBlue} 
-      \textbf{Power-law nonlinearity with maximally uniform distribution criterion for
-      improved neural network training in automatic speech recognition} \\
-      \LARGE \textbf{Chanwoo Kim, Mehul Kumar, Kwangyoun Kim, and Dhananjaya Gowda}
+      \textbf{End-to-end Training of a Large Vocabulary \\ End-to-end Speech Recognition System
+      } \\
+      \Large \textbf{
+      Chanwoo Kim, Sungsoo Kim, Kwangyoun Kim, Mehul Kumar,  Jiyeon Kim, \\ 
+      Kyungmin Lee, Changwoo Han, Abhinav Garg, Eunhyang Kim,  \\ 
+      Minkyoo Shin, Shatrughan Singh, Larry Heck, Dhananjaya Gowda
+      }
   \\
-\LARGE Samsung Research, Seoul, South Korea\\ % University/organization
-\large \{chanw.com, mk0211.shin, ky85.kim, d.gowda\}@samsung.com
+\Large Samsung Research, Seoul, South Korea\\ % University/organization
+{ \large \tt  \{chanw.com, ss216.kim, ky85.kim, mehul3.kumar, jstacey7.kim,} \\ 
+  \large \tt  {k.m.lee, cw1105.han, abhinav.garg, sc.ehkim.jin,} \\
+  \large \tt  {mk0211.shin, shatrughan.s, larry.h, d.gowda\}@samsung.com }
     \end{center}
@@
 %
-
-\vspace{1cm} % A bit of extra whitespace between the header and poster content
-
+%
+\vspace{-2mm} % A bit of extra whitespace between the header and poster content
+%
 %----------------------------------------------------------------------------------------
-
+%
 \begin{multicols}{2} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more
-
+%
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-
+%
+%
 \large
-
+%
 \color{Navy} % Navy color for the abstract
-
+%
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-
+%
 \color{SaddleBrown} % SaddleBrown color for the introduction
-
-\section{Motivation}
-
-\begin{enumerate}
-  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
-    training database \cite{n_jaitly_icml_workshop_2013_00}.
-  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
+%
+\section{Summary}
+%
 \begin{itemize}
-        \item We can apply the acoustic simulator after performing the VTLP
-          processing.
-        \item We may use a different window length for the frequency warping from
-          the one used in feature processing for performance optimization.
+\item Achieves the state of the art speech recognition performance for commercial products using an end-to-end pipeline that performs all of data reading,  large scale data augmentation \cite{c_kim_interspeech_2019_00}, power-mel feature extraction \cite{c_kim_asru_2019_00}, and  distributed neural network parameter updates in an “on-the-fly” way.
+\item Performs Vocal Tract Length Perturbation and Acoustic Simulation \cite{C_Kim_INTERSPEECH_2017_1} on the CPU queue using example servers.
+\item Performs Neural Beamforming \cite{j_heymann_icassp_2016_00} on the device side for further improvement in far-field noisy environments.
+\item Performs experiments both using the on-line MoCha \cite{k_kim_asru_2019_00} and the Bidirectional Full-Attention (BFA) approach.
 \end{itemize}
-\end{enumerate}
-
+%
+%
 \color{DarkSlateGray} % DarkSlateGray color for the rest of the content
-  \section{Maximization of Distribution Uniformity}
-
+  \section{Overall Structure}
+The overall structure is shown in Fig. \ref{fig:end_to_end_training_system}
+\begin{itemize}
+\item \textbf{Data reading}: Using sharded {\tt TFRecords} and {\tt tf.data}.
+\item \textbf{Data augmentation and feature extraction}: VTLP, AS, and power-mel feature extraction are running on the example servers.
+\item \textbf{Connection between the example servers and the GPU servers}: Using {\tt ZeroMQ} for asynchronous message queueing.
+\item \textbf{Distributed neural net training}: Training on the GPU server using {\tt horovod}.
+\end{itemize}
+%
+%
 \begin{Figure}
   \begin{center}
-    {
-      \includegraphics[width=170mm]{mel_filterbank_energy_histogram}
-      \label{fig:mel_filterbank_energy_histogram}
+    \resizebox{\textwidth}{!}{\input{../figures/end_to_end_training_system_poster.tex}}
+      \captionof{figure} { The Samsung Research end-to-end training framework for building an end-to-end
+  speech recognition system with multi CPU-GPU clusters and on-the-fly data
+  processing and augmentation pipeline.
      }
-    \\  
-    {
-      \includegraphics[width=170mm]{power_function_based_mud_output_histogram}
-      \label{fig:power_function_based_mud_output_histogram}
-    }   
-  \vspace{-2mm}
-    \\  
-    {
-      \includegraphics[width=170mm]{histogram_based_mud_output_histogram}
-      \label{fig:histogram_based_mud_output_histogram}
-    }   
-  \vspace{-2mm}
-    \captionof{figure} {
-      The Probability Density Functions for the third filterbank channel
-       of (a): the mel filterbank energy $p[m, l], l = 3$ in  
-       \eqref{eq:mel_filterbank_energy}, (b): the power-function based MUD 
-      output of this mel filterbank energy in \eqref{eq:power_mud}, (c) 
-      the histogram based-MUD in \eqref{eq:histogram_mud}. 
-      \label{fig:pdf_mud}
-    }   
-   \vspace{-7mm}
+     \label{fig:end_to_end_training_system}
   \end{center}
+\vspace{-5mm}
 \end{Figure}
-
-%\begin{center}
-%  \includegraphics[width=0.2\linewidth]{power_function_based_mud_output_histogram}
-
-%\captionof{figure}{
-%  \label{fig:bilinear_transform}
-%      The relation between the input frequency and the
-%      warped frequency using the bilinear transformation
-%      \eqref{eq:bilinear_transformation}.}
 %
-%\end{center}
-
-%\item \textbf{IFFT and OverLap Addition (OLA)} Re-synthesize the waveform.
-%\end{enumerate}
-
-%\begin{figure}%[!tbp]
-%\end{figure}
-
-\section{End-to-End Speech recognition}
-
-\begin{minipage}{1.0\linewidth}
+%
+%
+%
+\begin{minipage}[]{0.45\linewidth}
   {
@@
   \begin{center}
-  \resizebox{180mm}{!}{\input{../figures/e2e_asr_block_diagram_poster.tex}}
+  \resizebox{120mm}{!}{\input{../figures/e2e_asr_block_diagram_poster.tex}}
   \end{center}
 \captionof{figure}{ 
-  The structure of the entire end-to-end speech recognition system.}
+  The neural network structure for end-to-end speech recognition.}
   }
 \end{minipage}
-
-  We used the RETURNN speech recognition system
-  \cite{a_zeyer_interspeech_2018_00} with various modifications:
+%
+%
+\begin{minipage}[]{0.54\linewidth}
+  We used the RETURNN speech recognition system \cite{a_zeyer_interspeech_2018_00} with various modifications:
     \begin{itemize}
-      \item{Gradient clipping and learning-late warm-up.}
-      \item{Power-mel feature} Motivated by the power-law nonlinearity of ($(\cdot)^{\frac{1}{15}}$) in PNCC \cite{C_Kim_IEEETran_2016_1}.
-      \item{Modified shallow fusion with a Transformer LM}
-
+      \item{MoCha\cite{k_kim_asru_2019_00} and the modified beam search decoder.}
+      \item{Gradient clipping, modified learning-late warm-up, and so on.}
+      \item{Power-mel feature} Motivated by the power-law nonlinearity of ($(\cdot)^{\frac{1}{15}}$).
+      \item{Modified shallow fusion with a Transformer LM \cite{c_kim_interspeech_2019_00}}
         \begin{align}
@@
 \end{align}
-
+    \item{Example queues for efficient data augmentation}
     \end{itemize}
-
-%----------------------------------------------------------------------------------------
-%	OBJECTIVES
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-%	MATERIALS AND METHODS
-%----------------------------------------------------------------------------------------
-
+\end{minipage}
+%
+%
+\begin{Figure}
+  \captionsetup[subfigure]{justification=centering}
+    \centering
+    \begin{minipage}{0.49\linewidth}
+			\centering
+      {\includegraphics[width=175mm]{../figures/plot_example_server_time}  \label{fig:plot_example_server_time} }
+			{(a)}	
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+			\centering
+      {\includegraphics[width=175mm]{../figures/plot_gpu_time_percentage} \label{fig:plot_gpu_time_percentage} }
+			{(b)}	
+    \end{minipage}
+  \captionof{figure} {\label{fig:plot_example_server_performance}
+  The efficiency of the {\it example server} with respect to
+  the number of CPUs per GPU: (a) The required time to
+  process a single epoch during the training phase and (b)
+  the percentage of {\tt Tensorflow } computation time defined by
+  $t_{\text{session}} =  \frac{\text{Time Spent in {\tt Tensorflow}
+  Session}}{\text{Elapsed Time}}$.
+  The blue horizontal dotted lines in each figure represent the case
+  when data augmentation with example servers is not employed.
+  }
+\end{Figure}
+%
+%
 \section{Experimental Results}
+%
+%
+%
+%
 \begin{itemize}
-  \item For training, we used { \bf the Librispeech train-clean and
-    train-other}.
-  \item For evaluation, we used { \bf the test-clean and test-other of this Libri
-    Speech database. }
+\item \textbf{LibriSpeech experiments} (960-hr training and evaluation on 5.4-hr LibriSpeech {\tt test-clean}) \\
 \end{itemize}
-
 \begin{minipage}[b]{1.0\linewidth}
-  %\begin{table*}[!htbp]
+%\begin{table}[!tbhp]
   \renewcommand{\arraystretch}{1.3}
   \centering
-      \captionof{table}{\label{tbl:result}
-      Word Error Rates (WERs) obtained with MFCC, Power Mel filterbank
-      coefficients,  power function-based MUD processing, and
-      histogram-based MUD Processing on the LibriSpeech corpus
-      \cite{v_panayotov_icassp_2015_00}. 
+        \captionof{table}{\label{tbl:near_field_result}
+        Summary of Word Error Rates (WERs) obtained for different
+        LibriSpeech and {\tt Bixby } near-field end-to-end ASR models
+        with and without an RNN LM.
         }
         %\vspace{-3mm}
-      \begin{tabular}{| c | c  || c | c | c | c |}
+        \begin{tabular}{| c | c  || c | c |}
           \hline
-        \multicolumn{2}{| l ||}{Neural Network Structure}
-                               & \specialcell{MFCC}
-                               & \specialcell{$ ( \cdot ) ^ {\frac{1}{15}}$}
-                               & \specialcell{Power Function- \\ Based MUD}
-                               & \specialcell{Histogram- \\ Based MUD}   \\
+          \multicolumn{2}{| l ||}{Models}
+                                 & BFA
+                                 & MoChA \\
           \hline \hline
-        \multirow{3}{*}{\specialcell{1024 cell \\ ULSTM \\ MoCha}}
-                & test-clean  &   7.09  \% & \textcolor{blue}{\textbf{ 7.04 }} \%   &   7.10 \%  &  7.13 \%  \\
-                & test-other  &  20.60  \% & 19.76 \%
-                &  \textcolor{blue}{\textbf{19.64}} \%  & 20.03 \%  \\
-                & average     &  13.85  \% & 13.40 \%
-                &  \textcolor{blue}{\textbf{13.37}} \%  & 13.58 \%  \\
-        \hline \hline
-
-            \multirow{3}{*}{\specialcell{1536 cell \\ BLSTM \\ Full-Attention}}
-                & test-clean  &   4.06  \% & \textcolor{blue}{\textbf{3.94}} \%   &   4.02 \%  &  4.11 \%  \\
-                & test-other  &  13.97  \% & 13.56 \%
-                & \textcolor{blue}{\textbf{13.34}} \%  & 14.10 \%  \\
-                & average     &   9.02  \% &  8.75 \%
-                & \textcolor{blue}{\textbf{8.68}} \%  &  9.11 \%  \\
+          \multirow{3}{*}{\specialcell{LibriSpeech \\ (1536-cell) \\ test-clean}}
+                  & w/o LM  &   3.66  \% &  6.78  \%  \\
+                  & RNN-LM  &   2.85  \% &  5.54  \%  \\
+                  & Transformer LM  &   2.44  \% &   -   \\
+          \hline
+          \multirow{2}{*}{\specialcell{Bixby \\ (1024-cell) }}
+                  & w/o LM  &   8.25  \% &  10.77  \% \\
+                  & RNN-LM  &   7.92  \% &   9.95  \% \\
           \hline
        \end{tabular}
-     \vspace{-4mm}
+       \vspace{-2mm}
+%\end{table}
 \end{minipage}
+%
+%
+%
+%
+\begin{itemize}
+\item \textbf{Bixby English command-set experiments} (10,000-hr {\tt Bixby } training set and {\tt Bixby} command test sets) \\
+\item Note that the MoCha version of the system trained using  {\tt Bixby } training set was commercialized for on-device dictation for high-end Samsung mobile phones. \\
+\end{itemize}
+\begin{Figure}
+  \captionsetup[subfigure]{justification=centering}
+    \centering
+    \begin{minipage}{0.49\textwidth}
+			\centering
+      {\includegraphics[width=175mm]{../figures/plot_farfield_wer_tv}}
+			{(a)}	
+    \end{minipage}
+%
+    \begin{minipage}{0.49\textwidth}
+			\centering
+      {\includegraphics[width=175mm]{../figures/plot_farfield_wer_music}}
+		{(b)}
+    \end{minipage}
+%
+%
+  %\vspace{-6mm}
+ \captionof{figure} {\label{fig:plot_farfield_wer}
+  Speech recognition accuracy at different Signal-to-Noise Ratios (SNRs)
+  under three different noisy conditions: direct TV noise (a)
+  , music noise (b), and babble noise (c). NBF, VTLP, and AS
+  stand for Neural Beam Former (NBF) \cite{j_heymann_icassp_2016_00},
+  Vocal Tract Length Perturbation (VTLP) \cite{c_kim_interspeech_2019_00} , and
+  Acoustics Simulator (AS) \cite{c_kim_interspeech_2017_00},
+  respectively.
+  \vspace{-2mm}
+ }
+\end{Figure}
  %----------------------------------------------------------------------------------------
@@
 \color{SaddleBrown} % SaddleBrown color for the introduction
-\section{Conclusions}
+%\section{Conclusions}
+%%
+%\begin{enumerate}
+%\item We achieved 2.44 \% WER and 8.29 \% WER
+%  on the Librispeech {\it test-clean} and {\it test-other} databases.
+%%
+%\end{enumerate}
 %
-{ \color{red}
-We achieved 2.44 \% WER and 8.29 \% WER
-  on the Librispeech {\it test-clean} and {\it test-other} databases.
-To the best of our knowledge, the 2.44 \% WER on the {\it test-clean}
-is the best result ever reported on this database
-}
-%
-%
-\begin{enumerate}
-  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
-    training database. \cite{n_jaitly_icml_workshop_2013_00}
-  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
-    \begin{itemize}
-        \item We can apply the acoustic simulator after performing the VTLP
-          processing.
-        \item We may use a different window length (50 {\it ms}) for the frequency warping from
-          the one used in feature processing (25 {\it ms}).
-    \end{itemize}
-  \item Applies the power-mel feature.
-  \item Applies a modified shallow-fusion with a Transformer LM.
-\end{enumerate}
 \color{DarkSlateGray} % DarkSlateGray color for the rest of the content
 %----------------------------------------------------------------------------------------
+\small
 \bibliographystyle{IEEEtran}

### 2019-12-17 asru_2019_maximizing_uniformity_of_distribution/poster/main.tex
Update the paper

@@
 \LARGE Samsung Research, Seoul, South Korea\\ % University/organization
-\large \{chanw.com, mk0211.shin, ky85.kim, d.gowda\}@samsung.com
+\large \{chanw.com, mehul3.kumar, ky85.kim, d.gowda\}@samsung.com
     \end{center}
@@
 
-\section{Motivation}
+\section{Summary about Maximum Uniformity of Distribution (MUD)}
+%
+\begin{itemize}
+  \item We developed a novel approach for obtaining {the \color{Navy} nonlinearity function} in a {\it data-driven } way.
+  \item This approach is based on the assumption that neural-network training would be easier 
+  and the converged parameters would show better
+  performance when feature distribution is not too much
+  skewed or too much concentrated in an extremely narrow interval.
 
-\begin{enumerate}
-  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
-    training database \cite{n_jaitly_icml_workshop_2013_00}.
-  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
+  \item The criterion is to maximize {\color{Navy} the Uniformity of Distribution}.
+  \item We develop two different types of MUD. 
     \begin{itemize}
-        \item We can apply the acoustic simulator after performing the VTLP
-          processing.
-        \item We may use a different window length for the frequency warping from
-          the one used in feature processing for performance optimization.
+      \item Power Function-Based MUD
+      \item Histogram-Based MUD
     \end{itemize}
-\end{enumerate}
-
+  \item Power function-based MUD shows better results than the histogram-based MUD.
+  \item We achieved 4.02 \%  WER on test-clean and 13.34 \% WER on test-other without using any Language Models (LMs).
+  \item This approach may be extended to other domains as well.
+\end{itemize}
+%
+%
 \color{DarkSlateGray} % DarkSlateGray color for the rest of the content
@@
 
+\begin{itemize}
+  \item The MUD nonlinearity is applied to mel-filterbank energy for each channel.
+\end{itemize}
+
+\subsection{Power-function based maximization of distribution
+uniformity}
+%
+\begin{itemize}
+\item The transformation based on the power function:
+\begin{align}
+  \mathbf{Y} = \sigma_{p} \left(\mathbf{X} \right) = (X - x_{\text{min}})^{\alpha}.
+    \label{eq:power_mud}
+\end{align}
+%
+\item We expect $Y$ to follow the following uniform distribution:
+\begin{align}
+ \mathbf{Y} \sim 
+  \mathcal{U}(0, \left(x_{\text{max}} - x_{\text{min}} \right)^{\alpha} ).
+    \label{eq:pdf_y}
+\end{align}
+%
+\item
+The log likelihood of the data $X$ assuming the PDF in \eqref{eq:pdf_y}
+is given by (Refer to the paper for mathematical details):
+%
+%
+\begin{align}
+  \mathcal{L}\left(\alpha ; X\right) 
+      & = \sum_{i=0}^{N-1} \ln p_{\mathbf{X}} \left( x_i \right)  \nonumber \\
+      & = \sum_{i=0}^{N-1} 
+              \ln \left[ \frac{ \alpha (x_i - x_{\text{min}} )^{\alpha-1}}  
+              {\left(x_{\text{max}} - x_{\text{min}} \right)^{\alpha}} \right]  \nonumber \\
+      & = N \ln(\alpha) + \left(\alpha-1 \right) \sum_{i=0}^{N-1}
+        \ln \left(x_i - x_{\text{min}} \right)  
+       - N \alpha \ln \left(x_{\text{max}} - x_{\text{min}} \right).
+        \label{eq:x_likelihood}
+\end{align}
+%
+%
+%
+%
+%
+\item 
+%
+The following $\hat{\alpha}$ maximizes the log-likelihood of $\mathcal{L}\left(\alpha ; X\right)$
+(Refer to the paper for mathematical details).
+%
+%
+\begin{align}
+  \hat{\alpha} = \frac{1}{
+    \ln \left(\max \left\{x_i - x_{\text{min}}, \delta \right\} \right)
+    - \frac{1}{N} \sum_{i=0}^{N-1} \ln \left(x_i - x_{\text{min}}\right)}.
+  \label{eq:alpha_estimation}
+\end{align}
+%
+%
+\end{itemize}
+%
+%
+  \begin{Figure}
+    \begin{center}
+      \includegraphics[width=170mm]{estimated_power_coeff}
+      \captionof{figure} {
+        \label{fig:estimated_power_coeff}
+        The estimated power coefficients for each mel filterbank channels using
+        \eqref{eq:alpha_estimation}.
+      }
+    \end{center}
+    \vspace{-7mm}
+  \end{Figure}
+%
+%
+%
+\subsection{Histogram-based maximization of distribution uniformity}
+\begin{itemize}
+\item The distribution is uniformized using the empirical CDF (Refer to the paper for mathematical details):
+\begin{align}
+  \mathbf{Y} = \sigma_{np}(\mathbf{X}) 
+     = F_u^{-1} \left(\hat{F}_x(\mathbf{X})\right)
+      = \hat{F}_x(\mathbf{X}).
+  \label{eq:histogram_mud_simple}
+\end{align}
+\end{itemize}
+%
+%
+\begin{minipage}[]{0.54\linewidth}
   \begin{Figure}
@@
       \includegraphics[width=170mm]{mel_filterbank_energy_histogram}
-      \label{fig:mel_filterbank_energy_histogram}
+      \label{fig:mel_filterbank_energy_histogram} \\
+      (a)
     }   
@@
       \includegraphics[width=170mm]{power_function_based_mud_output_histogram}
-      \label{fig:power_function_based_mud_output_histogram}
+      \label{fig:power_function_based_mud_output_histogram} \\
+      (b)
     }   
-  \vspace{-2mm}
     \\  
@@
       \includegraphics[width=170mm]{histogram_based_mud_output_histogram}
-      \label{fig:histogram_based_mud_output_histogram}
+      \label{fig:histogram_based_mud_output_histogram} \\
+      (c)
     }   
-  \vspace{-2mm}
+    \\
     \captionof{figure} {
       The Probability Density Functions for the third filterbank channel
-       of (a): the mel filterbank energy $p[m, l], l = 3$ in  
-       \eqref{eq:mel_filterbank_energy}, (b): the power-function based MUD 
+       of (a): the mel filterbank energy $p[m, l], l = 3$ 
+       , (b): the power-function based MUD 
       output of this mel filterbank energy in \eqref{eq:power_mud}, (c) 
-      the histogram based-MUD in \eqref{eq:histogram_mud}. 
+      the histogram based-MUD in \eqref{eq:histogram_mud_simple}. 
       \label{fig:pdf_mud}
@@
 \end{Figure}
+\end{minipage}
+%
+%
+\begin{minipage}[]{0.45\linewidth}
+  \begin{Figure}
+  \begin{center}
+  \resizebox{150mm}{!}{\input{../figures/e2e_asr_block_diagram_poster.tex}}
+  \end{center}
+  \captionof{figure}{ 
+  The structure of the entire end-to-end speech recognition system.}
+  \end{Figure}
+\end{minipage}
 
+%
 %\begin{center}
@@
 \section{End-to-End Speech recognition}
-
-\begin{minipage}{1.0\linewidth}
-  {
-    \normalsize
-  \begin{center}
-  \resizebox{180mm}{!}{\input{../figures/e2e_asr_block_diagram_poster.tex}}
-  \end{center}
-\captionof{figure}{ 
-  The structure of the entire end-to-end speech recognition system.}
-  }
-\end{minipage}
-
-  We used the RETURNN speech recognition system
-  \cite{a_zeyer_interspeech_2018_00} with various modifications:
+ We used the RETURNN speech recognition system \cite{a_zeyer_interspeech_2018_00} with various modifications:
     \begin{itemize}
-      \item{Gradient clipping and learning-late warm-up.}
-      \item{Power-mel feature} Motivated by the power-law nonlinearity of ($(\cdot)^{\frac{1}{15}}$) in PNCC \cite{C_Kim_IEEETran_2016_1}.
-      \item{Modified shallow fusion with a Transformer LM}
-
-        \begin{align}
-  y_{0:L}^{*} = & \argmax_{y_{0:L}} \sum_{l=0}^{L-1} \Big[ \log P \left(y_l
-  |\vec{x}[0:M], y_{0:l} \right)
-  \nonumber \\
-                           & \qquad - \lambda_p \log P(y_l)
-                           + \lambda_{\text{lm}} \log P \left(y_l   |y_{0:l} \right)  \Big],
-                           \label{eq:lm_fusion}
-\end{align}
-
+      \item{MoCha\cite{k_kim_asru_2019_00} and the modified beam search decoder.}
+      \item{Gradient clipping, modified learning-late warm-up, and so on.}
     \end{itemize}
@@
 \section{Experimental Results}
+
 \begin{itemize}
-  \item For training, we used { \bf the Librispeech train-clean and
-    train-other}.
-  \item For evaluation, we used { \bf the test-clean and test-other of this Libri
-    Speech database. }
+\item \textbf{LibriSpeech experiments} (960-hr training and evaluation on LibriSpeech {\tt test-clean} and {\tt test-other} ) 
 \end{itemize}
@@
 \end{minipage}
+\begin{itemize}
+\item The Power-Function Based MUD shows slightly better result than the power-law nonlinearity with the power coefficient of $\frac{1}{15}$ \cite{
+C_Kim_IEEETran_2016_1}.
+\item We hypothesize that the reason why histogram-based MUD does slightly worse than the power-
+function based MUD is that it somewhat obscured the energy boundary between speech vs non-speech.
+\end{itemize}
  %----------------------------------------------------------------------------------------
@@
 %
-\color{SaddleBrown} % SaddleBrown color for the introduction
-\section{Conclusions}
-%
-{ \color{red}
-We achieved 2.44 \% WER and 8.29 \% WER
-  on the Librispeech {\it test-clean} and {\it test-other} databases.
-To the best of our knowledge, the 2.44 \% WER on the {\it test-clean}
-is the best result ever reported on this database
-}
-%
-%
-\begin{enumerate}
-  \item Applies Vocal Tract Length Perturbation (VTLP) to diversify the
-    training database. \cite{n_jaitly_icml_workshop_2013_00}
-  \item Resynthesizes VTLP-processed waveforms before performing feature extraction.
-    \begin{itemize}
-        \item We can apply the acoustic simulator after performing the VTLP
-          processing.
-        \item We may use a different window length (50 {\it ms}) for the frequency warping from
-          the one used in feature processing (25 {\it ms}).
-    \end{itemize}
-  \item Applies the power-mel feature.
-  \item Applies a modified shallow-fusion with a Transformer LM.
-\end{enumerate}
+
 \color{DarkSlateGray} % DarkSlateGray color for the rest of the content
 %----------------------------------------------------------------------------------------
+\small
 \bibliographystyle{IEEEtran}

### 2019-12-17 asru_2019_maximizing_uniformity_of_distribution/figures/batch.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+for file in `ls -1 *.eps`; do
+  epstopdf $file
+done

### 2019-12-17 asru_2019_maximizing_uniformity_of_distribution/poster/clean.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 
 outname="main"
-ext_list=("blg" "bbl" "log" "dvi" "aux" "pdf")
+ext_list=("blg" "bbl" "log" "dvi" "aux") # "pdf")
 for ext in ${ext_list[@]}; do
   command="rm -f ${outname}.${ext}"
   echo $command
